### 2018-11-16 paper/spad_single/sections/introduction.tex
first draft of paper

contributions
%
\begin{itemize}
	\item introduce idea of RGB + single SPAD depth imaging		
	\item ... gesture recognition, face authentication, ... (e.g. ``learning to be a depth camera'' microsoft paper)
	\item build prototype, demonstrate results		
\end{itemize}

### 2018-11-16 paper/spad_single/sections/results.tex
first draft of paper

\subsection{Implementation}

hardware, calibration, etc.

\subsection{Results}

### 2018-11-16 paper/spad_single/sections/method.tex
first draft of paper

\subsection{Monocular Depth Estimation}

\subsection{Global Depth Hints}

\begin{itemize}
	\item image formation model	
	\item training details
	\item simulations and comparison: qualitative and quantitative
\end{itemize}

### 2018-11-16 paper/spad_single/sections/related.tex
first draft of paper

\paragraph{Depth Imaging}

\begin{itemize}
	\item stereo and multiview
	\item structured illumination and random patterns (kinect, etc.), active stereo
	\item time of flight (continuous wave and pulsed)
	\item what we do: like pulsed but much simpler setup; no scanning, no spad array, ...
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}

\begin{itemize}
	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Deep Sensor Fusion}

global hints for super-resolution, colorization, depth estimation 
%
\begin{itemize}
	\item colorization
	\item david's 2018 paper for depth estimation and denoising (see david's 2019 sig paper for related work)
	\item what we do: slightly different application
\end{itemize}

### 2019-05-23 paper/spad_single/sections/method.tex
Working on the paper.

@@
-\subsection{Monocular Depth Estimation}
+In this section, we describe the histogram formation model for a single-pixel
+time-of-flight lidar sensor under diffuse, pulsed laser illumination. We also use
+this model to simulate the formation of a histogram given a depth map. 
+\subsection{Histogram Formation Model}
+Consider a laser which emits a pulse at time $t = 0$ with shape $g(t)$. The waveform passes through a diffuser
+which spreads the light evenly over some 3D scene $z(x,y)$, which we describe as
+depth as a function of $(x,y)$ position. 
+To assess the distribution of returning photons from the whole scene, we first consider photons returning from a single
+location $(x, y)$. The expected number of photon events detected 
+from this location in the time interval $(t, t + \Delta t)$ is given as
+\begin{equation}
+  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt. \label{single_loc_spad} 
+\end{equation}
 
-\subsection{Global Depth Hints}
+where $c$ is the speed of light, and $f$ models the temporal uncertainty in the
+detector. Since the detection of each photon can be described as a Bernoulli random variable,
+the total number of accumulated photons in this time interval follows a Poisson
+distribution according to
 
-\begin{itemize}
-	\item image formation model	
-	\item training details
-	\item simulations and comparison: qualitative and quantitative
-\end{itemize}
+\begin{equation}
+  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + d} \label{global_hints}
+\end{equation}
+
+where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
+photon counts due to the reflectance $r(x,y)$ of the scene and due to the
+inverse square falloff $1/z(x,y)^2$.
+In addition, $\eta$ is the detection probability of a photon
+triggering a SPAD event, and $d = \eta a + b$ is the number of ambient photons $a$
+and the number of ``dark count'' events $b$, which is a property of the SPAD.
+
+Pick an example scene, show side-by-side with depth map and histogram of gt
+depth and histogram from SPAD (to make intuitive)
+
+\subsection{Monocular depth estimation with global depth hints}
+Given a single RGB image $I(x,y)$ and a histogram of photon arrivals $h[n]$
+collected as in equation \ref{global_hints}, we seek to
+reconstruct the ground truth depth map $z(x,y)$.
+Our method has two parts. First, we initialize our estimate of the depth map from the single RGB
+image via a monocular depth estimator. Second, we refine this depth map using
+the captured histogram $h[n]$ via a process we call Differentiable Histogram Matching.
+Differentiable histogram matching as a tool for post-processing the image to
+match the depth map to the statistics we capture from the SPAD.
+
+\paragraph{Initialization via CNN}
+Convoluational Neural Networks have become increasingly capable of leveraging
+monocular depth cues from to produce accurate estimates of depth
+from only a single image. We therefore choose to initialize our depth map
+estimate $z^{(0)}(x,y)$ using
+a CNN. However, any depth estimator reliant on only a single
+view will be unable resolve the inherent scale ambiguity in the scene resulting
+from the tradeoff between size of and distance to an object. Our next step,
+differentiable histogram matching, will resolve this ambiguity using the depth
+information present in the SPAD histogram.
+
+\paragraph{Differentiable Histogram Matching}
+Given our initial depth map estimate, our goal is now to refine that depth map
+so that it agrees with the information provided by the SPAD histogram.
+Figure showing just the differentiable histogram matching part of the model.
+At a high level, our goal is to formulate the SPAD histogram formation model as
+a differentiable function of the depth map and RGB image so that the output
+$\hat h[n]$ of the SPAD simulation can be compared to the observed SPAD
+histogram $h[n]$ and the depth map can be optimized via gradient descent or
+other first-order method.
+Given per-pixel depth, we can simulate SPAD histogram formation using equation
+\ref{global_hints}, where we approximate $\lambda_{x,y}[n]$ using Kernel Density
+Estimation as:
+\begin{equation}
+  \hat \lambda^{(i)}_{x,y}[n] = \frac{1}{\sigma\sqrt{2 \pi}}\exp\paren*{-\frac{1}{2\sigma^2}(n - \hat z^{(i)}(x,y))} \label{KDE}
+\end{equation}
+where $\hat z^{(i)}(x, y)$ is our estimate of the depth at pixel $(x,y)$ at
+iteration $i$.
+
+Once we have $\lambda^{(i)}$, we compute $\hat h[n]$ according to the rest of
+the SPAD histogram formation model, neglecting the Poisson sampling, as follows
+\begin{equation}
+  \hat h[n] = \sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + d \label{diff_forward}
+\end{equation}
+model. (Explain where $d$ and $\eta$ come from.)
+Finally, given two histograms, we can compute the Sinkhorn Distance between
+them. As described in \ref{Cuturi et. al.}, the Sinkhorn Distance is a measure
+of distance between two probability distributions. It is particularly desirable
+to us because unlike other distances between probability distributions, such as
+the KL divergence or the simple RMSE, the Sinkhorn Distance scales with
+separation as well as magnitude. Furthermore, unlike the Wasserstein Distance
+from which it is derived, the computation of the Sinkhorn Distance can be
+computed via Sinkhorn Iterations, which are fast and differentiable.
+We refer the reader to \ref{Cuturi et. al.} for the details.
+``Minimize blah s.t. blah blah''
+\subsection{``How you actually solve it''}
+
+\subsection{Implementation Details}
+For the Monocular Depth Estimator, we use a pretrained version of the
+the Deep Ordinal Regression Network (DORN) \cite{}. We use the implementation of
+the Sinkhorn Iteration (for calculating the entropy-regularized Wasserstein
+Loss) from \ref Cuturi et. al. We update the depth map using gradient descent.
+Everything is implemented in PyTorch.
+
+Table with hyperparameters (defer to supplementary info?)
+- Kernel Density Estimation (sigma)
+- Sinkhorn Iterations (maximum number, epsilon tolerance)
+- Gradient Descent (learning rate, epsilon tolerance, max iterations)

### 2019-05-23 paper/spad_single/sections/results.tex
Working on the paper.

@@
 \subsection{Results} 
+% Table of quantitative results
+\begin{table}
+\begin{center}
+\begin{tabular}{cccc|ccc}
+  \toprule
+    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel & $log_{10}$ \\
+  \midrule
+    DORN & 1 & 2 & 3 & 4 & 5 & 6 \\ 
+  \bottomrule
+\end{tabular} 
+\end{center}
+\end{table}
+
+% Table of qualitative results
+\begin{table}
+  \begin{center}
+    \begin{tabular}{cccccc}
+      RGB & Albedo & Ground Truth & CNN & CNN + Raw Histogram & CNN + Albedo/Falloff \\
+      \includegraphics[width=4cm]{sections/figures/comparison_table/rgb_0.png} &
+      \includegraphics[width=4cm]{sections/figures/comparison_table/albedo_0.png} &
+      \includegraphics[width=4cm]{sections/figures/comparison_table/gt_0.png} &
+      \includegraphics[width=4cm]{sections/figures/comparison_table/cnn_0.png} &
+      \includegraphics[width=4cm]{sections/figures/comparison_table/cnn_rawhist_0.png} &
+      \includegraphics[width=4cm]{sections/figures/comparison_table/cnn_hist_0.png} \\ 
+    \end{tabular}
+  \end{center}
+\end{table}

### 2019-05-23 models/data/utils/spad_utils.py

@@ -187,17 +187,20 @@ class SimulateSpad:
         return sample
 
 
-def remove_dc_from_spad_batched(noisy_spad, bin_widths, lam=1e-2, eps=1e-5):
+def remove_dc_from_spad_batched(noisy_spad, bin_edges, lam=1e-2, eps=1e-5):
     """
     Batched, operates of batches of size N
     WARNING: Batching generally produces noisier answers.
     Works in numpy.
     :param noisy_spad: length NxC array with the raw spad histogram to denoise.
-    :param bin_widths: 1xC array with the bin widths in meters of the original bins.
+    :param bin_edges: (C+1) array with the edges of the bins
     """
     # print(noisy_spad.shape)
     # print(bin_widths.shape)
+
     N, C = noisy_spad.shape
+    assert bin_edges.shape == (C+1,)
+    bin_widths = bin_edges[1:] - bin_edges[:-1]
     # Equalize everything so DC appears uniform
     #     for i in range(N):
     #     spad = noisy_spad[i,:]
@@ -217,7 +220,7 @@ def remove_dc_from_spad_batched(noisy_spad, bin_widths, lam=1e-2, eps=1e-5):
     return signal_hist
 
 
-def remove_dc_from_spad(noisy_spad, bin_widths, lam=1e-2, eps=1e-5):
+def remove_dc_from_spad(noisy_spad, bin_edges, lam=1e-2, eps=1e-5):
     """
     Not batched, solves N convex problems where N is the batch size.
     For some reason, this gives better results.
@@ -230,8 +233,10 @@ def remove_dc_from_spad(noisy_spad, bin_widths, lam=1e-2, eps=1e-5):
     # print(noisy_spad.shape)
     # print(bin_widths.shape)
     assert len(noisy_spad.shape) == 2
-    assert len(bin_widths) == noisy_spad.shape[1]
     N, C = noisy_spad.shape
+    assert bin_edges.shape == (C+1,)
+    bin_widths = bin_edges[1:] - bin_edges[:-1]
+
     # Equalize everything so DC appears uniform
     denoised_spad = np.zeros_like(noisy_spad)
     for i in range(N):

### 2019-05-30 evaluate_dorn_sinkhorn_opt.py
updating master branch.

@@ -30,7 +30,7 @@ def cfg(data_config, spad_config):
             "sinkhorn_eps": 1e-4,
             "dc_eps": 1e-5,
             "remove_dc": spad_config["dc_count"] > 0.,
-            "use_albedo": spad_config["use_albedo"],
+            "use_scaling": spad_config["use_albedo"],
             "use_squared_falloff": spad_config["use_squared_falloff"],
             "lr": 1e3,
             "hints_len": 68,

### 2019-05-30 models/data/nyuv2_wonka_nohints_dataset.py

@@ -1,0 +1,53 @@
+import os
+import json
+
+import numpy as np
+from torch.utils.data import Dataset
+import cv2
+
+from torchvision import transforms
+from models.data.utils.transforms import (ResizeAll, RandomHorizontalFlipAll, Normalize,
+                                          AddDepthMask, ToTensorAll)
+
+from sacred import Experiment
+
+nyuv2_wonka_nohints_ingredient = Experiment('data_config')
+
+@nyuv2_wonka_nohints_ingredient.config
+def cfg():
+    data_name = "nyu_depth_v2_wonka"
+    root_dir = os.path.join("data", "nyu_depth_v2_wonka")
+
+class NYUDepthv2WonkaDataset(Dataset):
+    """
+    The split of the nyu_depth_v2 dataset given by
+    https://github.com/ialhashim/DenseDepth
+    """
+    def __init__(self, rootdir, transform=None):
+        self.rootdir = rootdir
+        self.depth = np.load(os.path.join(rootdir, "eigen_test_depth.npy"))
+        self.rgb = np.load(os.path.join(rootdir, "eigen_test_rgb.npy"))
+        self.crop = np.load(os.path.join(rootdir, "eigen_test_crop.npy"))
+        self.depth_cropped = self.depth[:,
+                                        self.crop[0]:self.crop[1]+1,
+                                        self.crop[2]:self.crop[3]+1
+                                       ]
+        self.rgb_cropped = self.depth[:,
+                                      self.crop[0]:self.crop[1]+1,
+                                      self.crop[2]:self.crop[3]+1,
+                                      :
+                                      ]
+        self.transform = transform
+
+    def __len__(self):
+        return self.depth.shape[0]
+
+    def __getitem__(self, i):
+        # Convert to torch tensor
+        # Flip channel order
+        sample = {
+            # GT Depth
+            # RGB
+        }
+        if self.transform is not None:
+            data = self.transf

### 2019-05-30 utils/figure_utils.py

@@ -23,7 +23,8 @@ def load_dataset_from_config(config, load_hints, load_nohints):
     """
     data_config = config["data_config"]
     # Future: Check data_name to choose the right dataset
-    del data_config["data_name"]
+    if "data_name" in data_config:
+        del data_config["data_name"]
     spad_config = None
     if "spad_config" in config:
         # With hints (probably)

### 2019-05-30 paper/spad_single/sections/results.tex
updating master branch.

--- 2018-11-16 paper/spad_single/sections/results.tex
@@
 \subsection{Results} 
+% Table of quantitative results
+\paragraph{NYU Depth v2}
+The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
+RGB-D data captured using a Microsoft Kinect. We used a version of DORN
+pretrained according to \cite{Fu. et al} as our CNN.
+\newpage
+\begin{table*}
+\begin{center}
+\begin{tabular}{lccc|ccc}
+  \toprule
+    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel & $log_{10}$ \\
+  \midrule
+Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
+Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
+DORN&0.828&0.965&0.992&0.509&0.115&0.051 \\
+  DORN (rescaled) & 0.871 & 0.969 & 0.991 & 0.514 & 0.075 & 0.048 \\
+Alhashim, Wonka (2019)&0.846&0.974&0.994&0.465&0.123&0.053 \\
+Alhashim, Wonka (2019) rescaled using GT depth"&0.895&\textbf{0.980}&\textbf{0.996}&\textbf{0.390}&\textbf{0.103}&\textbf{0.043} \\
+  \midrule
+  Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
+  Ours (albedo/falloff) & 0.798 & 0.960 & 0.988 & 0.615 & 0.143 & 0.068 \\
+  \bottomrule
+\end{tabular} 
+\end{center}
+\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
+\end{table*}
+
+% Table of qualitative results
+\begin{table*}
+  \begin{center}
+    \begin{tabularx}{\linewidth}{*{5}{X}}
+      RGB & Ground Truth & CNN & CNN + Raw Histogram & CNN + Albedo/Falloff \\
+        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_0.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_0.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_0.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_0.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_0.png} \\ 
+  & & RMSE = 0.462, WAS = 34.615 & RMSE = 0.263, WAS = 11.906 & RMSE = 0.271, WAS = 13.149 \\
+        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_1.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_1.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_1.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_1.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_1.png} \\ 
+  & & RMSE = 0.463, WAS = 9.620 & RMSE = 0.290, WAS = 5.765 & RMSE = 0.372, WAS = 3.854 \\
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_2.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_2.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_2.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_2.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_2.png} \\ 
+    & & RMSE = 0.667, WAS = 72.725 & RMSE = 0.471, WAS = 43.348 & RMSE = 0.584, WAS = 52.787 \\
+        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_3.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_3.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_3.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_3.png} &
+      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_3.png} \\ 
+  & & RMSE = 1.486, WAS = 31.845 & RMSE = 1.189, WAS = 21.868 & RMSE = 1.844, WAS = 121.540 \\
+    \end{tabularx}
+  \end{center}
+  \caption{\textbf{NYU Depth v2} Qualitative comparison of the raw output of
+    DORN, the corrected depth map when the ground-truth depth histogram is used,
+    and the corrected depth when the simulated SPAD measurements are used.}
+\end{table*}
+\begin{itemize}
+\item Overlay spad histograms?
+\item Show RMSE/delta1/etc.
+\item Show colorbars in the last column.
+\item Show inset squares and then show the zoomed regions in more detail?
+\end{itemize}

### 2019-05-30 models/DORN_sinkhorn_opt.py

@@ -4,8 +4,8 @@ import torch.nn.functional as F
 from torch.nn import MSELoss
 import numpy as np
 from models.data.utils.sid_utils import SIDTorch
-from models.sinkhorn_dist import optimize_depth_map
-from models.data.utils.spad_utils import remove_dc_from_spad
+from models.sinkhorn_dist import optimize_depth_map_masked
+from models.data.utils.spad_utils import remove_dc_from_spad, bgr2gray
 from torch.optim import SGD
 # import matplotlib
 # matplotlib.use("TKAgg")
@@ -158,35 +158,25 @@ class DORN_sinkhorn_opt:
             denoised_spad[denoised_spad < self.dc_eps] = self.dc_eps
         # Normalize to 1
         denoised_spad = denoised_spad / torch.sum(denoised_spad, dim=1, keepdim=True)
-        # Albedo check
-        albedo = None
-        alpha = 0. # Set alpha based on albedo
+        # Scaling check
+        scaling = None
         if self.use_albedo:
-            albedo = input_["albedo_orig"][:, 1:2, ...].to(device) / 255.
-            alpha = 1./torch.mean(albedo) - 1
-        print("alpha", alpha)
-
+            # intensity = input_["albedo_orig"][:, 1:2, ...].to(device) / 255.
+            scaling = bgr2gray(input_["rgb_orig"])
         # Squared depth check
         inv_squared_depths = None
         if self.use_squared_falloff:
             inv_squared_depths = (self.sid_obj.sid_bin_values[:68]**(-2)).unsqueeze(0).unsqueeze(-1).unsqueeze(-1).to(device)
-        # Actually run the optimization
-        mseloss = MSELoss()
-        if alpha > 0.:
-            regularizer = lambda x, x0: 1e-1 * mseloss(x, x0)
-        else:
-            regularizer = None
 
         with torch.enable_grad():
             depth_index_final, depth_img_final, depth_hist_final = \
-                optimize_depth_map(depth_init, sigma=self.sigma, n_bins=self.sid_bins,
-                                   cost_mat=self.cost_mat, lam=self.lam, spad_hist=denoised_spad,
-                                   lr=self.lr, num_sgd_iters=self.sgd_iters, num_sinkhorn_iters=self.sinkhorn_iters,
-                                   kde_eps=self.kde_eps,
-                                   sinkhorn_eps=self.sinkhorn_eps,
-                                   inv_squared_depths=inv_squared_depths,
-                                   albedo=albedo,
-                                   regularizer=regularizer)
[…]

### 2019-05-30 models/data/utils/wasserstein_loss.py

@@ -1,0 +1,47 @@
+import cvxpy as cp
+import numpy as np
+import matplotlib.pyplot as plt
+
+def wasserstein_loss(x, y, C, eps=1e-6):
+    """
+    Calculate the wasserstein loss between two histograms given the cost matrix.
+    :param h1, h2: Shape (N,) histograms. Should be nonnegative and sum to 1.
+    :param C: Cost matrix of shape (N,N).
+    """
+    assert np.abs(np.sum(x) - 1.) < eps and (x >= -eps).all()
+    assert np.abs(np.sum(y) - 1.) < eps and (y >= -eps).all()
+    assert x.shape == y.shape and len(x.shape) == 1 and len(y.shape) == 1
+    assert len(C.shape) == 2 and C.shape[0] == x.shape[0] and C.shape[1] == y.shape[0]
+
+    n = x.shape[0]
+    T = cp.Variable((n, n))
+    obj = cp.Minimize(cp.trace(T * C))
+    constr = [
+        T * np.ones(n) == x,
+        T.T * np.ones(n) == y,
+        T >= 0
+    ]
+    prob = cp.Problem(obj, constr)
+    prob.solve(solver="OSQP", eps_abs=eps)
+    return prob.value, T.value
+
+if __name__ == "__main__":
+    gaussian = lambda n, mu, sigma: np.exp(-1./(2*sigma^2)*(np.linspace(0, n, n) - mu)**2) # Ground truth depth
+    eps = 1e-3
+    n = 68 # Number of entries in the histogram
+    sigma = 6 # standard dev. of gaussian, in units of bins
+    mu_y = 20 # mean, in the interval [0,n]
+    y = gaussian(n, mu_y, sigma)
+    y[y < eps] = 0.
+    y = y / np.sum(y)
+
+    plt.figure()
+    plt.plot(y, label="target")
+    plt.title("Histograms")
+
+    mu_x = 40
+    x = gaussian(n, mu_x, sigma)
+    x[x < eps] = 0.
+    x = x / np.sum(x)
+    plt.plot(x, label="initial")
+    plt.legend()

### 2019-05-30 paper/spad_single/cvpr2019AuthorKit/latex/egpaper_final.tex

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{\LaTeX\ Author Guidelines for CVPR Proceedings}

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Look at previous CVPR abstracts to get a feel for style and length.
\end{abstract}

%%%%%%%%% BODY TEXT
\section{Introduction}

Please follow the steps outlined below when submitting your manuscript to
the IEEE Computer Society Press.  This style guide now has several
important modifications (for example, you are no longer warned against the
use of sticky tape to attach your artwork to the paper), so all authors
should read this new version.

%-------------------------------------------------------------------------
\subsection{Language}

All manuscripts must be in English.

\subsection{Dual submission}

Please refer to the author guidelines on the CVPR 2019 web page for a
discussion of the policy on dual submissions.

\subsection{Paper length}
Papers, excluding the references section,
must be no longer than eight pages in length. The references section
will not be included in the page count, and there is no limit on the
length of the references section. For example, a paper of eight pages
with two pages of references would have a total length of 10 pages.
{\bf There will be no extra page charges for CVPR 2019.}

Overlength papers will simply not be reviewed.  This includes papers
where the margins and formatting are deemed to have been significantly
altered from those laid down by this style guide.  Note that this
\LaTeX\ guide already sets figure captions and references in a smaller font.
The reason such papers will not be reviewed is that there is no provision for
supervised revisions of manuscripts.  The reviewing process cannot determine
the suitability of the paper for presentation in eight pages if it is
reviewed in eleven.

%-------------------------------------------------------------------------
\subsection{The ruler}
The \LaTeX\ style defines a printed ruler which should be present in the
version submitted for review.  The ruler is provided in order that
reviewers may comment on particular lines in the paper without
circumlocution.  If you are preparing a document using a non-\LaTeX\
document preparation system, please arrange for an equivalent ruler to
appear on the final output pages.  The presence or absence of the ruler
should not change the appearance of any other content on the page.  The
camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
note that the ruler measurements do not align well with lines in the paper
--- this turns out to be very difficult to do well when the paper contains
many figures and equations, and, when done, looks ugly.  Just use fractional
references (e.g.\ this line is $095.5$), although in most cases one would
expect that the approximate location will be adequate.

\subsection{Mathematics}

Please number all of your sections and displayed equations.  It is
important for readers to be able to refer to any particular equation.  Just
because you didn't refer to it in the text doesn't mean some future reader
might not need to refer to it.  It is cumbersome to have to use
circumlocutions like ``the equation second from the top of page 3 column
1''.  (Note that the ruler will not be present in the final copy, so is not
an alternative to equation numbers).  All authors will benefit from reading
Mermin's description of how to write mathematics:
\url{http://www.pamitc.org/documents/mermin.pdf}.

\subsection{Blind review}

Many authors misunderstand the concept of anonymizing for blind
review.  Blind review does not mean that one must remove
citations to one's own work---in fact it is often impossible to
review a paper unless the previous citations are known and
available.

Blind review means that you do not use the words ``my'' or ``our''
when citing previous work.  That is all.  (But see below for
techreports.)

Saying ``this builds on the work of Lucy Smith [1]'' does not say
that you are Lucy Smith; it says that you are building on her
work.  If you are Smith and Jones, do not say ``as we show in
[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
paper, include reference 7 as you would any other cited work.

An example of a bad paper just asking to be rejected:
\begin{quote}
\begin{center}
    An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of our
   previous paper [1], and show it to be inferior to all
   previously known methods.  Why the previous paper was
   accepted without this analysis is beyond me.

   [1] Removed for blind review
\end{quote}

An example of an acceptable paper:

\begin{quote}
\begin{center}
     An analysis of the frobnicatable foo filter.
\end{center}

   In this paper we present a performance analysis of the
   paper of Smith \etal [1], and show it to be inferior to
   all previously known methods.  Why the previous paper
   was accepted without this analysis is beyond me.

   [1] Smith, L and Jones, C. ``The frobnicatable foo
   filter, a fundamental contribution to human knowledge''.
   Nature 381(12), 1-213.
\end{quote}

If you are making a submission to another conference at the same time,
which covers similar or overlapping material, you may need to refer to that
submission in order to explain the differences, just as you would if you
had previously published related work.  In such cases, include the
anonymized parallel submission~\cite{Authors14} as additional material and
cite it as
\begin{quote}
[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
Supplied as additional material {\tt fg324.pdf}.
\end{quote}

Finally, you may feel you need to tell the reader that more details can be
found elsewhere, and refer them to a technical report.  For conference
submissions, the paper must stand on its own, and not {\em require} the
reviewer to go to a techreport for further details.  Thus, you may say in
the body of the paper ``further details may be found
in~\cite{Authors14b}''.  Then submit the techreport as additional material.
Again, you may not assume the reviewers will read this material.

Sometimes your paper is about a problem which you tested using a tool which
is widely known to be restricted to a single institution.  For example,
let's say it's 1969, you have solved a key problem on the Apollo lander,
and you believe that the CVPR70 audience would like to hear about your
solution.  The work is a development of your celebrated 1968 paper entitled
``Zero-g frobnication: How being the only people in the world with access to
the Apollo lander source code makes us a wow at parties'', by Zeus \etal.

You can handle this paper like any other.  Don't write ``We show how to
improve our previous work [Anonymous, 1968].  This time we tested the
algorithm on a lunar lander [name of lander removed for blind review]''.
That would be silly, and would immediately identify the authors. Instead
write the following:
\begin{quotation}
\noindent
   We describe a system for zero-g frobnication.  This
   system is new because it handles the following cases:
   A, B.  Previous systems [Zeus et al. 1968] didn't
   handle case B properly.  Ours handles it by including
   a foo term in the bar integral.

   ...

   The proposed system was integrated with the Apollo
   lunar lander, and went all the way to the moon, don't
   you know.  It displayed the following behaviours
   which show how well we solved cases A and B: ...
\end{quotation}
As you can see, the above text follows standard scientific convention,
reads better than the first version, and does not explicitly name you as
the authors.  A reviewer might think it likely that the new paper was
written by Zeus \etal, but cannot make any decision based on that guess.
He or she would have to be sure that no other authors could have been
contracted to solve problem B.
\medskip

\noindent
FAQ\medskip\\
{\bf Q:} Are acknowledgements OK?\\
{\bf A:} No.  Leave them for the final copy.\medskip\\
{\bf Q:} How do I cite my results reported in open challenges?
{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper. For your results, however, you should not identify yourself and should not mention your participation in the challenge. Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\

\begin{figure}[t]
\begin{center}
\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
\end{center}
   \caption{Example of caption.  It is set in Roman so that mathematics
   (always set in Roman: $B \sin A = A \sin B$) may be included without an
   ugly clash.}
\label{fig:long}
\label{fig:onecol}
\end{figure}

\subsection{Miscellaneous}

\noindent
Compare the following:\\
\begin{tabular}{ll}
 \verb'$conf_a$' &  $conf_a$ \\
 \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
\end{tabular}\\
See The \TeX book, p165.

The space after \eg, meaning ``for example'', should not be a
sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
\verb'\eg' macro takes care of this.

When citing a multi-author paper, you may save space by using ``et alia'',
shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
However, use it only when there are three or more authors.  Thus, the
following is correct: ``
   Frobnication has been trendy lately.
   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''

This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
because reference~\cite{Alpher03} has just two authors.  If you use the
\verb'\etal' macro provided, then you need not worry about double periods
when used at the end of a sentence as in Alpher \etal.

For this citation style, keep multiple citations in numerical (not
chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
\cite{Alpher02,Alpher03,Authors14}.

\begin{figure*}
\begin{center}
\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
\end{center}
   \caption{Example of a short caption, which should be centered.}
\label{fig:short}
\end{figure*}

%------------------------------------------------------------------------
\section{Formatting your paper}

All text must be in a two-column format. The total allowable width of the
text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
first page) should begin 1.0 inch (2.54 cm) from the top edge of the
page. The second and following pages should begin 1.0 inch (2.54 cm) from
the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
page.

%-------------------------------------------------------------------------
\subsection{Margins and page numbering}

All printed material, including text, illustrations, and charts, must be kept
within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
high.
Page numbers should be in footer with page numbers, centered and .75
inches from the bottom of the page and make it start at the correct page
number rather than the 4321 in the example.  To do this fine the line (around
line 23)
\begin{verbatim}
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\end{verbatim}
where the number 4321 is your assigned starting page.

Make sure the first page is numbered by commenting out the first page being
empty on line 46
\begin{verbatim}
%\thispagestyle{empty}
\end{verbatim}

%-------------------------------------------------------------------------
\subsection{Type-style and fonts}

Wherever Times is specified, Times Roman may also be used. If neither is
available on your word processor, please use the font closest in
appearance to Times to which you have access.

MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
the first page. The title should be in Times 14-point, boldface type.
Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
adverbs; do not capitalize articles, coordinate conjunctions, or
prepositions (unless the title begins with such a word). Leave two blank
lines after the title.

AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
and printed in Times 12-point, non-boldface type. This information is to
be followed by two blank lines.

The ABSTRACT and MAIN TEXT are to be in a two-column format.

MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
inch or 0.422 cm). Make sure your text is fully justified---that is,
flush left and flush right. Please do not place any additional blank
lines between paragraphs.

Figure and table captions should be 9-point Roman type as in
Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.

\noindent Callouts should be 9-point Helvetica, non-boldface type.
Initially capitalize only the first word of section titles and first-,
second-, and third-order headings.

FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
should be Times 12-point boldface, initially capitalized, flush left,
with one blank line before, and one blank line after.

SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
should be Times 11-point boldface, initially capitalized, flush left,
with one blank line before, and one after. If you require a third-order
heading (we discourage it), use 10-point Times, boldface, initially
capitalized, flush left, preceded by one blank line, followed by a period
and your text on the same line.

%-------------------------------------------------------------------------
\subsection{Footnotes}

Please use footnotes\footnote {This is what a footnote looks like.  It
often distracts the reader from the main flow of the argument.} sparingly.
Indeed, try to avoid footnotes altogether and include necessary peripheral
observations in
the text (within parentheses, if you prefer, as in this sentence).  If you
wish to use a footnote, place it at the bottom of the column on the page on
which it is referenced. Use Times 8-point type, single-spaced.

%-------------------------------------------------------------------------
\subsection{References}

List and number all bibliographical references in 9-point Times,
single-spaced, at the end of your paper. When referenced in the text,
enclose the citation number in square brackets, for
example~\cite{Authors14}.  Where appropriate, include the name(s) of
editors of referenced books.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|}
\hline
Method & Frobnability \\
\hline\hline
Theirs & Frumpy \\
Yours & Frobbly \\
Ours & Makes one's heart Frob\\
\hline
\end{tabular}
\end{center}
\caption{Results.   Ours is better.}
\end{table}

%-------------------------------------------------------------------------
\subsection{Illustrations, graphs, and photographs}

All graphics should be centered.  Please ensure that any point you wish to
make is resolvable in a printed copy of the paper.  Resize fonts in figures
to match the font in the body text, and choose line widths which render
effectively in print.  Many readers (and reviewers), even of an electronic
copy, will choose to print your paper in order to read it.  You cannot
insist that they do otherwise, and therefore must not assume that they can
zoom in to see tiny details on a graphic.

When placing figures in \LaTeX, it's almost always best to use
\verb+\includegraphics+, and to specify the  figure width as a multiple of
the line width as in the example below
{\small\begin{verbatim}
   \usepackage[dvips]{graphicx} ...
   \includegraphics[width=0.8\linewidth]
                   {myfile.eps}
\end{verbatim}
}

%-------------------------------------------------------------------------
\subsection{Color}

Please refer to the author guidelines on the CVPR 2019 web page for a discussion
of the use of color in your document.

%------------------------------------------------------------------------
\section{Final copy}

You must include your signed IEEE copyright release form when you submit
your finished paper. We MUST have this form before your paper can be
published in the proceedings.

Please direct any questions to the production editor in charge of these
proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
Fax (714) 761-1784.

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}

### 2019-05-30 paper/spad_single/sections/method.tex

--- 2018-11-16 paper/spad_single/sections/method.tex
@@
-\subsection{Monocular Depth Estimation}
+In this section, we describe the measurement model for a single-pixel
+time-of-flight lidar sensor under diffuse, pulsed laser illumination. 
+\subsection{Measurement Model}
+Consider a laser which emits a pulse at time $t = 0$ with time-varying intensity
+$g(t)$ uniformly illuminating some 3D scene. We parameterize the geometry of the
+scene as a height map $z(x, y)$.
+Neglecting albedo and falloff effects, an ideal detector counting photon events
+from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record
 
-\subsection{Global Depth Hints}
+\begin{equation}
+  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt \label{single_loc_spad} 
+\end{equation}
 
+where $c$ is the speed of light, and $f$ is a function that models the temporal uncertainty in the
+detector. Single-photon avalanche diodes (SPADs) are highly sensitive
+photodetectors which are able to record single photon events with high temporal
+precision \cite{Stuff}. Since the detection of each photon can be described with
+a Bernoulli random variable,
+the total number of accumulated photons in this time interval follows a Poisson
+distribution according to
+
+\begin{equation}
+  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+\end{equation}
+
+where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
+photon counts due to the reflectance $r(x,y)$ of the scene and due to the
+inverse square falloff $1/z(x,y)^2$.
+In addition, $\eta$ is the detection probability of a photon
+triggering a SPAD event, and $b = \eta a + d$ is the average number of background detections resulting
+from ambient photons $a$
+and erroneous ``dark count'' events $d$ resulting from noise within the SPAD.
+\newpage
+\begin{table*}[htbp]
+  \begin{center}
+    \begin{tabularx}{\linewidth}{*{2}{X}}
+      \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rgb.png} &
+      \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rawdepth.png} \\
+      \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/depth_hist.png} &
+      \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/spad_hist.png} \\
+    \end{tabularx}
+  \end{center}
+  \caption{Sample Image. Top Left is the RGB image. Top Right is ground truth
+    depth. Bottom Left is Raw ground truth depth histogram. Bottom Right is
+    simulated SPAD measurements. Notice how closer depths are magnified and far
+    depths are attenuated.}
+\end{table*}
+
+\subsection{Monocular depth estimation with global depth hints}
+Given a single RGB image $I(x,y)$ and a vector of photon arrivals $h[n]$
+described by equation \ref{global_hints}, we seek to
+reconstruct the ground truth depth map $z(x,y)$.
+Our method has two parts. First, we initialize our estimate of the depth map from the single RGB
+image via a monocular depth estimator described below. Second, we refine this depth map using
+the captured measurements $h[n]$ via a process we call Differentiable Histogram
+Matching (DHM).
+Differentiable histogram matching is a tool for post-processing the image to
+match the depth map to the statistics we capture from the SPAD.
+
+\paragraph{Initialization via CNN}
+Convoluational Neural Networks have become increasingly capable of leveraging
+monocular depth cues to produce accurate estimates of depth
+from only a single image. We therefore choose to initialize our depth map
+estimate $\hat z^{(0)}(x,y)$ using
+a CNN. However, any depth estimator reliant on only a single
+view will be unable to resolve the inherent scale ambiguity in the scene resulting
+from the tradeoff between size of and distance to an object. The next step,
+differentiable histogram matching, will resolve this ambiguity using the depth
+information present in the SPAD histogram.
+
+\paragraph{Differentiable Histogram Matching}
+Given our initial depth map estimate, our goal is now to refine that depth map
+so that it agrees with the information provided by the SPAD histogram.
+Figure showing just the differentiable histogram matching part of the model.
+At a high level, we perform local optimization over the pixels of the depth map
+to make it consistent with the observed measurements $h[n]$.
+Given per-pixel depth, we can simulate SPAD histogram formation using equation
+\ref{global_hints}, where we approximate $\lambda_{x,y}[n]$ using kernel density
+estimation \cite{something} as:
+\begin{equation}
+  \hat \lambda^{(i)}_{x,y}[n] = \frac{1}{\sigma\sqrt{2 \pi}}\exp\paren*{-\frac{1}{2\sigma^2}(n - \hat z^{(i)}(x,y))} \label{KDE}
+\end{equation}
+where $\hat z^{(i)}(x, y)$ is our estimate of the depth at pixel $(x,y)$ at
+iteration $i$.
+
+Once we have $\lambda^{(i)}$, we compute $\hat h[n]$ according to the rest of
+the SPAD histogram formation model (neglecting the Poisson sampling) as follows
+\begin{equation}
+  \hat h[n] = \sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b. \label{diff_forward}
+\end{equation}
+Finally, given two histograms, we can compute the Wasserstein Distance between
+them. As described in \ref{Cuturi et. al.}, the Wasserstein Distance or ``earth
+mover's distance'' measures the distance between two probability distributions
+by calculating the minimum cost of moving the mass required to turn the first
+distribution into the second. It is particularly desirable
+because unlike the KL divergence or the simple RMSE, the Wasserstein Distance scales with
+separation as well as magnitude (see figure). Although the computation of the
+Wasserstein Distance requires solving a linear program, there is a regularized
+version known as the dual-Sinkhorn Distance
+which can be computed via Sinkhorn-Knopp Iterations in a fast and differentiable manner.
+We refer the reader to \ref{Cuturi et. al.} for details, but provide the
+optimization problem here.
+
+Given histograms $h, \hat h$ in $\Delta^n$ and a cost matrix $C$ in $\R^{n \times
+  n}$, the dual-Sinkhorn Divergence is found by solving
+the optimization problem
+\begin{equation}
+    \begin{aligned}
+    &\text{minimize} && \langle W, C \rangle  - \frac{1}{\lambda}h(W) \\
+    &\text{subject to} && W^Th = \bm{1} \\
+    &                  && W\hat h = \bm{1} \\
+    &                  && W \succeq 0 \\
+  \end{aligned}
+\end{equation}
+where $W \in \Delta^{n \times n}$ is the optimization variable, $\bm{1}$ denotes the
+vector of all ones, $h(\cdot)$ is the entropy of a probability distribution, and
+$\langle \cdot, \cdot \rangle$ denotes the inner product of two matrices.
 \begin{itemize}
-	\item image formation model	
-	\item training details
-	\item simulations and comparison: qualitative and quantitative
+\item Pseudocode for sinkhorn iterations?
+  \item Not sure what figure to use...
 \end{itemize}
+\newpage
+\begin{figure}
+  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.png}
+  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
+  per-pixel depth estimate. We then perform gradient descent to optimize that
+  estimate using the SPAD forward model and the dual-Sinkhorn distance.}
+\end{figure}
+
+\subsection{Implementation Details}
+For the Monocular Depth Estimator, we use a pretrained version of the
+the Deep Ordinal Regression Network (DORN) \cite{}. We use the implementation of
+the Sinkhorn Iteration (for calculating the dual-Sinkhorn distance)
+from \ref{Cuturi et. al.} We update the depth map using gradient descent.
+Everything is implemented in PyTorch.
+We run the model on a NVIDIA Titan X GPU, where it takes approximately 5 seconds
+to fully process a single RGB-SPAD data pair.
+Table with hyperparameters (defer to supplementary info?)
+\begin{itemize}
+\item Kernel Density Estimation (sigma)
+\item Sinkhorn Iterations (maximum number, epsilon tolerance)
+\item Gradient Descent (learning rate, epsilon tolerance, max iterations)
+\item Simulation hyperparameters ($\eta, b$)
+\end{itemize}

### 2019-05-31 evaluate_nohints_sid_test_split.py
DenseDepth results replicated.

@@ -1,39 +1,27 @@
 #!/usr/bin/env python3
 import os
 import torch
-import json
-from torch.utils.data import DataLoader
-from utils.train_utils import init_randomness, worker_init_randomness
-from utils.eval_utils import evaluate_model_on_dataset, evaluate_model_on_data_entry
+from utils.train_utils import init_randomness
+from utils.eval_utils import evaluate_model_on_dataset
 from models.core.checkpoint import load_checkpoint, safe_makedir
 from models import make_model
 from sacred import Experiment
 from sacred.observers import FileStorageObserver
-from time import perf_counter
 
 # Dataset
-from models.data.nyuv2_official_hints_sid_dataset import nyuv2_hints_sid_ingredient, load_data
-from models.data.utils.spad_utils import spad_ingredient
+from models.data.nyuv2_test_split_dataset import nyuv2_test_split_ingredient, load_data
 
-ex = Experiment('eval_dorn_sinkhorn_opt', ingredients=[nyuv2_hints_sid_ingredient, spad_ingredient])
+ex = Experiment('eval_nohints_sid', ingredients=[nyuv2_test_split_ingredient])
+
+
+# Tensorboardx
+# writer = SummaryWriter()
 
 @ex.config
-def cfg(data_config, spad_config):
+def cfg(data_config):
     model_config = {                            # Load pretrained model for testing
-        "model_name": "DORN_sinkhorn_opt",
+        "model_name": "DORN_nyu_nohints",
         "model_params": {
-            "sgd_iters": 100,
-            "sinkhorn_iters": 40,
-            "sigma": 0.5,
-            "lam": 1e-2,
-            "kde_eps": 1e-4,
-            "sinkhorn_eps": 1e-4,
-            "dc_eps": 1e-5,
-            "remove_dc": spad_config["dc_count"] > 0.,
-            "use_intensity": spad_config["use_intensity"],
-            "use_squared_falloff": spad_config["use_squared_falloff"],
-            "lr": 1e3,
-            "hints_len": 68,
             "in_channels": 3,
             "in_height": 257,
             "in_width": 353,
@@ -47,36 +35,25 @@ def cfg(data_config, spad_config):
             "pretrained": True,
             "state_dict_file": os.path.join("models", "torch_params_nyuv2_BGR.pth.tar"),
         },
-        "model_state_dict_fn": None             # Keep as None
+        "model_state_dict_fn": None
     }
[…]

### 2019-05-31 models/__init__.py

@@ -4,6 +4,7 @@ from .DORN_hints import DORN_nyu_hints, DORN_nyu_hints_Unet, DORN_nyu_histogram_
 from .DORN_bayesian_opt import DORN_bayesian_opt
 from .DORN_sinkhorn_opt import DORN_sinkhorn_opt
 from .DORN_median_matching import DORN_median_matching
+from .DenseDepth_nohints import DenseDepth, DenseDepthMedianRescaling
 # import future models here
 
 

### 2019-05-31 paper/spad_single/sections/results.tex
DenseDepth results replicated.

@@
   DORN (rescaled) & 0.871 & 0.969 & 0.991 & 0.514 & 0.075 & 0.048 \\
-Alhashim, Wonka (2019)&0.846&0.974&0.994&0.465&0.123&0.053 \\
-Alhashim, Wonka (2019) rescaled using GT depth"&0.895&\textbf{0.980}&\textbf{0.996}&\textbf{0.390}&\textbf{0.103}&\textbf{0.043} \\
+Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
+Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
   \midrule

### 2019-05-31 models/data/nyuv2_test_split_dataset.py

@@ -1,0 +1,110 @@
+import os
+import json
+import torch
+import numpy as np
+from torch.utils.data import Dataset
+import cv2
+
+from torchvision import transforms
+from models.data.utils.transforms import (ResizeAll, Save, Normalize,
+                                          AddDepthMask, ToTensorAll)
+
+from sacred import Experiment
+
+nyuv2_test_split_ingredient = Experiment('data_config')
+
+@nyuv2_test_split_ingredient.config
+def cfg():
+    data_name = "nyu_depth_v2_test_split"
+    root_dir = os.path.join("data", "nyu_depth_v2_wonka")
+    dorn_mode = False # Default is Wonka Mode
+
+    min_depth = 0.
+    max_depth = 10.
+
+class NYUDepthv2TestDataset(Dataset):
+    """
+    The split of the nyu_depth_v2 dataset given by
+    https://github.com/ialhashim/DenseDepth
+    """
+    def __init__(self, rootdir, transform=None):
+        self.rootdir = rootdir
+        self.depth = np.load(os.path.join(rootdir, "eigen_test_depth.npy"))
+        self.rgb = np.load(os.path.join(rootdir, "eigen_test_rgb.npy"))
+        self.crop = np.load(os.path.join(rootdir, "eigen_test_crop.npy"))
+        self.depth_cropped = self.depth[:,
+                                        self.crop[0]:self.crop[1]+1,
+                                        self.crop[2]:self.crop[3]+1
+                                       ]
+        self.rgb_cropped = self.rgb[:,
+                                      self.crop[0]:self.crop[1]+1,
+                                      self.crop[2]:self.crop[3]+1,
+                                      :
+                                      ]
+        self.transform = transform
+
+    def __len__(self):
+        return self.depth.shape[0]
+
+    def __getitem__(self, i):
+        # Convert to torch tensor
+        # Flip channel order
+        sample = {
+            "depth_cropped": self.depth_cropped[i, :, :],
+            "rgb_cropped": self.rgb_cropped[i, :, :, :],
+            "depth": self.depth[i, :, :],
+            "rgb": self.rgb[i, :, :, :],
+            "crop": self.crop,
+        }
+        if self.transform is not None:
+            sample = self.transform(sample)
+        return sample
+
+
+@nyuv2_test_split_ingredient.capture
+def load_data(root_dir, min_depth, max_depth, dorn_mode):
+    """
+
[…]

### 2019-05-31 models/data/utils/spad_utils.py

@@ -13,16 +13,16 @@ def cfg():
     dc_count = 0.1*photon_count     # Simulates ambient + dark count (additional to photon_count
     fwhm_ps = 70.                   # Full-width-at-half-maximum of (Gaussian) SPAD jitter, in picoseconds
 
-    use_albedo = True
+    use_intensity = True
     use_squared_falloff = True
-    spad_comment = "use_albedo_{}".format(use_albedo) + "_" + \
+    spad_comment = "use_intensity_{}".format(use_intensity) + "_" + \
                    "use_squared_falloff_{}".format(use_squared_falloff) + "_" + \
                    "dc_count_{}".format(dc_count)
 
 @spad_ingredient.named_config
 def rawhist():
     dc_count = 0.
-    use_albedo = False
+    use_intensity = False
     use_squared_falloff = False
 
 
@@ -41,7 +41,7 @@ def bgr2gray(bgr):
 
 def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
                   spad_bins, photon_count, dc_count, fwhm_ps,
-                  use_albedo, use_squared_falloff):
+                  use_intensity, use_squared_falloff):
     """
     Works in numpy.
     :param depth_truth: The ground truth depth map (z, not distance...)
@@ -53,13 +53,13 @@ def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
     :param photon_count: The number of photons to collect
     :param dc_count: The additional fraction of photons to add to account for dark count + ambient light
     :param fwhm_ps: The full-width-at-half-maximum of the laser pulse jitter
-    :param use_albedo: Whether or not to take the albedo into account when simulating.
+    :param use_intensity: Whether or not to take an intensity image into account when simulating.
     :param use_squared_falloff: Whether or not to take the squared depth into account when simulating
     :return: A simulated spad.
     """
     # Only use the green channel to simulate
     weights = mask
-    if use_albedo:
+    if use_intensity:
         weights = weights * intensity
     if use_squared_falloff:
         weights = weights / (depth_truth ** 2 + 1e-6)

### 2019-05-31 utils/inspect_results.py

@@ -4,28 +4,28 @@ import numpy as np
 import json
 
 
-class Results:
-    """
-    For managing results of evaluation runs on various datasets.
-
-    Really a boilerplate class that abstracts away the idea of a directory with lots
-    of results files in it, and an index that tells you the unique ids of all the files
-    in the results directory.
-    """
-    def __init__(self, results_dir, index_file):
-        """
-
-        :param results_dir: A directory path to the root directory of the results files.
-        :param index_file: A file containing a (json-serialized) iterable of entries.
-        """
-        self.results_dir = results_dir
-        self.index_file = index_file
-
-        # Load the index
-        with open(index_file) as f:
-            self.entries = json.load(f)
-
-    def load_
+# class Results:
+#     """
+#     For managing results of evaluation runs on various datasets.
+#
+#     Really a boilerplate class that abstracts away the idea of a directory with lots
+#     of results files in it, and an index that tells you the unique ids of all the files
+#     in the results directory.
+#     """
+#     def __init__(self, results_dir, index_file):
+#         """
+#
+#         :param results_dir: A directory path to the root directory of the results files.
+#         :param index_file: A file containing a (json-serialized) iterable of entries.
+#         """
+#         self.results_dir = results_dir
+#         self.index_file = index_file
+#
+#         # Load the index
+#         with open(index_file) as f:
+#             self.entries = json.load(f)
+#
+#     def load_
 
 
 

### 2019-06-04 paper/spad_single/sections/results.tex
Sinkhorn opt for DenseDepth and DORN

--- 2019-05-30 paper/spad_single/sections/results.tex
@@
   \toprule
-    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel & $log_{10}$ \\
+    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel \downarrow & $log_{10} \downarrow$ \\
   \midrule
@@
 Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
-DORN&0.828&0.965&0.992&0.509&0.115&0.051 \\
-  DORN (rescaled) & 0.871 & 0.969 & 0.991 & 0.514 & 0.075 & 0.048 \\
-Alhashim, Wonka (2019)&0.846&0.974&0.994&0.465&0.123&0.053 \\
-Alhashim, Wonka (2019) rescaled using GT depth"&0.895&\textbf{0.980}&\textbf{0.996}&\textbf{0.390}&\textbf{0.103}&\textbf{0.043} \\
+DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
+  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
+Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
+Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
   \midrule

### 2019-06-04 models/data/nyuv2_test_split_dataset_hints_sid.py

@@ -8,10 +8,12 @@ import cv2
 from torchvision import transforms
 from models.data.utils.transforms import (ResizeAll, Save, Normalize,
                                           AddDepthMask, ToTensorAll)
+from models.data.utils.sid_utils import SID
+from models.data.utils.spad_utils import SimulateSpadIntensity, spad_ingredient
 
 from sacred import Experiment
 
-nyuv2_test_split_ingredient = Experiment('data_config')
+nyuv2_test_split_ingredient = Experiment('data_config', ingredients=[spad_ingredient])
 
 @nyuv2_test_split_ingredient.config
 def cfg():
@@ -21,6 +23,20 @@ def cfg():
 
     min_depth = 0.
     max_depth = 10.
+
+    # SID stuff (for DORN)
+    sid_bins = 68   # Number of bins (network outputs 2x this number of channels)
+    bin_edges = np.array(range(sid_bins + 1)).astype(np.float32)
+    dorn_decode = np.exp((bin_edges - 1) / 25 - 0.36)
+    d0 = dorn_decode[0]
+    d1 = dorn_decode[1]
+    # Algebra stuff to make the depth bins work out exactly like in the
+    # original DORN code.
+    alpha = (2 * d0 ** 2) / (d1 + d0)
+    beta = alpha * np.exp(sid_bins * np.log(2 * d0 / alpha - 1))
+    del bin_edges, dorn_decode, d0, d1
+    offset = 0.
+
 
 class NYUDepthv2TestDataset(Dataset):
     """
@@ -69,7 +85,10 @@ class NYUDepthv2TestDataset(Dataset):
 
 
 @nyuv2_test_split_ingredient.capture
-def load_data(root_dir, min_depth, max_depth, dorn_mode):
+def load_data(root_dir,
+              min_depth, max_depth, dorn_mode,
+              sid_bins, alpha, beta, offset,
+              spad_config):
     """
 
     :param root_dir:  The root directory from which to load the dataset
@@ -78,34 +97,51 @@ def load_data(root_dir, min_depth, max_depth, dorn_mode):
     """
     test = NYUDepthv2TestDataset(root_dir, transform=None, dorn_mode=dorn_mode)
 
+    # Give data entries as DORN expects
+    transform_mean = np.array([[[103.0626, 115.9029, 123.1516]]]).astype(np.float32)
+    transform_var = np.ones((1, 1, 3))
+    transform_list = [
[…]

### 2019-06-04 models/DORN_median_matching.py
Sinkhorn opt for DenseDepth and DORN

@@ -36,18 +36,35 @@ class DORN_median_matching(DORN_nyu_nohints):
                                                    frozen, pretrained,
                                                    state_dict_file)
 
+    def predict(self, input_, device, resize_output=True):
+        # one = perf_counter()
+        rgb = input_["rgb"].to(device)
+        # print("dataloader: model input")
+        # print(rgb[:,:,50:55,50:55])
+        # two = perf_counter()
+        depth_pred = self.forward(rgb)
+        # three = perf_counter()
+        # print("Forward pass: {}".format(three - two))
+        logprobs = self.to_logprobs(depth_pred)
+        if resize_output:
+            original_size = input_["rgb_orig"].size()[-2:]
+            # Note: align_corners=False gives same behavior as cv2.resize
+            depth_pred_full = F.interpolate(depth_pred, size=original_size,
+                                            mode="bilinear", align_corners=False)
+            logprobs_full = self.to_logprobs(depth_pred_full)
+            return self.ord_decode(logprobs_full, self.sid_obj)
+        return self.ord_decode(logprobs, self.sid_obj)
+
     def evaluate(self, data, device):
         # one = perf_counter()
-        _, logprobs = self.get_loss(data, device, resize_output=True)
-        pred = self.ord_decode(logprobs, self.sid_obj)
-
+        pred = self.predict(data, device, resize_output=True)
 
         # Median matching
         # Get median from GT depth
         gt = data["rawdepth_orig"]
         mask = data["mask_orig"]
         gt_median = torch.median(gt[mask > 0.])
-        pred_median = torch.median(pred)
+        pred_median = torch.median(pred[mask > 0.])
 
         pred_rescaled = torch.clamp(pred * (gt_median/pred_median), min=self.min_depth, max=self.max_depth)
         metrics = self.get_metrics(pred_rescaled,

### 2019-06-04 models/DORN_sinkhorn_opt.py

@@ -162,7 +162,7 @@ class DORN_sinkhorn_opt:
         scaling = None
         if self.use_intensity:
             # intensity = input_["albedo_orig"][:, 1:2, ...].to(device) / 255.
-            scaling = bgr2gray(input_["rgb_orig"])
+            scaling = bgr2gray(input_["rgb_cropped_orig"])
         # Squared depth check
         inv_squared_depths = None
         if self.use_squared_falloff:
@@ -184,7 +184,7 @@ class DORN_sinkhorn_opt:
             # Note: align_corners=False gives same behavior as cv2.resize
 
         # compute metrics
-        gt = input_["rawdepth_orig"].cpu()
+        gt = input_["depth_cropped_orig"].cpu()
         mask = input_["mask_orig"].cpu()
         metrics = self.get_metrics(pred, gt, mask)
 

### 2019-06-18 models/DenseDepth_models.py
Downloaded and processed nyuv2 labeled dataset.

@@ -215,6 +215,7 @@ class DenseDepthSinkhornOpt(DenseDepth):
                                           lr=self.lr, num_sgd_iters=self.sgd_iters, num_sinkhorn_iters=self.sinkhorn_iters,
                                           kde_eps=self.kde_eps,
                                           sinkhorn_eps=self.sinkhorn_eps,
+                                          min_sgd_iters=100,
                                           inv_squared_depths=inv_squared_depths,
                                           scaling=scaling, writer=self.writer, gt=gt,
                                           model=self)
@@ -240,8 +241,8 @@ class DenseDepthSinkhornOpt(DenseDepth):
             log_single_gray_img(self.writer, "depth/pred", pred, self.min_depth, self.max_depth)
             log_single_gray_img(self.writer, "img/mask", mask, 0., 1.)
             if scaling is not None:
-                print("min scaling", torch.min(scaling))
-                print("max scaling", torch.max(scaling))
+                # print("min scaling", torch.min(scaling))
+                # print("max scaling", torch.max(scaling))
                 log_single_gray_img(self.writer, "img/intensity", scaling, 0., 1.)
             rgb_img = vutils.make_grid(rgb_cropped/ 255, nrow=1)
             self.writer.add_image("img/rgb", rgb_img, 0)

### 2019-06-18 models/sinkhorn_dist.py

@@ -245,6 +245,7 @@ def optimize_depth_map_masked(x_index_init, mask, sigma, n_bins,
                               lr, num_sgd_iters, num_sinkhorn_iters,
                               kde_eps=1e-5,
                               sinkhorn_eps=1e-2,
+                              min_sgd_iters=0.,
                               inv_squared_depths=None,
                               scaling=None,
                               writer=None, gt=None, model=None):
@@ -262,6 +263,7 @@ def optimize_depth_map_masked(x_index_init, mask, sigma, n_bins,
     :param num_sinkhorn_iters: Maximum number of sinkhorn iteration steps to take.
     :param kde_eps: Epsilon used for KDE to prevent 0 values in histogram.
     :param sinkhorn_eps: Epsilon used to control stopping criterion for the sinkhorn iterations.
+    :param min_sgd_iters: Minimum number of SGD iterations to undergo before stopping.
     :param inv_squared_depths: 1/depth^2 for each bin in [0, n_bins-1]
     :param scaling: Per-pixel scaling image.
     :return:
@@ -310,10 +312,10 @@ def optimize_depth_map_masked(x_index_init, mask, sigma, n_bins,
             pred_temp = model.sid_obj.get_value_from_sid_index(torch.floor(x_best).detach().long())
             log_single_gray_img(writer, "depth/pred", pred_temp, model.min_depth, model.max_depth, global_step=i)
             # Diff image
-            add_diff_map(writer, "depth/diff", gt, pred_temp, i)
+            add_diff_map(writer, "depth/diff", gt.cpu(), pred_temp.cpu(), i)
 
             # RMSE
-            metrics = model.get_metrics(pred_temp, gt, mask)
+            metrics = model.get_metrics(pred_temp.cpu(), gt.cpu(), mask.cpu())
             writer.add_scalar("data/rmse", metrics["rmse"], i)
 
             # Histogram plot
@@ -338,7 +340,7 @@ def optimize_depth_map_masked(x_index_init, mask, sigma, n_bins,
             rel_improvement = np.abs(prev_loss - loss.item())/loss.item()
             print("rel_improvement", rel_improvement)
             # if loss.item() < sinkhorn_eps:
-            if rel_improvement < sinkhorn_eps:
+            if rel_improvement < sinkhorn_eps and i >= min_sgd_iters:
                 x_index = torch.clamp(x_index, min=0., max=n_bins).requires_grad_(True)
                 print("early stopping")
                 return x_best, x_hist

### 2019-06-18 paper/spad_single/sections/results.tex
Downloaded and processed nyuv2 labeled dataset.

@@
   \toprule
-    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel \downarrow & $log_{10} \downarrow$ \\
+    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
   \midrule
@@
   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
-  Ours (albedo/falloff) & 0.798 & 0.960 & 0.988 & 0.615 & 0.143 & 0.068 \\
+  Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
+  Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
+  \bottomrule
+\end{tabular} 
+\end{center}
+\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
+\end{table*}
+%%%
+\begin{table*}
+\begin{center}
+\begin{tabular}{lccc|ccc}
+  \toprule
+    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
+  \midrule
+  DORN (cite)&0.818&0.950&0.982&0.620&0.137&0.063 \\
+DenseNet(cite))&0.847&0.973&0.994&0.461&0.123&0.053 \\
+  \midrule
+  DORN  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
+  DORN (Wass)
+  DORN (Histogram Matching)
+ Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
+  DenseNet (Wass)
+  DenseNet (Histogram Matching)
+  \midrule
+  DORN (Median SPAD Rescaling)
+  DORN + Wasserstein (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
+  DenseDepth (Median SPAD Rescaling)
+  DenseDepth + Wasserstein (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
+  \midrule
   \bottomrule

### 2019-06-18 evaluate_dorn_sinkhorn_opt_test_split.py

@@ -106,10 +106,10 @@ def main(model_config,
 
     from tensorboardX import SummaryWriter
     from datetime import datetime
-    model.writer = SummaryWriter(log_dir=os.path.join("runs",
-                                                      datetime.now().strftime('%b%d'),
-                                                      datetime.now().strftime('%H-%M-%S_') + \
-                                                      "dorn_sinkhorn_opt"))
+    # model.writer = SummaryWriter(log_dir=os.path.join("runs",
+    #                                                   datetime.now().strftime('%b%d'),
+    #                                                   datetime.now().strftime('%H-%M-%S_') + \
+    #                                                   "dorn_sinkhorn_opt"))
 
     # Load the data
     dataset = load_data(dorn_mode=True)

### 2019-07-01 paper/spad_single/sections/results.tex
Filled out middle section of table, even though it doesn't match published work.

@@
   \midrule
-  DORN  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-  DORN (Wass)
-  DORN (Histogram Matching)
- Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
-  DenseNet (Wass)
-  DenseNet (Histogram Matching)
+  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
+  DORN (Wass) & - & - & - & - & - & - \\
+  DORN (Histogram Matching) & - & - & - & - & - & - \\
+  DenseNet (rescaled) &0.888 & 0.978&0.995&0.409&0.106&0.045 \\
+  DenseNet (Wass) & - & - & - & - & - & - \\ 
+  DenseNet (Histogram Matching) &\textbf{0.930} &\textbf{0.984}&\textbf{0.995}&\textbf{0.338}&\textbf{0.080}&\textbf{0.034}\\
   \midrule
-  DORN (Median SPAD Rescaling)
+  DORN (Median SPAD Rescaling) & - & - & - & - & - & - \\
   DORN + Wasserstein (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
-  DenseDepth (Median SPAD Rescaling)
+  DenseDepth (Median SPAD Rescaling) & - & - & - & - & - & - \\
   DenseDepth + Wasserstein (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\

### 2019-07-01 evaluate_dorn_hist_matching_wasserstein_nyuv2_labeled.py

@@ -1,0 +1,105 @@
+#!/usr/bin/env python3
+import os
+import torch
+from utils.train_utils import init_randomness
+from utils.eval_utils import evaluate_model_on_dataset
+from models.core.checkpoint import load_checkpoint, safe_makedir
+from models import make_model
+from sacred import Experiment
+from sacred.observers import FileStorageObserver
+
+# Dataset
+from models.data.nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+
+ex = Experiment('eval_dorn_nyuv2_labeled', ingredients=[nyuv2_labeled_ingredient])
+
+
+# Tensorboardx
+# writer = SummaryWriter()
+
+@ex.config
+def cfg(data_config):
+    model_config = {                            # Load pretrained model for testing
+        "model_name": "DORN_nyu_nohints",
+        "model_params": {
+            "in_channels": 3,
+            "in_height": 257,
+            "in_width": 353,
+            "sid_bins": 68,
+            "offset": 0.,
+            "min_depth": 0.,
+            "max_depth": 10.,
+            "alpha": 0.6569154266167957,
+            "beta": 9.972175646365525,
+            "frozen": True,
+            "pretrained": True,
+            "state_dict_file": os.path.join("models", "torch_params_nyuv2_BGR.pth.tar"),
+        },
+        "model_state_dict_fn": None
+    }
+
+    ckpt_file = None                            # Keep as None
+    dataset_type = "test"
+    save_outputs = True
+    seed = 95290421
+    small_run = 0
+
+    # hyperparams = ["sgd_iters", "sinkhorn_iters", "sigma", "lam", "kde_eps", "sinkhorn_eps"]
+    pdict = model_config["model_params"]
+    del pdict
+
+    # print(data_config.keys())
+    output_dir = os.path.join("results",
+                              data_config["data_name"],    # e.g. nyu_depth_v2
+                              "{}_{}".format(dataset_type, small_run),
+                              model_config["model_name"])  # e.g. DORN_nyu_nohints
+
+    safe_makedir(output_dir)
+    ex.observers.append(FileStorageObserver.create(os.path.join(output_dir, "runs")))
+
+    cuda_device = "0"                       # The gpu index to run on. Should be a string
+    os.environ["CUDA_VISIBLE_DEVICES"] = cuda_device
+    # print("after: {}".format(os.environ["CUDA_VISIBLE_DEVICES"]))
[…]

### 2019-07-01 evaluate_densedepth_hist_matching_wasserstein_nyuv2_labeled.py
Filled out middle section of table, even though it doesn't match published work.

@@ -24,8 +24,22 @@ ex = Experiment('densedepth_nyuv2_labeled', ingredients=[nyuv2_labeled_ingredien
 @ex.config
 def cfg(data_config):
     model_config = {                            # Load pretrained model for testing
-        "model_name": "DenseDepth",
+        "model_name": "DenseDepthHistogramMatchingWasserstein",
         "model_params": {
+            "sgd_iters": 100,
+            "sinkhorn_iters": 40,
+            "sigma": 0.5,
+            "lam": 1e1,
+            "kde_eps": 1e-4,
+            "sinkhorn_eps": 1e-7,
+            "dc_eps": 1e-5,
+            "lr": 1e5,
+            "min_depth": 0.,
+            "max_depth": 10.,
+            "sid_bins": 68,
+            "offset": 0.,
+            "alpha": 0.6569154266167957,
+            "beta": 9.972175646365525,
             "existing": os.path.join("models", "nyu.h5"),
         },
         "model_state_dict_fn": None
@@ -46,8 +60,10 @@ def cfg(data_config):
     safe_makedir(output_dir)
     ex.observers.append(FileStorageObserver.create(os.path.join(output_dir, "runs")))
 
-    cuda_device = "0"                       # The gpu index to run on. Should be a string
+    cuda_device = "0,1"  # The visible gpus. First one is the tensorflow, second one is pytorch.
     os.environ["CUDA_VISIBLE_DEVICES"] = cuda_device
+    # print("after: {}".format(os.environ["CUDA_VISIBLE_DEVICES"]))
+    device = torch.device("cuda:1" if torch.cuda.is_available() else "cpu")
     # print("after: {}".format(os.environ["CUDA_VISIBLE_DEVICES"]))
     if ckpt_file is not None:
         model_update, _, _ = load_checkpoint(ckpt_file)
@@ -64,10 +80,11 @@ def main(model_config,
          seed,
          small_run,
          dataset_type,
-         entry):
+         entry,
+         device):
     # Load the model
     model = make_model(**model_config)
-    # model.sid_obj.to(device)
+    model.sinkhorn_opt.to(device)
 
     from tensorboardX import SummaryWriter
     from datetime import datetime
@@ -82,13 +99,14 @@ def main(model_config,
     eval_fn = lambda input_, device: model.evaluate(input_["rgb"],
                                                     input_["crop"][0,:],
                                                     input_["depth_cropped"],
-                                                    torch.ones_like(input_["depth_cropped"]))
[…]

### 2019-07-01 evaluate_densedepth_sinkhorn_nyuv2_labeled.py

@@ -79,8 +79,8 @@ def main(model_config,
     # Load the data
     train, test = load_data(dorn_mode=False)
     dataset = train if dataset_type == "train" else test
-    eval_fn = lambda input_, device: model.evaluate(input_["rgb"].numpy(),
-                                                    input_["crop"][0,:].numpy(),
+    eval_fn = lambda input_, device: model.evaluate(input_["rgb"],
+                                                    input_["crop"][0,:],
                                                     input_["depth_cropped"],
                                                     torch.ones_like(input_["depth_cropped"]))
 

### 2019-07-01 evaluate_dorn_median_nyuv2_labeled.py

@@ -1,0 +1,102 @@
+#!/usr/bin/env python3
+import os
+import torch
+from utils.train_utils import init_randomness
+from utils.eval_utils import evaluate_model_on_dataset
+from models.core.checkpoint import load_checkpoint, safe_makedir
+from models import make_model
+from sacred import Experiment
+from sacred.observers import FileStorageObserver
+
+# Dataset
+from models.data.nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+
+ex = Experiment('eval_dorn_median_nyuv2_labeled', ingredients=[nyuv2_labeled_ingredient])
+
+
+# Tensorboardx
+# writer = SummaryWriter()
+
+@ex.config
+def cfg(data_config):
+    model_config = {                            # Load pretrained model for testing
+        "model_name": "DORN_median_matching",
+        "model_params": {
+            "in_channels": 3,
+            "in_height": 257,
+            "in_width": 353,
+            "sid_bins": 68,
+            "offset": 0.,
+            "min_depth": 0.,
+            "max_depth": 10.,
+            "alpha": 0.6569154266167957,
+            "beta": 9.972175646365525,
+            "frozen": True,
+            "pretrained": True,
+            "state_dict_file": os.path.join("models", "torch_params_nyuv2_BGR.pth.tar"),
+        },
+        "model_state_dict_fn": None
+    }
+
+    ckpt_file = None                            # Keep as None
+    dataset_type = "test"
+    save_outputs = True
+    seed = 95290421
+    small_run = 0
+
+    # print(data_config.keys())
+    output_dir = os.path.join("results",
+                              data_config["data_name"],    # e.g. nyu_depth_v2
+                              "{}_{}".format(dataset_type, small_run),
+                              model_config["model_name"])  # e.g. DORN_nyu_nohints
+
+    safe_makedir(output_dir)
+    ex.observers.append(FileStorageObserver.create(os.path.join(output_dir, "runs")))
+
+    cuda_device = "0"                       # The gpu index to run on. Should be a string
+    os.environ["CUDA_VISIBLE_DEVICES"] = cuda_device
+    # print("after: {}".format(os.environ["CUDA_VISIBLE_DEVICES"]))
+    device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
+    print("using device: {} (CUDA_VISIBLE_DEVICES = {})".format(device,
[…]

### 2019-07-01 models/data/data_utils/spad_utils.py

@@ -13,6 +13,7 @@ def cfg():
     dc_count = 0.1*photon_count     # Simulates ambient + dark count (additional to photon_count
     fwhm_ps = 70.                   # Full-width-at-half-maximum of (Gaussian) SPAD jitter, in picoseconds
 
+    use_poisson = True
     use_intensity = True
     use_squared_falloff = True
     spad_comment = "use_intensity_{}".format(use_intensity) + "_" + \
@@ -22,14 +23,15 @@ def cfg():
 @spad_ingredient.named_config
 def rawhist():
     dc_count = 0.
+    use_poisson = False
     use_intensity = False
     use_squared_falloff = False
 
 
 def bgr2gray(bgr):
     """
-    Numpy / Torch version of cv2.cvtColor(image, cv2.COLOR_BGR2GRAY).
-    :param bgr: tensor with channels in (B, G, R) order
+    Pytorch version of cv2.cvtColor(image, cv2.COLOR_BGR2GRAY).
+    :param bgr: NxCxHxW tensor with channels in (B, G, R) order
     :return: tensor with grayscale image
     """
     if len(bgr.shape) == 4:
@@ -41,7 +43,7 @@ def bgr2gray(bgr):
 
 def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
                   spad_bins, photon_count, dc_count, fwhm_ps,
-                  use_intensity, use_squared_falloff):
+                  use_poisson, use_intensity, use_squared_falloff):
     """
     Works in numpy.
     :param depth_truth: The ground truth depth map (z, not distance...)
@@ -53,6 +55,7 @@ def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
     :param photon_count: The number of photons to collect
     :param dc_count: The additional fraction of photons to add to account for dark count + ambient light
     :param fwhm_ps: The full-width-at-half-maximum of the laser pulse jitter
+    :param use_poisson: Whether or not to apply poisson noise at the end.
     :param use_intensity: Whether or not to take an intensity image into account when simulating.
     :param use_squared_falloff: Whether or not to take the squared depth into account when simulating
     :return: A simulated spad.
@@ -83,7 +86,8 @@ def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
     spad_counts = np.clip(spad_counts, a_min=0., a_max=None)
     # Apply poisson
     # print(np.min(spad_counts))
-    spad_counts = np.random.poisson(spad_counts)
+    if use_poisson:
[…]

### 2019-07-18 evaluate_densedepth_median_nyuv2_labeled.py
New file structure, setup.py, finished new weighted histogram matching method.

@@ -40,7 +40,7 @@ def cfg(data_config):
     # print(data_config.keys())
     output_dir = os.path.join("results",
                               data_config["data_name"],    # e.g. nyu_depth_v2
-                              "{}_{}".format("test", small_run),
+                              "{}_{}".format(dataset_type, small_run),
                               model_config["model_name"])  # e.g. DORN_nyu_nohints
 
     safe_makedir(output_dir)
@@ -71,10 +71,6 @@ def main(model_config,
 
     from tensorboardX import SummaryWriter
     from datetime import datetime
-    model.writer = SummaryWriter(log_dir=os.path.join("runs",
-                                                      datetime.now().strftime('%b%d'),
-                                                      datetime.now().strftime('%H-%M-%S_') + \
-                                                      "densedepth_nohints"))
 
     # Load the data
     train, test = load_data(dorn_mode=False)

### 2019-07-18 models/__init__.py

@@ -1,6 +1,7 @@
 from .denoising_unet import DenoisingUnetModel
 from .DORN_nohints import DORN_nyu_nohints
-from .DORN_hints import DORN_nyu_hints, DORN_nyu_hints_Unet, DORN_nyu_histogram_matching
+from .DORN_hints import DORN_nyu_hints, DORN_nyu_hints_Unet, DORN_nyu_histogram_matching, \
+                        DORN_histogram_matching_wass
 from .DORN_bayesian_opt import DORN_bayesian_opt
 from .DORN_sinkhorn_opt import DORN_sinkhorn_opt
 from .DORN_median_matching import DORN_median_matching

### 2019-07-18 nyuv2/dorn/nyuv2_labeled_dataset.py

@@ -1,0 +1,176 @@
+import os
+import torch
+import numpy as np
+from torch.utils.data import Dataset
+
+from torchvision import transforms
+from models.data.data_utils.transforms import (ResizeAll, Save, Normalize,
+                                               AddDepthMask, ToTensorAll)
+
+from sacred import Experiment
+
+nyuv2_labeled_ingredient = Experiment('data_config')
+
+@nyuv2_labeled_ingredient.config
+def cfg():
+    data_name = "nyu_depth_v2_labeled"
+    root_dir = os.path.join("data", "nyu_depth_v2_labeled_numpy")
+    train_files = {
+        "rgb": "train_images.npy",
+        "rgb_cropped": "train_images_cropped.npy",
+        "depth": "train_depths.npy",
+        "depth_cropped": "train_depths_cropped.npy",
+        "rawdepth": "train_rawDepths.npy",
+        "rawdepth_cropped": "train_rawDepths_cropped.npy"
+    }
+    test_files = {
+        "rgb": "test_images.npy",
+        "rgb_cropped": "test_images_cropped",
+        "depth": "test_depths.npy",
+        "depth_cropped": "test_depths_cropped.npy",
+        "rawdepth": "test_rawDepths.npy",
+        "rawdepth_cropped": "test_rawDepths_cropped.npy"
+    }
+    crop = (20, 460,  24, 616)
+
+    min_depth = 0.
+    max_depth = 10.
+
+
+class NYUDepthv2LabeledDataset(Dataset):
+    """
+    The official NYUv2 Labeled dataset, loaded from numpy files.
+    Evaluation crop specified in a separate numpy file.
+    """
+    def __init__(self, rootdir, rgb_file, depth_file, rawdepth_file, crop, transform=None,
+                 bgr_mode=False):
+        """
+
+        :param rootdir:
+        :param rgb_file:
+        :param depth_file:
+        :param rawdepth_file:
+        :param crop_file:
+        :param transform:
+        :param bgr_mode:
+        :param channels_first: True for tensorflow, False for pytorch
+        """
+        self.rootdir = rootdir
+        self.bgr_mode = bgr_mode # set to True if you're loading data for DORN.
+        self.depth = np.load(os.path.join(rootdir, depth_file))        # H x W x N
+        self.rawdepth = np.load(os.path.join(rootdir, rawdepth_file))  # H x W x N
+        self.rgb = np.load(os.path.join(rootdir, rgb_file))            # H x W x C x N
[…]

### 2019-07-18 setup.py

@@ -1,0 +1,10 @@
+from distutils.core import setup
+
+setup(
+    name="spad_single",
+    version="0.0.1",
+    packages=[
+        "models",
+        "utils",
+    ]
+)

### 2019-07-18 wasserstein.py

@@ -1,25 +1,0 @@
-import numpy as np
-import cvxpy as cp
-
-def wasserstein_loss(hist0, hist1, cost_mat, **solver_kwargs):
-    """
-    :param hist0: (N,) numpy array, summing to 1
-    :param hist1: (N,) numpy array, summing to 1
-    :param cost_mat: (N, N) numpy array
-    """
-    assert hist0.shape == hist1.shape
-    assert len(hist0.shape) == 1
-    assert len(cost_mat.shape) == 2
-    assert cost_mat.shape[0] == cost_mat.shape[1]
-    assert hist0.shape[0] == cost_mat.shape[0]
-    N = hist0.shape[0]
-    T = cp.Variable((N, N))
-    obj = cp.Minimize(cp.trace(T.T*cost_mat))
-    constr = [
-        cp.sum(T, axis=0) == hist0,
-        cp.sum(T, axis=1) == hist1,
-        T >= 0.
-    ]
-    prob = cp.Problem(obj, constr)
-    prob.solve(solver="OSQP", **solver_kwargs)
-    return prob.value, T.value

### 2019-07-18 wasserstein_hist_match.py

@@ -1,57 +1,0 @@
-import numpy as np
-from wasserstein import wasserstein_loss
-
-def get_pixel_movements(init_hist, gt_hist, cost_mat, opt_eps=1e-4):
-    """
-    init_hist: In pixel counts. Shape (N,)
-    gt_hist: In pixel counts Shape (M,)
-    cost_mat: Shape (M, N)
-    opt_eps: Threshold below which we zero out all entries of the T matrix.
-    """
-    _, T = wasserstein_loss(init_hist/np.sum(init_hist),
-                            gt_hist/np.sum(gt_hist),
-                            cost_mat, eps_rel=1e-10)
-    
-    T[T < opt_eps] = 0.
-    T[:, np.where(init_hist == 0)] = 0.
-    T_marginal = np.sum(T, axis=0)
-    marginal_nonzero = np.nonzero(T_marginal)
-    T_cond = np.zeros_like(T)
-    T_cond[:, marginal_nonzero] = T[:,marginal_nonzero]/T_marginal[marginal_nonzero]
-
-    T_count = T_cond * init_hist
-    # Correct last nonzero entry in each column so that np.sum(T_count, axis=0) = init_hist
-    for col in range(T_cond.shape[1]):   
-        nonzero_rows = np.nonzero(T_cond[:, col])[0]
-        if len(nonzero_rows) > 0:
-            last_nonzero_row = np.sort(nonzero_rows)[-1]
-            T_count[last_nonzero_row, col] += init_hist[col] - np.sum(T_count, axis=0)[col]
-    return T_count
-
-
-def move_pixels_according_to(T_count, init_index, weights):
-    assert init_index.shape == weights.shape
-    marginal_nonzero = np.nonzero(np.sum(T_count, axis=0))[0]
-    pred_index = np.zeros_like(init_index)
-    index_sets = [np.where(init_index == bin_index) for bin_index in range(T_count.shape[1])]
-    for old_bin in marginal_nonzero: # Indexes columns
-        weight_moved = 0
-        curr = 0
-        for new_bin in range(T_count.shape[0]): # Indexes rows
-            weight_to_move = T_count[new_bin, old_bin]
-            rows, cols = index_sets[old_bin]
-            total = 0.
-            while total < weight_to_move and curr < len(rows):
-                total += weights[rows[curr], cols[curr]]
-                pred_index[rows[curr], cols[curr]] = new_bin
-                curr += 1
[…]

### 2019-07-18 paper/spad_single/sections/results.tex
New file structure, setup.py, finished new weighted histogram matching method.

@@
   \midrule
-  DORN (cite)&0.818&0.950&0.982&0.620&0.137&0.063 \\
-DenseNet(cite))&0.847&0.973&0.994&0.461&0.123&0.053 \\
+  DORN (cite)&0.846&0.954&0.983&0.501&0.120&0.053 \\
+DenseNet(cite))&0.847&0.973&0.994&0.461&0.123&0.054 \\
   \midrule
   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-  DORN (Wass) & - & - & - & - & - & - \\
-  DORN (Histogram Matching) & - & - & - & - & - & - \\
+  DORN (Wass) & 0.847 & 0.953 & 0.983 & 0.499 & 0.117 & 0.053 \\
+  DORN (Histogram Matching) & 0.902 & 0.973 & 0.991 & 0.424 & 0.099 & 0.042 \\
   DenseNet (rescaled) &0.888 & 0.978&0.995&0.409&0.106&0.045 \\

### 2019-07-18 models/DenseDepth_models.py

@@ -142,7 +142,7 @@ class DenseDepthHistogramMatching(DenseDepth):
         pred_init = self.forward(rgb.numpy())
         # pred_sid_index = self.sid.get_sid_index_from_value(pred_init)
         # gt_hist, _ = np.histogram(gt.cpu().numpy(), bins=self.sid.sid_bin_edges)
-        pred = self.hist_match(pred_init, gt_orig)
+        pred = self.hist_match(pred_init, gt_orig.numpy())
         pred = torch.from_numpy(pred).cpu().unsqueeze(0).float()
         pred = pred[...,crop[0]:crop[1], crop[2]:crop[3]]
         metrics = self.get_metrics(pred, gt, mask)
@@ -211,7 +211,7 @@ class DenseDepthHistogramMatchingWasserstein(DenseDepth):
                                         sid_bins=sid_bins,
                                         alpha=alpha, beta=beta, offset=offset)
 
-    def evaluate(self, rgb, crop, gt, mask, device):
+    def predict(self, rgb, crop, gt, mask, device):
         """
 
         :param rgb: N x H' x W' x C numpy array
@@ -221,7 +221,7 @@ class DenseDepthHistogramMatchingWasserstein(DenseDepth):
         :return:
         """
         # Run RGB through cnn to get depth_init
-        pred_init = self.predict(rgb.numpy())
+        pred_init = self.forward(rgb.numpy())
         pred_init = pred_init[:, crop[0]:crop[1], crop[2]:crop[3]]
 
         pred_init = torch.from_numpy(pred_init).unsqueeze(0).float().to(device)
@@ -229,20 +229,25 @@ class DenseDepthHistogramMatchingWasserstein(DenseDepth):
         extended_bin_edges = np.append(extended_bin_edges, float('inf'))
         gt_hist, _ = np.histogram(gt.cpu().numpy(), bins=extended_bin_edges)
         gt_hist = torch.from_numpy(gt_hist).unsqueeze(0).unsqueeze(-1).unsqueeze(-1).float().to(device)
-        rgb = rgb.permute(0, 3, 1, 2).to(device)
+        rgb = rgb.permute(0, 3, 1, 2).to(device)  # N x C x H x W
 
         mask = mask.to(device)
-        pred = self.sinkhorn_opt.optimize(pred_init, torch.flip(rgb, dims=(1,)), gt_hist, mask, device)
+        pred = self.sinkhorn_opt.optimize(pred_init, torch.flip(rgb, dims=(1,)), gt_hist, mask, gt)
+
[…]

### 2019-07-18 models/sinkhorn_opt.py

@@ -17,7 +17,7 @@ from models.loss import get_depth_metrics
 from utils.inspect_results import add_hist_plot, log_single_gray_img
 
 from models.DORN_nohints import DORN_nyu_nohints
-from models.sinkhorn_dist import optimize_depth_map_masked
+from models.sinkhorn_dist import optimize_depth_map_masked, optimize_depth_map_masked_adam
 
 class SinkhornOpt:
     """
@@ -54,7 +54,7 @@ class SinkhornOpt:
         self.cost_mat = torch.from_numpy(C).float()
 
         self.optimize_depth_map = lambda depth_index_init, mask, spad, scaling, gt: \
-            optimize_depth_map_masked(depth_index_init, mask, sigma=self.sigma, n_bins=self.sid_bins,
+            optimize_depth_map_masked_adam(depth_index_init, mask, sigma=self.sigma, n_bins=self.sid_bins,
                                       cost_mat=self.cost_mat, lam=self.lam, gt_hist=spad,
                                       lr=self.lr, num_sgd_iters=self.sgd_iters,
                                       num_sinkhorn_iters=self.sinkhorn_iters,
@@ -75,11 +75,11 @@ class SinkhornOpt:
     def optimize(self, depth_init, bgr, spad, mask, gt=None):
         """
         Works in pytorch.
-        :param depth_init:
-        :param bgr:
-        :param spad:
-        :param mask:
-        :param gt:
+        :param depth_init: N x 1 x H x W
+        :param bgr: N x C x H x W
+        :param spad: 1 x C' x H x W
+        :param mask: N x 1 x H x W
+        :param gt: N x 1 x H x W
         :return:
         """
         scaling = None
@@ -87,13 +87,15 @@ class SinkhornOpt:
             scaling = bgr2gray(bgr)/255.
             if self.writer is not None:
                 log_single_gray_img(self.writer, "img/intensity", scaling, 0., 1.)
-
+        if self.writer is not None:
+            rgb_img = vutils.make_grid(torch.flip(bgr, dims=(1,)) / 255, nrow=1)
+            self.writer.add_image("img/rgb", rgb_img, 0)
         depth_index_init = self.sid_obj.get_sid_index_from_value(depth_init)
         with torch.enable_grad():
             depth_index_final, _ = self.optimize_depth_map(depth_index_init, mask, spad, scaling, gt)
         depth_index_final = torch.floor(depth_index_final).detach().long()
[…]

### 2019-07-18 nyuv2/simulate_spad/spad_utils.py

@@ -1,0 +1,383 @@
+import numpy as np
+import torch
+import cvxpy as cp
+from scipy.signal import fftconvolve
+from sacred import Experiment
+
+spad_ingredient = Experiment("spad_config")
+
+@spad_ingredient.config
+def cfg():
+    spad_bins = 1024                # Number of bins to capture
+    photon_count = 1e6              # Number of real photons that we get
+    dc_count = 0.1*photon_count     # Simulates ambient + dark count (additional to photon_count
+    fwhm_ps = 70.                   # Full-width-at-half-maximum of (Gaussian) SPAD jitter, in picoseconds
+
+    use_poisson = True
+    use_intensity = True
+    use_squared_falloff = True
+    spad_comment = "use_intensity_{}".format(use_intensity) + "_" + \
+                   "use_squared_falloff_{}".format(use_squared_falloff) + "_" + \
+                   "dc_count_{}".format(dc_count)
+
+@spad_ingredient.named_config
+def rawhist():
+    dc_count = 0.
+    use_poisson = False
+    use_intensity = False
+    use_squared_falloff = False
+
+
+def bgr2gray(bgr):
+    """
+    Pytorch version of cv2.cvtColor(image, cv2.COLOR_BGR2GRAY).
+    :param bgr: NxCxHxW tensor with channels in (B, G, R) order
+    :return: tensor with grayscale image
+    """
+    if len(bgr.shape) == 4:
+        # Shape is N x 3 x H x W
+        return 0.2989 * bgr[:,2:3,:,:] + 0.5870 * bgr[:,1:2,:,:] + 0.1140 * bgr[:,0:1,:,:]
+    # Otherwise, shape is H x W x 3
+    return 0.2989 * bgr[:,:,2:3] + 0.5870 * bgr[:,:,1:2] + 0.1140 * bgr[:,:,0:1]
+
+
+def simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
+                  spad_bins, photon_count, dc_count, fwhm_ps,
+                  use_poisson, use_intensity, use_squared_falloff):
+    """
+    Works in numpy.
+    :param depth_truth: The ground truth depth map (z, not distance...)
+    :param albedo: The albedo map, aligned with the ground truth depth map.
+    :param mask: The mask of valid pixels
+    :param min_depth: The minimum depth value (used for the discretization).
+    :param max_depth: The maximum depth value (used for the discretization).
+    :param spad_bins: The number of spad bins to simulate
+    :param photon_count: The number of photons to collect
[…]

### 2019-07-18 utils/inspect_results.py

@@ -42,10 +42,10 @@ def log_single_gray_img(writer, name, img_tensor, min, max, global_step=0):
     writer.add_image(name, img, global_step=global_step)
 
 
-def add_diff_map(writer, name, gt_tensor, img_tensor, global_step=0):
-    diff = gt_tensor - img_tensor
+def add_color_map(writer, name, tensor, global_step=0, **imshow_kwargs):
+    # diff = gt_tensor - img_tensor
     fig = plt.figure()
-    plt.imshow(diff.cpu().numpy().squeeze())
+    plt.imshow(tensor.cpu().numpy().squeeze(), **imshow_kwargs)
     plt.colorbar()
     writer.add_figure(name, fig, global_step=global_step)
 
@@ -117,6 +117,13 @@ def find_max_differential(loss_diffs, loss_names):
     # rel_abs_diff_sorted = sorted(loss_diffs.items(), key=lambda x: x[1]["rel_abs_diff"], reverse=False)
     # rel_sqr_diff_sorted = sorted(loss_diffs.items(), key=lambda x: x[1]["rel_sqr_diff"], reverse=False)
 
+
+def depth_pt_to_img(filepath):
+    data = torch.load(filepath)
+    entry = data["entry"]
+    img = data["pred"]
+    save_image(img, "{}.png".format(entry), nrow=1, padding=0, range=(0., 10.), normalize=True)
+
 #
 # def find_pixelwise_diffs(img1, img2):
 #     """
@@ -126,5 +133,5 @@ def find_max_differential(loss_diffs, loss_names):
 #     :return: absolute value of difference
 #     """
 #     return np.abs(img1 - img2)
-
+# results/nyu_depth_v2_labeled/test_0/DORN_median_matching/1_out.pt
 

### 2019-08-08 paper/spad_single/sections/hardware.tex
Paper update

\subsection{Setup}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/hardware.jpeg}
  \caption{\textbf{Hardware setup}}
\end{figure}
\begin{itemize}
  \item{Description of hardware used}
  \item{Images of scenes used}
\end{itemize}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
  \caption{\textbf{Hardware results}}
\end{figure}

### 2019-08-08 paper/spad_single/sections/introduction.tex
Paper update

@@
 \begin{itemize}
-	\item introduce idea of RGB + single SPAD depth imaging		
-	\item ... gesture recognition, face authentication, ... (e.g. ``learning to be a depth camera'' microsoft paper)
-	\item build prototype, demonstrate results		
+	\item We introduce the idea of augmenting an RGB camera with a single-pixel
+    SPAD to address scale ambiguity error in monocular depth estimators.	
+  \item We analyze our approach on indoor scenes using the NYU Depth v2 dataset.
+    We demonstrate that our approach is able to resolve scale ambiguity while
+    being fast and easy to implement.
+	\item We build a hardware prototype and evaluate the efficacy of our
+    approach on real-world data. 
 \end{itemize}

### 2019-08-09 paper/spad_single/sections/simulation.tex
Wavelet Denoising, then dc removal.

--- 2019-07-18 paper/spad_single/sections/results.tex
@@
-\subsection{Implementation}
-
-hardware, calibration, etc.
-
-\subsection{Results} 
-% Table of quantitative results
+\subsection{Implementation Details}
+\begin{itemize}
+  \item Number of bins used, depth range, laser parameters, use of intensity
+    image.
+  \item Using
+\end{itemize}
 \paragraph{NYU Depth v2}
@@
 
-% Table of qualitative results
-\begin{table*}
-  \begin{center}
-    \begin{tabularx}{\linewidth}{*{5}{X}}
-      RGB & Ground Truth & CNN & CNN + Raw Histogram & CNN + Albedo/Falloff \\
-        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_0.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_0.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_0.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_0.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_0.png} \\ 
-  & & RMSE = 0.462, WAS = 34.615 & RMSE = 0.263, WAS = 11.906 & RMSE = 0.271, WAS = 13.149 \\
-        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_1.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_1.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_1.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_1.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_1.png} \\ 
-  & & RMSE = 0.463, WAS = 9.620 & RMSE = 0.290, WAS = 5.765 & RMSE = 0.372, WAS = 3.854 \\
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_2.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_2.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_2.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_2.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_2.png} \\ 
-    & & RMSE = 0.667, WAS = 72.725 & RMSE = 0.471, WAS = 43.348 & RMSE = 0.584, WAS = 52.787 \\
-        \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/rgb_3.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/gt_3.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_diff_3.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_rawhist_diff_3.png} &
-      \includegraphics[width=\textwidth/6-5pt]{sections/figures/comparison_table/cnn_hist_diff_3.png} \\ 
-  & & RMSE = 1.486, WAS = 31.845 & RMSE = 1.189, WAS = 21.868 & RMSE = 1.844, WAS = 121.540 \\
-    \end{tabularx}
-  \end{center}
-  \caption{\textbf{NYU Depth v2} Qualitative comparison of the raw output of
-    DORN, the corrected depth map when the ground-truth depth histogram is used,
-    and the corrected depth when the simulated SPAD measurements are used.}
-\end{table*}
-\begin{itemize}
-\item Overlay spad histograms?
-\item Show RMSE/delta1/etc.
-\item Show colorbars in the last column.
-\item Show inset squares and then show the zoomed regions in more detail?
-\end{itemize}
+\begin{figure}
+  \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
+  \caption{\textbf{Comparing our results with other methods}}
+\end{figure}

### 2019-08-09 nyuv2/weighted_histogram_matching/evaluate_densedepth.py

@@ -6,7 +6,7 @@ from sacred import Experiment
 from weighted_histogram_matching import image_histogram_match
 from models.data.data_utils.sid_utils import SID
 from spad_utils import rescale_bins
-from remove_dc_from_spad import remove_dc_from_spad_poisson
+from remove_dc_from_spad import remove_dc_from_spad_poisson, remove_dc_from_spad_ambient_estimate
 from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
 
 from models.loss import get_depth_metrics
@@ -29,7 +29,8 @@ def cfg(data_config):
         dc_count,
         use_jitter,
         use_poisson)
-    spad_file = os.path.join(data_dir, "{}_spad.npy".format(hyper_string))
+    spad_file = os.path.join(data_dir, "{}_spad{}.npy".format(hyper_string,
+                                                               "_denoised" if dc_count > 0. else ""))
     densedepth_depth_file = os.path.join(data_dir, "densedepth_{}_outputs.npy".format(dataset_type))
 
     # SID params
@@ -41,6 +42,7 @@ def cfg(data_config):
     # SPAD Denoising params
     lam = 1e1 if use_poisson else 1e-1
     eps_rel = 1e-5
+    n_std = 0.5
 
     entry = None
     save_outputs = True
@@ -53,7 +55,8 @@ def run(dataset_type,
         spad_file,
         densedepth_depth_file,
         hyper_string,
-        sid_bins, alpha, beta, offset, lam, eps_rel,
+        sid_bins, alpha, beta, offset,
+        lam, eps_rel, n_std,
         entry, save_outputs, small_run, output_dir):
     # Load all the data:
     print("Loading SPAD data from {}".format(spad_file))
@@ -101,7 +104,7 @@ def run(dataset_type,
             #                                             global_min_depth=np.min(depth_data),
             #                                             n_std=1. if use_poisson else 0.01)
             # Rescale SPAD_data
-            spad_rescaled = rescale_bins(spad, min_depth, max_depth, sid_obj)
+            # spad_rescaled = rescale_bins(spad, min_depth, max_depth, sid_obj)
             weights = np.ones_like(depth_data[i, 0, ...])
             if use_intensity:
                 weights = intensity_data[i, 0, ...]
@@ -112,11 +115,23 @@ def run(dataset_type,
                 #                                            sid_obj.sid_bin_values[:-2]**2,
[…]

### 2019-08-09 nyuv2/weighted_histogram_matching/matlab/denoise_spad.m

@@ -1,0 +1,24 @@
+clear all; close all;
+files = {"test_int_True_fall_True_dc_100000.0_jit_False_poiss_True_spad.mat", ...
+         "test_int_True_fall_True_dc_20000.0_jit_False_poiss_True_spad.mat", ...
+         "test_int_True_fall_True_dc_10000.0_jit_False_poiss_True_spad.mat"};
+
+for i=1:length(files)
+    file = files{i};
+    data = load(file);
+    spad = double(data.data);
+    spad_denoised = wdenoise(spad', 10, 'DenoisingMethod', 'BlockJS')';
+    newFile = join([extractBefore(files{i}, ".mat"), "_denoised.mat"],"");
+    save(newFile, 'spad_denoised')
+end
+
+% Diagnostic
+figure;
+bar(spad(1,1:100)),set(gca, 'yscale', 'log');
+figure;
+bar(spad_denoised(1,1:100)),set(gca, 'yscale', 'log');
+
+figure;
+bar(spad(1,250:350)),set(gca, 'yscale', 'log');
+figure;
+bar(spad_denoised(1, 250:350)),set(gca, 'yscale', 'log');

### 2019-08-14 paper/spad_single/sections/simulation.tex
Median matching and gt hist matching, plus table draft 1.

@@
 \begin{center}
-\begin{tabular}{lccc|ccc}
-  \toprule
-    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
-  \midrule
-  DORN (cite)&0.846&0.954&0.983&0.501&0.120&0.053 \\
-DenseNet(cite))&0.847&0.973&0.994&0.461&0.123&0.054 \\
-  \midrule
-  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-  DORN (Wass) & 0.847 & 0.953 & 0.983 & 0.499 & 0.117 & 0.053 \\
-  DORN (Histogram Matching) & 0.902 & 0.973 & 0.991 & 0.424 & 0.099 & 0.042 \\
-  DenseNet (rescaled) &0.888 & 0.978&0.995&0.409&0.106&0.045 \\
-  DenseNet (Wass) & - & - & - & - & - & - \\ 
-  DenseNet (Histogram Matching) &\textbf{0.930} &\textbf{0.984}&\textbf{0.995}&\textbf{0.338}&\textbf{0.080}&\textbf{0.034}\\
-  \midrule
-  DORN (Median SPAD Rescaling) & - & - & - & - & - & - \\
-  DORN + Wasserstein (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
-  DenseDepth (Median SPAD Rescaling) & - & - & - & - & - & - \\
-  DenseDepth + Wasserstein (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
-  \midrule
-  \bottomrule
-\end{tabular} 
+\input{sections/figures/sim_table.tex}
 \end{center}
-\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
 \end{table*}
-
 \begin{figure}

### 2019-08-14 paper/spad_single/sections/figures/refresh_tables.sh
Median matching and gt hist matching, plus table draft 1.

@@ -1,0 +1,1 @@
+rsync -r markn1@ares:~/spad_single/nyuv2/weighted_histogram_matching/figures/sim_table.tex ~/Documents/Stanford/ares/spad_single/paper/spad_single/sections/figures/sim_table.tex

### 2019-08-16 kitti/gt_hist_matching/evaluate_densedepth.py
Realsense + starting kitti

@@ -1,0 +1,85 @@
+#! /usr/bin/env python3
+
+import os
+import torch
+import pandas as pd
+import numpy as np
+from sacred import Experiment
+from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+from histogram_matching import hist_match
+
+from models.loss import get_depth_metrics
+
+ex = Experiment("densedepth_gt_hist_matching", ingredients=[nyuv2_labeled_ingredient])
+
+
+@ex.config
+def cfg(data_config):
+    dataset_type = "test"
+    entry = None
+    save_outputs = True
+    seed = 95290421
+    small_run = 0
+    input_file = os.path.join("data", "densedepth_{}_outputs.npy".format(dataset_type))
+
+    output_dir = "results"
+
+
+
+@ex.automain
+def run(dataset_type,
+        entry,
+        save_outputs,
+        small_run,
+        input_file,
+        output_dir):
+    dataset = load_data(channels_first=False, dataset_type=dataset_type)
+    cnn_data = np.load(input_file)
+
+    if entry is None:
+        metric_list = ["delta1", "delta2", "delta3", "rel_abs_diff", "rmse", "mse", "log10", "weight"]
+        metrics = np.zeros((len(dataset) if not small_run else small_run, len(metric_list)))
+        entry_list = []
+        outputs = []
+        for i in range(len(dataset)):
+            if small_run and i == small_run:
+                break
+            print("Running {}[{}]".format(dataset_type, i))
+            entry_list.append(i)
+            init = cnn_data[i, ...]
+            gt = dataset[i]["depth_cropped"]
+
+            pred = hist_match(init, gt.cpu().numpy())
+
+            pred_metrics = get_depth_metrics(torch.from_numpy(pred).float(),
+                                             gt,
+                                             torch.ones_like(gt))
+            for j, metric_name in enumerate(metric_list[:-1]):
+                metrics[i, j] = pred_metrics[metric_name]
+
+            metrics[i, -1] = torch.numel(gt)
+            # Option to save outputs:
+            if save_outputs:
+                outputs.append(pred)
+
+        if save_outputs:
+            np.save(os.path.join(output_dir, "densedepth_gt_hist_{}_outputs.npy".format(dataset_type)),
+                    np.concatenate(outputs, axis=0))
+
+        # Save metrics using pandas
[…]

### 2019-08-16 kitti/gt_hist_matching/evaluate_dorn.py

@@ -1,0 +1,85 @@
+#! /usr/bin/env python3
+
+import os
+import torch
+import pandas as pd
+import numpy as np
+from sacred import Experiment
+from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+from histogram_matching import hist_match
+
+from models.loss import get_depth_metrics
+
+ex = Experiment("dorn_gt_hist_matching", ingredients=[nyuv2_labeled_ingredient])
+
+
+@ex.config
+def cfg(data_config):
+    dataset_type = "test"
+    entry = None
+    save_outputs = True
+    seed = 95290421
+    small_run = 0
+    input_file = os.path.join("data", "dorn_{}_outputs.npy".format(dataset_type))
+
+    output_dir = "results"
+
+
+
+@ex.automain
+def run(dataset_type,
+        entry,
+        save_outputs,
+        small_run,
+        input_file,
+        output_dir):
+    dataset = load_data(channels_first=False, dataset_type=dataset_type)
+    cnn_data = np.load(input_file)
+
+    if entry is None:
+        metric_list = ["delta1", "delta2", "delta3", "rel_abs_diff", "rmse", "mse", "log10", "weight"]
+        metrics = np.zeros((len(dataset) if not small_run else small_run, len(metric_list)))
+        entry_list = []
+        outputs = []
+        for i in range(len(dataset)):
+            if small_run and i == small_run:
+                break
+            print("Running {}[{}]".format(dataset_type, i))
+            entry_list.append(i)
+            init = cnn_data[i, ...]
+            gt = dataset[i]["depth_cropped"]
+
+            pred = hist_match(init, gt.cpu().numpy())
+
+            pred_metrics = get_depth_metrics(torch.from_numpy(pred).float(),
+                                             gt,
+                                             torch.ones_like(gt))
+            for j, metric_name in enumerate(metric_list[:-1]):
+                metrics[i, j] = pred_metrics[metric_name]
+
+            metrics[i, -1] = torch.numel(gt)
+            # Option to save outputs:
+            if save_outputs:
+                outputs.append(pred)
+
+        if save_outputs:
+            np.save(os.path.join(output_dir, "dorn_gt_hist_{}_outputs.npy".format(dataset_type)),
+                    np.concatenate(outputs, axis=0))
+
+        # Save metrics using pandas
[…]

### 2019-08-16 paper/spad_single/sections/introduction.tex
Realsense + starting kitti

@@
-contributions
 %
+\subsection{Context}
+Estimating depth from images is an important imaging problem, as dense depth
+maps are useful precursors for high-level scene understanding tasks like
+segmentation and pose estimation (cite cite cite) and mid-level perception (of
+which depth estimation is an important part) has been shown to be very useful
+for e.g. training robots to navigate their environments. While traditional approaches to depth
+estimation use multiple cameras or structure-from-motion, convolutional neural
+networks have also demonstrated reasonable performance on the so-called
+monocular depth estimation task, where the network is trained to produce a dense
+depth map given only a single RGB image of the scene.
+\subsection{Problem Statement}
+While deep monocular depth estimators have demonstrated strong performance (cite
+cite) and even some generalizability across scene types, the task they are solving is fundamentally
+underconstrained due to \textit{inherent scale ambiguity}, i.e. the unresolvable
+tradeoff between size and distance in monocular images. This ambiguity could be
+resolved by adding an additional camera and calculating a disparity map, but
+this method still fails on textureless regions and areas with lots of
+occlusions. Other approaches use FMCW or time-of-flight LiDAR technologies,
+but these approaches are currently expensive and bulky. 
+\subsection{Proposed approach}
+In this paper, we show that by augmenting the RGB image with a histogram of
+depth information, we can achieve substantially improved performance
+(and generalizability) over state-of-the-art monocular depth
+estimators. By performing an exact, weighted histogram matching on the output
+depth map of the depth estimator, we can match the depth histogram of the scene
+to the depth histogram of our estimate. Such a histogram can be captured
+relatively inexpensively using only a single pixel single-photon avalanche diode
+(SPAD) and pulsed laser illumination diffused over the field of view.
+\subsection{Impact}
+Our method is a lightweight postprocessing step that substantially improves
+the quality of depth maps produced by monocular depth estimators. It can be
+applied to any method to improve the accuracy instantly. (Our method also
+helps neural-network-based methods generalize across scene types easily.)
+\subsection{Limitations}
+Our method is not without limitations, however. It still requires a laser and
+single-pixel detector, and as such, is sensitive to ambient photons. Our method,
+which is a fundamentally a variant of histogram matching, is, like histogram
+matching, unable to transpose the values of pixels (i.e. if pixel $a$ is farther
+than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
+In other words, our method is not able to resolve ordinal depth errors
+(errors where an object is wrongly placed closer or farther
+relative to another object). Finally, our method is non-differentiable, and is
+therefore unsuitable for end-to-end optimization of multi-part networks.
+
 \begin{itemize}
@@
     being fast and easy to implement.
+  \item (Potentially) We investigate the ability of our method to 
+    help generalization of monocular depth estimators across scene types. 
+    We (hopefully) demonstrate that our method allows monocular depth
+    estimators to perform well even on completely different scene types.
 	\item We build a hardware prototype and evaluate the efficacy of our

### 2019-08-16 kitti/gt_hist_matching/DenseDepthModel.py

@@ -1,0 +1,63 @@
+import torch
+import numpy as np
+
+import os
+
+from models.loss import get_depth_metrics
+
+from DenseDepth.model import create_model
+from DenseDepth.utils import scale_up, predict
+
+
+class DenseDepth:
+    """
+    DenseDepth Network
+
+    https://github.com/ialhashim/DenseDepth
+
+    Meant to be run as a part of a larger network.
+
+    Only works in eval mode.
+
+    Thin wrapper around the Keras implementation.
+    """
+    def __init__(self, existing=os.path.join("models", "nyu.h5"), crop=(20, 460,  24, 616)):
+        """
+
+        :param existing:
+        :param crop: default crop. Only used if no crop is provided to the predict function.
+        """
+        self.model = create_model(existing)
+        self.crop = np.array(crop)
+
+    def forward(self, rgb):
+        """
+        Works in numpy.
+        """
+        pred = scale_up(2, predict(self.model, rgb/255,
+                                   minDepth=10, maxDepth=1000, batch_size=1)[:,:,:,0]) * 10.0
+        pred_flip = scale_up(2, predict(self.model, rgb[...,::-1,:]/255,
+                                        minDepth=10, maxDepth=1000, batch_size=1)[:,:,:,0]) * 10.0
+        pred_final = 0.5*pred + 0.5*pred_flip[:,:,::-1]
+        return pred_final
+
+    def predict(self, rgb):
+        return self.forward(rgb)
+
+    def evaluate(self, rgb, gt, mask):
+        """
+        Takes torch tensors, but returns a torch tensor prediction.
+        :param rgb: N x H x W x C in RGB order (not BGR)
+        :param crop: length-4 array with crop pixel coordinates
+        :param gt: N x H x W x C
+        :return: torch tensor prediction, metrics dict, and number of valid pixels
+        """
+        pred = self.predict(rgb.cpu().numpy())
+        pred = pred[:, self.crop[0]:self.crop[1], self.crop[2]:self.crop[3]]
+        pred = torch.from_numpy(pred).cpu().unsqueeze(0).float()
+        metrics = self.get_metrics(pred, gt.cpu(), mask.cpu())
+        return pred, metrics, torch.sum(mask).item()
+
+    @staticmethod
+    def get_metrics(pred, gt, mask):
+        return get_depth_metrics(pred, gt, mask)

### 2019-08-21 paper/spad_single/sections/simulation.tex
Inpainting realsense data and working on the paper figures.

@@
 \newpage
-\begin{table*}
-\begin{center}
-\begin{tabular}{lccc|ccc}
-  \toprule
-    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
-  \midrule
-Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
-Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
-DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
-  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
-Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
-  \midrule
-  Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
-  Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
-  Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
-  \bottomrule
-\end{tabular} 
-\end{center}
-\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
-\end{table*}
+% \begin{table*}
+% \begin{center}
+% \begin{tabular}{lccc|ccc}
+%   \toprule
+%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
+%   \midrule
+% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
+% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
+% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
+%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
+% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
+% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
+%   \midrule
+%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
+%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
+%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
+%   \bottomrule
+% \end{tabular} 
+% \end{center}
+% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
+% \end{table*}
 %%%
@@
 \input{sections/figures/sim_table.tex}
+\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
+  that metric, while underline indicates second best.}
 \end{center}
 \end{table*}
-\begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
-  \caption{\textbf{Comparing our results with other methods}}
-\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_18_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_21_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_25_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_285_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_42_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_52_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_53_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_103_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_224_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_226_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_352_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_362_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_379_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_107_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_187_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_140_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_244_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_527_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_219_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_329_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_346_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_616_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_390_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_412_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_420_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_428_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_457_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_477_comparison.png}
+  \caption{Results on DenseDepth}
+\end{figure*}
+%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_499_comparison.png}
+%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_258_comparison.png}
+%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_341_comparison.png}
+
+% Densedepth:
+% - Office: 18, 21
+% - Bathroom: 25, 194, 285
+% - Bookstore: 42
+% - Kitchen: 52, 53, 103, 224, 226, 352, 362, 379
+% - Office: 107, 187
+% - Living Room: 140, 244, 527, 529
+% - Dining Room: 219, 329, 346, 616
+% - Bedroom: 390, 412, 420, 428, 457*, 468*, 477, 499
+% Failure Cases: 258, 338(?), 341, 537 649 (minor)
+% 
+% DORN:
+% - Office: 8, 14, 15, 23, 26
+% - Living room: 63, 67, 140, 170, 522, 548, 569, 585, 633
+% - Office: 105, 220, 252, 259* (interesting)
+% - Kitchen: 178
+% - Dining Room: 219
+% - Bathroom: 280, 293, 313
+% - Bedroom: 413, 477, 502
+% 
+% Failure Cases: 96, 266(?)
+
+% \begin{figure}
+%   \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
+%   \caption{\textbf{Comparing our results with other methods}}
+% \end{figure}

### 2019-08-21 nyuv2/realsense/capture.py

@@ -1,109 +1,0 @@
-#!/usr/bin/env python3
-# This script requires the pyrealsense2 wrapper for librealsense.
-# For installation instructions, see:
-# Windows/Linux:
-# https://github.com/IntelRealSense/librealsense
-# Mac:
-# https://github.com/GitwellAnyohub/Real_Sensible_Moseq/blob/master/bash_and_install/install_realsense_sdk_mac_os.sh
-
-import sys, os
-sys.path.append("/usr/local/lib")   # Necessary for pyrealsense2 import for my install on mac
-import pyrealsense2 as rs
-import numpy as np
-import cv2
-from argparse import ArgumentParser
-
-parser = ArgumentParser(description="Capturing data from the realsense")
-parser.add_argument("--output-dir", default="testing", help="The directory to save the captured images to.")
-args = parser.parse_args()
-
-def safe_makedir(path):
-    """Makes a directory, or returns if the directory
-    already exists.
-
-    Taken from:
-    https://stackoverflow.com/questions/273192/how-can-i-safely-create-a-nested-directory-in-python
-    """
-    try:
-        os.makedirs(path)
-    except OSError:
-        if not os.path.isdir(path):
-            raise
-
-safe_makedir(args.output_dir)
-
-# Create a pipeline
-pipeline = rs.pipeline()
-
-# Create a config and configure the pipeline to stream
-#  different resolutions of color and depth streams
-config = rs.config()
-# config.enable_stream(rs.stream.depth, 640, 360, rs.format.z16, 30)
-config.enable_stream(rs.stream.depth, 640, 480, rs.format.z16, 30)
-config.enable_stream(rs.stream.color, 640, 480, rs.format.bgr8, 30)
-
-# Start streaming
-profile = pipeline.start(config)
-
-# Getting the depth sensor's depth scale (see rs-align example for explanation)
-depth_sensor = profile.get_device().first_depth_sensor()
-depth_scale = depth_sensor.get_depth_scale()
-print("Depth Scale is: ", depth_scale)
-
-# We will be removing the background of objects more than
-#  clipping_distance_in_meters meters away
-clipping_distance_in_meters = 10.  # 10 meters
-clipping_distance = clipping_distance_in_meters / depth_scale
-
-# Create an align object
-# rs.align allows us to perform alignment of depth frames to others frames
-# The "align_to" is the stream type to which we plan to align depth frames.
-align_to = rs.stream.color
-align = rs.align(align_to)
-
-# Streaming loop
[…]

### 2019-08-21 nyuv2/realsense/matlab/nyu_utils/ConvertRGBDParsave.m

@@ -1,8 +1,0 @@
-function ConvertRGBDParsave(albedo_out, dist_out, intensity_out, dist_out_hr, albedo, dist, intensity, dist_hr)
-    save(albedo_out, 'albedo');
-    save(dist_out, 'dist');
-    save(intensity_out, 'intensity');
-    save(dist_out_hr, 'dist_hr');    
-
-end
-

### 2019-08-27 paper/spad_single/sections/method.tex
Updated paper, realsense simulation complete, ordnet created.

--- 2018-11-16 paper/spad_single/sections/method.tex
@@
-\subsection{Monocular Depth Estimation}
+In this section, we describe the measurement model for a single-pixel
+time-of-flight lidar sensor under diffuse, pulsed laser illumination. 
+\subsection{Measurement Model}
+Consider a laser which emits a pulse at time $t = 0$ with time-varying intensity
+$g(t)$ uniformly illuminating some 3D scene. We parameterize the geometry of the
+scene as a height map $z(x, y)$.
+Neglecting albedo and falloff effects, an ideal detector counting photon events
+from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record
 
-\subsection{Global Depth Hints}
+\begin{equation}
+  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt \label{single_loc_spad} 
+\end{equation}
 
+where $c$ is the speed of light, and $f$ is a function that models the temporal uncertainty in the
+detector. Single-photon avalanche diodes (SPADs) are highly sensitive
+photodetectors which are able to record single photon events with high temporal
+precision \cite{Stuff}. Since the event corresponding to the detection of a
+photon can be described with a Bernoulli random variable,
+the total number of accumulated photons in this time interval follows a Poisson
+distribution according to
+
+\begin{equation}
+  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+\end{equation}
+
+where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
+photon counts due to the reflectance $r(x,y)$ of the scene and due to the
+inverse square falloff $1/z(x,y)^2$.
+In addition, $\eta$ is the detection probability of a photon
+triggering a SPAD event, and $b = \eta a + d$ is the average number of background detections resulting
+from ambient photons $a$
+and erroneous ``dark count'' events $d$ resulting from noise within the SPAD.
+% \newpage
+% \begin{table*}[htbp]
+%   \begin{center}
+  %   \begin{tabularx}{\linewidth}{*{2}{X}}
+  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rgb.png} &
+  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rawdepth.png} \\
+  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/depth_hist.png} &
+  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/spad_hist.png} \\
+  %   \end{tabularx}
+  % \end{center}
+  % \caption{Sample Image. Top Left is the RGB image. Top Right is ground truth
+  %   depth. Bottom Left is Raw ground truth depth histogram. Bottom Right is
+  %   simulated SPAD measurements. Notice how closer depths are magnified and far
+  %   depths are attenuated.}
+% \end{table*}
+
+\subsection{Monocular depth estimation with global depth hints}
+Given a single RGB image $I(x,y)$ and a vector of photon arrivals $h[n]$
+described by equation \ref{global_hints}, we seek to
+reconstruct the ground truth depth map $z(x,y)$.
+Our method has two parts. First, we \textbf{initialize} our estimate of the depth map from the single RGB
+image via a monocular depth estimator described below. Second, we \textbf{refine} this depth map using
+the captured measurements $h[n]$ via exact histogram matching.
+
+\paragraph{Initialization}
+The first step in our method is to produce an initial estimate of ground truth
+depth. Convolutional Neural Networks have been shown to produce accurate, if poorly-scaled, estimates of depth
+from only a single image. We therefore choose to initialize our depth map
+estimate $\hat z^{(0)}(x,y)$ using
+a CNN. However, any depth estimator reliant on only a single
+view may be used for this step. Furthermore, in the larger context of our
+algorithm, it is more important that the network predict the correct ordinal
+relationships between pixels - that is, to predict the correct relative ordering
+of pixels $a$ and $b$, rather than to get all pixels exactly correct.
+
+\paragraph{Exact Histogram Matching}
+\begin{figure}
+  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.jpeg}
+  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
+  per-pixel depth estimate. Then we perform exact histogram matching using
+  intensity-weighted pixel values on the corrected SPAD data.}
+\end{figure}
+An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
+pixels of the image whose value lies in the range $[b_i, b_i+1)$.
+Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
+$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
+h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
+The full details of the exact histogram matching algorithm can be found in
+\cite{Morovic2002}.
+
+However, for our purposes, we need to modify our algorithm to accommodate
+differing per-pixel weights. We can account for squared depth falloff
+
+\paragraph{SPAD Denoising}
 \begin{itemize}
-	\item image formation model	
-	\item training details
-	\item simulations and comparison: qualitative and quantitative
+  \item Talk about histogram matching in the ideal case, jump straight to intensity 
+  \item Talk about histogram matching in our case, and how it approaches the
+    ideal case. Discuss the following corrections 
+    \begin{itemize}
+      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
+        then the ambient estimate to get rid of the noise floor.
+      \item Falloff
     \end{itemize}
+  \item Talk about how the histogram matching works with intensity
+    considerations applied, briefly.
+  \item We don't address jitter or poisson noise.
+\end{itemize}
+\begin{equation}
+  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+\end{equation}
+Given a SPAD with histogram $h$ according to the above equation, we first
+process the SPAD to remove the effects of some of the terms. First, we 
+\subsection{Implementation Details}
+For the Monocular Depth Estimator, we use pretrained versions of the
+the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
+The exact histogram matching method is as described in \cite{}.

### 2019-08-27 paper/spad_single/sections/related.tex
Paper update
Updated paper, realsense simulation complete, ordnet created.

@@
-\paragraph{Depth Imaging}
-
-\begin{itemize}
-	\item stereo and multiview
-	\item structured illumination and random patterns (kinect, etc.), active stereo
-	\item time of flight (continuous wave and pulsed)
-	\item what we do: like pulsed but much simpler setup; no scanning, no spad array, ...
-\end{itemize}
+% \paragraph{Depth Imaging}
+% Include in intro, don't necessarily need it here.
+% Conventional approaches to estimating depth from images include stereo-based
+% approaches 
+% \begin{itemize}
+% 	\item stereo and multiview
+% 	\item structured illumination and random patterns (kinect, etc.), active stereo
+% 	\item time of flight (continuous wave and pulsed)
+% 	\item what we do: like pulsed but much simpler setup; no scanning, no spad array, ...
+% \end{itemize}
 
@@
 \paragraph{Monocular Depth Estimation}
+Previous non-deep approaches used Markov Random Fields \cite{Saxena2006},
+geometric approaches \cite{Hoiem2005}, and non-parametric, SIFT-based methods
+\cite{Karsch2014}.
+More recently, deep neural networks have been applied to the problem of estimating depth from a
+single image. Eigen et. al. \cite{Eigen2014} use a multi-scale neural network to
+predict depth at multiple scales. Godard et. al. \cite{Godard2017} use an
+unsupervised approach (i.e. that does not require ground truth depth) that
+trains a network using stereo pairs to produce disparity maps from
+single images, which can then be used to recover the depth. Fu et. al.
+\cite{Fu2018} combined a logarithmic depth discretization scheme with a novel
+ordinal regression approach. Various experiments using different types of
+encoder networks (e.g. ResNet, DenseNet) \cite{Laina2016} \cite{Alhashim2018}
+have also been employed with some success, as have approaches mixing deep
+learning with conditional random fields \cite{Xu2017}, and attention-based
+approaches \cite{Xu2018} \cite{Hao2018}.
 
-\begin{itemize}
-	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
-	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
-\end{itemize}
+Despite achieving remarkable success on the monocular depth estimation task, none of these methods are able to
+resolve inherent scale ambiguity in a principled manner (being monocular in nature). By combining a monocular
+depth estimator with a depth histogram, our method is able to do so.
+
+% \begin{itemize}
+% 	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
+% 	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
+% \end{itemize}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Deep Sensor Fusion}
+\paragraph{Depth Imaging and Sensor Fusion with SPADs}
+Previous work (see \cite{Horaud2016} for a survey) has been able to use
+single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in
+tandem with various scanning or DMD devices to capture 3D volumes of photon arrivals
+that can be used to reconstruct depth. Lindell et. al. \cite{Lindell2018} use a
+LinoSPAD and epipolar scanline and fuse the SPAD data with an RGB image to
+produce high-quality depth.  Our approach uses a single pixel SPAD but
+does not require any scanning or DMD mechanism.
 
-global hints for super-resolution, colorization, depth estimation 
+A parallel approach called 3D flash LiDAR uses a laser with an optical diffuser
+as the illumination source and a 2D array of SPADs to capture the 3D volume
+\cite{Stoppa2007, Niclass2005}. Such arrays are capable of reconstructing high
+quality depth but remain relatively low resolution. Other arrays are able to
+achieve higher resolution, but suffer from low fill factor \cite{Veerappan2011} or
+sacrifice per-pixel TDC \cite{Zhang2018}.
+
+Our approach uses flash LiDAR but requires only a single pixel 
+sensor.
+(Still need to flesh out this section more with some higher resolution SPAD arrays)
+% \begin{itemize}
+%   \item Scanned single-pixel and 1D arrays, but scanning is hard
+%   \item high resolution arrays -> challenging to do TDC
+%   \item Individual (non-scanning) SPADs already exist in e.g. iPhoneX, but use
+%     is limited to proximity sensors.
+%   \item What we do: No array (easier), no scanning (easier), much cheaper,
+%     combined with RGB camera to do high-resolution depth imaging, a more complex
+%     task.
+% \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \paragraph{Deep Sensor Fusion}
+% Maybe mention in previous section? 
+% global hints for super-resolution, colorization, depth estimation 
 %
-\begin{itemize}
-	\item colorization
-	\item david's 2018 paper for depth estimation and denoising (see david's 2019 sig paper for related work)
-	\item what we do: slightly different application
-\end{itemize}
+% \begin{itemize}
+	% \item colorization
+	% \item david's 2018 paper for depth estimation and denoising (see david's 2019 sig paper for related work)
+	% \item what we do: slightly different application
+% \end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\paragraph{Histogram Matching and Global Hints}
+Histogram matching or histogram specification is a well-known image processing
+technique \cite{Gonzalez2008} for adjusting an image so that it's histogram
+matches some pre-specified histogram (often derived from another image).
+Nikolova et. al. \cite{Nikolova2013} use optimization to recover a strict
+ordering of the image pixels that allows an exact histogram match to be
+obtained. Morovic et. al \cite{Morovic2002} provide a simple and concise method
+that also achieves an exact histogram match while being very fast.
+In the image reconstruction space, Swoboda and Schnörr \cite{Swoboda2013} use a
+histogram to form an image prior based on the Wasserstein distance for image
+denoising and inpainting. Rother et. al. \cite{Rother2006} use a histogram prior
+to create an energy function that penalizes foreground segmentations with
+dissimilar histograms. In a slightly different vein, Zhang et. al.
+\cite{Zhang2017} train a neural network to produce realistically colorized
+images given only a black-and-white image and a histogram of global color information.
+
+Our method is essentially a modified form of the algorithm in
+\cite{Morovic2002}, modified for our particular use case. Also worth noting is
+the fact that most algorithms compute histograms from existing images, whereas
+our method mesaures the depth histogram indirectly using photon arrivals.
+%
+% \begin{itemize}
+%   \item Exact histogram matching paper used in this work
+%   \item Wasserstein-based optimization techniques for
+%     histogram-based regularization
+% \end{itemize}

### 2019-08-27 nyuv2/ordnet/OrdNet.py

@@ -1,0 +1,99 @@
+import torch
+import torch.nn as nn
+import torch.nn.functional as F
+import numpy as np
+from collections import OrderedDict
+from torchvision.models.densenet import densenet169
+
+class UpBlock(nn.Module):
+    def __init__(self, in_channels, out_channels):
+        super(UpBlock, self).__init__()
+
+        self.upsample = nn.Upsample(scale_factor=2, mode="bilinear", align_corners=True)
+        self.convA = nn.Conv2d(in_channels=in_channels, out_channels=out_channels, kernel_size=3, padding=1, stride=1)
+        self.convB = nn.Conv2d(in_channels=out_channels, out_channels=out_channels, kernel_size=3, padding=1, stride=1)
+
+    def forward(self, x, concat_with):
+        x = self.upsample(x)
+        x = torch.cat((x, concat_with), dim=1)
+        x = self.convA(x)
+        x = F.leaky_relu(x, negative_slope=0.2, inplace=True)
+        x = self.convB(x)
+        x = F.leaky_relu(x, negative_slope=0.2, inplace=True)
+        return x
+        def upproject(tensor, filters, name, concat_with):
+            up_i = BilinearUpSampling2D((2, 2), name=name + '_upsampling2d')(tensor)
+            up_i = Concatenate(name=name + '_concat')(
+                [up_i, base_model.get_layer(concat_with).output])  # Skip connection
+            up_i = Conv2D(filters=filters, kernel_size=3, strides=1, padding='same', name=name + '_convA')(up_i)
+            up_i = LeakyReLU(alpha=0.2)(up_i)
+            up_i = Conv2D(filters=filters, kernel_size=3, strides=1, padding='same', name=name + '_convB')(up_i)
+            up_i = LeakyReLU(alpha=0.2)(up_i)
+            return up_i
+
+        # Decoder Layers
+        decoder = Conv2D(filters=decode_filters, kernel_size=1, padding='same', input_shape=base_model_output_shape,
+                         name='conv2')(base_model.output)
+
+        decoder = upproject(decoder, int(decode_filters / 2), 'up1', concat_with='pool3_pool')
+        decoder = upproject(decoder, int(decode_filters / 4), 'up2', concat_with='pool2_pool')
+        decoder = upproject(decoder, int(decode_filters / 8), 'up3', concat_with='pool1')
[…]

### 2019-08-27 paper/spad_single/sections/introduction.tex
Updated paper, realsense simulation complete, ordnet created.

--- 2019-08-08 paper/spad_single/sections/introduction.tex
@@
-contributions
-%
+\subsection{Introduction}
+Estimating depth from images is an important open problem with applications
+to robotics, autonomous driving, and medical imaging. Dense depth maps are
+useful precursors to higher-level scene understanding tasks such as pose
+estimation and object detection.
+
+However, traditional approaches to depth estimation, such as stereo, suffer from lower performance
+when confronted with small angles or faraway objects.
+More exotic approaches use FMCW or time-of-flight LiDAR technologies,
+but these approaches are currently expensive and bulky.
+
+The most promising solution to these issues uses deep learning and 
+convolutional neural networks to perform \textit{monocular depth estimation},
+estimating dense depth maps from single RGB images. 
+However, this problem is underconstrained due to \textit{inherent scale ambiguity}, the unresolvable
+tradeoff between size and distance in single images. In practice, this issue commonly
+manifests itself in many monocular depth networks, and indeed, 
+Wonka et. al. (cite) showed that if the method has oracle access to the ground truth
+median depth, then correcting the output of the CNN to match this median
+depth produces better depth maps both qualitatively and quantitatively.
+
+In this paper, we go further and show that by augmenting the RGB image with a histogram of
+global image depths, we can achieve substantially improved performance
+(and generalizability) over state-of-the-art monocular depth
+estimators. By performing an exact, weighted histogram matching on the output
+depth map of the depth estimator, we can match the depth histogram of the scene
+to the depth histogram of our estimate. This histogram matching is described in
+(cite) and is flexible enough to accommodate different pixel reflectances in the
+RGB image. Finally, this histogram can be captured
+relatively inexpensively using only a single pixel single-photon avalanche diode
+(SPAD) and pulsed laser illumination diffused over the field of view, 
+representing a significant improvement in cost and simplicity over multi-pixel LiDAR
+arrays with expensive scanning mechanisms. It is
+worth noting that SPADs of this type have already made their way into existing
+smartphones, such as the iPhone X, and will likely play a role in future mobile sensing platforms as well.
+
+Our method is not without limitations. It still requires a laser and
+single-pixel LiDAR detector, and as such, is sensitive to ambient photons. Being 
+a variant of histogram matching, our method is unable to transpose the
+values of pixels (i.e. if pixel $a$ is farther
+than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
+In other words, our method is not able to resolve ordinal depth errors
+(errors where an object is wrongly placed closer or farther
+relative to another object). Finally, our method is non-differentiable, and is
+therefore unsuitable for end-to-end optimization of multi-part networks.
+
 \begin{itemize}
-	\item We introduce the idea of augmenting an RGB camera with a single-pixel
-    SPAD to address scale ambiguity error in monocular depth estimators.	
+	\item We introduce the idea of augmenting an RGB camera with a global depth 
+    histogram to address scale ambiguity error in monocular depth estimators.	
   \item We analyze our approach on indoor scenes using the NYU Depth v2 dataset.
@@
 	\item We build a hardware prototype and evaluate the efficacy of our
-    approach on real-world data. 
+    approach on real-world data, assessing both the the quality and the ability of our method
+    to help generalization of monocular depth estimators across scene types. 
 \end{itemize}

### 2019-08-27 paper/spad_single/sections/simulation.tex
Updated paper, realsense simulation complete, ordnet created.

@@
 RGB-D data captured using a Microsoft Kinect. We used a version of DORN
-pretrained according to \cite{Fu. et al} as our CNN.
+pretrained according to \cite{Fu2018} as our CNN.
 \newpage
@@
 \caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
-  that metric, while underline indicates second best.}
+  that metric, while underline indicates second best. The proposed scheme
+  outperforms DenseDepth and DORN on all metrics, and even outperforms the
+  median rescaling scheme, which has access to the true median depth value.}
 \end{center}
 \end{table*}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_258_comparison.png}
+  \caption{Selected Results on DenseDepth. First two examples demonstrate
+    capability of proposed method to correct initial scaling/translation errors.
+    Last example shows potential pitfall when ordinal depth is predicted incorrectly.}
+\end{figure*}
 
@@
 %   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_341_comparison.png}
-
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_8_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_14_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_15_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_23_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_26_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_63_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_67_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_140_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_170_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_522_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_548_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_569_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_585_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_633_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_105_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_220_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_252_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_259_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_178_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_219_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_280_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_293_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_313_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_413_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_477_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_502_comparison.png}
+%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
+%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
+  \caption{Results on DORN}
+\end{figure*}
 % Densedepth:

### 2019-08-27 nyuv2/realsense/simulate_spad.py

@@ -1,0 +1,87 @@
+#! /usr/bin/env python3
+import numpy as np
+import os
+import torch
+from torch.utils.data._utils.collate import default_collate
+import cvxpy as cp
+from scipy.signal import fftconvolve
+from sacred import Experiment
+from png_dataset import png_ingredient, load_data
+from spad_utils import simulate_spad
+
+spad_ingredient = Experiment("spad_config", ingredients=[png_ingredient])
+
+@spad_ingredient.config
+def cfg(data_config):
+    spad_bins = 1024                # Number of bins to capture
+    photon_count = 1e6              # Number of real photons that we get
+    dc_count = 0.1*photon_count     # Simulates ambient + dark count (additional to photon_count
+    fwhm_ps = 70.                   # Full-width-at-half-maximum of (Gaussian) SPAD jitter, in picoseconds
+
+    use_poisson = True
+    use_intensity = True
+    use_squared_falloff = True
+    use_jitter = True
+
+    min_depth = data_config["min_depth"]
+    max_depth = data_config["max_depth"]
+
+    dataset_type = "realsense"
+
+    # Output directory
+    output_dir = "data"
+
+@spad_ingredient.capture
+def simulate_spad_passthrough(depth_truth, intensity, mask, min_depth, max_depth,
+                              spad_bins, photon_count, dc_count, fwhm_ps,
+                              use_poisson, use_intensity, use_squared_falloff,
+                              use_jitter):
+    return simulate_spad(depth_truth, intensity, mask, min_depth, max_depth,
+                  spad_bins, photon_count, dc_count, fwhm_ps,
+                  use_poisson, use_intensity, use_squared_falloff,
+                  use_jitter)
+
+def rgb2gray(img):
+    return 0.2989 * img[:, 0:1, ...] + 0.5870 * img[:, 1:2, ...] + 0.1140 * img[:, 2:3, ...]
+
+@spad_ingredient.automain
+def run(dataset_type,
+        output_dir,
+        use_intensity,
+        use_squared_falloff,
+        dc_count,
+        use_jitter,
+        use_poisson,
+        _config):  # The entire config dict for this experiment
+    print("dataset_type: {}".format(dataset_type))
+    dataset = load_data(channels_first=True)
+    all_spad_counts = []
+    all_intensities = []
+    for i in range(len(dataset)):
+        print("Simulating SPAD for entry {}".format(i))
+        data = default_collate([dataset[i]])
+
[…]

### 2019-08-27 nyuv2/realsense/weighted_histogram_matching.py

@@ -1,0 +1,125 @@
+# %load weighted_histogram_matching.py
+import numpy as np
+
+def find_movement(hist_from, hist_to):
+    """Gives the movements from hist_from (column sum)
+    to hist_to (row sum).
+
+    Based on Morovic et. al 2002 A fast, non-iterative, and exact histogram matching algorithm.
+
+    hist_from and hist_to should sum to the same value
+    """
+    movement = np.zeros((len(hist_from), len(hist_to)))
+    for row in range(len(hist_from)):
+        for col in range(len(hist_to)):
+            pixels_rem = hist_from[row] - np.sum(movement[row, :col])
+            pixels_req = hist_to[col] - np.sum(movement[:row, col])
+            # if np.minimum(pixels_rem, pixels_req) < 0:
+            #     print(row, col)
+            #     print(hist_from[row])
+            #     print(hist_to[col])
+            #     print(pixels_rem, pixels_req)
+            #     raise Exception()
+            movement[row, col] = np.clip(np.minimum(pixels_rem, pixels_req), a_min=0., a_max=None)
+    return movement
+
+
+def move_pixels(T, init_index, weights):
+    assert init_index.shape == weights.shape
+    pred_index = np.zeros_like(init_index)
+    cpfs = np.cumsum(T, axis=1)
+
+    
+    for row in range(init_index.shape[0]):
+        for col in range(init_index.shape[1]):
+            i = init_index[row, col]
+            cpf = cpfs[i]
+            p = np.random.uniform(0, cpf[-1])
+            for j in range(len(cpf)):
+                if cpf[j] >= p:
+                    pred_index[row, col] = j
+                    if T[i,j] > weights[row, col]:
+                        # Leave some small positive mass here so that future pixels don't clip to 0.
+                        T[i, j] = T[i, j] - weights[row, col]
+                    break
+    return pred_index
+
+
+def move_pixels_vectorized(T, init_index, weights):
+    assert init_index.shape == weights.shape
+    pred_index = np.zeros_like(init_index)
+    cpfs = np.cumsum(T, axis=1)  # Sum across columns
+    pixel_cpfs = cpfs[init_index, :]  # Per-pixel cpf, cpf goes along axis 2
[…]

### 2019-09-09 paper/spad_single/sections/method.tex
Analyzing captured results.

@@
-In this section, we describe the measurement model for a single-pixel
+In this section, we begin by outlining some core ideas of monocular depth
+estimation. We then describe the measurement model for a single-pixel
 time-of-flight lidar sensor under diffuse, pulsed laser illumination. 
+Finally, we explain our histogram matching procedure.
+\subsection{Monocular Depth Estimation}
+To acquire an initial depth estimate from our RGB image, we need a monocular
+depth estimator. In this paper, we investigate two networks, DORN \cite{Fu2018}
+and DenseDepth \cite{Alhashim2018}. We choose these for their high individual
+performance on the monocular depth estimation task on both NYU Depth v2 and
+KITTI. To clarify, however, for both networks, separate weights are learned for
+NYU Depth v2 and for the KITTI dataset, and no models are provided that have
+been trained on both datasets. We will use $f(\cdot)$ to refer to the neural network.
+
+We pass our RGB image $I$ through the network $f$ to obtain $z_{init}$, our
+initial depth estimate.
+Let us leave this for now and return to it after discussing our measurement
+model. 
 \subsection{Measurement Model}
 Consider a laser which emits a pulse at time $t = 0$ with time-varying intensity
-$g(t)$ uniformly illuminating some 3D scene. We parameterize the geometry of the
+$g(t)$ uniformly illuminating some scene. We parameterize the geometry of the
 scene as a height map $z(x, y)$.
-Neglecting albedo and falloff effects, an ideal detector counting photon events
+Neglecting albedo and falloff effects, as well as radial corrections, an ideal detector counting photon events
 from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record

### 2019-09-09 paper/spad_single/sections/simulation.tex
Analyzing captured results.

--- 2019-08-14 paper/spad_single/sections/simulation.tex
@@
 RGB-D data captured using a Microsoft Kinect. We used a version of DORN
-pretrained according to \cite{Fu. et al} as our CNN.
+pretrained according to \cite{Fu2018} as our CNN.
 \newpage
-\begin{table*}
-\begin{center}
-\begin{tabular}{lccc|ccc}
-  \toprule
-    & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
-  \midrule
-Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
-Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
-DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
-  DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
-Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
-  \midrule
-  Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
-  Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
-  Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
-  \bottomrule
-\end{tabular} 
-\end{center}
-\caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
-\end{table*}
+% \begin{table*}
+% \begin{center}
+% \begin{tabular}{lccc|ccc}
+%   \toprule
+%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
+%   \midrule
+% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
+% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
+% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
+%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
+% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
+% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
+%   \midrule
+%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
+%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
+%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
+%   \bottomrule
+% \end{tabular} 
+% \end{center}
+% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
+% \end{table*}
 %%%
@@
 \input{sections/figures/sim_table.tex}
+\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
+  that metric, while underline indicates second best. The proposed scheme
+  outperforms DenseDepth and DORN on all metrics, and even outperforms the
+  median rescaling scheme, which has access to the true median depth value.}
 \end{center}
 \end{table*}
-\begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
-  \caption{\textbf{Comparing our results with other methods}}
-\end{figure}
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
+  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_258_comparison.png}
+  \caption{Selected Results on DenseDepth. First two examples demonstrate
+    capability of proposed method to correct initial scaling/translation errors.
+    Last example shows potential pitfall when ordinal depth is predicted incorrectly.}
+\end{figure*}
+
+% \begin{figure}
+%   \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
+%   \caption{\textbf{Comparing our results with other methods}}
+% \end{figure}

### 2019-09-09 data/code_nyu/simulated_data/nyu_utils/depth_rel2depth_abs.m

@@ -9,7 +9,7 @@
 %
 % Returns:
 %   imgDepthAbs - 480x640 depth image whose values are in meters, rather
-%                 than the internal depth values used by the kinect.
+%                 than the internal depth values used by the captured.
 function imgDepthAbs = depth_rel2depth_abs(imgDepthOrig)
   assert(isa(imgDepthOrig, 'double'));
 

### 2019-09-09 data/code_nyu/simulated_data/nyu_utils/get_timestamp_from_filename.m

@@ -8,7 +8,7 @@
 %
 %
 % Args:
-%   filename - the path to the raw kinect output file.
+%   filename - the path to the raw captured output file.
 %
 % Returns:
 %   matlabTime - the matlab time which can be passed to datestr

### 2019-09-09 nyuv2/captured/capture_utils.py

@@ -1,0 +1,82 @@
+import h5py
+import numpy as np
+
+def loadmat_h5py(file):
+    output = {}
+    with h5py.File(file, 'r') as f:
+        for k, v in f.items():
+            output[k] = np.array(v)
+    return output
+
+
+def z_to_r_kinect(z):
+    fc = [1053.622, 1047.508]  # Focal length in pixels
+    yy, xx = np.meshgrid(range(z.shape[0]), range(z.shape[1]), indexing="ij")
+    x = (xx * z) / fc[0]
+    y = (yy * z) / fc[1]
+    r = np.sqrt(x**2 + y**2 + z**2)
+    return r
+
+
+def r_to_z_kinect(r):
+    fc = [1053.622, 1047.508]  # Focal length in pixels
+    yy, xx = np.meshgrid(range(r.shape[0]), range(r.shape[1]), indexing="ij")
+    z = r / np.sqrt((xx/fc[0])**2 + (yy/fc[1])**2 + 1)
+    return z
+
+
+def rescale_bins(spad_counts, min_depth, max_depth, sid_obj):
+    """
+    Works in Numpy
+    :param spad_counts: The histogram of spad counts to rescale.
+    :param min_depth: The minimum depth of the histogram.
+    :param max_depth: The maximum depth of the histogram.
+    :param sid_obj: An object representing a SID.
+    :return: A rescaled histogram in time to be according to the SID
+
+    Assign photons to sid bins proportionally according to the amount of overlap between
+    the sid bin range and the spad_count bin.
+    """
+
+    sid_bin_edges_m = sid_obj.sid_bin_edges - sid_obj.offset
+#     print(sid_bin_edges_m)
+    # Convert sid_bin_edges_m into units of spad bins
+    sid_bin_edges_bin = sid_bin_edges_m * len(spad_counts) / (max_depth - min_depth)
+    sid_bin_edges_bin -= sid_bin_edges_bin[0]  # Start at 0
+    sid_bin_edges_bin[-1] = np.floor(sid_bin_edges_bin[-1])
+    # print(sid_bin_edges_bin[-1])
+    # Map spad_counts onto sid_bin indices
+    print(sid_bin_edges_bin)
+    sid_counts = np.zeros(sid_obj.sid_bins)
+    for i in range(sid_obj.sid_bins):
+#         print(i)
+        left = sid_bin_edges_bin[i]
[…]

### 2019-09-09 nyuv2/captured/data/register_depth.m

@@ -1,0 +1,8 @@
+kinect_file = "8_29_kitchen_scene/kinect.mat";
+load(kinect_file)
+
+%% Perform alignment according to NYU Depth v2
+camera_params;
+
+depth_im_swapped = double(swapbytes(depth_im));
+[depthOut, rgbOut] = project_depth_map(depth_im_swapped, rgb_im);

### 2019-09-09 nyuv2/captured/data/toolbox_nyu_depth_v2/kinectv2_camera_params.m

@@ -1,0 +1,45 @@
+% Intrinsic parameters taken from Kim et. al 2015.
+%   
+% Extrinsic parameters taken from factory row for Basso et. al. 2018.
+% 
+
+% The maximum depth used, in meters.
+maxDepth = 10;
+
+% RGB Intrinsic Parameters
+fx_rgb = 5.1885790117450188e+02;
+fy_rgb = 5.1946961112127485e+02;
+cx_rgb = 3.2558244941119034e+02;
+cy_rgb = 2.5373616633400465e+02;
+
+% RGB Distortion Parameters
+k1_rgb =  2.0796615318809061e-01;
+k2_rgb = -5.8613825163911781e-01;
+p1_rgb = 7.2231363135888329e-04;
+p2_rgb = 1.0479627195765181e-03;
+k3_rgb = 4.9856986684705107e-01;
+
+% Depth Intrinsic Parameters
+fx_d = 5.8262448167737955e+02;
+fy_d = 5.8269103270988637e+02;
+cx_d = 3.1304475870804731e+02;
+cy_d = 2.3844389626620386e+02;
+
+% RGB Distortion Parameters
+k1_d = -9.9897236553084481e-02;
+k2_d = 3.9065324602765344e-01;
+p1_d = 1.9290592870229277e-03;
+p2_d = -1.9422022475975055e-03;
+k3_d = -5.1031725053400578e-01;
+
+% Rotation
+R = eye(3);
+
+% 3D Translation
+t_x = 0.052;
+t_z = 0.0;
+t_y = 0.0;
+
+% Parameters for making depth absolute.
+depthParam1 = 351.3;
+depthParam2 = 1092.5;

### 2019-09-09 nyuv2/captured/evaluate_densedepth.py

@@ -1,0 +1,234 @@
+import os
+import numpy as np
+import torch
+import pandas as pd
+from sacred import Experiment
+from weighted_histogram_matching import image_histogram_match
+from models.data.data_utils.sid_utils import SID
+from spad_utils import rescale_bins
+from remove_dc_from_spad import remove_dc_from_spad_poisson, remove_dc_from_spad_ambient_estimate, remove_dc_from_spad_edge
+from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+
+from models.loss import get_depth_metrics
+
+ex = Experiment("densedepth_weighted_hist_match", ingredients=[nyuv2_labeled_ingredient])
+
+@ex.config
+def cfg(data_config):
+    data_dir = "data"
+    spad_file = "spad.npy"
+    densedepth_depth_file = "rgb.npy"
+
+    # SID params
+    sid_bins = 140
+    alpha = 0.6569154266167957
+    beta = 9.972175646365525
+    offset = 0
+
+    entry = None
+    save_outputs = True
+    small_run = 0
+    output_dir = "results"
+
+
+@ex.automain
+def run(dataset_type,
+        spad_file,
+        densedepth_depth_file,
+        hyper_string,
+        sid_bins, alpha, beta, offset,
+        entry, save_outputs, small_run, output_dir):
+    # Load all the data:
+    print("Loading SPAD data from {}".format(spad_file))
+    spad_dict = np.load(spad_file, allow_pickle=True).item()
+    spad_data = spad_dict["spad"]
+    intensity_data = spad_dict["intensity"]
+    spad_config = spad_dict["config"]
+    print("Loading depth data from {}".format(densedepth_depth_file))
+    depth_data = np.load(densedepth_depth_file)
+    dataset = load_data(channels_first=True, dataset_type=dataset_type)
+
+    # Read SPAD config and determine proper course of action
+    dc_count = spad_config["dc_count"]
+    ambient = spad_config["dc_count"]/spad_config["spad_bins"]
+    use_intensity = spad_config["use_intensity"]
+    use_squared_falloff = spad_config["use_squared_falloff"]
+    use_poisson = spad_config["use_poisson"]
+    min_depth = spad_config["min_depth"]
+    max_depth = spad_config["max_depth"]
+
+    print("ambient: ", ambient)
+    print("dc_count: ", dc_count)
+    print("use_intensity: ", use_intensity)
[…]

### 2019-09-09 nyuv2/captured/mat_to_npy.py

@@ -1,0 +1,20 @@
+#! /usr/bin/env python3
+
+import scipy.io as sio
+import numpy as np
+
+# Extract root
+def mat_to_npy(spad_file):
+    root = spad_file.rpartition(".")[0]
+    npy_file = root + ".npy"
+    spad_data = sio.loadmat(spad_file)
+    np.save(npy_file, spad_data)
+    print("{} -> {}".format(spad_file, npy_file))
+
+if __name__ == '__main__':
+    # Get the file path somehow
+    spad_files = [
+        "spad1.mat"
+    ]
+    for file in spad_files:
+        mat_to_npy(file)

### 2019-09-09 nyuv2/captured/png_dataset.py

@@ -1,0 +1,186 @@
+import os
+import torch
+import cv2
+import numpy as np
+from torch.utils.data import Dataset
+
+from torchvision import transforms
+from models.data.data_utils.transforms import (ResizeAll, Save, Normalize,
+                                               AddDepthMask, ToTensorAll)
+
+from sacred import Experiment
+
+png_ingredient = Experiment('data_config')
+
+
+@png_ingredient.config
+def cfg():
+    data_name = "realsense_packard"
+    rootdir = "data"
+
+    # scene_folder: number_of_images
+    scene_dict = {
+        "conf_room": 4,
+        "couches": 3,
+        "kitchen": 3,
+        "kitchen2": 4,
+        "office": 4,
+        "office2": 4,
+        "third_floor": 5,
+    }
+
+    crop = (20, 460,  24, 616)
+
+    min_depth = 0.
+    max_depth = 10.
+
+
+class PNGDataset(Dataset):
+    """
+    Dataset of images in a 1-deep directory structure.
+    """
+    def __init__(self, rootdir, scene_dict, min_depth, max_depth, crop, transform=None, bgr_mode=False):
+        """
+
+        :param rootdir:
+        :param rgb_file:
+        :param depth_file:
+        :param rawdepth_file:
+        :param crop_file:
+        :param transform:
+        :param bgr_mode:
+        :param channels_first: True for tensorflow, False for pytorch
+        """
+        def process_depth_img(img, min_depth, max_depth):
+            if img.dtype == np.uint16:
+                img = img * (max_depth - min_depth) / (2 ** 16 - 1) + min_depth
+            elif img.dtype == np.uint8:
+                img = img * (max_depth - min_depth) / (2 ** 8 - 1) + min_depth
+            else:
+                raise TypeError("PNGDataset: Unknown image data type: {}".format(img.dtype))
+            return img
+
+        self.rootdir = rootdir
+        self.scene_dict = scene_dict
+        self.min_depth = min_depth
+        self.max_depth = max_depth
+        self.crop = crop
+        self.transform = transform
+        self.bgr_mode = bgr_mode # set to True if you're loading data for DORN.
+
+        # Load Images
+        depth = []
+        rawDepth = []
+        imgs = []
+        self.i_to_entry = []
+        self.entry_to_i = {}
+        for scene, n_img in scene_dict.items():
+            for i in range(n_img):
+                # print("loading {}[{}]".format(scene, i))
+                depthFile = os.path.join(rootdir, scene, "{}_depth.png".format(i))
[…]

### 2019-09-09 nyuv2/ordnet/loss.py

@@ -1,9 +1,5 @@
 import torch
 
-def scale_invariant_error(pred, gt):
-    """
-    Taken from Eigen et. al. Multi Scale Network paper
-    :param pred: Predicted Depth, N x C x H x W
-    :param gt: Ground Truth Depth, N x C x H x W
-    :return: The scale invariant error
-    """
+
+
+# Try other more exotic list/ranking based losses?

### 2019-09-09 nyuv2/ordnet/train.py

@@ -3,6 +3,8 @@
 import os
 import torch
 from torch.utils.data import DataLoader
+import torch.optim as optim
+import torch.optim.lr_scheduler as lr_scheduler
 from OrdNet import OrdNet
 from tensorboardX import SummaryWriter
 from models.core.checkpoint import safe_makedir
@@ -25,10 +27,23 @@ def load_model(checkpoint=None):
 
 def load_optimizer(param_groups, lr, checkpoint=None):
     if checkpoint is None:
-        return torch.optim.Adam(param_groups, lr)
-    optimizer = torch.optim.Adam(param_groups, lr)
+        return optim.Adam(param_groups, lr)
+    optimizer = optim.Adam(param_groups, lr)
     optimizer.load_state_dict(torch.load(checkpoint))
     return optimizer
+
+def scale_invariant_error(pred, gt, lam = 1., eps=1e-5):
+    """
+    Taken from Eigen et. al. Multi Scale Network paper
+    :param pred: Predicted Depth, N x C x H x W
+    :param gt: Ground Truth Depth, N x C x H x W
+    :param lam: tradeoff parameter that controls strength of ordinal term.
+    :param eps: Amount to add to pred and gt to avoid numerical issues
+    :return: The scale invariant error
+    """
+    d = torch.log(pred + eps) - torch.log(gt + eps)
+    loss = torch.mean(d**2) - (lam/torch.numel(d)**2) * torch.sum(d)**2
+    return loss
 
 @ex.config
 def cfg(data_config):
@@ -36,16 +51,17 @@ def cfg(data_config):
     checkpoint = None
     batch_size = 5      # Batch size
     lr = 1e-5           # Initial Learning Rate
-    num_epochs = 5      # Number of epochs to train
-    lr_decay = 1e-1     # Amount to decay learning rate every epoch
+    num_epochs = 10     # Number of epochs to train
+    milestones = [5, 7] # When to decay the learning rate
+    lr_decay = 1e-1     # Amount to decay learning rate at milestone epochs
 
     ckpt_config = {
         "ckpt_file": None,
         "ckpt_dir": "model",
         "run_id": os.path.join(datetime.now().strftime('%b%d'),
-                               datetime.now().strftime('%H-%M-%S_')) +
+                               datetime.now().strftime('%H-%M-%S_') +
                                model_name,
-                               data_config["data_name"],
+                               data_config["data_name"]),
[…]

### 2019-09-09 nyuv2/realsense/data/matlab/nyu_utils/fill_depth_colorization.m

@@ -1,4 +1,4 @@
-% Preprocesses the kinect depth image using a gray scale version of the
+% Preprocesses the captured depth image using a gray scale version of the
 % RGB image as a weighting for the smoothing. This code is a slight
 % adaptation of Anat Levin's colorization code:
 %

### 2019-09-09 nyuv2/realsense/data/matlab/nyu_utils/get_projection_mask.m

@@ -1,5 +1,5 @@
 % Gets a mask for the projected images that is most conservative with
-% respect to the regions that maintain the kinect depth signal following
+% respect to the regions that maintain the captured depth signal following
 % projection.
 %
 % Returns: 

### 2019-09-09 paper/spad_single/sections/method.tex
Pushing through a bunch of random commits.

--- 2019-05-30 paper/spad_single/sections/method.tex
@@
 
-\paragraph{Differentiable Histogram Matching}
-Given our initial depth map estimate, our goal is now to refine that depth map
-so that it agrees with the information provided by the SPAD histogram.
-Figure showing just the differentiable histogram matching part of the model.
-At a high level, we perform local optimization over the pixels of the depth map
-to make it consistent with the observed measurements $h[n]$.
-Given per-pixel depth, we can simulate SPAD histogram formation using equation
-\ref{global_hints}, where we approximate $\lambda_{x,y}[n]$ using kernel density
-estimation \cite{something} as:
-\begin{equation}
-  \hat \lambda^{(i)}_{x,y}[n] = \frac{1}{\sigma\sqrt{2 \pi}}\exp\paren*{-\frac{1}{2\sigma^2}(n - \hat z^{(i)}(x,y))} \label{KDE}
-\end{equation}
-where $\hat z^{(i)}(x, y)$ is our estimate of the depth at pixel $(x,y)$ at
-iteration $i$.
-
-Once we have $\lambda^{(i)}$, we compute $\hat h[n]$ according to the rest of
-the SPAD histogram formation model (neglecting the Poisson sampling) as follows
-\begin{equation}
-  \hat h[n] = \sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b. \label{diff_forward}
-\end{equation}
-Finally, given two histograms, we can compute the Wasserstein Distance between
-them. As described in \ref{Cuturi et. al.}, the Wasserstein Distance or ``earth
-mover's distance'' measures the distance between two probability distributions
-by calculating the minimum cost of moving the mass required to turn the first
-distribution into the second. It is particularly desirable
-because unlike the KL divergence or the simple RMSE, the Wasserstein Distance scales with
-separation as well as magnitude (see figure). Although the computation of the
-Wasserstein Distance requires solving a linear program, there is a regularized
-version known as the dual-Sinkhorn Distance
-which can be computed via Sinkhorn-Knopp Iterations in a fast and differentiable manner.
-We refer the reader to \ref{Cuturi et. al.} for details, but provide the
-optimization problem here.
-
-Given histograms $h, \hat h$ in $\Delta^n$ and a cost matrix $C$ in $\R^{n \times
-  n}$, the dual-Sinkhorn Divergence is found by solving
-the optimization problem
-\begin{equation}
-    \begin{aligned}
-    &\text{minimize} && \langle W, C \rangle  - \frac{1}{\lambda}h(W) \\
-    &\text{subject to} && W^Th = \bm{1} \\
-    &                  && W\hat h = \bm{1} \\
-    &                  && W \succeq 0 \\
-  \end{aligned}
-\end{equation}
-where $W \in \Delta^{n \times n}$ is the optimization variable, $\bm{1}$ denotes the
-vector of all ones, $h(\cdot)$ is the entropy of a probability distribution, and
-$\langle \cdot, \cdot \rangle$ denotes the inner product of two matrices.
+\paragraph{SPAD Denoising}
 \begin{itemize}
-\item Pseudocode for sinkhorn iterations?
-  \item Not sure what figure to use...
+  \item Discuss MLE for SPAD denoising
+  \item Write optimization problem for SPAD denoising
+  \item Show performance on a few examples 
 \end{itemize}
-\newpage
+\paragraph{Exact Histogram Matching}
 \begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.png}
+  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.jpeg}
   \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
   per-pixel depth estimate. We then perform gradient descent to optimize that
-  estimate using the SPAD forward model and the dual-Sinkhorn distance.}
+  estimate using the SPAD forward model and the dual-Sinkhorn distance
+  .}
 \end{figure}
+An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
+pixels of the image whose value lies in the range $[b_i, b_i+1)$.
+Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
+$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
+h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
 
 \subsection{Implementation Details}
-For the Monocular Depth Estimator, we use a pretrained version of the
-the Deep Ordinal Regression Network (DORN) \cite{}. We use the implementation of
-the Sinkhorn Iteration (for calculating the dual-Sinkhorn distance)
-from \ref{Cuturi et. al.} We update the depth map using gradient descent.
-Everything is implemented in PyTorch.
-We run the model on a NVIDIA Titan X GPU, where it takes approximately 5 seconds
-to fully process a single RGB-SPAD data pair.
-Table with hyperparameters (defer to supplementary info?)
-\begin{itemize}
-\item Kernel Density Estimation (sigma)
-\item Sinkhorn Iterations (maximum number, epsilon tolerance)
-\item Gradient Descent (learning rate, epsilon tolerance, max iterations)
-\item Simulation hyperparameters ($\eta, b$)
-\end{itemize}
+For the Monocular Depth Estimator, we use pretrained versions of the
+the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
+The exact histogram matching method is as described in \cite{}.

### 2019-09-09 nyuv2/captured/data/register_depth.m

@@ -1,8 +1,0 @@
-kinect_file = "8_29_kitchen_scene/kinect.mat";
-load(kinect_file)
-
-%% Perform alignment according to NYU Depth v2
-camera_params;
-
-depth_im_swapped = double(swapbytes(depth_im));
-[depthOut, rgbOut] = project_depth_map(depth_im_swapped, rgb_im);

### 2019-09-09 nyuv2/ordnet/loss.py

@@ -1,5 +1,0 @@
-import torch
-
-
-
-# Try other more exotic list/ranking based losses?

### 2019-09-09 nyuv2/realsense/DenseDepth/demo.py

@@ -1,416 +1,0 @@
-import os
-import sys
-import glob
-import time
-import math
-import argparse
-import numpy as np
-
-# Computer Vision
-import cv2
-from scipy import ndimage
-from skimage.transform import resize
-
-# Visualization
-import matplotlib.pyplot as plt
-plasma = plt.get_cmap('plasma')
-
-# UI and OpenGL
-from PySide2 import QtCore, QtGui, QtWidgets, QtOpenGL
-from OpenGL import GL, GLU
-from OpenGL.arrays import vbo
-from OpenGL.GL import shaders
-import glm
-
-# Argument Parser
-parser = argparse.ArgumentParser(description='High Quality Monocular Depth Estimation via Transfer Learning')
-parser.add_argument('--model', default='nyu.h5', type=str, help='Trained Keras model file.')
-args = parser.parse_args()
-
-# Image shapes
-height_rgb, width_rgb = 480, 640
-height_depth, width_depth = height_rgb // 2, width_rgb // 2
-rgb_width = width_rgb
-rgb_height = height_rgb
-
-import tensorflow as tf
-global graph,model
-graph = tf.get_default_graph()
-
-def load_model():
-    # Kerasa / TensorFlow
-    os.environ['TF_CPP_MIN_LOG_LEVEL'] = '5'
-    from keras.models import load_model
-    from layers import BilinearUpSampling2D
-
-    # Custom object needed for inference and training
-    custom_objects = {'BilinearUpSampling2D': BilinearUpSampling2D, 'depth_loss_function': None}
-
-    # Load model into GPU / CPU
-    return load_model(args.model, custom_objects=custom_objects, compile=False)
-
-# Function timing
-ticTime = time.time()
-def tic(): global ticTime; ticTime = time.time()
-def toc(): print('{0} seconds.'.format(time.time() - ticTime))
-
-# Conversion from Numpy to QImage and back
-def np_to_qimage(a):
-    im = a.copy()
-    return QtGui.QImage(im.data, im.shape[1], im.shape[0], im.strides[0], QtGui.QImage.Format_RGB888).copy()
-    
-def qimage_to_np(img):
-    img = img.convertToFormat(QtGui.QImage.Format.Format_ARGB32)
-    return np.array(img.constBits()).reshape(img.height(), img.width(), 4)
-
-# Compute edge magnitudes
-def edges(d):
-    dx = ndimage.sobel(d, 0)  # horizontal derivative
[…]

### 2019-09-09 nyuv2/realsense/DenseDepth/test.py

@@ -1,40 +1,0 @@
-import os
-import glob
-import argparse
-
-# Kerasa / TensorFlow
-os.environ['TF_CPP_MIN_LOG_LEVEL'] = '5'
-from keras.models import load_model
-from layers import BilinearUpSampling2D
-from loss import depth_loss_function
-from utils import predict, load_images, display_images
-from matplotlib import pyplot as plt
-
-# Argument Parser
-parser = argparse.ArgumentParser(description='High Quality Monocular Depth Estimation via Transfer Learning')
-parser.add_argument('--model', default='nyu.h5', type=str, help='Trained Keras model file.')
-parser.add_argument('--input', default='examples/*.png', type=str, help='Input filename or folder.')
-args = parser.parse_args()
-
-# Custom object needed for inference and training
-custom_objects = {'BilinearUpSampling2D': BilinearUpSampling2D, 'depth_loss_function': depth_loss_function}
-
-print('Loading model...')
-
-# Load model into GPU / CPU
-model = load_model(args.model, custom_objects=custom_objects, compile=False)
-
-print('\nModel loaded ({0}).'.format(args.model))
-
-# Input images
-inputs = load_images( glob.glob(args.input) )
-print('\nLoaded ({0}) images of size {1}.'.format(inputs.shape[0], inputs.shape[1:]))
-
-# Compute results
-outputs = predict(model, inputs)
-
-# Display results
-viz = display_images(outputs.copy(), inputs.copy())
-plt.figure(figsize=(10,5))
-plt.imshow(viz)
-plt.show()

### 2019-09-09 nyuv2/realsense/data/matlab/nyu_utils/get_accel_data.m

@@ -1,4 +1,4 @@
-% Returns the accelerometer data coming from the captured.
+% Returns the accelerometer data coming from the kinect.
 %
 % Args:
 %   filename - the filename of the .dump file.

### 2019-09-09 nyuv2/realsense/data/matlab/nyu_utils/get_projection_mask.m

@@ -1,5 +1,5 @@
 % Gets a mask for the projected images that is most conservative with
-% respect to the regions that maintain the captured depth signal following
+% respect to the regions that maintain the kinect depth signal following
 % projection.
 %
 % Returns: 

### 2019-09-09 nyuv2/weighted_histogram_matching/MiDaSModel.py

@@ -1,44 +1,0 @@
-import torch
-import numpy as np
-from MiDaS.monodepth_net import MonoDepthNet
-import MiDaS.utils as utils
-
-
-def get_midas(model_path, device="cpu"):
-    model = MonoDepthNet(model_path)
-    model.to(device)
-    model.eval()
-    return model
-
-
-def midas_predict(model, img, depth_range, device):
-    """
-    Predict depth from RGB
-    :param model: a midas model
-    :param img: RGB image in 0-1
-    :param depth_range: Range of output depths (e.g. (0., 10) for NYUv2)
-    :param device: torch.device object to run on
-    :return: Inverse Depth image, same size as RGB image, scaled to be in the output range.
-    """
-    assert depth_range[0] < depth_range[1]
-    assert depth_range[0] >= 0.
-    img_input = utils.resize_image(img)
-    img_input = img_input.to(device)
-
-    # compute
-    with torch.no_grad():
-        idepth = model.forward(img_input)
-
-    idepth = utils.resize_depth(idepth, img.shape[1], img.shape[0])
-
-    idepth_min = idepth.min()
-    idepth_max = idepth.max()
-
-    # Arbitrarily cap at 1./depth_range[1] + 10 for "infinite depth"
-    idepth_range = (1. / depth_range[1],
-                    1. / depth_range[0] if depth_range[0] > 0 else 1. / depth_range[1] + 10.)
-    idepth_scaled = (idepth_range[1] - idepth_range[0]) * \
-                    (idepth - idepth_min) / (idepth_max - idepth_min) + \
-                    idepth_range[0]
-    depth_scaled = 1. / idepth_scaled
-    return depth_scaled

### 2019-09-18 paper/spad_single/cvpr2019/supplement.tex
Camera alignment, distortion correction, working on supplement figure.

\documentclass[10pt,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{array}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{multirow}
\input{mark_defs.tex}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{4321}
\begin{document}

%%%%%%%%% TITLE
\title{Supplementary Information: Improving Monocular Depth Estimation with
  Global Depth Histogram Matching}

\maketitle
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_18_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_21_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_25_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_285_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_42_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_52_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_53_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_103_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_224_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_226_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_352_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_362_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_379_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_107_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_187_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_140_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_244_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_527_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_219_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_329_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_346_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_616_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_390_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_412_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_420_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_428_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_457_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_477_comparison.png}
  \caption{Results on DenseDepth}
\end{figure*}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_499_comparison.png}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_258_comparison.png}
%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_341_comparison.png}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_8_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_14_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_15_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_23_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_26_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_63_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_67_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_140_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_170_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_522_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_548_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_569_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_585_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_633_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_105_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_220_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_252_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_259_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_178_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_219_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_280_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_293_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_313_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_413_comparison.png}
  \caption{Results on DORN}
\end{figure*}
\begin{figure*}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_477_comparison.png}
  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_502_comparison.png}
%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
  \caption{Results on DORN}
\end{figure*}
% Densedepth:
% - Office: 18, 21
% - Bathroom: 25, 194, 285
% - Bookstore: 42
% - Kitchen: 52, 53, 103, 224, 226, 352, 362, 379
% - Office: 107, 187
% - Living Room: 140, 244, 527, 529
% - Dining Room: 219, 329, 346, 616
% - Bedroom: 390, 412, 420, 428, 457*, 468*, 477, 499
% Failure Cases: 258, 338(?), 341, 537 649 (minor)
% 
% DORN:
% - Office: 8, 14, 15, 23, 26
% - Living room: 63, 67, 140, 170, 522, 548, 569, 585, 633
% - Office: 105, 220, 252, 259* (interesting)
% - Kitchen: 178
% - Dining Room: 219
% - Bathroom: 280, 293, 313
% - Bedroom: 413, 477, 502
% 
% Failure Cases: 96, 266(?)

\end{document}

### 2019-09-18 paper/spad_single/sections/hardware.tex
Camera alignment, distortion correction, working on supplement figure.

@@
 \end{itemize}
-\begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
-  \caption{\textbf{Hardware results}}
-\end{figure}
+% \begin{figure}
+%  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
+%  \caption{\textbf{Hardware results}}
+% \end{figure}
+%       "8_29_kitchen_scene",
+%       "8_29_conference_room_scene",
+%       "8_30_conference_room2_scene",
+%       "8_30_Hallway",
+%       "8_30_poster_scene",
+%       "8_30_small_lab_scene",
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{p{5mm}ccccc}
+      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+      &
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/gt_z_proj_crop.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
+      & RGB &  &  &  & \\
+      &
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/rgb_cropped.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\
+
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/gt_z_proj_crop.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/rgb_cropped.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\
+
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/gt_z_proj_crop.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/rgb_cropped.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
+    \end{tabular}
+    \caption{Captured results initialized using the MiDaS CNN.
+      Second row shows absolute difference between above estimates and ground truth.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{ccccc}
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_init_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
+
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/rgb_cropped.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_init_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
+      & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\
+
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\
+
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/rgb_cropped.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
+      & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\
+
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\
+
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/rgb_cropped.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
+      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
+      & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\
+
+%      (a)&(b)&(c)&(d)&(e)\\
+    \end{tabular}
+    \caption{Captured results initialized using the MiDaS CNN. (a) RGB image.
+      (b) Ground Truth Depth. (c) Initial Depth Estimate. (d) SPAD-median
+      Rescaled Estimate. (e) SPAD Histogram Matched Estimate.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}

### 2019-09-18 nyuv2/captured/camera_utils.py

@@ -1,0 +1,80 @@
+import scipy.io as sio
+import numpy as np
+import cv2
+
+def undistort_img(img, fc, pc, rdc, tdc):
+    if len(rdc) == 2:
+        rdc = np.append(rdc, 0.)
+    distortionCoefficients = np.concatenate((rdc[:2], tdc, rdc[2:]))
+    cameraMatrix = np.array([[fc[0], 0.,     pc[0]],
+                             [0.,     fc[1], pc[1]],
+                             [0.,     0.,    1.]])
+    img_undist = cv2.undistort(img, cameraMatrix, distortionCoefficients)
+    return img_undist
+
+
+def extract_camera_intrinsics(CameraParameters):
+    """
+    Get intrinsics from param struct
+    """
+    focalLength = CameraParameters["FocalLength"][0]
+    principalPoint = CameraParameters["PrincipalPoint"][0]
+    radialDistortion = CameraParameters["RadialDistortion"][0]
+    tangentialDistortion = CameraParameters["TangentialDistortion"][0]
+    return focalLength, principalPoint, radialDistortion, tangentialDistortion
+
+
+def extract_camera_params(filepath):
+    arr = sio.loadmat(filepath)
+    param_struct = arr["param_struct"]
+    RotationOfCamera2 = param_struct["RotationOfCamera2"][0][0]
+    TranslationOfCamera2 = param_struct["TranslationOfCamera2"][0][0][0]
+    cp1 = param_struct["CameraParameters1"][0][0][0][0]
+    cp2 = param_struct["CameraParameters2"][0][0][0][0]
+
+    fc1, pc1, rdc1, tdc1 = extract_camera_intrinsics(cp1)
+    fc2, pc2, rdc2, tdc2 = extract_camera_intrinsics(cp2)
+    return fc1, fc2, pc1, pc2, rdc1, rdc2, tdc1, tdc2, RotationOfCamera2, TranslationOfCamera2
+
+
+def project_depth(z, z_mask, imagesize2, fc1, fc2, pc1, pc2, RotationOfCamera2, TranslationOfCamera2):
+    """
+    Project a depth map z from camera 1 to camera 2, given the rotation matrix and translation vectors.
+
+    Does not account for any distortion.
+
+    Pay attention that the units of z and the units of the translation vector match.
+
+    :param z: Input depth map
+    :param imagesize2: Size of output image
[…]

### 2019-09-18 nyuv2/captured/capture_utils.py

@@ -1,5 +1,9 @@
+import os
 import h5py
+import cv2
 import numpy as np
+from remove_dc_from_spad import remove_dc_from_spad_edge
+import matplotlib.pyplot as plt
 
 def loadmat_h5py(file):
     output = {}
@@ -8,9 +12,11 @@ def loadmat_h5py(file):
             output[k] = np.array(v)
     return output
 
+fc_kinect = [1053.622, 1047.508]
+fc_spad = [758.2466, 791.2153]
 
-def z_to_r_kinect(z):
-    fc = [1053.622, 1047.508]  # Focal length in pixels
+
+def z_to_r(z, fc):
     yy, xx = np.meshgrid(range(z.shape[0]), range(z.shape[1]), indexing="ij")
     x = (xx * z) / fc[0]
     y = (yy * z) / fc[1]
@@ -18,8 +24,7 @@ def z_to_r_kinect(z):
     return r
 
 
-def r_to_z_kinect(r):
-    fc = [1053.622, 1047.508]  # Focal length in pixels
+def r_to_z(r, fc):
     yy, xx = np.meshgrid(range(r.shape[0]), range(r.shape[1]), indexing="ij")
     z = r / np.sqrt((xx/fc[0])**2 + (yy/fc[1])**2 + 1)
     return z
@@ -46,7 +51,7 @@ def rescale_bins(spad_counts, min_depth, max_depth, sid_obj):
     sid_bin_edges_bin[-1] = np.floor(sid_bin_edges_bin[-1])
     # print(sid_bin_edges_bin[-1])
     # Map spad_counts onto sid_bin indices
-    print(sid_bin_edges_bin)
+    # print(sid_bin_edges_bin)
     sid_counts = np.zeros(sid_obj.sid_bins)
     for i in range(sid_obj.sid_bins):
 #         print(i)
@@ -79,4 +84,99 @@ def normals_from_depth(z):
     return n
 
 
+def get_closer_to_mod(lower, upper, mod):
+    """
+    Adjusts lower and upper so that their difference is 0 (mod mod)
+    :param lower: smaller number
+    :param upper: larger number
+    :param mod: the modulus
+    :return: pair (lower_modified, upper_modified) such that upper_modified - lower_modified = 0 (mod mod)
+    """
+    assert lower <= upper
+    diff = (upper - lower) % mod
+    if diff > mod//2:
+        diff = diff - mod # Negative
+    lower_correction = diff//2
[…]

### 2019-09-18 nyuv2/captured/remove_dc_from_spad.py

@@ -218,6 +218,7 @@ def remove_dc_from_spad_edge(spad, ambient, grad_th=1e3, n_std=1.):
     spad[last+1:] = 0.
     return np.clip(spad - ambient, a_min=0., a_max=None)
 
+
 import sklearn.mixture as skmix
 def remove_dc_from_spad_gmm(h, n_components=4, weight_concentration_prior=1e0, depth_values=None, axs=None):
     assert len(h.shape) == 1

### 2019-09-18 nyuv2/gt_hist_matching/evaluate_midas.py

@@ -1,0 +1,85 @@
+#! /usr/bin/env python3
+
+import os
+import torch
+import pandas as pd
+import numpy as np
+from sacred import Experiment
+from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+from histogram_matching import hist_match
+
+from models.loss import get_depth_metrics
+
+ex = Experiment("midas_gt_hist_matching", ingredients=[nyuv2_labeled_ingredient])
+
+
+@ex.config
+def cfg(data_config):
+    dataset_type = "test"
+    entry = None
+    save_outputs = True
+    seed = 95290421
+    small_run = 0
+    input_file = os.path.join("data", "midas_{}_outputs.npy".format(dataset_type))
+
+    output_dir = "results"
+
+
+
+@ex.automain
+def run(dataset_type,
+        entry,
+        save_outputs,
+        small_run,
+        input_file,
+        output_dir):
+    dataset = load_data(channels_first=False, dataset_type=dataset_type)
+    cnn_data = np.load(input_file)
+
+    if entry is None:
+        metric_list = ["delta1", "delta2", "delta3", "rel_abs_diff", "rmse", "mse", "log10", "weight"]
+        metrics = np.zeros((len(dataset) if not small_run else small_run, len(metric_list)))
+        entry_list = []
+        outputs = []
+        for i in range(len(dataset)):
+            if small_run and i == small_run:
+                break
+            print("Running {}[{}]".format(dataset_type, i))
+            entry_list.append(i)
+            init = cnn_data[i, ...]
+            gt = dataset[i]["depth_cropped"]
+
+            pred = hist_match(init, gt.cpu().numpy())
+
+            pred_metrics = get_depth_metrics(torch.from_numpy(pred).float(),
+                                             gt,
+                                             torch.ones_like(gt))
+            for j, metric_name in enumerate(metric_list[:-1]):
+                metrics[i, j] = pred_metrics[metric_name]
+
+            metrics[i, -1] = torch.numel(gt)
+            # Option to save outputs:
+            if save_outputs:
+                outputs.append(pred)
+
+        if save_outputs:
+            np.save(os.path.join(output_dir, "midas_gt_hist_{}_outputs.npy".format(dataset_type)),
+                    np.concatenate(outputs, axis=0))
+
+        # Save metrics using pandas
+        metrics_df = pd.DataFrame(data=metrics, index=entry_list, columns=metric_list)
[…]

### 2019-09-18 nyuv2/weighted_histogram_matching/evaluate_midas.py

@@ -1,0 +1,256 @@
+import os
+import numpy as np
+import torch
+import pandas as pd
+from sacred import Experiment
+from weighted_histogram_matching import image_histogram_match
+from models.data.data_utils.sid_utils import SID
+from spad_utils import rescale_bins
+from remove_dc_from_spad import remove_dc_from_spad_poisson, remove_dc_from_spad_ambient_estimate, remove_dc_from_spad_edge
+from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+
+from models.loss import get_depth_metrics
+
+ex = Experiment("midas_weighted_hist_match", ingredients=[nyuv2_labeled_ingredient])
+
+@ex.config
+def cfg(data_config):
+    data_dir = "data"
+    dataset_type = "test"
+    use_intensity = True
+    use_squared_falloff = True
+    dc_count = 1e5
+    use_jitter = True
+    use_poisson = True
+    hyper_string = "{}_int_{}_fall_{}_dc_{}_jit_{}_poiss_{}".format(
+        dataset_type,
+        use_intensity,
+        use_squared_falloff,
+        dc_count,
+        use_jitter,
+        use_poisson)
+    # spad_file = os.path.join(data_dir, "{}_spad{}.npy".format(hyper_string,
+    #                                                            "_denoised" if dc_count > 0. and use_poisson else ""))
+    spad_file = os.path.join(data_dir, "{}_spad.npy".format(hyper_string))
+    midas_depth_file = os.path.join(data_dir, "midas_{}_outputs.npy".format(dataset_type))
+
+    # SID params
+    sid_bins = 140
+    alpha = 0.6569154266167957
+    beta = 9.972175646365525
+    offset = 0
+
+    # SPAD Denoising params
+    lam = 1e1 if use_poisson else 1e-1
+    eps_rel = 1e-5
+    n_std = 0.5
+
+    entry = None
+    save_outputs = True
+    small_run = 0
+    output_dir = "results"
+
+
+@ex.automain
+def run(dataset_type,
+        spad_file,
+        midas_depth_file,
+        hyper_string,
+        sid_bins, alpha, beta, offset,
+        lam, eps_rel, n_std,
+        entry, save_outputs, small_run, output_dir):
+    # Load all the data:
+    print("Loading SPAD data from {}".format(spad_file))
+    spad_dict = np.load(spad_file, allow_pickle=True).item()
+    spad_data = spad_dict["spad"]
[…]

### 2019-09-19 paper/spad_single/cvpr2019/supplement.tex
Finalizing captured results figure, adding results for densedepth.

@@
 
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
+      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
+%      & RGB &  &  &  & \\
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
+      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/densedepth/8_29_conference_room_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
+    \end{tabular}
+    \caption{Captured results initialized using the DenseDepth CNN.
+      Second row shows absolute difference between above estimates and ground truth.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
+      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
+      & & & & & \\
+
+      & 
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/diff_colorbar.pdf}\\
+      & RGB & \input{sections/figures/captured/densedepth/8_30_Hallway/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/densedepth/8_30_poster_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/densedepth/8_30_small_lab_scene/rmses.tex}\\
+
+%      (a)&(b)&(c)&(d)&(e)\\
+    \end{tabular}
+    \caption{Captured results initialized using the DenseDepth CNN.
+      Second row shows absolute difference between above estimates and ground truth.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}
+
 \end{document}

### 2019-09-19 paper/spad_single/sections/hardware.tex
Finalizing captured results figure, adding results for densedepth.

--- 2019-08-08 paper/spad_single/sections/hardware.tex
@@
 \end{itemize}
-\begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
-  \caption{\textbf{Hardware results}}
-\end{figure}
+% \begin{figure}
+%  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
+%  \caption{\textbf{Hardware results}}
+% \end{figure}
+%       "8_29_kitchen_scene",
+%       "8_29_conference_room_scene",
+%       "8_30_conference_room2_scene",
+%       "8_30_Hallway",
+%       "8_30_poster_scene",
+%       "8_30_small_lab_scene",
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
+      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
+%      & RGB &  &  &  & \\
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
+      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
+    \end{tabular}
+    \caption{Captured results initialized using the MiDaS CNN.
+      Second row shows absolute difference between above estimates and ground truth.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}
+\begin{figure*}[t!]
+    \centering
+    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
+      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
+      & & & & & \\
+
+      & 
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
+      & RGB & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\
+
+      \rule{0pt}{3ex}  & & & & & \\
+      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\
+
+      &
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/rgb_cropped_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
+      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
+      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
+      & & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\
+
+%      (a)&(b)&(c)&(d)&(e)\\
+    \end{tabular}
+    \caption{Captured results initialized using the MiDaS CNN.
+      Second row shows absolute difference between above estimates and ground truth.}
+    \label{fig:midas_captured}
+%    \vspace{-1.5em}
+\end{figure*}

### 2019-09-19 nyuv2/midas/loss.py

@@ -1,0 +1,86 @@
+import numpy as np
+
+def get_depth_metrics(depth_pred, depth_truth, mask):
+    """
+    Takes torch tensors.
+    :param depth_pred: Depth prediction
+    :param depth_truth: Ground truth
+    :param mask: Masks off invalid pixels
+    :return: Dictionary of metrics
+    """
+    metrics = dict()
+    # deltas
+    metrics["delta1"] = delta(depth_pred, depth_truth, mask, 1.25)
+    metrics["delta2"] = delta(depth_pred, depth_truth, mask, 1.25 ** 2)
+    metrics["delta3"] = delta(depth_pred, depth_truth, mask, 1.25 ** 3)
+    # rel_abs_diff
+    metrics["rel_abs_diff"] = rel_abs_diff(depth_pred, depth_truth, mask)
+    # rel_sqr_diff
+    metrics["rel_sqr_diff"] = rel_sqr_diff(depth_pred, depth_truth, mask)
+    # log10
+    metrics["log10"] = log10(depth_pred, depth_truth, mask)
+    # mse
+    metrics["mse"] = mse(depth_pred, depth_truth, mask)
+    # rmse
+    metrics["rmse"] = rmse(depth_pred, depth_truth, mask)
+    # rmse(log)
+    metrics["log_rmse"] = rmse(np.log(depth_pred),
+                               np.log(depth_truth),
+                               mask)
+    # print(metrics)
+    return metrics
+
+def delta(prediction, target, mask, threshold):
+    """
+    Given prediction and target, compute the fraction of indices i
+    such that
+    max(prediction[i]/target[i], target[i]/prediction[i]) < threshold
+    """
+    # print(prediction.dtype)
+    # print(mask.dtype)
+    # print(target.dtype)
+    c = np.maximum(prediction[mask > 0]/target[mask > 0], target[mask > 0]/prediction[mask > 0])
+    return np.sum((c < threshold))/(np.sum(mask))
+
+def mse(prediction, target, mask):
+    """
+    Return the MSE of prediction and target
+    """
+    return np.mean((prediction[mask > 0] - target[mask > 0])**2)
+
+
+def rmse(prediction, target, mask):
+    """
+    Return the RMSE of prediction and target
+    """
+    return np.sqrt(mse(prediction, target, mask))
+
+
+def log10(prediction, target, mask):
+    """
+    Return the log10 loss metric:
[…]

### 2019-09-19 nyuv2/weighted_histogram_matching/run_midas.py

@@ -14,7 +14,7 @@ import numpy as np
 import pandas as pd
 
 # Model
-from MiDaSModel import get_midas, midas_gt_predict
+from MiDaSModel import get_midas, midas_gt_predict, midas_gt_predict_masked
 # Dataset
 from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
 
@@ -81,11 +81,13 @@ def main(model_path,
                 entry_list.append(entry)
                 print("Evaluating {}".format(data["entry"][0]))
                 # pred, pred_metrics = model.evaluate(data, device)
-                pred = midas_gt_predict(model, data["rgb"].cpu().numpy().squeeze(),
-                                        data["depth_cropped"].cpu().numpy().squeeze(), crop, device)
+                pred = midas_gt_predict_masked(model, data["rgb"].cpu().numpy().squeeze(),
+                                               data["rawdepth_cropped"].cpu().numpy().squeeze(),
+                                               data["mask_cropped"].cpu().numpy().squeeze(),
+                                               crop, device)
 
                 pred = torch.from_numpy(pred).unsqueeze(0).unsqueeze(0).float()
-                pred_metrics = get_depth_metrics(pred, data["depth_cropped"], torch.ones_like(pred))
+                pred_metrics = get_depth_metrics(pred, data["rawdepth_cropped"], data["mask_cropped"])
                 print(pred_metrics)
                 for j, metric_name in enumerate(metric_list[:-1]):
                     metrics[i, j] = pred_metrics[metric_name]

### 2019-09-26 paper/spad_single/cvpr2020/egpaper_for_review.tex
Switching paper format, finishing up supplement figures.

--- 2019-05-30 paper/spad_single/cvpr2019AuthorKit/latex/egpaper_final.tex
@@
 % Include other packages here, before hyperref.
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{bm}
+\usepackage{multirow}
+\usepackage{float}
+\usepackage[utf8x]{inputenc}
+\input{mark_defs.tex}
 
@@
 % run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
-
-\cvprfinalcopy % *** Uncomment this line for the final submission
+\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+%\cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
-%%%%%%%%% TITLE
-\title{\LaTeX\ Author Guidelines for CVPR Proceedings}
+\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching}
 
@@
 \end{abstract}
+\section{Introduction}
+\input{sections/introduction}
 
-%%%%%%%%% BODY TEXT
-\section{Introduction}
+\section{Related Work}
+\input{sections/related}
 
-Please follow the steps outlined below when submitting your manuscript to
-the IEEE Computer Society Press.  This style guide now has several
-important modifications (for example, you are no longer warned against the
-use of sticky tape to attach your artwork to the paper), so all authors
-should read this new version.
+\section{Method}
+\input{sections/method}
 
-%-------------------------------------------------------------------------
-\subsection{Language}
+\section{Simulation}
+\input{sections/simulation}
 
-All manuscripts must be in English.
+\section{Hardware Prototype}
+\input{sections/hardware}
 
-\subsection{Dual submission}
-
-Please refer to the author guidelines on the CVPR 2019 web page for a
-discussion of the policy on dual submissions.
-
-\subsection{Paper length}
-Papers, excluding the references section,
-must be no longer than eight pages in length. The references section
-will not be included in the page count, and there is no limit on the
-length of the references section. For example, a paper of eight pages
-with two pages of references would have a total length of 10 pages.
-{\bf There will be no extra page charges for CVPR 2019.}
-
-Overlength papers will simply not be reviewed.  This includes papers
-where the margins and formatting are deemed to have been significantly
-altered from those laid down by this style guide.  Note that this
-\LaTeX\ guide already sets figure captions and references in a smaller font.
-The reason such papers will not be reviewed is that there is no provision for
-supervised revisions of manuscripts.  The reviewing process cannot determine
-the suitability of the paper for presentation in eight pages if it is
-reviewed in eleven.
-
-%-------------------------------------------------------------------------
-\subsection{The ruler}
-The \LaTeX\ style defines a printed ruler which should be present in the
-version submitted for review.  The ruler is provided in order that
-reviewers may comment on particular lines in the paper without
-circumlocution.  If you are preparing a document using a non-\LaTeX\
-document preparation system, please arrange for an equivalent ruler to
-appear on the final output pages.  The presence or absence of the ruler
-should not change the appearance of any other content on the page.  The
-camera ready copy should not contain a ruler. (\LaTeX\ users may uncomment
-the \verb'\cvprfinalcopy' command in the document preamble.)  Reviewers:
-note that the ruler measurements do not align well with lines in the paper
---- this turns out to be very difficult to do well when the paper contains
-many figures and equations, and, when done, looks ugly.  Just use fractional
-references (e.g.\ this line is $095.5$), although in most cases one would
-expect that the approximate location will be adequate.
-
-\subsection{Mathematics}
-
-Please number all of your sections and displayed equations.  It is
-important for readers to be able to refer to any particular equation.  Just
-because you didn't refer to it in the text doesn't mean some future reader
-might not need to refer to it.  It is cumbersome to have to use
-circumlocutions like ``the equation second from the top of page 3 column
-1''.  (Note that the ruler will not be present in the final copy, so is not
-an alternative to equation numbers).  All authors will benefit from reading
-Mermin's description of how to write mathematics:
-\url{http://www.pamitc.org/documents/mermin.pdf}.
-
-\subsection{Blind review}
-
-Many authors misunderstand the concept of anonymizing for blind
-review.  Blind review does not mean that one must remove
-citations to one's own work---in fact it is often impossible to
-review a paper unless the previous citations are known and
-available.
-
-Blind review means that you do not use the words ``my'' or ``our''
-when citing previous work.  That is all.  (But see below for
-techreports.)
-
-Saying ``this builds on the work of Lucy Smith [1]'' does not say
-that you are Lucy Smith; it says that you are building on her
-work.  If you are Smith and Jones, do not say ``as we show in
-[7]'', say ``as Smith and Jones show in [7]'' and at the end of the
-paper, include reference 7 as you would any other cited work.
-
-An example of a bad paper just asking to be rejected:
-\begin{quote}
-\begin{center}
-    An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of our
-   previous paper [1], and show it to be inferior to all
-   previously known methods.  Why the previous paper was
-   accepted without this analysis is beyond me.
-
-   [1] Removed for blind review
-\end{quote}
-
-An example of an acceptable paper:
-
-\begin{quote}
-\begin{center}
-     An analysis of the frobnicatable foo filter.
-\end{center}
-
-   In this paper we present a performance analysis of the
-   paper of Smith \etal [1], and show it to be inferior to
-   all previously known methods.  Why the previous paper
-   was accepted without this analysis is beyond me.
-
-   [1] Smith, L and Jones, C. ``The frobnicatable foo
-   filter, a fundamental contribution to human knowledge''.
-   Nature 381(12), 1-213.
-\end{quote}
-
-If you are making a submission to another conference at the same time,
-which covers similar or overlapping material, you may need to refer to that
-submission in order to explain the differences, just as you would if you
-had previously published related work.  In such cases, include the
-anonymized parallel submission~\cite{Authors14} as additional material and
-cite it as
-\begin{quote}
-[1] Authors. ``The frobnicatable foo filter'', F\&G 2014 Submission ID 324,
-Supplied as additional material {\tt fg324.pdf}.
-\end{quote}
-
-Finally, you may feel you need to tell the reader that more details can be
-found elsewhere, and refer them to a technical report.  For conference
-submissions, the paper must stand on its own, and not {\em require} the
-reviewer to go to a techreport for further details.  Thus, you may say in
-the body of the paper ``further details may be found
-in~\cite{Authors14b}''.  Then submit the techreport as additional material.
-Again, you may not assume the reviewers will read this material.
-
-Sometimes your paper is about a problem which you tested using a tool which
-is widely known to be restricted to a single institution.  For example,
-let's say it's 1969, you have solved a key problem on the Apollo lander,
-and you believe that the CVPR70 audience would like to hear about your
-solution.  The work is a development of your celebrated 1968 paper entitled
-``Zero-g frobnication: How being the only people in the world with access to
-the Apollo lander source code makes us a wow at parties'', by Zeus \etal.
-
-You can handle this paper like any other.  Don't write ``We show how to
-improve our previous work [Anonymous, 1968].  This time we tested the
-algorithm on a lunar lander [name of lander removed for blind review]''.
-That would be silly, and would immediately identify the authors. Instead
-write the following:
-\begin{quotation}
-\noindent
-   We describe a system for zero-g frobnication.  This
-   system is new because it handles the following cases:
-   A, B.  Previous systems [Zeus et al. 1968] didn't
-   handle case B properly.  Ours handles it by including
-   a foo term in the bar integral.
-
-   ...
-
-   The proposed system was integrated with the Apollo
-   lunar lander, and went all the way to the moon, don't
-   you know.  It displayed the following behaviours
-   which show how well we solved cases A and B: ...
-\end{quotation}
-As you can see, the above text follows standard scientific convention,
-reads better than the first version, and does not explicitly name you as
-the authors.  A reviewer might think it likely that the new paper was
-written by Zeus \etal, but cannot make any decision based on that guess.
-He or she would have to be sure that no other authors could have been
-contracted to solve problem B.
-\medskip
-
-\noindent
-FAQ\medskip\\
-{\bf Q:} Are acknowledgements OK?\\
-{\bf A:} No.  Leave them for the final copy.\medskip\\
-{\bf Q:} How do I cite my results reported in open challenges?
-{\bf A:} To conform with the double blind review policy, you can report results of other challenge participants together with your results in your paper.
-For your results, however, you should not identify yourself and should not mention your participation in the challenge.
-Instead present your results referring to the method proposed in your paper and draw conclusions based on the experimental comparison to other results.\medskip\\
-
-\begin{figure}[t]
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{0.9\linewidth}{0pt}}
-   %\includegraphics[width=0.8\linewidth]{egfigure.eps}
-\end{center}
-   \caption{Example of caption.  It is set in Roman so that mathematics
-   (always set in Roman: $B \sin A = A \sin B$) may be included without an
-   ugly clash.}
-\label{fig:long}
-\label{fig:onecol}
-\end{figure}
-
-\subsection{Miscellaneous}
-
-\noindent
-Compare the following:\\
-\begin{tabular}{ll}
- \verb'$conf_a$' &  $conf_a$ \\
- \verb'$\mathit{conf}_a$' & $\mathit{conf}_a$
-\end{tabular}\\
-See The \TeX book, p165.
-
-The space after \eg, meaning ``for example'', should not be a
-sentence-ending space. So \eg is correct, {\em e.g.} is not.  The provided
-\verb'\eg' macro takes care of this.
-
-When citing a multi-author paper, you may save space by using ``et alia'',
-shortened to ``\etal'' (not ``{\em et.\ al.}'' as ``{\em et}'' is a complete word.)
-However, use it only when there are three or more authors.  Thus, the
-following is correct: ``
-   Frobnication has been trendy lately.
-   It was introduced by Alpher~\cite{Alpher02}, and subsequently developed by
-   Alpher and Fotheringham-Smythe~\cite{Alpher03}, and Alpher \etal~\cite{Alpher04}.''
-
-This is incorrect: ``... subsequently developed by Alpher \etal~\cite{Alpher03} ...''
-because reference~\cite{Alpher03} has just two authors.  If you use the
-\verb'\etal' macro provided, then you need not worry about double periods
-when used at the end of a sentence as in Alpher \etal.
-
-For this citation style, keep multiple citations in numerical (not
-chronological) order, so prefer \cite{Alpher03,Alpher02,Authors14} to
-\cite{Alpher02,Alpher03,Authors14}.
-
-\begin{figure*}
-\begin{center}
-\fbox{\rule{0pt}{2in} \rule{.9\linewidth}{0pt}}
-\end{center}
-   \caption{Example of a short caption, which should be centered.}
-\label{fig:short}
-\end{figure*}
-
-%------------------------------------------------------------------------
-\section{Formatting your paper}
-
-All text must be in a two-column format. The total allowable width of the
-text area is $6\frac78$ inches (17.5 cm) wide by $8\frac78$ inches (22.54
-cm) high. Columns are to be $3\frac14$ inches (8.25 cm) wide, with a
-$\frac{5}{16}$ inch (0.8 cm) space between them. The main title (on the
-first page) should begin 1.0 inch (2.54 cm) from the top edge of the
-page. The second and following pages should begin 1.0 inch (2.54 cm) from
-the top edge. On all pages, the bottom margin should be 1-1/8 inches (2.86
-cm) from the bottom edge of the page for $8.5 \times 11$-inch paper; for A4
-paper, approximately 1-5/8 inches (4.13 cm) from the bottom edge of the
-page.
-
-%-------------------------------------------------------------------------
-\subsection{Margins and page numbering}
-
-All printed material, including text, illustrations, and charts, must be kept
-within a print area 6-7/8 inches (17.5 cm) wide by 8-7/8 inches (22.54 cm)
-high.
-Page numbers should be in footer with page numbers, centered and .75
-inches from the bottom of the page and make it start at the correct page
-number rather than the 4321 in the example.  To do this fine the line (around
-line 23)
-\begin{verbatim}
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\end{verbatim}
-where the number 4321 is your assigned starting page.
-
-Make sure the first page is numbered by commenting out the first page being
-empty on line 46
-\begin{verbatim}
-%\thispagestyle{empty}
-\end{verbatim}
-
-%-------------------------------------------------------------------------
-\subsection{Type-style and fonts}
-
-Wherever Times is specified, Times Roman may also be used. If neither is
-available on your word processor, please use the font closest in
-appearance to Times to which you have access.
-
-MAIN TITLE. Center the title 1-3/8 inches (3.49 cm) from the top edge of
-the first page. The title should be in Times 14-point, boldface type.
-Capitalize the first letter of nouns, pronouns, verbs, adjectives, and
-adverbs; do not capitalize articles, coordinate conjunctions, or
-prepositions (unless the title begins with such a word). Leave two blank
-lines after the title.
-
-AUTHOR NAME(s) and AFFILIATION(s) are to be centered beneath the title
-and printed in Times 12-point, non-boldface type. This information is to
-be followed by two blank lines.
-
-The ABSTRACT and MAIN TEXT are to be in a two-column format.
-
-MAIN TEXT. Type main text in 10-point Times, single-spaced. Do NOT use
-double-spacing. All paragraphs should be indented 1 pica (approx. 1/6
-inch or 0.422 cm). Make sure your text is fully justified---that is,
-flush left and flush right. Please do not place any additional blank
-lines between paragraphs.
-
-Figure and table captions should be 9-point Roman type as in
-Figures~\ref{fig:onecol} and~\ref{fig:short}.  Short captions should be centred.
-
-\noindent Callouts should be 9-point Helvetica, non-boldface type.
-Initially capitalize only the first word of section titles and first-,
-second-, and third-order headings.
-
-FIRST-ORDER HEADINGS. (For example, {\large \bf 1. Introduction})
-should be Times 12-point boldface, initially capitalized, flush left,
-with one blank line before, and one blank line after.
-
-SECOND-ORDER HEADINGS. (For example, { \bf 1.1. Database elements})
-should be Times 11-point boldface, initially capitalized, flush left,
-with one blank line before, and one after. If you require a third-order
-heading (we discourage it), use 10-point Times, boldface, initially
-capitalized, flush left, preceded by one blank line, followed by a period
-and your text on the same line.
-
-%-------------------------------------------------------------------------
-\subsection{Footnotes}
-
-Please use footnotes\footnote {This is what a footnote looks like.  It
-often distracts the reader from the main flow of the argument.} sparingly.
-Indeed, try to avoid footnotes altogether and include necessary peripheral
-observations in
-the text (within parentheses, if you prefer, as in this sentence).  If you
-wish to use a footnote, place it at the bottom of the column on the page on
-which it is referenced. Use Times 8-point type, single-spaced.
-
-%-------------------------------------------------------------------------
-\subsection{References}
-
-List and number all bibliographical references in 9-point Times,
-single-spaced, at the end of your paper. When referenced in the text,
-enclose the citation number in square brackets, for
-example~\cite{Authors14}.  Where appropriate, include the name(s) of
-editors of referenced books.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|c|}
-\hline
-Method & Frobnability \\
-\hline\hline
-Theirs & Frumpy \\
-Yours & Frobbly \\
-Ours & Makes one's heart Frob\\
-\hline
-\end{tabular}
-\end{center}
-\caption{Results.   Ours is better.}
-\end{table}
-
-%-------------------------------------------------------------------------
-\subsection{Illustrations, graphs, and photographs}
-
-All graphics should be centered.  Please ensure that any point you wish to
-make is resolvable in a printed copy of the paper.  Resize fonts in figures
-to match the font in the body text, and choose line widths which render
-effectively in print.  Many readers (and reviewers), even of an electronic
-copy, will choose to print your paper in order to read it.  You cannot
-insist that they do otherwise, and therefore must not assume that they can
-zoom in to see tiny details on a graphic.
-
-When placing figures in \LaTeX, it's almost always best to use
-\verb+\includegraphics+, and to specify the  figure width as a multiple of
-the line width as in the example below
-{\small\begin{verbatim}
-   \usepackage[dvips]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]
-                   {myfile.eps}
-\end{verbatim}
-}
-
-%-------------------------------------------------------------------------
-\subsection{Color}
-
-Please refer to the author guidelines on the CVPR 2019 web page for a discussion
-of the use of color in your document.
-
-%------------------------------------------------------------------------
-\section{Final copy}
-
-You must include your signed IEEE copyright release form when you submit
-your finished paper. We MUST have this form before your paper can be
-published in the proceedings.
-
-Please direct any questions to the production editor in charge of these
-proceedings at the IEEE Computer Society Press: Phone (714) 821-8380, or
-Fax (714) 761-1784.
+\section{Discussion}
+\input{sections/discussion}
 
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{egbib}
+\bibliography{bib}
 }

### 2019-09-26 paper/spad_single/sections/supplement/hardware_comparison.tex
Switching paper format, finishing up supplement figures.

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}

%% MiDaS outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/midas/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/midas/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
%% DenseDepth outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/densedepth/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densdepth_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured}
%    \vspace{-1.5em}
\end{figure*}
%% DORN outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{sections/figures/captured/dorn/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

### 2019-09-26 nyuv2/captured/dorn_analyze_all_scenes.py

@@ -72,6 +72,19 @@ def cfg():
                                                                 os.environ["CUDA_VISIBLE_DEVICES"]))
 
 
+def dorn_predict(model, rgb):
+    """
+    :param rgb: RGB image in [0, 255]
+    :return:
+    """
+    rgb_torch = torch.from_numpy(rgb.transpose(2, 0, 1).copy()).float().unsqueeze(0)
+    # print(rgb_torch.shape)
+    bgr = model.preprocess(rgb_torch)
+    # print(bgr.shape)
+    z_init_torch = model.predict(bgr, resize_output=(rgb_torch.shape[2], rgb_torch.shape[3]))
+    z_init = z_init_torch.cpu().numpy().squeeze()
+    return z_init
+
 @ex.automain
 def analyze(data_dir, calibration_file, scenes, offsets, output_dir,
             bin_width_ps, bin_width_m,
@@ -81,6 +94,7 @@ def analyze(data_dir, calibration_file, scenes, offsets, output_dir,
             ambient_max_depth_bin,
             device):
     model = DORN()
+    model.eval()
     fc_kinect, fc_spad, pc_kinect, pc_spad, rdc_kinect, rdc_spad, tdc_kinect, tdc_spad, \
         RotationOfSpad, TranslationOfSpad = extract_camera_params(calibration_file)
     # print(fc_kinect)
@@ -132,20 +146,16 @@ def analyze(data_dir, calibration_file, scenes, offsets, output_dir,
                                              RotationOfKinect, TranslationOfKinect/1e3)
         gt_z_proj_crop = gt_z_proj[crop[0]+offset[0]:crop[1]+offset[0],
                                    crop[2]+offset[1]:crop[3]+offset[1]]
-        mask_proj_crop = mask_proj[crop[0]+offset[0]:crop[1]+offset[0],
-                                   crop[2]+offset[1]:crop[3]+offset[1]]
+        gt_z_proj_crop = signal.medfilt(gt_z_proj_crop, kernel_size=5)
+        # mask_proj_crop = mask_proj[crop[0]+offset[0]:crop[1]+offset[0],
+        #                            crop[2]+offset[1]:crop[3]+offset[1]]
+        mask_proj_crop = (gt_z_proj_crop >= min_depth).astype('float').squeeze()
 
         # Process SPAD
         spad_sid = preprocess_spad(spad_single_relevant, ambient_estimate, min_depth, max_depth, sid_obj)
 
[…]

### 2019-09-26 nyuv2/captured/midas_analyze_all_scenes.py

@@ -133,8 +133,10 @@ def analyze(data_dir, calibration_file, scenes, offsets, output_dir,
                                              RotationOfKinect, TranslationOfKinect/1e3)
         gt_z_proj_crop = gt_z_proj[crop[0]+offset[0]:crop[1]+offset[0],
                                    crop[2]+offset[1]:crop[3]+offset[1]]
-        mask_proj_crop = mask_proj[crop[0]+offset[0]:crop[1]+offset[0],
-                                   crop[2]+offset[1]:crop[3]+offset[1]]
+        gt_z_proj_crop = signal.medfilt(gt_z_proj_crop, kernel_size=5)
+        # mask_proj_crop = mask_proj[crop[0]+offset[0]:crop[1]+offset[0],
+        #                            crop[2]+offset[1]:crop[3]+offset[1]]
+        mask_proj_crop = (gt_z_proj_crop >= min_depth).astype('float').squeeze()
 
         # Process SPAD
         spad_sid = preprocess_spad(spad_single_relevant, ambient_estimate, min_depth, max_depth, sid_obj)

### 2019-09-30 paper/spad_single/sections/simulation.tex
Camera alignment, distortion correction, working on supplement figure.
Updated paper figure.

@@
 %%%
-\begin{table*}
+\begin{figure*}[!t]
 \begin{center}
@@
   outperforms DenseDepth and DORN on all metrics, and even outperforms the
-  median rescaling scheme, which has access to the true median depth value.}
+  median rescaling scheme, which has access to the true median depth value. Note
+that we do not report metrics for MiDaS or MiDaS with median rescaling, as MiDaS
+does not output metric depth.}
 \end{center}
-\end{table*}
+\end{figure*}
 
@@
 \end{figure*}
-
-% \begin{figure}
-%   \includegraphics[width=\textwidth/2]{sections/figures/comparison.jpeg}
-%   \caption{\textbf{Comparing our results with other methods}}
-% \end{figure}

### 2019-09-30 nyuv2/captured/capture_utils.py

@@ -5,6 +5,9 @@ import numpy as np
 from remove_dc_from_spad import remove_dc_from_spad_edge
 import matplotlib.pyplot as plt
 
+from models.data.data_utils.sid_utils import SID
+
+
 def loadmat_h5py(file):
     output = {}
     with h5py.File(file, 'r') as f:
@@ -125,9 +128,14 @@ def save_depth_image(img, vmin, vmax, filepath):
     savefig_no_whitespace(filepath)
 
 
-def depth_imwrite(img, vmin, vmax, filepath):
-    # Scale depth to be in [0, 1]
-    img_scaled = ((img * 255)/(vmax - vmin)).astype('int')
+def depth_imwrite(img, filepath):
+    """
+    Save the image, scaling it to be in [0,255] first.
+    :param img:
+    :param filepath:
+    :return:
+    """
+    img_scaled = ((img - np.min(img)) * 255./(np.max(img) - np.min(img))).astype('int')
     cv2.imwrite(filepath + ".png", img_scaled)
 
 
@@ -147,9 +155,20 @@ def preprocess_spad(spad_single, ambient_estimate, min_depth, max_depth, sid_obj
     bin_values = (bin_edges[1:] + bin_edges[:-1]) / 2
     spad_corrected = spad_denoised * bin_values ** 2
 
+    # Scale SID object to maximize bin utilization
+    min_depth_bin = np.min(np.nonzero(spad_corrected))
+    max_depth_bin = np.max(np.nonzero(spad_corrected))
+    min_depth_pred = bin_values[min_depth_bin]
+    max_depth_pred = bin_values[max_depth_bin]
+    sid_obj_pred = SID(sid_bins=sid_obj.sid_bins,
+                       alpha=min_depth_pred,
+                       beta=max_depth_pred,
+                       offset=0.)
+
     # Convert to SID
-    spad_sid = rescale_bins(spad_corrected, min_depth, max_depth, sid_obj)
-    return spad_sid
+    spad_sid = rescale_bins(spad_corrected[min_depth_bin:max_depth_bin+1],
+                            min_depth_pred, max_depth_pred, sid_obj_pred)
+    return spad_sid, sid_obj_pred
 
 
 def load_and_crop_kinect(rootdir, calibration_file="calibration.mat", kinect_file="kinect.mat"):

### 2019-09-30 nyuv2/captured/midas_analyze_all_scenes.py

@@ -16,7 +16,7 @@ from capture_utils import loadmat_h5py, z_to_r, r_to_z, rescale_bins, normals_fr
 from models.data.data_utils.sid_utils import SID
 from models.loss import get_depth_metrics
 from remove_dc_from_spad import remove_dc_from_spad_edge
-from weighted_histogram_matching import image_histogram_match
+from weighted_histogram_matching import image_histogram_match, image_histogram_match_variable_bin
 # from spad_utils import rescale_bins
 
 from camera_utils import extract_camera_params, project_depth, undistort_img
@@ -36,21 +36,21 @@ def cfg():
     calibration_file = os.path.join(data_dir, "calibration", "camera_params.mat")
     scenes = [
         # "8_29_lab_scene",
-        "8_29_kitchen_scene",
-        "8_29_conference_room_scene",
-        "8_30_conference_room2_scene",
-        "8_30_Hallway",
-        "8_30_poster_scene",
+        # "8_29_kitchen_scene",
+        # "8_29_conference_room_scene",
+        # "8_30_conference_room2_scene",
+        # "8_30_Hallway",
+        # "8_30_poster_scene",
         "8_30_small_lab_scene",
     ]
     # Relative shift of projected depth to rgb (found empirically)
     offsets = [
         # (0, 0),
-        (-10, -8),
-        (-16, -12),
-        (-16, -12),
-        (0, 0),
-        (0, 0),
+        # (-10, -8),
+        # (-16, -12),
+        # (-16, -12),
+        # (0, 0),
+        # (0, 0),
         (0, 0)
     ]
 
@@ -63,7 +63,7 @@ def cfg():
     max_depth_bin = np.floor(9./bin_width_m).astype('int')
     min_depth = min_depth_bin * bin_width_m
     max_depth = (max_depth_bin + 1) * bin_width_m
-    sid_obj = SID(sid_bins=140, alpha=min_depth, beta=max_depth, offset=0)
+    sid_obj_init = SID(sid_bins=140, alpha=min_depth, beta=max_depth, offset=0)
     ambient_max_depth_bin = 100
 
     cuda_device = "0"                       # The gpu index to run on. Should be a string
@@ -78,7 +78,7 @@ def analyze(data_dir, calibration_file, scenes, offsets, output_dir,
             bin_width_ps, bin_width_m,
[…]

### 2019-09-30 nyuv2/captured/weighted_histogram_matching.py

@@ -95,6 +95,21 @@ def image_histogram_match(init, gt_hist, weights, sid_obj):
     return pred, (init_index, init_hist, pred_index, pred_hist, T_count)
 
 
+def image_histogram_match_variable_bin(init, gt_hist, weights, sid_obj_init, sid_obj_pred):
+    weights = weights * (np.sum(gt_hist) / np.sum(weights))
+    init_index = np.clip(sid_obj_init.get_sid_index_from_value(init),
+                         a_min=0, a_max=sid_obj_init.sid_bins - 1)
+    init_hist, _ = np.histogram(init_index, weights=weights, bins=range(sid_obj_init.sid_bins + 1))
+    if (gt_hist < 0).any():
+        print("Negative values in gt_hist")
+        raise Exception()
+    T_count = find_movement(init_hist, gt_hist)
+    pred_index = move_pixels_vectorized(T_count, init_index, weights)
+    pred = sid_obj_pred.get_value_from_sid_index(pred_index)
+    pred_hist, _ = np.histogram(pred_index, weights=weights, bins=range(len(gt_hist) + 1))
+    return pred, (init_index, init_hist, pred_index, pred_hist, T_count)
+
+
 def image_histogram_match_lin(init, gt_hist, weights, min_depth, max_depth):
     weights = weights * (np.sum(gt_hist) / np.sum(weights))
     n_bins = len(gt_hist)

### 2019-09-30 nyuv2/gt_hist_matching/MiDaSModel.py

@@ -11,15 +11,17 @@ def get_midas(model_path, device="cpu"):
     return model
 
 
-def midas_idepth_predict(model, img, device):
+def midas_predict(model, img, depth_range, device):
     """
     Predict depth from RGB
     :param model: a midas model
-    :param img: RGB image in 0-1 (numpy)
+    :param img: RGB image in 0-1
+    :param depth_range: Range of output depths (e.g. (0., 10) for NYUv2)
     :param device: torch.device object to run on
     :return: Inverse Depth image, same size as RGB image, scaled to be in the output range.
     """
-
+    assert depth_range[0] < depth_range[1]
+    assert depth_range[0] >= 0.
     img_input = utils.resize_image(img)
     img_input = img_input.to(device)
 
@@ -28,13 +30,6 @@ def midas_idepth_predict(model, img, device):
         idepth = model.forward(img_input)
 
     idepth = utils.resize_depth(idepth, img.shape[1], img.shape[0])
-    return idepth
-
-
-def midas_predict(model, img, depth_range, device):
-    assert depth_range[0] < depth_range[1]
-    assert depth_range[0] >= 0.
-    idepth = midas_idepth_predict(model, img, depth_range, device)
 
     idepth_min = idepth.min()
     idepth_max = idepth.max()
@@ -45,34 +40,5 @@ def midas_predict(model, img, depth_range, device):
     idepth_scaled = (idepth_range[1] - idepth_range[0]) * \
                     (idepth - idepth_min) / (idepth_max - idepth_min) + \
                     idepth_range[0]
-    return idepth_scaled
-
-
-def midas_gt_predict(model, img, gt, crop, device):
-    """
-    Original MiDaS method for scaling the raw prediction using least squares.
-    :param model:
-    :param img:
-    :param gt:
-    :param device:
-    :return:
-    """
-    assert (gt > 0.).all()
-    idepth = midas_idepth_predict(model, img, device)
-    # print(idepth.shape)
-    idepth = idepth[crop[0]:crop[1], crop[2]:crop[3]]
-    # Use Least Squares to align the prediction to ground truth
-
-    igt = 1./gt
-
-    idepth_vec = np.hstack((idepth.reshape(-1, 1), np.ones((np.size(idepth), 1))))
-    igt_vec = igt.reshape(-1, 1)
[…]

### 2019-09-30 nyuv2/gt_hist_matching/run_midas.py

@@ -14,7 +14,7 @@ import numpy as np
 import pandas as pd
 
 # Model
-from MiDaSModel import get_midas, midas_gt_predict
+from MiDaSModel import get_midas, midas_predict
 # Dataset
 from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
 
@@ -81,11 +81,19 @@ def main(model_path,
                 entry_list.append(entry)
                 print("Evaluating {}".format(data["entry"][0]))
                 # pred, pred_metrics = model.evaluate(data, device)
-                pred = midas_gt_predict(model, data["rgb"].cpu().numpy().squeeze(),
-                                        data["depth_cropped"].cpu().numpy().squeeze(), crop, device)
+                print(torch.max(data["rgb_cropped"]))
+                pred = midas_predict(model,
+                                     data["rgb_cropped"].cpu().numpy().squeeze()/255.,
+                                     depth_range=(1e-1, 10.),
+                                     device=device)
+
+                # pred = midas_gt_predict_masked(model, data["rgb"].cpu().numpy().squeeze(),
+                #                                data["rawdepth_cropped"].cpu().numpy().squeeze(),
+                #                                data["mask_cropped"].cpu().numpy().squeeze(),
+                #                                crop, device)
 
                 pred = torch.from_numpy(pred).unsqueeze(0).unsqueeze(0).float()
-                pred_metrics = get_depth_metrics(pred, data["depth_cropped"], torch.ones_like(pred))
+                pred_metrics = get_depth_metrics(pred, data["rawdepth_cropped"], data["mask_cropped"])
                 print(pred_metrics)
                 for j, metric_name in enumerate(metric_list[:-1]):
                     metrics[i, j] = pred_metrics[metric_name]

### 2019-09-30 nyuv2/midas/evaluate.py

@@ -68,10 +68,11 @@ def main(model_path,
 
 if __name__ == '__main__':
     model_path = os.path.join("MiDaS", "model.pt")
-    crop = (20, 460, 24, 616)   # Standard crop
+    # crop = (20, 460, 24, 616)   # Standard crop
+    crop = (0, 480, 0, 640)       # No crop
 
     output_dir = "results"
-    cuda_device = "0"  # The gpu index to run on. Should be a string
+    cuda_device = "3"  # The gpu index to run on. Should be a string
     os.environ["CUDA_VISIBLE_DEVICES"] = cuda_device
     device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
     print("using device: {} (CUDA_VISIBLE_DEVICES = {})".format(device,

### 2019-09-30 nyuv2/midas/lsq_scale_shift.py

@@ -1,0 +1,7 @@
+import numpy as np
+
+def lsq_scale_shift(pred, target, mask):
+    pred_vec= np.hstack((pred[mask > 0].reshape(-1, 1), np.ones((np.size(pred[mask > 0]), 1))))
+    target_vec = target[mask > 0].reshape(-1, 1)
+    scaleshift, _, _, _ = np.linalg.lstsq(pred_vec.T.dot(pred_vec), pred_vec.T.dot(target_vec), rcond=None)
+    return scaleshift

### 2019-10-02 paper/cvpr2020/sections/hardware.tex
Cleaning up paper folder.

\subsection{Setup}
\begin{figure}[H]
  \includegraphics[width=\textwidth/2]{sections/figures/prototype_single_col.png}
  \caption{Prototype scanning setup. The pulsed light from the laser travels
    through a beam splitter before being guided by the galvo to the scene.
    Returning light is measured by the single-pixel SPAD. The RGB camera of a
    Kinect v2 is used to capture the monocular RGB image (the depth camera is
    not used)}
  \label{fig:prototype}
\end{figure}

### 2019-10-02 paper/cvpr2020/sections/introduction.tex
Cleaning up paper folder.

--- 2019-08-27 paper/spad_single/sections/introduction.tex
@@
-\subsection{Introduction}
 Estimating depth from images is an important open problem with applications
@@
 
+\begin{figure}
+  \caption{Our method uses the SPAD's histogram to rescale the initial depth
+    estimate from the CNN to align with the ground truth depth.}
+\end{figure}
 Our method is not without limitations. It still requires a laser and

### 2019-10-02 paper/cvpr2020/supplement.tex
Cleaning up paper folder.

--- 2019-09-18 paper/spad_single/cvpr2019/supplement.tex
@@
 \maketitle
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_18_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_21_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_25_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_285_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_42_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_52_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_53_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_103_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_224_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_226_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_352_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_362_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_379_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_107_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_187_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_140_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_244_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_527_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_529_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_219_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_329_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_346_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_616_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_390_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_412_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_420_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_428_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_457_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_477_comparison.png}
-  \caption{Results on DenseDepth}
-\end{figure*}
-%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_499_comparison.png}
-%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_258_comparison.png}
-%   \includegraphics[height=3cm]{sections/figures/comparison/densedepth_341_comparison.png}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_8_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_14_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_15_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_23_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_26_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_63_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_67_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_140_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_170_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_522_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_548_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_569_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_585_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_633_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_105_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_220_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_252_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_259_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_178_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_219_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_280_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_293_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_313_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_413_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_477_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_502_comparison.png}
-%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
-%  \includegraphics[width=\textwidth]{sections/figures/comparison/dorn_428_comparison.png}
-  \caption{Results on DORN}
-\end{figure*}
-% Densedepth:
-% - Office: 18, 21
-% - Bathroom: 25, 194, 285
-% - Bookstore: 42
-% - Kitchen: 52, 53, 103, 224, 226, 352, 362, 379
-% - Office: 107, 187
-% - Living Room: 140, 244, 527, 529
-% - Dining Room: 219, 329, 346, 616
-% - Bedroom: 390, 412, 420, 428, 457*, 468*, 477, 499
-% Failure Cases: 258, 338(?), 341, 537 649 (minor)
-% 
-% DORN:
-% - Office: 8, 14, 15, 23, 26
-% - Living room: 63, 67, 140, 170, 522, 548, 569, 585, 633
-% - Office: 105, 220, 252, 259* (interesting)
-% - Kitchen: 178
-% - Dining Room: 219
-% - Bathroom: 280, 293, 313
-% - Bedroom: 413, 477, 502
-% 
-% Failure Cases: 96, 266(?)
-
+% \input{sections/supplement/simulation_comparison.tex} 
+\input{sections/supplement/hardware_comparison.tex}
 \end{document}

### 2019-10-03 paper/cvpr2020/sections/discussion.tex
pass over introduction

short summary

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Limitations}

\begin{itemize}
	\item laser power vs range tradeoff; may be limited to short--medium range
	\item if the monocular depth estimation fails, so will the histogram matching 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}

### 2019-10-03 paper/cvpr2020/sections/introduction.tex
pass over introduction

@@
-Estimating depth from images is an important open problem with applications
-to robotics, autonomous driving, and medical imaging. Dense depth maps are
-useful precursors to higher-level scene understanding tasks such as pose
-estimation and object detection.
+%Estimating depth from images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
+Dense depth maps are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.
 
-However, traditional approaches to depth estimation, such as stereo, suffer from lower performance
-when confronted with small angles or faraway objects.
-More exotic approaches use FMCW or time-of-flight LiDAR technologies,
-but these approaches are currently expensive and bulky.
+Depth sensing is vital for the success of many computer vision tasks, such as navigation~\cite{geiger2013vision}, robotic vision, semantic segmentation~\cite{ren2012rgb,silberman2012indoor,gupta2013perceptual}, 3D object detection~\cite{shrivastava2013building,lin2013holistic,gupta2014learning,song2014sliding,song2016deep}, and 3D object classification~\cite{wu20153d,maturana2015voxnet,qi2016volumetric}.
+However, traditional depth sensing techniques require multiple cameras, active illumination, camera motion, or other aspects that may make their deployment challenging.
 
-The most promising solution to these issues uses deep learning and 
-convolutional neural networks to perform \textit{monocular depth estimation},
-estimating dense depth maps from single RGB images. 
-However, this problem is underconstrained due to \textit{inherent scale ambiguity}, the unresolvable
-tradeoff between size and distance in single images. In practice, this issue commonly
-manifests itself in many monocular depth networks, and indeed, 
-Wonka et. al. (cite) showed that if the method has oracle access to the ground truth
-median depth, then correcting the output of the CNN to match this median
-depth produces better depth maps both qualitatively and quantitatively.
+One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE)~\cite{Saxena2006,Eigen2014,Laina2016,Fu2018,Alhashim2018}.
+Given a single RGB image, a monocular depth estimator uses pictorial cues in the image, such as perspective, occlusion, shading, and relative object size, to predict a dense depth map of the scene.
+While neural networks solving the MDE problem have significantly improved over the last years, this remains an ill-posed inverse problem with inherent scale ambiguity.
+Pictorial cues alone allow for the ordinal depth, that is the relative ordering of objects in a scene, to be robustly estimated~\cite{Eigen2014,Fu2018}.
+However, MDE approaches to date are incapable of reliably estimating absolute distances of a scene.
+Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle access to the ground truth median scene depth, then correcting the output of the estimator to match this median depth produces accurate absolute depth maps.
 
-In this paper, we go further and show that by augmenting the RGB image with a histogram of
-global image depths, we can achieve substantially improved performance
-(and generalizability) over state-of-the-art monocular depth
-estimators. By performing an exact, weighted histogram matching on the output
-depth map of the depth estimator, we can match the depth histogram of the scene
-to the depth histogram of our estimate. This histogram matching is described in
-(cite) and is flexible enough to accommodate different pixel reflectances in the
-RGB image. Finally, this histogram can be captured
-relatively inexpensively using only a single pixel single-photon avalanche diode
-(SPAD) and pulsed laser illumination diffused over the field of view, 
-representing a significant improvement in cost and simplicity over multi-pixel LiDAR
-arrays with expensive scanning mechanisms. It is
-worth noting that SPADs of this type have already made their way into existing
-smartphones, such as the iPhone X, and will likely play a role in future mobile sensing platforms as well.
+%For example, a larger object at a far distance to the camera results in the same 2D camera image as a smaller object of the same type that is closer to the camera.
+Therefore, MDE approaches to date are incapable of reliably estimating absolute distances of a scene.
+Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle access to the ground truth median depth, then correcting the output of the CNN to match this median depth produces accurate absolute depth maps both qualitatively and quantitatively.
+
+% move to discussion
+%However, traditional approaches to depth estimation, such as stereo, suffer from lower performance when confronted with small angles or faraway objects.
+More exotic approaches use FMCW or time-of-flight LiDAR technologies, but these approaches are currently expensive and bulky.
+
+%The most promising solution to these issues uses deep learning and convolutional neural networks to perform \textit{monocular depth estimation}, estimating dense depth maps from single RGB images.
+However, this problem is underconstrained due to \textit{inherent scale ambiguity}, the unresolvable tradeoff between size and distance in single images.
+In practice, this issue commonly manifests itself in many monocular depth networks, and indeed, Wonka et.
+al.
+(cite) showed that if the method has oracle access to the ground truth median depth, then correcting the output of the CNN to match this median depth produces better depth maps both qualitatively and quantitatively.
+
+While access to ground truth depth is impossible in a realistic scenario, one of our primary insights is that low-cost sensors capable of capturing aggregated depth information of a scene are readily available and already part of the sensor suite of many cellphones.
+These proximity sensors, for example deployed in Apple's iPhones, contain a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense the distance of one ray direction in front of the camera.
+Coupled with high-power laser sources, SPADs also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}.
+Whereas individual SPADs are easy to fabricate and sufficiently cost effective to be deployed in consumer electronics, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost.
+A single or a few SPADs could certainly be used together with a raster scanning mechanism, which is typical for LiDAR systems, but the mechanical complexity of such a system prevents usage in mobile devices and the inherent tradeoff between scan speed and resolution makes it difficult to capture high-resolution depth maps at high framerates.
+
+Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way.
+Rather than optically focusing them to record the distance along one ray, we diffuse the emitted light and the detector over the entire scene.
+This allows us to directly capture the integrated depth of the scene---a depth histogram.
+Technically, a diffused SPAD does not record a true depth histogram but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise.
+However, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram while keeping in mind that they are not exactly the same.
+
+%In this paper, we go further and show that by augmenting the RGB image with a histogram of global image depths, we can achieve substantially improved performance (and generalizability) over state-of-the-art monocular depth estimators.
+By performing an exact, weighted histogram matching on the output depth map of the depth estimator, we can match the depth histogram of the scene to the depth histogram of our estimate.
+This histogram matching is described in (cite) and is flexible enough to accommodate different pixel reflectances in the RGB image.
+Finally, this histogram can be captured relatively inexpensively using only a single pixel single-photon avalanche diode (SPAD) and pulsed laser illumination diffused over the field of view, representing a significant improvement in cost and simplicity over multi-pixel LiDAR arrays with expensive scanning mechanisms.
+It is worth noting that SPADs of this type have already made their way into existing smartphones, such as the iPhone X, and will likely play a role in future mobile sensing platforms as well.
 
@@
 \end{figure}
-Our method is not without limitations. It still requires a laser and
-single-pixel LiDAR detector, and as such, is sensitive to ambient photons. Being 
-a variant of histogram matching, our method is unable to transpose the
-values of pixels (i.e. if pixel $a$ is farther
-than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
-In other words, our method is not able to resolve ordinal depth errors
-(errors where an object is wrongly placed closer or farther
-relative to another object). Finally, our method is non-differentiable, and is
-therefore unsuitable for end-to-end optimization of multi-part networks.
 
+% move to discussion
+%Our method is not without limitations.
+It still requires a laser and single-pixel LiDAR detector, and as such, is sensitive to ambient photons.
+Being  a variant of histogram matching, our method is unable to transpose the values of pixels (i.e.
+if pixel $a$ is farther than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
+In other words, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object).
+Finally, our method is non-differentiable, and is therefore unsuitable for end-to-end optimization of multi-part networks.
+
+In this paper, we develop a sensor fusion strategy that processes the ordinal depth computed by some monocular depth estimator to match the output of the diffused SPAD.
+With extensive simulations, we demonstrate that our approach achieves substantial improvements in the quality of the estimated depth maps, comparable to the oracle median depth, disregarding which specific depth estimator is used.
+Moreover, we build an RGB-SPAD camera prototype and again demonstrate that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes than a monocular depth estimator alone.
+With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.
+Specifically, we make the following contributions:
+%
 \begin{itemize}
-	\item We introduce the idea of augmenting an RGB camera with a global depth 
-    histogram to address scale ambiguity error in monocular depth estimators.	
-  \item We analyze our approach on indoor scenes using the NYU Depth v2 dataset.
-    We demonstrate that our approach is able to resolve scale ambiguity while
-    being fast and easy to implement.
-	\item We build a hardware prototype and evaluate the efficacy of our
-    approach on real-world data, assessing both the the quality and the ability of our method
-    to help generalization of monocular depth estimators across scene types. 
+	\item We introduce the idea of augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
+  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
+	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types.
 \end{itemize}

### 2019-10-03 nyuv2/captured/analyze_all_scenes.py
Teaser figure.

@@ -1,0 +1,252 @@
+#! /usr/bin/env python3
+import os
+import cv2
+import numpy as np
+import scipy.io as sio
+import scipy.signal as signal
+import torch
+
+# Models
+from DenseDepthModel import DenseDepth
+from DORN import DORN
+from MiDaSModel import get_midas, midas_predict
+from capture_utils import loadmat_h5py, z_to_r, r_to_z, rescale_bins, normals_from_depth, \
+                          get_closer_to_mod, load_spad, preprocess_spad, load_and_crop_kinect, get_hist_med, \
+                          depth_imwrite, savefig_no_whitespace
+from models.data.data_utils.sid_utils import SID
+from models.loss import get_depth_metrics
+from remove_dc_from_spad import remove_dc_from_spad_edge
+from weighted_histogram_matching import image_histogram_match, image_histogram_match_variable_bin
+# from spad_utils import rescale_bins
+
+from camera_utils import extract_camera_params, project_depth, undistort_img
+
+from models.core.checkpoint import safe_makedir
+
+import h5py
+import matplotlib.pyplot as plt
+
+from sacred import Experiment
+
+ex = Experiment("midas_analyze_all_scenes")
+
+@ex.config
+def cfg():
+    data_dir = "data"
+    calibration_file = os.path.join(data_dir, "calibration", "camera_params.mat")
+    # Offset is a pixel-wise offset to adjust the crop and compensate for calibration drift
+    # bin_width_ps is the bin width in picoseconds of the SPAD for that particular scene
+    # min_r and max_r are set to reject direct reflections off the beam splitter.
+    scenes = {
+        "8_29_kitchen_scene": {"offset": (-10, -8), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_29_conference_room_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_conference_room2_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_poster_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
[…]

### 2019-10-03 nyuv2/captured/matlab/inpaint_captured.m

@@ -1,0 +1,33 @@
+% Inpainting the small realsense dataset
+% Parameters
+addpath('nyu_utils');
+rootdir = "../figures";
+models = {'midas'}
+scenes = {"8_29_kitchen_scene", "8_29_conference_room_scene", "8_30_conference_room2_scene", "8_30_Hallway", ...
+          "8_30_poster_scene", "8_30_small_lab_scene", "8_31_outdoor3"}
+n_images = [4, 3, 3, 4, 4, 4, 5];
+%maxDepth = 10;
+
+% Inpaint and save
+for m = 1:length(models)
+    for s = 1:length(scenes)
+        disp(join(["Inpainting ", models{m}, "[", scenes{s}, "]"], ""))
+        sceneDir = join([rootdir, models{m}, scenes{s}], "/");
+        % Load Images
+        rgbFile = join([sceneDir, "rgb_cropped.png"], "/");
+        rgb = double(imread(rgbFile));
+        depthFile = join([sceneDir, "gt_z_proj_crop.png"], "/");
+        rawDepth = double(imread(depthFile));
+        % Inpaint depth using depth and rgb
+    %     rawDepthCropped = crop_image(rawDepth);
+        depthFilled = fill_depth_colorization(rgb, rawDepth);
+%        depthFilled(depthFilled > maxDepth) = maxDepth;
+
+        % Save images
+        depthFilledFile = join([sceneDir, "gt_z_proj_crop_filled.png"], "/");
+        depthFilledImg = uint16(depthFilled);
+        imwrite(depthFilledImg, depthFilledFile)
+    end
+end
+
+

### 2019-10-03 paper/cvpr2020/main.tex
slight change

--- 2019-09-26 paper/spad_single/cvpr2020/egpaper_for_review.tex
@@
 % Include other packages here, before hyperref.
-\usepackage{booktabs}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{bm}
-\usepackage{multirow}
-\usepackage{float}
-\usepackage[utf8x]{inputenc}
-\input{mark_defs.tex}
+%\usepackage{booktabs}
+%\usepackage{caption}
+%\usepackage{subcaption}
+%\usepackage{array}
+%\usepackage{tabularx}
+%\usepackage{bm}
+%\usepackage{multirow}
+%\usepackage{float}
+%\usepackage[utf8x]{inputenc}
+
+%\input{mark_defs.tex}
 
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-%\cvprfinalcopy % *** Uncomment this line for the final submission
+
+% \cvprfinalcopy % *** Uncomment this line for the final submission
 
@@
 
+\graphicspath{{"H:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}{}}
+
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
+\ifcvprfinal\pagestyle{empty}\fi
 \begin{document}
 
-\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching}
+%%%%%%%%% TITLE
+\title{Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD}
 
@@
 \begin{abstract}
-   The ABSTRACT is to be in fully-justified italicized text, at the top
-   of the left-hand column, below the author and affiliation
-   information. Use the word ``Abstract'' as the title, in 12-point
-   Times, boldface type, centered relative to the column, initially
-   capitalized. The abstract is to be in 10-point, single-spaced type.
-   Leave two blank lines after the Abstract, then begin the main text.
-   Look at previous CVPR abstracts to get a feel for style and length.
+abstract
 \end{abstract}
+
+%%%%%%%%% BODY TEXT
+
 \section{Introduction}
+\label{sec:intro}
 \input{sections/introduction}
@@
 \section{Related Work}
+\label{sec:related}
 \input{sections/related}
@@
 \section{Method}
+\label{sec:method}
 \input{sections/method}
 
-\section{Simulation}
+\section{Evaluation and Assessment}
+\label{sec:evaluation}
 \input{sections/simulation}
 
-\section{Hardware Prototype}
+\section{Experimental Demonstration}
+\label{sec:prototype}
 \input{sections/hardware}
@@
 \section{Discussion}
+\label{sec:discussion}
 \input{sections/discussion}
@@
 \bibliographystyle{ieee_fullname}
-\bibliography{bib}
+\bibliography{references}
 }

### 2019-10-04 paper/cvpr2020/main.tex
New script for syncing figures, added gdrive to graphics path

@@
 % Include other packages here, before hyperref.
-%\usepackage{booktabs}
-%\usepackage{caption}
-%\usepackage{subcaption}
-%\usepackage{array}
-%\usepackage{tabularx}
-%\usepackage{bm}
-%\usepackage{multirow}
-%\usepackage{float}
-%\usepackage[utf8x]{inputenc}
-
-%\input{mark_defs.tex}
+\usepackage{booktabs}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{array}
+\usepackage{tabularx}
+\usepackage{bm}
+\usepackage{multirow}
+\usepackage{float}
+\usepackage[utf8x]{inputenc}
+\input{mark_defs.tex}
 
@@
 
-\graphicspath{{"H:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}{}}
-
+\graphicspath{{"H:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}
+    {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready

### 2019-10-04 paper/cvpr2020/sections/related.tex

--- 2019-08-27 paper/spad_single/sections/related.tex
@@
 \paragraph{Monocular Depth Estimation}
-Previous non-deep approaches used Markov Random Fields \cite{Saxena2006},
-geometric approaches \cite{Hoiem2005}, and non-parametric, SIFT-based methods
-\cite{Karsch2014}.
-More recently, deep neural networks have been applied to the problem of estimating depth from a
-single image. Eigen et. al. \cite{Eigen2014} use a multi-scale neural network to
-predict depth at multiple scales. Godard et. al. \cite{Godard2017} use an
-unsupervised approach (i.e. that does not require ground truth depth) that
-trains a network using stereo pairs to produce disparity maps from
-single images, which can then be used to recover the depth. Fu et. al.
-\cite{Fu2018} combined a logarithmic depth discretization scheme with a novel
-ordinal regression approach. Various experiments using different types of
-encoder networks (e.g. ResNet, DenseNet) \cite{Laina2016} \cite{Alhashim2018}
-have also been employed with some success, as have approaches mixing deep
-learning with conditional random fields \cite{Xu2017}, and attention-based
-approaches \cite{Xu2018} \cite{Hao2018}.
+%
+Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}.
+More recently, deep neural networks have been applied to this problem.
+For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
+predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combined a logarithmic depth discretization scheme with an ordinal regression loss function.
+Various experiments using different types of encoder networks (e.g.
+ResNet, DenseNet)~\cite{Laina2016,Alhashim2018} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Xu2018,Hao2018}.
+Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.
 
-Despite achieving remarkable success on the monocular depth estimation task, none of these methods are able to
-resolve inherent scale ambiguity in a principled manner (being monocular in nature). By combining a monocular
-depth estimator with a depth histogram, our method is able to do so.
-
-% \begin{itemize}
-% 	\item summary of architectures and cost functions: u-net type architecture with reverse huber loss
-% 	\item what we do: same thing, but augment with global hints (inspired by these approaches, we do ...)
-% \end{itemize}
+Despite achieving remarkable success on estimating ordinal depth from a single image, none of these methods are able to resolve inherent scale ambiguity in a principled manner.
+We introduce a new approach that leverages existing monocular depth estimation networks but disambiguates their output with depth histogram-like measurements obtained from a single, diffused SPAD.
 
@@
 \paragraph{Depth Imaging and Sensor Fusion with SPADs}
+%
+Emerging single-photon LiDAR systems use single photon avalanche diodes (SPADs) to record the time of flight of individual photons.
+Whereas the SPAD detectors can be fabricated using standard CMOS processes, the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate in a cost effective way.
+For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Lamb2010,Kirmani:2014,pawlikowska2017single,Li:2019}.
+Unfortunately, scanning a scene at high resolution and high framerates is challenging and scanners are expensive, difficult to calibrate, and prone to mechanical failure.
+To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2016linospad,burri2017linospad,OToole2017}.
+
+WORK IN PROGRESS
+
 Previous work (see \cite{Horaud2016} for a survey) has been able to use

### 2019-10-04 paper/cvpr2020/main.tex
pass over related and teaser caption

@@
 
-\graphicspath{{"H:/Shared drives/Stanford Computational
-    Imaging/Projects/single_spad_depth/figures/"}
-    {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
+\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready

### 2019-10-04 paper/cvpr2020/sections/introduction.tex
Teaser figure.
New script for syncing figures, added gdrive to graphics path
pass over related and teaser caption

@@
-%Estimating depth from images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
+Estimating depth from images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
 Dense depth maps are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.
@@
 
+\begin{figure}
+  \includegraphics[width=\linewidth]{teaser.pdf}
+  \caption{Monocular depth estimation predicts a depth map (upper right) from a single RGB image (upper left).
+Unfortunately, this is an ill-posed problem subject to ambuguity that prevents reliable absolute depth estimation (error, inset image).
+The proposed method uses the transient measured by a diffused SPAD (lower left), which closely resembles the shape of a histogram of the ground truth depth map, to correct the output of the depth estimation and optimize the quality of the estimated absolute depth.}
+  \label{fig:teaser}
+\end{figure}
+
 While access to ground truth depth is impossible in a realistic scenario, one of our primary insights is that low-cost sensors capable of capturing aggregated depth information of a scene are readily available and already part of the sensor suite of many cellphones.
@@
 It is worth noting that SPADs of this type have already made their way into existing smartphones, such as the iPhone X, and will likely play a role in future mobile sensing platforms as well.
-
-\begin{figure}
-  \caption{Our method uses the SPAD's histogram to rescale the initial depth
-    estimate from the CNN to align with the ground truth depth.}
-\end{figure}
 

### 2019-10-04 paper/cvpr2020/sections/related.tex
pass over related and teaser caption

@@
 Emerging single-photon LiDAR systems use single photon avalanche diodes (SPADs) to record the time of flight of individual photons.
-Whereas the SPAD detectors can be fabricated using standard CMOS processes, the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate in a cost effective way.
+Whereas SPAD detectors can be fabricated using standard CMOS processes, the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost.
 For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Lamb2010,Kirmani:2014,pawlikowska2017single,Li:2019}.
-Unfortunately, scanning a scene at high resolution and high framerates is challenging and scanners are expensive, difficult to calibrate, and prone to mechanical failure.
-To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2016linospad,burri2017linospad,OToole2017}.
+Unfortunately, this makes it challenging to scan dynamic scenes at high resolution and scanners can also be expensive, difficult to calibrate, and prone to mechanical failure.
+To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2016linospad,burri2017linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}.
+Yet, single-pixel SPADs remain the only viable option for low cost consumer devices today.
 
-WORK IN PROGRESS
+The proposed method uses a single-pixel SPAD, but rather than aiming it at one point in the scene as proximity sensors do, we propose to diffuse it along with the pulsed light source.
+This is a unique configuration that allows us capture a transient that closely resembles the shape of the depth histogram of the scene.
+We develop a sensor fusion algorithm to combine the output of a monocular depth estimator and this depth histogram to achieve more reliable absolute depth estimation.
+While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, in that work an intensity image was primarily used to guide a denoising and upsampling step of recorded 2D SPAD array.
 
-Previous work (see \cite{Horaud2016} for a survey) has been able to use
-single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in
-tandem with various scanning or DMD devices to capture 3D volumes of photon arrivals
-that can be used to reconstruct depth. Lindell et. al. \cite{Lindell2018} use a
-LinoSPAD and epipolar scanline and fuse the SPAD data with an RGB image to
-produce high-quality depth.  Our approach uses a single pixel SPAD but
-does not require any scanning or DMD mechanism.
+%Previous work (see \cite{Horaud2016} for a survey) has been able to use single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in tandem with various scanning or DMD devices to capture 3D volumes of photon arrivals that can be used to reconstruct depth.
+Lindell et.
+al.
+\cite{Lindell2018} use a LinoSPAD and epipolar scanline and fuse the SPAD data with an RGB image to produce high-quality depth.
+Our approach uses a single pixel SPAD but does not require any scanning or DMD mechanism.
 
-A parallel approach called 3D flash LiDAR uses a laser with an optical diffuser
-as the illumination source and a 2D array of SPADs to capture the 3D volume
-\cite{Stoppa2007, Niclass2005}. Such arrays are capable of reconstructing high
-quality depth but remain relatively low resolution. Other arrays are able to
-achieve higher resolution, but suffer from low fill factor \cite{Veerappan2011} or
-sacrifice per-pixel TDC \cite{Zhang2018}.
+%A parallel approach called 3D flash LiDAR uses a laser with an optical diffuser
+%as the illumination source and a 2D array of SPADs to capture the 3D volume
+%\cite{Stoppa2007, Niclass2005}. Such arrays are capable of reconstructing high
+%quality depth but remain relatively low resolution. Other arrays are able to
+%achieve higher resolution, but suffer from low fill factor \cite{Veerappan2011} or
+%sacrifice per-pixel TDC \cite{Zhang2018}.
 
-Our approach uses flash LiDAR but requires only a single pixel 
-sensor.
-(Still need to flesh out this section more with some higher resolution SPAD arrays)
 % \begin{itemize}

### 2019-10-04 paper/cvpr2020/sections/method.tex
New script for syncing figures, added gdrive to graphics path
pass over first part of methods section

--- 2019-08-27 paper/spad_single/sections/method.tex
@@
-In this section, we describe the measurement model for a single-pixel
-time-of-flight lidar sensor under diffuse, pulsed laser illumination. 
-\subsection{Measurement Model}
-Consider a laser which emits a pulse at time $t = 0$ with time-varying intensity
-$g(t)$ uniformly illuminating some 3D scene. We parameterize the geometry of the
-scene as a height map $z(x, y)$.
-Neglecting albedo and falloff effects, an ideal detector counting photon events
-from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record
+Monocular depth estimation is a well-explored, yet active area of research (see Sec.~\ref{sec:related}).
+Any network trained for the MDE task takes as input an RGB image and estimates the depth map of the scene.
+Our approach augments existing MDE networks but is agnostic to the specific type of depth estimator.
+Indeed we show in Section~\ref{sec:evaluation} that our histogram matching technique equally improves a variety of different pre-trained estimators.
+In the remainder of this section, we therefore focus on modeling the image formation of a diffused single-photon avalanche diode (SPAD) and develop an approach to correcting an estimated depth map to match the global scene information captured by the SPAD.
 
+%In this section, we describe the measurement model for a single-pixel time-of-flight lidar sensor under diffuse, pulsed laser illumination.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Image Formation Model of a Diffused SPAD}
+
+Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying intensity $g(t)$ illuminating some 3D scene.
+We parameterize the geometry of the scene as a height map $z(x, y)$, where each of the 3D points has also some unknown reflectivity $\alpha$ at the wavelength of the laser.
+Ignoring interreflections of the emitted light within the scene, a single-pixel diffused SPAD then integrates all the light scattered back from the scene towards the detector as
+%
 \begin{equation}
-  \lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt \label{single_loc_spad} 
+	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \alpha \left( x,y \right) g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
+	\label{eq:pulse_integral} 
 \end{equation}  
+%
+where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the diffuser.
+In this formulation, $\alpha$ also absorbs the square distance falloff of light and we assume that the diffuser spreads light uniformly over all angles.
+Each time such a light pulse is emitted into the scene and scattered back to the detector, the single-pixel SPAD time-stamps up to one of the returning photons with some probability.
+This is not necessarily the first returning photon.
+The process is repeated millions of times per second with the specific number of emitted pulsed being controlled by the repetition rate of the laser, which is typically adjusted to match the deadtime of the SPAD~\cite{Heide:2018}.
+Each detected photon arrival event is discretized into a histogram $h$ of the form
+%
+\begin{equation}
+  h[n] \sim \mathcal{P} \left( \eta \int_{n\Delta t}^{(n+1)\Delta t} \left(f * s \right) \left( t \right)  dt + b \right),	
+	\label{eq:spad_measurements}
+\end{equation}
+%
+where $(n\Delta t, (n+1) \Delta t)$ models the $n^{th}$ time interval of the temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$ is a function that models the temporal uncertainty in the detector, and $b$ represents ambient background light and falsely detected photons known as dark count.
+As derived in previous work, the combination of signal, background, and noise can be modeled as an inhomogeneous Poisson process $\mathcal{P}$~\cite{Kirmani:2014,Shin2015}.
 
-where $c$ is the speed of light, and $f$ is a function that models the temporal uncertainty in the
-detector. Single-photon avalanche diodes (SPADs) are highly sensitive
-photodetectors which are able to record single photon events with high temporal
-precision \cite{Stuff}. Since the event corresponding to the detection of a
-photon can be described with a Bernoulli random variable,
-the total number of accumulated photons in this time interval follows a Poisson
-distribution according to
-
-\begin{equation}
-  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
-\end{equation}
-
-where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
-photon counts due to the reflectance $r(x,y)$ of the scene and due to the
-inverse square falloff $1/z(x,y)^2$.
-In addition, $\eta$ is the detection probability of a photon
-triggering a SPAD event, and $b = \eta a + d$ is the average number of background detections resulting
-from ambient photons $a$
-and erroneous ``dark count'' events $d$ resulting from noise within the SPAD.
-% \newpage
-% \begin{table*}[htbp]
-%   \begin{center}
-  %   \begin{tabularx}{\linewidth}{*{2}{X}}
-  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rgb.png} &
-  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rawdepth.png} \\
-  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/depth_hist.png} &
-  %     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/spad_hist.png} \\
-  %   \end{tabularx}
-  % \end{center}
-  % \caption{Sample Image. Top Left is the RGB image. Top Right is ground truth
-  %   depth. Bottom Left is Raw ground truth depth histogram. Bottom Right is
-  %   simulated SPAD measurements. Notice how closer depths are magnified and far
-  %   depths are attenuated.}
-% \end{table*}
-
+%Neglecting albedo and falloff effects, an ideal detector counting photon events
+%from a location $(x,y)$ in the time interval $(n\Delta t, (n+1) \Delta t)$ would record
+%
+%\begin{equation}
+  %\lambda_{x,y}[n] = \int_{n\Delta t}^{(n+1) \Delta t} (f * g)\paren*{t - 2z(x,y)/c} dt \label{single_loc_spad} 
+%\end{equation}  
+%
+%where $c$ is the speed of light, and $f$ is a function that models the temporal uncertainty in the
+%detector. Single-photon avalanche diodes (SPADs) are highly sensitive
+%photodetectors which are able to record single photon events with high temporal
+%precision \cite{Stuff}. Since the event corresponding to the detection of a
+%photon can be described with a Bernoulli random variable,
+%the total number of accumulated photons in this time interval follows a Poisson
+%distribution according to
+%
+%\begin{equation}
+  %h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+%\end{equation}
+%
+%where $\alpha_{x,y} = r_{x,y}/z(x,y)^2$ captures the attenuation of the
+%photon counts due to the reflectance $r(x,y)$ of the scene and due to the
+%inverse square falloff $1/z(x,y)^2$.
+%In addition, $\eta$ is the detection probability of a photon
+%triggering a SPAD event, and $b = \eta a + d$ is the average number of background detections resulting
+%from ambient photons $a$
+%and erroneous ``dark count'' events $d$ resulting from noise within the SPAD.
+%% \newpage
+%% \begin{table*}[htbp]
+%%   \begin{center}
+  %%   \begin{tabularx}{\linewidth}{*{2}{X}}
+  %%     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rgb.png} &
+  %%     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/rawdepth.png} \\
+  %%     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/depth_hist.png} &
+  %%     \includegraphics[width=\textwidth/2-5pt]{sections/figures/spad_example/spad_hist.png} \\
+  %%   \end{tabularx}
+  %% \end{center}
+  %% \caption{Sample Image. Top Left is the RGB image. Top Right is ground truth
+  %%   depth. Bottom Left is Raw ground truth depth histogram. Bottom Right is
+  %%   simulated SPAD measurements. Notice how closer depths are magnified and far
+  %%   depths are attenuated.}
+%% \end{table*}
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Monocular depth estimation with global depth hints}
@@
 \begin{figure}
-  \includegraphics[width=\textwidth/2]{sections/figures/full_pipeline/full_pipeline.jpeg}
+  \includegraphics[width=\textwidth/2]{full_pipeline.jpeg}
   \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial

### 2019-10-04 paper/cvpr2020/sections/related.tex
quick pass over last part of related work

@@
 \paragraph{Histogram Matching and Global Hints}
-Histogram matching or histogram specification is a well-known image processing
-technique \cite{Gonzalez2008} for adjusting an image so that it's histogram
-matches some pre-specified histogram (often derived from another image).
-Nikolova et. al. \cite{Nikolova2013} use optimization to recover a strict
-ordering of the image pixels that allows an exact histogram match to be
-obtained. Morovic et. al \cite{Morovic2002} provide a simple and concise method
-that also achieves an exact histogram match while being very fast.
-In the image reconstruction space, Swoboda and Schnörr \cite{Swoboda2013} use a
-histogram to form an image prior based on the Wasserstein distance for image
-denoising and inpainting. Rother et. al. \cite{Rother2006} use a histogram prior
-to create an energy function that penalizes foreground segmentations with
-dissimilar histograms. In a slightly different vein, Zhang et. al.
-\cite{Zhang2017} train a neural network to produce realistically colorized
-images given only a black-and-white image and a histogram of global color information.
+%
+Histogram matching is a well-known image processing technique for adjusting an image so that its histogram matches some pre-specified histogram (often derived from another image)~\cite{gonzales1977gray,Gonzalez2008}.
+Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels that allows an exact histogram match to be obtained.
+Morovic et al.~\cite{Morovic2002} provide a simple and concise method that also achieves an exact histogram match while being very fast.
+In the image reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram to form an image prior based on the Wasserstein distance for image denoising and inpainting.
+Rother et al.~\cite{Rother2006} use a histogram prior to create an energy function that penalizes foreground segmentations with dissimilar histograms.
+In a slightly different vein, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.
 
-Our method is essentially a modified form of the algorithm in
-\cite{Morovic2002}, modified for our particular use case. Also worth noting is
-the fact that most algorithms compute histograms from existing images, whereas
-our method mesaures the depth histogram indirectly using photon arrivals.
+\textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case.
+Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work.
+We can say something like ``Inspired by Morovic et al., we do something'' but then we also need to highlight how our method is different.
+Perhaps concisely summarize how you adapt it for our SPAD model.
 %

### 2019-10-05 paper/cvpr2020/main.tex
pass over hardware section

@@
 
-\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
+\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready

### 2019-10-05 paper/cvpr2020/sections/hardware.tex
New script for syncing figures, added gdrive to graphics path
pass over hardware section

@@
-\subsection{Setup}
 \begin{figure}[H]
-  \includegraphics[width=\textwidth/2]{sections/figures/prototype_single_col.png}
+  \includegraphics[width=\linewidth]{prototype_single_col.png}
   \caption{Prototype scanning setup. The pulsed light from the laser travels
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Prototype RGB-SPAD Camera Hardware}
+
+As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (\textcolor{red}{DETAILS}), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
+The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
+The SPAD records temporal histograms with \textcolor{red}{XX} bins, each with a width of \textcolor{red}{XX}~ps.
+SPAD and laser are co-axially aligned using a beam splitter (\textcolor{red}{DETAILS}).
+The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is \textcolor{red}{XX}~ps.
+A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
+The ground truth depth map is raster-scanned at a resolution of \textcolor{red}{$X \times Y$} pixels.
+The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
+This allows us to validate the accuracy of the proposed histogram matching algorithm that only uses the single histogram of the diffused SPAD and compare it with ground truth.
+Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.
+
+\textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
+
+Missing:
+%
+\begin{itemize}
+\item beamsplitter model
+\item resolution of ground truth depth
+\item laser wavelength etc
+\item RGB resolution
+\item do we also have Kinect depth maps for comparuson?
+\item combined SPAD jitter and pulse width
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Experimental Results}

### 2019-10-07 paper/cvpr2020/sections/hardware.tex
minor update

@@
 
+% The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
+
 As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (\textcolor{red}{DETAILS}), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
-The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
-The SPAD records temporal histograms with \textcolor{red}{XX} bins, each with a width of \textcolor{red}{XX}~ps.
-SPAD and laser are co-axially aligned using a beam splitter (\textcolor{red}{DETAILS}).
-The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is \textcolor{red}{XX}~ps.
+The laser operates at 670~nm with a pulse repetition rate of 20~MHz with a peak power of 450~mW and average power of 0.5~mW.
+The SPAD records temporal histograms with 65536 bins, each corresponding to a time window of 4~ps.
+SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
+The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm.
 A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
@@
 \begin{itemize}
-\item beamsplitter model
 \item resolution of ground truth depth
-\item laser wavelength etc
 \item RGB resolution
-\item do we also have Kinect depth maps for comparuson?
-\item combined SPAD jitter and pulse width
+\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
 \end{itemize}

### 2019-10-07 paper/cvpr2020/sections/hardware.tex
minor update

@@
 
-As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (\textcolor{red}{DETAILS}), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
-The laser operates at 670~nm with a pulse repetition rate of 20~MHz with a peak power of 450~mW and average power of 0.5~mW.
+As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
+The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.
 The SPAD records temporal histograms with 65536 bins, each corresponding to a time window of 4~ps.
@@
 A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
-The ground truth depth map is raster-scanned at a resolution of \textcolor{red}{$X \times Y$} pixels.
+The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels.
 The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
@@
 \begin{itemize}
-\item resolution of ground truth depth
-\item RGB resolution
+\item RGB resolution used for MDE
 \item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424

### 2019-10-07 paper/cvpr2020/main.tex
Updated teaser, moved supplement figures to gdrive.

--- 2019-10-04 paper/cvpr2020/main.tex
@@
 
-\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
+\graphicspath{{"G:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
+    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
+  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready

### 2019-10-07 paper/cvpr2020/sections/supplement/hardware_comparison.tex
Updated teaser, moved supplement figures to gdrive.

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}

%% MiDaS outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/midas/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/midas/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/densedepth/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured}
%    \vspace{-1.5em}
\end{figure*}
%% DenseDepth outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/densedepth/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/densedepth/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densdepth_captured}
%    \vspace{-1.5em}
\end{figure*}

\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.15in, height=1.15in]{captured/dorn/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured}
%    \vspace{-1.5em}
\end{figure*}
%% DORN outdoor scene
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=1.15in]{captured/dorn/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_outdoor_captured}
%    \vspace{-1.5em}
\end{figure*}

### 2019-10-07 paper/cvpr2020/supplement.tex
minor update
Updated teaser, moved supplement figures to gdrive.

@@
 
+\graphicspath{{"G:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
+    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
+  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
+
 \def\cvprPaperID{****} % *** Enter the CVPR Paper ID here

### 2019-10-07 paper/cvpr2020/sections/figures/sync_figures.sh

@@ -1,8 +1,10 @@
-#!/bin/bash
+#!/usr/bin/env bash
 # Sync figures with Google Drive or other folders so everyone can see them
 gdrive="/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/";
-rsync captured/midas/8_30_small_lab_scene/teaser.eps "$gdrive"
+rsync captured/midas/8_30_small_lab_scene/teaser.pdf "$gdrive"
 rsync full_pipeline/full_pipeline.jpeg "$gdrive"
 shopt -s extglob  #Allows for | in bash pattern matching below
 rsync -r comparison/densedepth_?(468|194|258)_comparison.png "$gdrive/comparison"
-rsync prototype_single_col.png "$gdrive"
+rsync prototype_single_col.pdf "$gdrive"
+rsync -R ././captured/**/**/?(gt_z_proj_crop_depth_fig|z_init_depth_fig|z_med_scaled_depth_fig|z_pred_depth_fig|rgb_cropped_fig|z_init_diff_fig|z_med_scaled_diff_fig|z_pred_diff_fig).png "$gdrive"
+rsync -R ././captured/**/**/?(diff_colorbar|depth_colorbar).pdf "$gdrive" 

### 2019-10-07 paper/cvpr2020/sections/method.tex
Added pseudocode for exact histogram matching.

@@
 As derived in previous work, the combination of signal, background, and noise can be modeled as an inhomogeneous Poisson process $\mathcal{P}$~\cite{Kirmani:2014,Shin2015}.
+
+\paragraph{SPAD Denoising}
+\begin{itemize}
+  \item Talk about histogram matching in the ideal case, jump straight to intensity 
+  \item Talk about histogram matching in our case, and how it approaches the
+    ideal case. Discuss the following corrections 
+    \begin{itemize}
+      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
+        then the ambient estimate to get rid of the noise floor.
+      \item Falloff
+    \end{itemize}
+  \item Talk about how the histogram matching works with intensity
+    considerations applied, briefly.
+  \item We don't address jitter or poisson noise.
+\end{itemize}
+\begin{equation}
+  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+\end{equation}
+Given a SPAD with histogram $h$ according to the above equation, we first
+process the SPAD to remove the effects of some of the terms. First, we
 
@@
 \paragraph{Exact Histogram Matching}
-\begin{figure}
-  \includegraphics[width=\textwidth/2]{full_pipeline.jpeg}
+\begin{figure*}
+  \centering
+  \includegraphics[height=2.5in]{full_pipeline.jpeg}
   \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
@@
   intensity-weighted pixel values on the corrected SPAD data.}
-\end{figure}
+\end{figure*}
 An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
@@
 
+\begin{algorithm}[H]
+ \caption{Exact Histogram Matching} 
+ \label{alg:ehm}
+ \input{sections/figures/exact_hist_matching_pseudo.tex}
+\end{algorithm}
+
 However, for our purposes, we need to modify our algorithm to accommodate
@@
 
-\paragraph{SPAD Denoising}
-\begin{itemize}
-  \item Talk about histogram matching in the ideal case, jump straight to intensity 
-  \item Talk about histogram matching in our case, and how it approaches the
-    ideal case. Discuss the following corrections 
-    \begin{itemize}
-      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
-        then the ambient estimate to get rid of the noise floor.
-      \item Falloff
-    \end{itemize}
-  \item Talk about how the histogram matching works with intensity
-    considerations applied, briefly.
-  \item We don't address jitter or poisson noise.
-\end{itemize}
-\begin{equation}
-  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
-\end{equation}
-Given a SPAD with histogram $h$ according to the above equation, we first
-process the SPAD to remove the effects of some of the terms. First, we 
 \subsection{Implementation Details}

### 2019-10-07 paper/cvpr2020/sections/method.tex
Added SPAD denoising paragraph.

@@
 \paragraph{SPAD Denoising}
-\begin{itemize}
-  \item Talk about histogram matching in the ideal case, jump straight to intensity 
-  \item Talk about histogram matching in our case, and how it approaches the
-    ideal case. Discuss the following corrections 
-    \begin{itemize}
-      \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
-        then the ambient estimate to get rid of the noise floor.
-      \item Falloff
-    \end{itemize}
-  \item Talk about how the histogram matching works with intensity
-    considerations applied, briefly.
-  \item We don't address jitter or poisson noise.
-\end{itemize}
-\begin{equation}
-  h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
-\end{equation}
-Given a SPAD with histogram $h$ according to the above equation, we first
-process the SPAD to remove the effects of some of the terms. First, we
+To remove the ambient and dark count photons from the histogram, we apply a
+preprocessing step. First, we compute an estimate of the combined ambient
+and dark count rate $\hat b$ by averaging $N$ of the first bins together. We then
+note that that shining a laser through a 2D diffuser and
+measuring a single pixel is very physically similar to recording a single 
+non-line-of-sight measurement. We
+compute the first difference of the histogram and find the first and last edges 
+$i_{first}$ and $i_{last}$ where $\abs{h_i - h_{i+1}}$ is
+significantly larger than what would be expected given the rate $b$. From
+\cite{Xin2019}, these edges
+correspond to the discontinuties in the depth map 
+at the closest and furthest image depths, and therefore all of the signal
+photons must be in the bins between these two edges. We refine these estimates by
+computing $i'_{first} = \max_{i}\mset{i}{h_i > \hat b, i < i_{first}}$ and
+$i'_{last} = \min_{i} \mset{i}{h_i > \hat b, i > i_{last}}$
+Finally, we reject all photons outside of the valid range by clamping those bins
+to 0, and we subtract our ambient estimate from the photons within the valid
+range, giving a denoised histogram
+\[(h_{denoised})_i = \begin{cases}
+    0 & i < i'_{first} \\
+    max(h_i - \hat b, 0) & i'_{first} \leq i \leq i'_{last} \\
+    0 & i > i'_{last} \\
+  \end{cases}.\]
+% \begin{itemize}
+%   \item Talk about histogram matching in the ideal case, jump straight to intensity 
+%   \item Talk about histogram matching in our case, and how it approaches the
+%     ideal case. Discuss the following corrections 
+%     \begin{itemize}
+%       \item Ambient/DC - Use \cite{Xin2019} to justify looking for large edges,
+%         then the ambient estimate to get rid of the noise floor.
+%       \item Falloff
+%     \end{itemize}
+%   \item Talk about how the histogram matching works with intensity
+%     considerations applied, briefly.
+%   \item We don't address jitter or poisson noise.
+% \end{itemize}
+% \begin{equation}
+%   h[n] \sim \mathcal{P}\paren*{\sum_{x,y}\alpha_{x,y}\eta \lambda_{x,y}[n] + b} \label{global_hints}
+% \end{equation}
+% Given a SPAD with histogram $h$ according to the above equation, we first
+% process the SPAD to remove the effects of some of the terms. First, we
 

### 2019-10-07 paper/cvpr2020/sections/hardware.tex
Updated teaser, moved supplement figures to gdrive.
Update paper, add z compensation for SPAD.

@@
 \begin{figure}[H]
-  \includegraphics[width=\linewidth]{prototype_single_col.png}
+  \includegraphics[width=\linewidth]{prototype_single_col.pdf}
   \caption{Prototype scanning setup. The pulsed light from the laser travels
@@
 
-\textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
+We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
+the scanning system using the standard camera calibration toolbox in MATLAB.
+In general it is impossible to compensate for the offset between camera and
+SPAD, but we do add the z displacement from spad to kinect to partially
+compensate for it.
+% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
 

### 2019-10-07 paper/cvpr2020/sections/related.tex
Update paper, add z compensation for SPAD.

@@
 
-\textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case.
+Because the single SPAD produces a weighted histogram of the depth map, we adapt
+the algorithm in Morovic et al. to accommodate general per-pixel
+weights, which allows us to compensate for different scene reflectances during
+the histogram matching.
+% \textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case.
 Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work.

### 2019-10-07 nyuv2/captured/analyze_all_scenes.py

@@ -44,17 +44,17 @@ def cfg():
         "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
         "8_30_poster_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
         "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_31_outdoor3": {"offset": (0, 0), "bin_width_ps": 32, "min_r": 0.4, "max_r": 14.8},
+        "8_31_outdoor3": {"offset": (0, 0), "bin_width_ps": 32, "min_r": 0.4, "max_r": 11.},
     }
     # Relative shift of projected depth to rgb (found empirically)
     # rgb in [0, 255]
     models = {
         "midas": {"load": lambda model_path, device: get_midas("MiDaS/model.pt", device),
                   "run": lambda model, rgb, depth_range, device: midas_predict(model, rgb/255., depth_range, device)},
-        # "dorn": {"load": lambda model_path, device: DORN(),
-        #          "run": lambda model, rgb, depth_range, device: dorn_predict(model, rgb)},
-        # "densedepth": {"load": lambda model_path, device: DenseDepth().to(device),
-        #                "run": lambda model, rgb, depth_range, device: model.predict(rgb).squeeze()}
+        "dorn": {"load": lambda model_path, device: DORN(),
+                 "run": lambda model, rgb, depth_range, device: dorn_predict(model, rgb)},
+        "densedepth": {"load": lambda model_path, device: load_densedepth(model_path, device),
+                       "run": lambda model, rgb, depth_range, device: model.predict(rgb).squeeze()}
     }
     use_intensity = True
     figures_dir = "figures" if use_intensity else "figures_no_intensity"
@@ -64,6 +64,11 @@ def cfg():
     device = torch.device("cuda" if torch.cuda.is_available() else "cpu")
     print("using device: {} (CUDA_VISIBLE_DEVICES = {})".format(device,
                                                                 os.environ["CUDA_VISIBLE_DEVICES"]))
+
+def load_densedepth(model_path, device):
+    model = DenseDepth()
+    model.model.to(device)
+    return model
 
 def dorn_predict(model, rgb):
     """
[…]

### 2019-10-07 nyuv2/captured/camera_utils.py

@@ -2,7 +2,11 @@ import scipy.io as sio
 import numpy as np
 import cv2
 
-def undistort_img(img, fc, pc, rdc, tdc):
+def undistort_img(img, FocalLength, PrincipalPoint, RadialDistortion, TangentialDistortion):
+    fc = FocalLength
+    pc = PrincipalPoint
+    rdc = RadialDistortion
+    tdc = TangentialDistortion
     if len(rdc) == 2:
         rdc = np.append(rdc, 0.)
     distortionCoefficients = np.concatenate((rdc[:2], tdc, rdc[2:]))
@@ -17,11 +21,10 @@ def extract_camera_intrinsics(CameraParameters):
     """
     Get intrinsics from param struct
     """
-    focalLength = CameraParameters["FocalLength"][0]
-    principalPoint = CameraParameters["PrincipalPoint"][0]
-    radialDistortion = CameraParameters["RadialDistortion"][0]
-    tangentialDistortion = CameraParameters["TangentialDistortion"][0]
-    return focalLength, principalPoint, radialDistortion, tangentialDistortion
+    out = {}
+    for k in ["FocalLength", "PrincipalPoint", "RadialDistortion", "TangentialDistortion"]:
+        out[k] = CameraParameters[k][0]
+    return out
 
 
 def extract_camera_params(filepath):
@@ -32,9 +35,10 @@ def extract_camera_params(filepath):
     cp1 = param_struct["CameraParameters1"][0][0][0][0]
     cp2 = param_struct["CameraParameters2"][0][0][0][0]
 
-    fc1, pc1, rdc1, tdc1 = extract_camera_intrinsics(cp1)
-    fc2, pc2, rdc2, tdc2 = extract_camera_intrinsics(cp2)
-    return fc1, fc2, pc1, pc2, rdc1, rdc2, tdc1, tdc2, RotationOfCamera2, TranslationOfCamera2
+    camera_params1 = extract_camera_intrinsics(cp1)
+    camera_params2 = extract_camera_intrinsics(cp2)
+
+    return camera_params1, camera_params2, RotationOfCamera2, TranslationOfCamera2
 
 
 def project_depth(z, z_mask, imagesize2, fc1, fc2, pc1, pc2, RotationOfCamera2, TranslationOfCamera2):

### 2019-10-07 nyuv2/captured/capture_utils.py

@@ -135,7 +135,7 @@ def depth_imwrite(img, filepath):
     :param filepath:
     :return:
     """
-    img_scaled = ((img - np.min(img)) * 255./(np.max(img) - np.min(img))).astype('int')
+    img_scaled = ((img - np.min(img)) * 65535./(np.max(img) - np.min(img))).astype(np.uint16)
     cv2.imwrite(filepath + ".png", img_scaled)
 
 
@@ -153,7 +153,8 @@ def preprocess_spad(spad_single, ambient_estimate, min_depth, max_depth, sid_obj
     # Correct Falloff
     bin_edges = np.linspace(min_depth, max_depth, len(spad_denoised) + 1)
     bin_values = (bin_edges[1:] + bin_edges[:-1]) / 2
-    spad_corrected = spad_denoised * bin_values ** 2
+    # spad_corrected = spad_denoised * bin_values ** 2
+    spad_corrected = spad_denoised * bin_values ** 4
 
     # Scale SID object to maximize bin utilization
     min_depth_bin = np.min(np.nonzero(spad_corrected))
@@ -197,5 +198,5 @@ def load_and_crop_kinect(rootdir, calibration_file="calibration.mat", kinect_fil
     rgb_cropped = kinect_rgb[crop[0]:crop[1], crop[2]:crop[3], :]
 
     # Intensity
-    intensity = rgb_cropped[:, :, 0] / 225.
+    intensity = rgb_cropped[:, :, 0] / 255.
     return kinect_rgb, rgb_cropped, intensity, crop

### 2019-10-09 paper/cvpr2020/main.tex
Added pseudocode for exact histogram matching.
full pass over experimental results section

--- 2019-10-04 paper/cvpr2020/main.tex
@@
 \usepackage[utf8x]{inputenc}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{algorithmicx}
+
+\usepackage{dblfloatfix}
+
 \input{mark_defs.tex}
@@
 
-\graphicspath{{"G:/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}{}}
+\graphicspath{{"G:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
+    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
+  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready

### 2019-10-09 paper/cvpr2020/sections/hardware.tex
full pass over experimental results section

--- 2019-10-07 paper/cvpr2020/sections/hardware.tex
@@
 
-\textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
-
-Missing:
+%We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
+%the scanning system using the standard camera calibration toolbox in MATLAB.
+%In general it is impossible to compensate for the offset between camera and
+%SPAD, but we do add the z displacement from spad to kinect to partially
+%compensate for it.
+%% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
 %
-\begin{itemize}
-\item RGB resolution used for MDE
-\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
-\end{itemize}
+%Missing:
+%%
+%\begin{itemize}
+%\item RGB resolution used for MDE
+%\item do we also have Kinect depth maps for comparison? (yes) kinect resolution: RGB is 1920x1080 and depth camera is 512x424
+%\end{itemize}
 
@@
 \subsection{Experimental Results}
+
+Using this prototype, we captured a number of scenes as shown in Figure~\ref{fig:results_captured} and in the supplement.
+We downsample the reference RGB image to a resolution of $XX \times XX$~px and directly feed into a monocular depth estimation algorithm.
+In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested.
+Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement.
+The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).
+
+In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonable well.
+However, the root mean squared error (RMSE) for these two scenes is relatively high with 2.4--2.9~m (see red/white error maps in Fig.~\ref{fig:results_captured}).
+The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m.
+The ``Poster'' scene is meant to confuse the CNN---it shows a flat poster with a printed scene.
+As expected, the CNN predicts that the statue is closer than the arches in the background, which is incorrect in this case.
+The proposed method uses the SPAD histogram to correctly flatten the estimated depth map.
+
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{captured_results_main}
+	\caption{Experimental results.
+For each scene, we record an RGB image (lower left subimages) and a ground truth depth map that is raster-scanned with the SPAD (upper left subimages).
+A monocular depth CNN often predicts the ordinal depth well (top two scenes), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages) as shown by the error maps and root mean squared error (RMSE) for each example (lower center and right subimages).
+The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print.
+Our method is able to correct this error.
+}
+	\label{fig:results_captured}
+\end{figure}

### 2019-10-09 paper/cvpr2020/supplement.tex
full pass over experimental results section

--- 2019-10-02 paper/cvpr2020/supplement.tex
@@
 
+\graphicspath{{"G:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
+    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
+    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
+  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
+
 \def\cvprPaperID{****} % *** Enter the CVPR Paper ID here

### 2019-10-09 paper/cvpr2020/sections/method.tex
pass over simulated results section

@@
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{full_pipeline.jpeg}
+  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
+  per-pixel depth estimate. Then we perform exact histogram matching using
+  intensity-weighted pixel values on the corrected SPAD data.}
+\end{figure}
+
 Monocular depth estimation is a well-explored, yet active area of research (see Sec.~\ref{sec:related}).
@@
 \paragraph{Exact Histogram Matching}
-\begin{figure*}
-  \centering
-  \includegraphics[height=2.5in]{full_pipeline.jpeg}
-  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
-  per-pixel depth estimate. Then we perform exact histogram matching using
-  intensity-weighted pixel values on the corrected SPAD data.}
-\end{figure*}
+
 An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
@@
 
-\subsection{Implementation Details}
-For the Monocular Depth Estimator, we use pretrained versions of the
-the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
-The exact histogram matching method is as described in \cite{}.
+%\subsection{Implementation Details}
+%For the Monocular Depth Estimator, we use pretrained versions of the
+%the Deep Ordinal Regression Network (DORN) \cite{} and the DenseDepth Network.
+%The exact histogram matching method is as described in \cite{}.

### 2019-10-09 paper/cvpr2020/sections/related.tex
pass over simulated results section

@@
 We introduce a new approach that leverages existing monocular depth estimation networks but disambiguates their output with depth histogram-like measurements obtained from a single, diffused SPAD.
+Other approaches to disambiguating monocular depth estimation, for example using optimized freeform lenses~\cite{Wu:2019,Chang:2019:DeepOptics3D} or dual-pixel sensors~\cite{Garg:2019}, these approaches require custom lenses or sensors and specialized image reconstruction methods.
+In contrast, our diffused SPAD can simply be added to an existing camera, as it is on many cellphones already, and it does not require the standard camera ISP to be changed.
 

### 2019-10-09 paper/cvpr2020/sections/simulation.tex
New script for syncing figures, added gdrive to graphics path
pass over simulated results section

--- 2019-09-30 paper/spad_single/sections/simulation.tex
@@
-\subsection{Implementation Details}
-\begin{itemize}
-  \item Number of bins used, depth range, laser parameters, use of intensity
-    image.
-  \item Using
-\end{itemize}
-\paragraph{NYU Depth v2}
-The NYU Depth v2 Dataset consists of 249 training and 215 testing scenes of
-RGB-D data captured using a Microsoft Kinect. We used a version of DORN
-pretrained according to \cite{Fu2018} as our CNN.
-\newpage
-% \begin{table*}
-% \begin{center}
-% \begin{tabular}{lccc|ccc}
-%   \toprule
-%     & $\delta^1 \uparrow$ & $\delta^2\uparrow$ & $\delta^3 \uparrow$ & RMSE $\downarrow$ & rel $\downarrow$ & $log_{10} \downarrow$ \\
-%   \midrule
-% Eigen et. al. & 0.769 & 0.950 & 0.988 & 0.641 & 0.158 & - \\ 
-% Laina et. al.&0.811&0.953&0.988&0.573&0.127&0.055 \\
-% DORN&0.818&0.950&0.982&0.620&0.137&0.063 \\
-%   DORN (rescaled) & 0.872 & 0.967 & 0.989 & 0.548 & 0.111 & 0.048 \\
-% Alhashim, Wonka (2019)&0.847&0.973&0.994&0.548(0.461)&0.123&0.053 \\
-% Alhashim, Wonka (2019) rescaled using GT depth"&0.888&\textbf{0.978}&\textbf{0.995}&\textbf{0.499}(0.409)&\textbf{0.106}&\textbf{0.045} \\
-%   \midrule
-%   Ours (raw depth counts) & \textbf{0.899} & 0.970 & 0.990 & 0.529 & 0.199 & 0.055 \\
-%   Ours (DORN) (intensity/falloff) & 0.835 & 0.953 & 0.984 & 0.521 & 0.129 & 0.060 \\
-%   Ours (DenseDepth) (intensity/falloff) & 0.867 & 0.974 & 0.994 & 0.445 & 0.114 & 0.050 \\
-%   \bottomrule
-% \end{tabular} 
-% \end{center}
-% \caption{Results on the NYU Depth v2 test set \cite{nyudepth}.}
-% \end{table*}
-%%%
 \begin{figure*}[!t]
@@
 \input{sections/figures/sim_table.tex}
-\caption{Simulated Results on NYU Depth v2. Bold indicates best performance for
-  that metric, while underline indicates second best. The proposed scheme
-  outperforms DenseDepth and DORN on all metrics, and even outperforms the
-  median rescaling scheme, which has access to the true median depth value. Note
-that we do not report metrics for MiDaS or MiDaS with median rescaling, as MiDaS
-does not output metric depth.}
+\caption{Quantitative evaluation using NYU Depth v2.
+Bold indicates best performance for that metric, while underline indicates second best.
+The proposed scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or even outperforms the median rescaling scheme and histogram matching with the exact depth map histogram, even though these methods have access to ground truth.
+}
 \end{center}
@@
 
-\begin{figure*}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_468_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_194_comparison.png}
-  \includegraphics[width=\textwidth]{sections/figures/comparison/densedepth_258_comparison.png}
-  \caption{Selected Results on DenseDepth. First two examples demonstrate
-    capability of proposed method to correct initial scaling/translation errors.
-    Last example shows potential pitfall when ordinal depth is predicted incorrectly.}
+\begin{figure*}[!t]
+  \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.png}
+  \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.png}
+  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
+  \caption{Simulated results from NYU v2 computed with the DenseDepth CNN.
+The depth maps estimated by the CNN are reasonable, but contain systematic error.
+Oracle access to the ground truth depth maps, either through the median depth or the depth histogram, can remove this error and correct the depth maps.
+The proposed method uses a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
+	\label{fig:results_simulated}
 \end{figure*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Implementation Details}
+
+We use the NYU Depth v2 dataset to evaluate our method.
+This dataset consists of 249~training and 215~testing scenes of RGB-D data captured using a Microsoft Kinect.
+\textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Simulated Results}
+
+We show an extensive quantitative evaluation in Table~1.
+Here, we evaluate three recent monocular depth estimation techniques: DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and MiDaS~\cite{Lasinger:2019}.
+To evaluate the quality of DORN and DenseDepth, we report various standard error metrics.
+Moreover, we show a simple post-processing step that rescales their outputs by the median ground truth depth~\cite{Alhashim2018}.
+We also show the results of histogram matching the output of the CNNs with the ground truth depth map histogram.
+Note that we do not report the quality of the direct output of MiDaS as this algorithm does not output metric depth.
+However, we do show its output histogram matched with the ground truth depth map histogram.
+In all cases, post-processing the estimated depth maps either with the median depth or depth histogram significantly improves the absolute depth estimation, often by a large margin compared to the raw output of the CNNs.
+Unfortunately, ground truth depth is typically not accessible so neither of these two post-processing methods are viable in practical application scenarios.
+
+We simulate the measurements of a single diffused SPAD as discussed in Section~\ref{sec:method} and also add Poisson noise and background signal.
+In table~1, results are shown for several different signal-to-background ratios (SBRs).
+We see that the proposed method achieves high-quality results for correcting the raw depth map estimated by the respective CNNs for all cases.
+The quality of the resulting depth maps is almost as good as that achieved with the oracle ground truth histogram, which can be interpreted as an approximate upper bound on the performance, despite a relatively high amount of noise and background signal.
+These results demonstrate that the proposed method is agnostic to the specific depth estimation CNN applied to get the initial depth map and that it generally achieves significant improvements in the estimated depth maps, clearly surpassing the variation of performance between depth estimation CNNs.
+
+In Figure~\ref{fig:results_simulated}, we also show qualitative results of our simulations.
+For each of these scenes, we show the RGB reference image, the ground truth depth map, the raw output of the DenseDepth CNN, the result of rescaling the CNN output by the median ground truth depth, the result of histogram-matching the CNN output by the ground truth depth map histogram, and the result achieved by the proposed method for an SBR of 100.
+Error maps for all the depth estimation methods are shown.
+As expected, the CNN outputs depth maps that look reasonable but that have an average root mean squared error (RMSE) of about 50--60~cm.
+Re-scaling this depth map by the median ground truth depth value slightly improves the quality and histogram-matching it with the ground truth depth histogram improves the depth map a lot.
+The quality of the proposed method is close to that using the oracle histogram, despite relying on noisy SPAD measurements.
+Additional simulations using DenseDepth and other depth estimation CNNs for a variety of scenes are shown in the supplement.

### 2019-10-10 paper/cvpr2020/sections/method.tex
Pass over methods section.

@@
 %
-where $(n\Delta t, (n+1) \Delta t)$ models the $n^{th}$ time interval of the temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$ is a function that models the temporal uncertainty in the detector, and $b$ represents ambient background light and falsely detected photons known as dark count.
-As derived in previous work, the combination of signal, background, and noise can be modeled as an inhomogeneous Poisson process $\mathcal{P}$~\cite{Kirmani:2014,Shin2015}.
+where $(n\Delta t, (n+1) \Delta t)$ models the $n^{th}$ time interval of the
+temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
+is a function that models the temporal uncertainty in the detector, and $b$
+represents ambient background light and falsely detected photons known as dark
+count. As derived in previous work, the combination of signal, background, and
+noise can be modeled as an inhomogeneous Poisson process
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019} we adopt the term
+\textit{transient} for our histogram $h[n]$.
 
-\paragraph{SPAD Denoising}
+\subsection{Ambient Rejection and Falloff Correction}
 To remove the ambient and dark count photons from the histogram, we apply a
-preprocessing step. First, we compute an estimate of the combined ambient
-and dark count rate $\hat b$ by averaging $N$ of the first bins together. We then
+preprocessing step. Assuming that the first $N$ bins of the SPAD histogram
+contain only ambient and dark count photons (this is equivalent to assuming the
+minimum image depth is larger than $N \cdot c\Delta T/2$), we estimate 
+and dark count rate $b$ as $\hat b = \frac{1}{N}\sum_{n=0}^N h[n]$ We then
 note that that shining a laser through a 2D diffuser and
@@
 non-line-of-sight measurement. We
-compute the first difference of the histogram and find the first and last edges 
-$i_{first}$ and $i_{last}$ where $\abs{h_i - h_{i+1}}$ is
-significantly larger than what would be expected given the rate $b$. From
-\cite{Xin2019}, these edges
+compute the absolute first difference $d[n] = \abs{h[n] - h[n+1]}$ and find 
+the set of edges. Intuitively, given a sufficiently large value of $b$, the Poisson sample
+$h[n] \sim \mathcal{P}(b)$ should behave roughly like a Gaussian with variance $b$, and the difference
+$h[n] - h[n+1]$ should behave like a Gaussian with variance $2b$. Therefore, we
+can detect edges that occur between bins that contain actual signal photons and
+bins that do not by computing the set 
+\begin{equation}
+  \mathcal{E} = \mset{n}{d[n] > \alpha\sqrt{2\hat b}}.
+  \label{eq:edge_set}
+\end{equation}
+In this work, we use $\alpha = 2$.
+We identify the closest and furthest edges $n_{first} = \min \mathcal{E}$ and
+$n_{last} = \max \mathcal{E}$.
+From \cite{Xin2019} Proposition 3, these edges
 correspond to the discontinuties in the depth map 
 at the closest and furthest image depths, and therefore all of the signal
-photons must be in the bins between these two edges. We refine these estimates by
-computing $i'_{first} = \max_{i}\mset{i}{h_i > \hat b, i < i_{first}}$ and
-$i'_{last} = \min_{i} \mset{i}{h_i > \hat b, i > i_{last}}$
+photons must be in the bins between these two edges.
+We refine these estimates by
+computing $n'_{first} = \max\set{n_{first}}\cup\mset{n}{h[n] > \hat b, n \leq n_{first}}$ and
+$n'_{last} = \min\set{n_{last}}\cup\mset{n}{h[n] > \hat b, n \geq n_{last}}$
 Finally, we reject all photons outside of the valid range by clamping those bins
 to 0, and we subtract our ambient estimate from the photons within the valid
-range, giving a denoised histogram
-\[(h_{denoised})_i = \begin{cases}
-    0 & i < i'_{first} \\
-    max(h_i - \hat b, 0) & i'_{first} \leq i \leq i'_{last} \\
-    0 & i > i'_{last} \\
-  \end{cases}.\]
+range, giving an ambient-free transient
+\begin{equation}
+  h'_{clean}[n] = \begin{cases}
+    0 & n < n'_{first} \\
+    \max(h[n] - \hat b, 0) & n'_{first} \leq n \leq n'_{last} \\
+    0 & n > n'_{last} \\
+  \end{cases}.
+  \label{eq:h_clean}
+\end{equation}
+To compensate for the radiometric falloff, we scale each bin by its squared depth,
+which is consistent with our hardware prototype's radiometric falloff model.
+This gives
+\begin{equation}
+  h_{clean}[n] = h'_{clean}[n] \cdot r_n^2
+  \label{eq:h_scaled}
+\end{equation}
+where $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the depth
+corresponding to bin $n$
+As a final preprocessing step, we re-bin the transient, applying the Spacing-Increasing Discretization
+(SID) of \cite{Fu2018} to produce $h_{target}$. This reduces the number of bins in the histogram
+matching procedure, giving speedups while maintaining performance. In this work,
+we use 140 bins for the simulated results and 600 bins for the captured results.
+
 % \begin{itemize}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Monocular depth estimation with global depth hints}
-Given a single RGB image $I(x,y)$ and a vector of photon arrivals $h[n]$
-described by equation \ref{global_hints}, we seek to
-reconstruct the ground truth depth map $z(x,y)$.
-Our method has two parts. First, we \textbf{initialize} our estimate of the depth map from the single RGB
-image via a monocular depth estimator described below. Second, we \textbf{refine} this depth map using
-the captured measurements $h[n]$ via exact histogram matching.
+% \subsection{Monocular depth estimation with global depth hints}
+% Given a single RGB image $I(x,y)$ and a vector of photon arrivals $h[n]$
+% described by equation \ref{global_hints}, we seek to
+% reconstruct the ground truth depth map $z(x,y)$.
+% Our method has two parts. First, we \textbf{initialize} our estimate of the depth map from the single RGB
+% image via a monocular depth estimator described below. Second, we \textbf{refine} this depth map using
+% the captured measurements $h[n]$ via exact histogram matching.
 
-\paragraph{Initialization}
-The first step in our method is to produce an initial estimate of ground truth
-depth. Convolutional Neural Networks have been shown to produce accurate, if poorly-scaled, estimates of depth
-from only a single image. We therefore choose to initialize our depth map
-estimate $\hat z^{(0)}(x,y)$ using
-a CNN. However, any depth estimator reliant on only a single
-view may be used for this step. Furthermore, in the larger context of our
-algorithm, it is more important that the network predict the correct ordinal
-relationships between pixels - that is, to predict the correct relative ordering
-of pixels $a$ and $b$, rather than to get all pixels exactly correct.
+% \paragraph{Initialization}
+% The first step in our method is to produce an initial estimate of ground truth
+% depth. Convolutional Neural Networks have been shown to produce accurate, if poorly-scaled, estimates of depth
+% from only a single image. We therefore choose to initialize our depth map
+% estimate $\hat z^{(0)}(x,y)$ using
+% a CNN. However, any depth estimator reliant on only a single
+% view may be used for this step. Furthermore, in the larger context of our
+% algorithm, it is more important that the network predict the correct ordinal
+% relationships between pixels - that is, to predict the correct relative ordering
+% of pixels $a$ and $b$, rather than to get all pixels exactly correct.
 
-\paragraph{Exact Histogram Matching}
+\subsection{Exact Histogram Matching}
+% \begin{algorithm}[H]
+%  \caption{Exact Histogram Matching} 
+%  \label{alg:ehm}
+%  \input{sections/figures/exact_hist_matching_pseudo.tex}
+% \end{algorithm}
+Exact histogram matching is a procedure that takes a source image and a target
+histogram and maps the pixel values of the source image so that the image's
+histogram matches the target histogram. Given a single RGB image, we pass it
+through an MDE to produce a depth map $\hat z_0 \in [\ell, u]^{M \times N}$
+where $\ell$ and $u$ are the lower and upper bounds of the depth range of
+interest, respectively. In a parallel processing step,
+we compute an estimate of the scene albedo using an intrinsic imaging method and
+take the color channel of the resulting albedo image that corresponds to the
+wavelength of the laser illumination. This gives a reflectance estimate $W \in
+[0, 1]^{M \times N}$. We
+then compute a weighted histogram $h_{source}$of the depth map $\hat z_0$ where the
+per-pixel weights are given by $W$, and the bin edges are given by the SID
+discretization algorithm of \cite{Fu2018}.
 
-An image's \textit{histogram} is a pair of vectors $(h, b)$ where $h_i$ is the number of
-pixels of the image whose value lies in the range $[b_i, b_i+1)$.
-Then, given a source image $S$ with histogram $(h_s, b)$ and a target histogram
-$(h_t, b)$, histogram matching generates a new image $M$ such that $h_m \approx
-h_t$ and the pixel values in $M$ are in the same relative order as in $S$.
-The full details of the exact histogram matching algorithm can be found in
-\cite{Morovic2002}.
+We match the histogram $h_{source}$ to $h_{target}$ using the method of
+\cite{Morovic2002}. We compute a pixel movement
+matrix $T$ such that $T_{mn}$ is the amount of mass to move from $h_{source}[m]$
+to $h_{target}$. We do so using the procedure outlined in \ref{alg:pixel_movement}
 
 \begin{algorithm}[H]
- \caption{Exact Histogram Matching} 
+ \caption{Pixel Movement} 
  \label{alg:ehm}
- \input{sections/figures/exact_hist_matching_pseudo.tex}
+ \begin{algorithmic}
+  \Procedure{FindMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
+    \State Initialize $T$ as an $M \times N$ array.
+    \For{$m$ in $1,\ldots,M$}
+      \For{$n$ in $1,\ldots,N$}
+        \State $p_s \gets \sum_{\ell=1}^{n-1} T[m, \ell]$
+        \State $p_t \gets \sum_{\ell=1}^{m-1} T[\ell, n]$
+        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
+      \EndFor
+    \EndFor
+    \State \textbf{return} $T$
+  \EndProcedure
+ \end{algorithmic}
 \end{algorithm}
 
-However, for our purposes, we need to modify our algorithm to accommodate
-differing per-pixel weights. We can account for squared depth falloff
-
+Finally, for a pixel $z_0[i, j]$ in depth bin $k$, we sample the new depth bin from the
+distribution $T[k, :]/\sum_{n=1}^NT[k,n]$ (which is a distribution over target
+depth bins $1,\ldots,N$) to get the bin of $\hat z[i,j]$. We can then apply the
+standard SID decoding procedure to get the depth corresponding to that bin
+\textcolor{red}{Does the above seem reasonable to include? Not sure if the
+  pseudocode is helpful/necessary or not.}
 %\subsection{Implementation Details}

### 2019-10-10 paper/cvpr2020/sections/simulation.tex
Pass over methods section.

@@
 
-We use the NYU Depth v2 dataset to evaluate our method.
-This dataset consists of 249~training and 215~testing scenes of RGB-D data captured using a Microsoft Kinect.
-\textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
+We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
+249~training and 215~testing scenes of RGB-D data captured using a Microsoft
+Kinect.
+We compute the standard intensity image (i.e. the Y
+component of the YCbCr image, scaled to be in $[0,1]$) from the RGB input. We compute the weighted depth
+histogram of the ground truth depth image using these intensity weights, and sum
+over the spatial dimension to get a 1D histogram $h$. We multiply each bin by
+$1/d^2$, which accounts for the radiometric falloff, and convolve with the SPAD
+jitter kernel, which we model as a standard Gaussian with a full-width
+half-maximum of 70ps. We scale this histogram by a signal photon count (set at
+$s = 10^6$) and then add a fixed number of photons $b \in \set{10^5, 2\times 10^4, 10^4}$ evenly distributed across all
+bins to simulate the ambient and dark count photons, modeling
+signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
+we Poisson sample each bin to get the final simulated SPAD transient.
+% \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
 

### 2019-10-10 paper/cvpr2020/sections/method.tex
added 1/r2 in methods

@@
 Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying intensity $g(t)$ illuminating some 3D scene.
-We parameterize the geometry of the scene as a height map $z(x, y)$, where each of the 3D points has also some unknown reflectivity $\alpha$ at the wavelength of the laser.
+We parameterize the geometry of the scene as a depth map $z(x, y)$, where each of the 3D points has also some unknown reflectivity $\alpha$ at the wavelength of the laser.
 Ignoring interreflections of the emitted light within the scene, a single-pixel diffused SPAD then integrates all the light scattered back from the scene towards the detector as
@@
 \begin{equation}
-	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \alpha \left( x,y \right) g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
+	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2}  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
 	\label{eq:pulse_integral} 
@@
 where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the diffuser.
-In this formulation, $\alpha$ also absorbs the square distance falloff of light and we assume that the diffuser spreads light uniformly over all angles.
+In this formulation, we assume that the diffuser spreads light uniformly over all angles.
 Each time such a light pulse is emitted into the scene and scattered back to the detector, the single-pixel SPAD time-stamps up to one of the returning photons with some probability.

### 2019-10-12 paper/cvpr2020/sections/hardware.tex
pass over simulated results section
Removed whitespace from comparison figure.

@@
-\begin{figure}[H]
-  \includegraphics[width=\linewidth]{prototype_single_col.pdf}
+\begin{figure}[t!]
+	\centering
+  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
   \caption{Prototype scanning setup. The pulsed light from the laser travels
@@
 The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.
-The SPAD records temporal histograms with 65536 bins, each corresponding to a time window of 4~ps.
+The SPAD records temporal histograms with 16384 bins, each corresponding to a time window of 16~ps.
 SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
@@
 
-Using this prototype, we captured a number of scenes as shown in Figure~\ref{fig:results_captured} and in the supplement.
-We downsample the reference RGB image to a resolution of $XX \times XX$~px and directly feed into a monocular depth estimation algorithm.
+Using this prototype, we captured a number of scenes as shown in
+Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
+to have dimensions that are multiples of 32. For DORN only, we further
+downsample the image to a resolution of $353 \times 257$. We then feed this RGB
+image into the monocular depth estimation algorithm.
 In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested.

### 2019-10-12 paper/cvpr2020/sections/figures/sync_figures.sh

@@ -4,7 +4,8 @@ gdrive="/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projec
 rsync captured/midas/8_30_small_lab_scene/teaser.pdf "$gdrive"
 rsync full_pipeline/full_pipeline.jpeg "$gdrive"
 shopt -s extglob  #Allows for | in bash pattern matching below
-rsync -r comparison/densedepth_?(468|194|258)_comparison.png "$gdrive/comparison"
+rsync -r comparison/densedepth_?(468|194|258)_comparison.pdf "$gdrive/comparison"
+rsync comparison.pdf "$gdrive"
 rsync prototype_single_col.pdf "$gdrive"
 rsync -R ././captured/**/**/?(gt_z_proj_crop_depth_fig|z_init_depth_fig|z_med_scaled_depth_fig|z_pred_depth_fig|rgb_cropped_fig|z_init_diff_fig|z_med_scaled_diff_fig|z_pred_diff_fig).png "$gdrive"
 rsync -R ././captured/**/**/?(diff_colorbar|depth_colorbar).pdf "$gdrive" 

### 2019-10-14 paper/cvpr2020/sections/hardware.tex
Updated method figure and supplement.

@@
 
-%We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
-%the scanning system using the standard camera calibration toolbox in MATLAB.
-%In general it is impossible to compensate for the offset between camera and
-%SPAD, but we do add the z displacement from spad to kinect to partially
-%compensate for it.
+We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
+the scanning system using the standard camera calibration toolbox in MATLAB.
+Once the SPAD volume has been summed over the spatial dimensions, it is unclear
+how to warp the resulting 1D transient to the RGB camera's perspective (in a
+single-pixel flash LiDAR setup, the $512 \times 512$ ground truth data is not
+available). However, we do shift the 1D transient by the $z$ displacement
+between the SPAD and the RGB camera to partially account for this.
+
 %% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}

### 2019-10-14 paper/cvpr2020/sections/method.tex
Updated method figure.
Updated method figure and supplement.

@@
   \centering
-  \includegraphics[width=\columnwidth]{full_pipeline.jpeg}
+  \includegraphics[width=\columnwidth]{method.pdf}
   \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
@@
 contain only ambient and dark count photons (this is equivalent to assuming the
-minimum image depth is larger than $N \cdot c\Delta T/2$), we estimate 
+minimum image depth is larger than $Nc\Delta T/2$), we estimate 
 and dark count rate $b$ as $\hat b = \frac{1}{N}\sum_{n=0}^N h[n]$ We then
@@
 \begin{equation}
-  \mathcal{E} = \mset{n}{d[n] > \alpha\sqrt{2\hat b}}.
+  \mathcal{E} = \mset{n}{d[n] > \beta\sqrt{2\hat b}}.
   \label{eq:edge_set}
 \end{equation}
-In this work, we use $\alpha = 2$.
+In this work, we use $\beta = 5$.
 We identify the closest and furthest edges $n_{first} = \min \mathcal{E}$ and
@@
   \Procedure{FindMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
-    \State Initialize $T$ as an $M \times N$ array.
+    \State Initialize $T$ as an $M \times N$ array of zeros.
     \For{$m$ in $1,\ldots,M$}
@@
 
-Finally, for a pixel $z_0[i, j]$ in depth bin $k$, we sample the new depth bin from the
+Finally, once we have obtained $T$, for a pixel $z_0[i, j]$ in depth bin $k$, we sample the new depth bin from the
 distribution $T[k, :]/\sum_{n=1}^NT[k,n]$ (which is a distribution over target

### 2019-10-14 paper/cvpr2020/sections/simulation.tex
Removed whitespace from comparison figure.
Updated method figure and supplement.

@@
 \begin{figure*}[!t]
-  \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.png}
-  \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.png}
+  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
+  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
+  \includegraphics[width=\textwidth]{comparison.pdf}
   %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
@@
 over the spatial dimension to get a 1D histogram $h$. We multiply each bin by
-$1/d^2$, which accounts for the radiometric falloff, and convolve with the SPAD
+$1/z^2$, which accounts for the radiometric falloff, and convolve with the SPAD
 jitter kernel, which we model as a standard Gaussian with a full-width
@@
 signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
-we Poisson sample each bin to get the final simulated SPAD transient.
+we Poisson sample each bin to get the final simulated SPAD transient (neglecting
+pile-up).
 % \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}

### 2019-10-15 paper/cvpr2020/sections/method.tex
Updated all figures with better z correction.

@@
 noise can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019} we adopt the term
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019}, we adopt the term
 \textit{transient} for our histogram $h[n]$.
@@
 \subsection{Ambient Rejection and Falloff Correction}
-To remove the ambient and dark count photons from the histogram, we apply a
-preprocessing step. Assuming that the first $N$ bins of the SPAD histogram
+To remove the ambient and dark count photons from the transient, we apply a
+preprocessing step. Assuming that the first $N$ bins of the SPAD transient
 contain only ambient and dark count photons (this is equivalent to assuming the
 minimum image depth is larger than $Nc\Delta T/2$), we estimate 
-and dark count rate $b$ as $\hat b = \frac{1}{N}\sum_{n=0}^N h[n]$ We then
-note that that shining a laser through a 2D diffuser and
-measuring a single pixel is very physically similar to recording a single 
-non-line-of-sight measurement. We
-compute the absolute first difference $d[n] = \abs{h[n] - h[n+1]}$ and find 
-the set of edges. Intuitively, given a sufficiently large value of $b$, the Poisson sample
-$h[n] \sim \mathcal{P}(b)$ should behave roughly like a Gaussian with variance $b$, and the difference
-$h[n] - h[n+1]$ should behave like a Gaussian with variance $2b$. Therefore, we
-can detect edges that occur between bins that contain actual signal photons and
-bins that do not by computing the set 
+and dark count rate $b$ as $\hat b = \frac{1}{N}\sum_{n=0}^N h[n]$. 
+We compute the absolute first difference $d[n] = \abs{h[n] - h[n+1]}$ and find 
+the set of edges. Intuitively, for adjacent non-signal-photon bins, $n_a$ and
+$n_a+1$, given a sufficiently large value of $b$, the Poisson random variable
+$h[n_a] \sim \mathcal{P}(b)$ should behave roughly like a Gaussian with variance $b$, and the difference
+$h[n_a] - h[n_a+1]$ should behave like a Gaussian with mean $0$ and variance $2b$. Therefore, we
+can locate candidates for discontinuities $d[n]$ that occur between signal bins and non-signal bins
+by computing the set 
 \begin{equation}
@@
 In this work, we use $\beta = 5$.
-We identify the closest and furthest edges $n_{first} = \min \mathcal{E}$ and
-$n_{last} = \max \mathcal{E}$.
-From \cite{Xin2019} Proposition 3, these edges
+We extract the closest and furthest edges $n_{first} = \min \mathcal{E}$ and
+$n_{last} = \max \mathcal{E}$ respectively.
+From \cite{Xin2019} Proposition 3 (noting that shining a laser through a 2D
+diffuser and accumulating the measurements into a single pixel is physically
+similar to recording a single non-line-of-sight measurement), these edges should
 correspond to the discontinuties in the depth map 

### 2019-10-15 paper/cvpr2020/sections/related.tex
Updated all figures with better z correction.

@@
 For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
-predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combined a logarithmic depth discretization scheme with an ordinal regression loss function.
+predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function.
 Various experiments using different types of encoder networks (e.g.

### 2019-10-15 nyuv2/captured/analyze_all_scenes.py

@@ -38,12 +38,12 @@ def cfg():
     # bin_width_ps is the bin width in picoseconds of the SPAD for that particular scene
     # min_r and max_r are set to reject direct reflections off the beam splitter.
     scenes = {
-        # "8_29_kitchen_scene": {"offset": (-10, -8), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        # "8_29_conference_room_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        # "8_30_conference_room2_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        # "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        # "8_30_poster_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        # "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_29_kitchen_scene": {"offset": (-10, -8), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_29_conference_room_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_conference_room2_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_poster_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
         "8_31_outdoor3": {"offset": (0, 0), "bin_width_ps": 32, "min_r": 0.4, "max_r": 11.},
     }
     # rgb in [0, 255]
@@ -104,8 +104,9 @@ def analyze(figures_dir, data_dir, calibration_file, models, scenes, use_intensi
             min_depth_bin = np.floor(min_r / bin_width_m).astype('int')
             max_depth_bin = np.floor(max_r / bin_width_m).astype('int')
             # Compensate for z translation only
[…]

### 2019-10-16 paper/cvpr2020/main.tex
pass over simulated results section
added paper to discuss
David's comments.

@@
+% TODO:
+%@article{caramazza2018neural,
+%  title={Neural network identification of people hidden from view with a single-pixel, single-photon detector},
+%  author={Caramazza, Piergiorgio and Boccolini, Alessandro and Buschek, Daniel and Hullin, Matthias and Higham, Catherine F and Henderson, Robert and Murray-Smith, Roderick and Faccio, Daniele},
+%  journal={Scientific reports},
+%  volume={8},
+%  number={1},
+%  pages={11945},
+%  year={2018},
+%  publisher={Nature Publishing Group}
+%}
+%
+
 \documentclass[10pt,twocolumn,letterpaper]{article}
@@
 %%%%%%%%% TITLE
-\title{Optimizing Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD}
+\title{Optimizing Monocular Depth Estimation with Global Depth Histogram
+  Matching using a Single SPAD Transient}
 
@@
 First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
+{\tt\small secondauthor@i2.org
+\end{document}
+}
 }

### 2019-10-16 paper/cvpr2020/sections/method.tex
David's comments.

--- 2019-10-14 paper/cvpr2020/sections/method.tex
@@
 
-Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying intensity $g(t)$ illuminating some 3D scene.
-We parameterize the geometry of the scene as a depth map $z(x, y)$, where each of the 3D points has also some unknown reflectivity $\alpha$ at the wavelength of the laser.
-Ignoring interreflections of the emitted light within the scene, a single-pixel diffused SPAD then integrates all the light scattered back from the scene towards the detector as
+Consider a diffused laser that emits a pulse at time $t = 0$ with time-varying
+intensity $g(t)$ illuminating some 3D scene. We parameterize the geometry of the
+scene as a distance map $z(x, y)$, where each of the 3D points has also some
+unknown reflectivity $\alpha$ at the wavelength of the laser. Ignoring
+interreflections of the emitted light within the scene, a single-pixel diffused
+SPAD integrates the light scattered back from the scene towards the
+detector as
 %
@@
 %
-where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the diffuser.
-In this formulation, we assume that the diffuser spreads light uniformly over all angles.
-Each time such a light pulse is emitted into the scene and scattered back to the detector, the single-pixel SPAD time-stamps up to one of the returning photons with some probability.
-This is not necessarily the first returning photon.
-The process is repeated millions of times per second with the specific number of emitted pulsed being controlled by the repetition rate of the laser, which is typically adjusted to match the deadtime of the SPAD~\cite{Heide:2018}.
-Each detected photon arrival event is discretized into a histogram $h$ of the form
+where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the
+diffuser. In this formulation, we assume that the diffuser spreads light
+uniformly over all angles. Each time such a light pulse is emitted into the
+scene and scattered back to the detector,
+the single-pixel SPAD time-stamps up to one of the returning photons with some
+probability. The process is
+repeated millions of times per second with the specific number of emitted pulses
+being controlled by the repetition rate of the laser.
+Each detected
+photon arrival event is discretized into a histogram $h$ of the form
 %
@@
 is a function that models the temporal uncertainty in the detector, and $b$
-represents ambient background light and falsely detected photons known as dark
-count. As derived in previous work, the combination of signal, background, and
+represents ambient background light and false positive detections known as \textit{dark
+count}. As derived in previous work, the combination of signal, background, and
 noise can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019} we adopt the term
-\textit{transient} for our histogram $h[n]$.
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019}, we adopt the term
+\textit{transient} for the histogram $h[n]$.
 
 \subsection{Ambient Rejection and Falloff Correction}
-To remove the ambient and dark count photons from the histogram, we apply a
-preprocessing step. Assuming that the first $N$ bins of the SPAD histogram
+Before histogram matching can be applied, the raw SPAD transient is processed in
+three stages.
+
+In the first stage, we remove the ambient and dark count photons from the transient. 
+We compute an estimate of $b$ by assuming that the first $N$ bins of the SPAD transient
 contain only ambient and dark count photons (this is equivalent to assuming the
-minimum image depth is larger than $Nc\Delta T/2$), we estimate 
-and dark count rate $b$ as $\hat b = \frac{1}{N}\sum_{n=0}^N h[n]$ We then
-note that that shining a laser through a 2D diffuser and
-measuring a single pixel is very physically similar to recording a single 
-non-line-of-sight measurement. We
-compute the absolute first difference $d[n] = \abs{h[n] - h[n+1]}$ and find 
-the set of edges. Intuitively, given a sufficiently large value of $b$, the Poisson sample
-$h[n] \sim \mathcal{P}(b)$ should behave roughly like a Gaussian with variance $b$, and the difference
-$h[n] - h[n+1]$ should behave like a Gaussian with variance $2b$. Therefore, we
-can detect edges that occur between bins that contain actual signal photons and
-bins that do not by computing the set 
+minimum image distance is larger than $Nc\Delta T/2$) as:
+\begin{equation}
+  \hat b = \frac{1}{N}\sum_{n=0}^N h[n]. 
+  \label{eq:ambient_estimate}
+\end{equation}
+We identify the first and last bins $n_{first}$ and $n_{last}$
+corresponding to the minimum and maximum scene depths. We do this with a simple
+edge thresholding procedure, computing the absolute first difference $d[n] =
+\abs{h[n] - h[n+1]}$. If $h[n]$ and $h[n+1]$ are sampled according to $\mathcal{P}(b)$ and $b$ is large, then 
+$h[n] - h[n+1]$ is well-approximated with a Gaussian with mean $0$ and variance $2b$.
+Therefore, we can extract a candidate edge set $\mathcal{E}$ as:
 \begin{equation}
@@
 \end{equation}
-In this work, we use $\beta = 5$.
-We identify the closest and furthest edges $n_{first} = \min \mathcal{E}$ and
-$n_{last} = \max \mathcal{E}$.
-From \cite{Xin2019} Proposition 3, these edges
-correspond to the discontinuties in the depth map 
-at the closest and furthest image depths, and therefore all of the signal
-photons must be in the bins between these two edges.
-We refine these estimates by
-computing $n'_{first} = \max\set{n_{first}}\cup\mset{n}{h[n] > \hat b, n \leq n_{first}}$ and
-$n'_{last} = \min\set{n_{last}}\cup\mset{n}{h[n] > \hat b, n \geq n_{last}}$
+In this work, we use $\beta = 5$, as it gives good results across both simulated
+and captured data.
+We compute initial estimates $n'_{first} = \min \mathcal{E}$ and
+$n'_{last} = \paren*{\max \mathcal{E}} + 1$ respectively. By appealing to Proposition 3 in
+\cite{Xin2019} and noting the similarity of our approach to collecting a single
+non-line-of-sight SPAD measurement we can conclude that our estimates must be
+close to the true values of $n_{first}$ and $n_{last}$.
+We refine these estimates by walking them outwards until their bin values drop
+below the ambient estimate $\hat b$, resulting in
+$\hat n_{first} = \max\paren*{\set{n'_{first}}\cup\mset{n}{h[n] > \hat b, n \leq n'_{first}}}$ and
+$\hat n_{last} = \min\paren*{\set{n'_{last}}\cup\mset{n}{h[n] > \hat b, n \geq n'_{last}}}$.
 Finally, we reject all photons outside of the valid range by clamping those bins
 to 0, and we subtract our ambient estimate from the photons within the valid
-range, giving an ambient-free transient
+range:
 \begin{equation}
   h'_{clean}[n] = \begin{cases}
-    0 & n < n'_{first} \\
-    \max(h[n] - \hat b, 0) & n'_{first} \leq n \leq n'_{last} \\
-    0 & n > n'_{last} \\
+    0 & n < \hat n_{first} \\
+    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
+    0 & n > \hat n_{last} \\
   \end{cases}.
@@
 \end{equation}
-To compensate for the radiometric falloff, we scale each bin by its squared depth,
-which is consistent with our hardware prototype's radiometric falloff model.
-This gives
+
+In the second stage, we set 
 \begin{equation}
@@
 where $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the depth
-corresponding to bin $n$
-As a final preprocessing step, we re-bin the transient, applying the Spacing-Increasing Discretization
-(SID) of \cite{Fu2018} to produce $h_{target}$. This reduces the number of bins in the histogram
-matching procedure, giving speedups while maintaining performance. In this work,
-we use 140 bins for the simulated results and 600 bins for the captured results.
+corresponding to bin $n$. This compensates for the radiometric falloff in a way
+that is consistent with our hardware prototype's falloff model
+
+In the final stage, we re-bin the transient, applying the Spacing-Increasing Discretization
+(SID) of \cite{Fu2018} to produce $h_{target}$. This discretization scheme is
+exponential rather than linear, allocating more bins to closer distances and fewer
+bins to farther distances. The bin edges $t_i$ are given by the following equation,
+parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
+\begin{equation}
+  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad i = 0,\ldots, K.
+  \label{eq:sid_bin_edges}
+\end{equation}
+This reduces the number of bins in the histogram
+matching procedure, giving speedups while maintaining performance. For the
+simulated results,
+we use $K = 140$ bins, and $(\ell, u) = (0.657, 9.972)$, (these numbers are
+inspired by the discretization scheme for the original DORN network in
+\cite{Fu2018})
+ For the indoor caputred results, we use $K = 600$ bins, and $(\ell, u)=(0.4, 9) + \epsilon$ 
+and for the outdoor captured results, we use $K=600$ and $(\ell, u)=(0.4, 11) +
+\epsilon$ where $\epsilon \approx 0.094$ is the $z$ offset between the
+SPAD and the Kinect (see Hardware for details).
 
@@
 
-\subsection{Exact Histogram Matching}
+\subsection{Histogram Matching}
 % \begin{algorithm}[H]
@@
 % \end{algorithm}
-Exact histogram matching is a procedure that takes a source image and a target
+Histogram matching is a procedure that takes a source image and a target
 histogram and maps the pixel values of the source image so that the image's
 histogram matches the target histogram. Given a single RGB image, we pass it
-through an MDE to produce a depth map $\hat z_0 \in [\ell, u]^{M \times N}$
-where $\ell$ and $u$ are the lower and upper bounds of the depth range of
-interest, respectively. In a parallel processing step,
-we compute an estimate of the scene albedo using an intrinsic imaging method and
+through an MDE to produce a depth map. In a parallel processing step,
+we compute an estimate $W$ of the scene albedo using an intrinsic imaging method and
 take the color channel of the resulting albedo image that corresponds to the
-wavelength of the laser illumination. This gives a reflectance estimate $W \in
-[0, 1]^{M \times N}$. We
-then compute a weighted histogram $h_{source}$of the depth map $\hat z_0$ where the
+wavelength of the laser illumination.
+We then compute a weighted histogram $h_{source}$ of the depth map $\hat z_0$ where the
 per-pixel weights are given by $W$, and the bin edges are given by the SID
-discretization algorithm of \cite{Fu2018}.
+discretization algorithm in \cite{Fu2018}.
 
@@
 \cite{Morovic2002}. We compute a pixel movement
-matrix $T$ such that $T_{mn}$ is the amount of mass to move from $h_{source}[m]$
-to $h_{target}$. We do so using the procedure outlined in \ref{alg:pixel_movement}
+matrix $T$ such that $T[m, n]$ is the amount of mass that must be moved from $h_{source}[m]$
+to $h_{target}[n]$. We do so using the procedure outlined in \ref{alg:ehm}
 
@@
       \For{$n$ in $1,\ldots,N$}
-        \State $p_s \gets \sum_{\ell=1}^{n-1} T[m, \ell]$
-        \State $p_t \gets \sum_{\ell=1}^{m-1} T[\ell, n]$
+        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
+        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
         \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
@@
 
-Finally, once we have obtained $T$, for a pixel $z_0[i, j]$ in depth bin $k$, we sample the new depth bin from the
+Finally, once we have obtained $T$, for a pixel $z_0[i, j]$ in bin $k$, we sample the new bin from the
 distribution $T[k, :]/\sum_{n=1}^NT[k,n]$ (which is a distribution over target

### 2019-10-17 paper/cvpr2020/sections/supplement/hardware_comparison.tex
Updated method figure and supplement.
Working on supplement, revised get_hist_med to actually get the median.

@@
-\begin{figure*}[t!]
+\begin{figure}[H]
     \centering
@@
     \caption{Captured results initialized using the MiDaS CNN.
-      Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:midas_captured}
+      Second row shows absolute difference between above estimates and ground
+      truth. MiDaS does not output metric depth, so the CNN depth maps are
+      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
+      accurate ordinal depth, leading to stronger performance of our histogram
+      matching compared to other methods.}
+    \label{fig:midas_captured_1}
 %    \vspace{-1.5em}
-\end{figure*}
-\begin{figure*}[t!]
+\end{figure}
+\begin{figure}[H]
     \centering
@@
     \caption{Captured results initialized using the MiDaS CNN.
-      Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:midas_captured}
+      Second row shows absolute difference between above estimates and ground truth.MiDaS does not output metric depth, so the CNN depth maps are
+      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
+      accurate ordinal depth, leading to stronger performance of our histogram
+      matching compared to other methods.}
+    \label{fig:midas_captured_2}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}
 
-%% MiDaS outdoor scene
-\begin{figure*}[t!]
+% %% MiDaS outdoor scene
+\begin{figure}[H]
     \centering
@@
     \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
-      Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:midas_outdoor_captured}
+      Second row shows absolute difference between above estimates and ground
+      truth. MiDaS does not output metric depth, so the CNN depth map is
+      scaled to be in the range $(0.494, 11.094)$ by default. However, MiDaS does produce
+      accurate ordinal depth, leading to stronger performance of our histogram
+      matching compared to other methods.
+}
+    \label{fig:midas_captured_3}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[t!]
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:densedepth_captured}
+    \label{fig:densedepth_captured_1}
 %    \vspace{-1.5em}
-\end{figure*}
-\begin{figure*}[t!]
+\end{figure}
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:densedepth_captured}
+    \label{fig:densedepth_captured_2}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}
 %% DenseDepth outdoor scene
-\begin{figure*}[t!]
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:densedepth_outdoor_captured}
+    \label{fig:densedepth_captured_3}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\begin{figure*}[t!]
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:densdepth_captured}
+    \label{fig:dorn_captured_1}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}
 
-\begin{figure*}[t!]
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:dorn_captured}
+    \label{fig:dorn_captured_2}
 %    \vspace{-1.5em}
-\end{figure*}
-%% DORN outdoor scene
-\begin{figure*}[t!]
+\end{figure}
+% %% DORN outdoor scene
+% \begin{figure}
+%     \centering
+%     \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{1.15in}}c}
+%       \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
+%       &
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_init_depth_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_med_scaled_depth_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_pred_depth_fig.png}&
+%       \includegraphics[height=1.15in]{captured/dorn/8_31_outdoor3/depth_colorbar.pdf}\\
+% %      & RGB &  &  &  & \\
+%       &
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/rgb_cropped_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_init_diff_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_med_scaled_diff_fig.png}&
+%       \includegraphics[height=1.15in, width=1.15in]{captured/dorn/8_31_outdoor3/z_pred_diff_fig.png}&
+%       \includegraphics[height=1.15in]{captured/dorn/8_31_outdoor3/diff_colorbar.pdf}\\
+%       & RGB & \input{sections/figures/captured/dorn/8_31_outdoor3/rmses.tex}& \\ 
+%     \end{tabular}
+%     \caption{Captured results initialized using the DORN CNN on an outdoor scene.
+%       Second row shows absolute difference between above estimates and ground truth.}
+%     \label{fig:dorn_outdoor_captured}
+% %    \vspace{-1.5em}
+% \end{figure}
+
+\begin{figure}[H]
     \centering
@@
       Second row shows absolute difference between above estimates and ground truth.}
-    \label{fig:dorn_outdoor_captured}
+    \label{fig:dorn_captured_3}
 %    \vspace{-1.5em}
-\end{figure*}
+\end{figure}

### 2019-10-17 paper/cvpr2020/supplement.tex
Updated method figure and supplement.
Working on supplement, revised get_hist_med to actually get the median.

@@
 \usepackage{multirow}
+\usepackage{float}
+\usepackage[utf8x]{inputenc}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{algorithmicx}
+
+\usepackage{dblfloatfix}
+
 \input{mark_defs.tex}
+
 % If you comment hyperref and then uncomment it, you should delete
@@
 \maketitle
-% \input{sections/supplement/simulation_comparison.tex}
+\section{Ablation study on number of SID bins}
+\begin{itemize}
+  \item Simulation: 70, 140, 210, 280 bins
+  \item Captured: 70, 140, 210, 280 bins
+\end{itemize}
+Compare RMSE and runtime.
+\section{Ablation study on effect of reflectance estimation}
+\begin{itemize}
+  \item Intensity used to initialize histogram, not used to move pixels
+  \item Intensity used to initialize histogram and move pixels
+  \item Intensity not used to initialize histogram, used to move pixels
+  \item Intensity not used to initialize histogram, not used to move pixels
+\end{itemize}
+Compare RMSE and runtime.
+
+\section{Additional results on NYU Depth v2}
+Figures \ref{fig:densedepth_1}--\ref{fig:dorn_3} show additional results
+for our method on the NYU Depth v2 dataset when the depth estimate is
+initialized with the DenseDepth \cite{Alhashim2018} (Figures
+\ref{fig:densedepth_1}--\ref{fig:densedepth_3}), and DORN \cite{Fu2018} (Figures
+\ref{fig:dorn_1}--\ref{fig:dorn_3}) monocular depth estimators.
+% and MiDaS \cite{MiDaS} (Figures \ref{midas_1} -- \ref{midas_3}).
+% network of \cite{Alhashim2019}.
+We compare the output of the network $z_0$, the
+median-rescaled network output (where the depth map $z_0$ is scaled pixel-wise by a
+scalar $\frac{\text{median}(z_{GT})}{\text{median}(z_0)}$, $z_{GT}$ being the
+ground truth depth map), the network output matched to the ground truth depth histogram, and the output of
+our histogram matching method under a signal-to-background ratio (SBR) of 100.
+We use the Y channel of the YCbCr-transformed RGB image as our reflectance map
+for both SPAD simulation and histogram matching.
+We show absolute difference maps and also give
+the root-mean-square error (RMSE) for each example.
+\input{sections/supplement/simulation_comparison.tex}
+
+\section{Additional results for hardware prototype}
+Figures \ref{fig:midas_captured_1}--\ref{fig:dorn_captured_3} show all the
+captured results when the depth estimate is initialized with the MiDaS
+\cite{Lasinger:2019} (Figures \ref{fig:midas_captured_1}--\ref{fig:midas_captured_3}),
+DenseDepth (Figures \ref{fig:densedepth_captured_1}--\ref{fig:densedepth_captured_3}),
+and DORN (Figures \ref{fig:dorn_captured_1}--\ref{fig:dorn_captured_3}). We compare
+the output of the network $z_0$, the mean-rescaled network output where the
+depth map $z_0$ has been scaled pixel-wise by the scalar
+$\frac{\text{median}(h_{target})}{\text{median}(z_0)}$ ($h_{target}$ is the
+processed SPAD transient), and the output of our method. As our laser is red, we
+use the R channel of the RGB image as our reflectance map. We show absolute
+difference maps and also give the root-mean-square-error (RMSE) for each
+example.
+
+Black pixels in the ground truth depth correspond to locations where our scanner
+was unable to produce an accurate depth estimate (this can occur for a variety
+of reasons including dark albedo and surface specularity). These pixels are masked off and not used in the RMSE
+calculation, and appear as an absolute difference of 0 in the difference maps.
 \input{sections/supplement/hardware_comparison.tex}
+
+{\small
+\bibliographystyle{ieee_fullname}
+\bibliography{references}
+}
+
 \end{document}

### 2019-10-17 nyuv2/captured/capture_utils.py

@@ -105,9 +105,10 @@ def get_closer_to_mod(lower, upper, mod):
 
 def get_hist_med(histogram):
     """Returns the mean bin value"""
-    idx = np.array(range(len(histogram)))
     pdf = histogram/np.sum(histogram)
-    return np.floor(idx.dot(pdf))
+    cdf = np.cumsum(pdf)
+    med = (cdf > 0.5).argmax()
+    return med
 
 
 def savefig_no_whitespace(filepath):

### 2019-10-17 nyuv2/weighted_histogram_matching/evaluate_densedepth.py

@@ -9,6 +9,7 @@ from spad_utils import rescale_bins
 from remove_dc_from_spad import remove_dc_from_spad_poisson, remove_dc_from_spad_ambient_estimate,\
     remove_dc_from_spad_edge
 from nyuv2_labeled_dataset import nyuv2_labeled_ingredient, load_data
+from models.core.checkpoint import safe_makedir
 
 from models.loss import get_depth_metrics
 
@@ -71,6 +72,8 @@ def run(dataset_type,
         sid_bins, alpha, beta, offset,
         intensity_ablation, vectorized,
         entry, save_outputs, small_run, output_dir):
+    safe_makedir(output_dir)
+
     # Load all the data:
     print("Loading SPAD data from {}".format(spad_file))
     spad_dict = np.load(spad_file, allow_pickle=True).item()

### 2019-10-18 paper/cvpr2020/main.tex
Working on supplement, revised get_hist_med to actually get the median.
pass over paper

@@
 \usepackage{algorithmicx}
-
 \usepackage{dblfloatfix}
@@
 
-\graphicspath{{"G:/Shared drives/Stanford Computational
+\graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
     Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
@@
 First line of institution2 address\\
-{\tt\small secondauthor@i2.org
-\end{document}
-}
+{\tt\small secondauthor@i2.org}
 }

### 2019-10-18 paper/cvpr2020/sections/hardware.tex
Updated all figures with better z correction.
pass over paper

@@
     through a beam splitter before being guided by the galvo to the scene.
-    Returning light is measured by the single-pixel SPAD. The RGB camera of a
-    Kinect v2 is used to capture the monocular RGB image (the depth camera is
-    not used)}
+    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
+    camera is used to capture the image used to generate the monocular depth estimate
+    (the depth camera is not used).}
   \label{fig:prototype}
@@
 The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.
-The SPAD records temporal histograms with 16384 bins, each corresponding to a time window of 16~ps.
-SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
+
+The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps.
+The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
 The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm.
 A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
-The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels.
-The single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
-This allows us to validate the accuracy of the proposed histogram matching algorithm that only uses the single histogram of the diffused SPAD and compare it with ground truth.
+The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
+This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparison with the captured depth.
 Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.
@@
 the scanning system using the standard camera calibration toolbox in MATLAB.
-Once the SPAD volume has been summed over the spatial dimensions, it is unclear
-how to warp the resulting 1D transient to the RGB camera's perspective (in a
-single-pixel flash LiDAR setup, the $512 \times 512$ ground truth data is not
-available). However, we do shift the 1D transient by the $z$ displacement
-between the SPAD and the RGB camera to partially account for this.
+While the SPAD histogram and RGB image are captured from slightly different viewpoints, we approximately calibrate the SPAD histogram for this by shifting the 1D transient by the calibrated $z$ offset from the RGB camera.
+%We use the camera extrinsics to Once the SPAD volume has been summed over the spatial dimensions, it is unclear
+%how to warp the resulting 1D transient to the RGB camera's perspective (in a
+%single-pixel flash LiDAR setup, the $512 \times 512$ ground truth data is not
+%available). However, we do shift the 1D transient by the $z$ displacement
+%between the SPAD and the RGB camera to partially account for this.
 
+We re-bin the captured 1D transient for the indoor captured results 
+using Equation~\ref{eq:sid_bin_edges} with $K = 600$ bins, and $(\ell, u)=(0.4, 9.)$.
+For the outdoor captured result, we use $K=600$ and $(\ell, u)=(0.4, 11)$. 
 %% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
@@
 
-Using this prototype, we captured a number of scenes as shown in
+Using the hardware prototype, we captured a number of scenes as shown in
 Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
@@
 
-In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonable well.
-However, the root mean squared error (RMSE) for these two scenes is relatively high with 2.4--2.9~m (see red/white error maps in Fig.~\ref{fig:results_captured}).
+In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonably well.
+However, the root mean squared error (RMSE) for these two scenes is relatively high ranging from 2.6--3.2~m (see red/white error maps in Fig.~\ref{fig:results_captured}).
 The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{captured_results_main}
+	\includegraphics[width=\columnwidth]{captured.pdf}
 	\caption{Experimental results.
-For each scene, we record an RGB image (lower left subimages) and a ground truth depth map that is raster-scanned with the SPAD (upper left subimages).
-A monocular depth CNN often predicts the ordinal depth well (top two scenes), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages) as shown by the error maps and root mean squared error (RMSE) for each example (lower center and right subimages).
+For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left subimages).
+A monocular depth CNN predicts an initial depth map (top middle subimages), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages).
+As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right subimages).
 The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print.

### 2019-10-18 paper/cvpr2020/sections/method.tex
pass over paper

@@
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{method.pdf}
-  \caption{\textbf{Overview of the full pipeline} We use a CNN to get an initial
-  per-pixel depth estimate. Then we perform exact histogram matching using
-  intensity-weighted pixel values on the corrected SPAD data.}
-\end{figure}
-
-Monocular depth estimation is a well-explored, yet active area of research (see Sec.~\ref{sec:related}).
-Any network trained for the MDE task takes as input an RGB image and estimates the depth map of the scene.
-Our approach augments existing MDE networks but is agnostic to the specific type of depth estimator.
-Indeed we show in Section~\ref{sec:evaluation} that our histogram matching technique equally improves a variety of different pre-trained estimators.
-In the remainder of this section, we therefore focus on modeling the image formation of a diffused single-photon avalanche diode (SPAD) and develop an approach to correcting an estimated depth map to match the global scene information captured by the SPAD.
+In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD).
+We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the diffused SPAD.
 
@@
 interreflections of the emitted light within the scene, a single-pixel diffused
-SPAD integrates the light scattered back from the scene towards the
-detector as
+SPAD integrates light scattered back from the scene onto the detector as
 %
 \begin{equation}
-	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2}  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
+	s \left( t \right)= \int_{\Omega_x} \int_{\Omega_y} \frac{\alpha \left( x,y \right)}{z(x,y)^2} \cdot  g \left( t - \frac{2z(x,y)}{c} \right) dx dy ,
 	\label{eq:pulse_integral} 
@@
 %
-where $c$ is the speed of light and $\Omega_{x,y}$ is the angular range of the
-diffuser. In this formulation, we assume that the diffuser spreads light
-uniformly over all angles. Each time such a light pulse is emitted into the
-scene and scattered back to the detector,
-the single-pixel SPAD time-stamps up to one of the returning photons with some
-probability. The process is
-repeated millions of times per second with the specific number of emitted pulses
-being controlled by the repetition rate of the laser.
-Each detected
-photon arrival event is discretized into a histogram $h$ of the form
+where $c$ is the speed of light, $\Omega_{x,y}$ is the spatial extent of the
+diffused light, and we assume that the light is diffused uniformly over the
+scene points. Each time such a light pulse is emitted into the scene and
+scattered back to the detector, the single-pixel SPAD time-stamps up to one of
+the returning photons with some probability. The process is repeated millions of
+times per second with the specific number of emitted pulses being controlled by
+the repetition rate of the laser.  Each detected photon arrival event is
+discretized into a histogram $h$ of the form
 %
@@
 %
-where $(n\Delta t, (n+1) \Delta t)$ models the $n^{th}$ time interval of the
+where $(n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
 temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
 is a function that models the temporal uncertainty in the detector, and $b$
-represents ambient background light and false positive detections known as \textit{dark
-count}. As derived in previous work, the combination of signal, background, and
-noise can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, as in \cite{Xin2019}, we adopt the term
-\textit{transient} for the histogram $h[n]$.
+represents background detections from ambient light and false positive detections known as \textit{dark
+count}. As derived in previous work, the combination of signal and background
+can be modeled as an inhomogeneous Poisson process
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, we adopt the term
+\textit{transient} for the histogram $h[n]$~\cite{Xin2019}.
 
-\subsection{Ambient Rejection and Falloff Correction}
-Before histogram matching can be applied, the raw SPAD transient is processed in
-three stages.
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{method.pdf}
+  \caption{\textbf{Overview of processing pipeline} The processing pipeline uses
+      the input SPAD measurements and an RGB image to produce an accurate depth
+      map. The SPAD measurements are pre-processed to adjust for ambient photon
+      detections, radiometric falloff factors, and to calibrate the bin widths.
+      From the RGB image, an MDE estimates an initial depth map
+      and the scene reflectance is estimated. A reflectance-weighted
+      depth histogram is compared to the processed SPAD measurements to
+      calculate a histogram matching matrix which is used to output the corrected depth map.
+  }
+  \label{fig:pipeline}
+\end{figure}
 
-In the first stage, we remove the ambient and dark count photons from the transient. 
-We compute an estimate of $b$ by assuming that the first $N$ bins of the SPAD transient
-contain only ambient and dark count photons (this is equivalent to assuming the
-minimum image distance is larger than $Nc\Delta T/2$) as:
+\subsection{Ambient Rejection and Falloff Correction} Before performing
+histogram matching, we apply three pre-processing steps to (1)
+remove background counts from the transient, (2) compensate for distance
+falloff effects, and (3) re-bin the histogram to improve relative accuracy
+with increasing distance. An overview of the processing pipeline, including
+these preprocessing steps and the histogram matching procedure is depicted in
+Figure~\ref{fig:pipeline}.
+
+In the first step, we remove the background counts from the
+transient by initally estimating the average amount of background counts
+in each time bin. For nearly all natural scenes, the closest objects to the
+camera are a finite distance away, and so the first bins of the SPAD
+measurement contain only background counts without any backscattered
+signal. We can therefore estimate the
+average number of background and noise counts $\hat{b}$ as 
+%
 \begin{equation}
@@
 \end{equation}
-We identify the first and last bins $n_{first}$ and $n_{last}$
-corresponding to the minimum and maximum scene depths. We do this with a simple
-edge thresholding procedure, computing the absolute first difference $d[n] =
-\abs{h[n] - h[n+1]}$. If $h[n]$ and $h[n+1]$ are sampled according to $\mathcal{P}(b)$ and $b$ is large, then 
-$h[n] - h[n+1]$ is well-approximated with a Gaussian with mean $0$ and variance $2b$.
-Therefore, we can extract a candidate edge set $\mathcal{E}$ as:
+%
+where we choose the number of bins $N$ to correspond to time
+values before the backscattered signal arrives.
+
+While simply subtracting $\hat{b}$ from the measurements would remove many of
+the background counts, a large number of bins containing only background counts would still
+have non-zero values, resulting in a skewed
+estimate after applying histogram matching.  Instead, we estimate the temporal
+support of histogram bins containing signal photons (\ie the range of depths the
+scene) and only subtract $\hat{b}$ from these bins. We assume that other
+histogram bins contain only background counts that can be discarded.
+
+Specifically, we identify the first and last bins that record backscattered signal
+photons by locating discontinuities in the recorded counts~\cite{Xin2019}. An initial spike in
+the measurements at bin $n_\text{first}$ results from the onset of backscattered signal from the closest
+object, and a steep dropoff occurs after bin $n_\text{last}$ after backscattered photons from the
+furthest object are recorded. 
+We estimate $n_\text{first}$ and $n_\text{last}$ by calculating  
+first order differences of the histogram $d[n] = \abs{h[n] - h[n+1]}$. 
+For a moderate number of background counts, the variance of $h[n] - h[n+1]$ can be approximated  
+as a Gaussian with mean $0$ and variance $2b$, and we identify candidate discontinuities
+$\mathcal{E}$ with a threshold on the measured differences:
+%
 \begin{equation}
@@
 \end{equation}
-In this work, we use $\beta = 5$, as it gives good results across both simulated
-and captured data.
-We compute initial estimates $n'_{first} = \min \mathcal{E}$ and
-$n'_{last} = \paren*{\max \mathcal{E}} + 1$ respectively. By appealing to Proposition 3 in
-\cite{Xin2019} and noting the similarity of our approach to collecting a single
-non-line-of-sight SPAD measurement we can conclude that our estimates must be
-close to the true values of $n_{first}$ and $n_{last}$.
-We refine these estimates by walking them outwards until their bin values drop
-below the ambient estimate $\hat b$, resulting in
-$\hat n_{first} = \max\paren*{\set{n'_{first}}\cup\mset{n}{h[n] > \hat b, n \leq n'_{first}}}$ and
-$\hat n_{last} = \min\paren*{\set{n'_{last}}\cup\mset{n}{h[n] > \hat b, n \geq n'_{last}}}$.
-Finally, we reject all photons outside of the valid range by clamping those bins
-to 0, and we subtract our ambient estimate from the photons within the valid
-range:
+We find that $\beta = 5$ yields good results across both simulated and captured
+data.
+
+Initial estimates $n'_\text{first}$ and $n'_\text{last}$ are set to the minimum
+value in $\mathcal{E}$ and the maximum value, incremented by one bin. 
+Then, we refine these estimates by selecting the closest bins that remain above
+a threshold $\tau$ such that
 \begin{equation}
-  h'_{clean}[n] = \begin{cases}
-    0 & n < \hat n_{first} \\
-    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
-    0 & n > \hat n_{last} \\
-  \end{cases}.
-  \label{eq:h_clean}
+    \begin{split}
+        &\hat n_\text{first}=\min\{n : h[n] > \tau, h[n+1] > \tau,
+            \cdots, h[n'_\text{first}] > \tau\}\\
+        &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
+    \cdots, h[n+1] > \tau, h[n] > \tau\}.
+    \end{split}
 \end{equation}
+The remaining ambient counts are discarded by settings the recorded counts to
+zero for all bins where $n < n_\text{last}$ and $n > n_\text{last}$.
 
-In the second stage, we set 
+%Finally, we reject all photons outside of the valid range by
+%clamping those bins to 0, and we subtract our ambient estimate from the photons
+%within the valid range:
+%\begin{equation}
+%  h'_{clean}[n] = \begin{cases}
+%    0 & n < \hat n_{first} \\
+%    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
+%    0 & n > \hat n_{last} \\
+%  \end{cases}.
+%  \label{eq:h_clean}
+%\end{equation}
+
+In the second step, we compensate for distance falloff effects by multiplying the histogram
+by distance-dependent scaling factor,
 \begin{equation}
-  h_{clean}[n] = h'_{clean}[n] \cdot r_n^2
+    h'[n] = h[n] \cdot r_n^2.
   \label{eq:h_scaled}
 \end{equation}
-where $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the depth
-corresponding to bin $n$. This compensates for the radiometric falloff in a way
-that is consistent with our hardware prototype's falloff model
+Here, $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
+corresponding to bin $n$, and this radiometric falloff model is consistent with
+measurements captured with our hardware prototype.
 
-In the final stage, we re-bin the transient, applying the Spacing-Increasing Discretization
-(SID) of \cite{Fu2018} to produce $h_{target}$. This discretization scheme is
-exponential rather than linear, allocating more bins to closer distances and fewer
-bins to farther distances. The bin edges $t_i$ are given by the following equation,
+Last, we re-bin the transient so that the bin widths increase for increasingly
+distant objects. We select the Spacing-Increasing Discretization
+(SID) method of \cite{Fu2018}, which changes the bin widths according to an  
+exponential function, allocating more bins to closer distances and fewer
+bins to farther distances for a fixed number of bins. The bin edges $t_i$ are
+given by the following equation,
 parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
@@
 \end{equation}
-This reduces the number of bins in the histogram
-matching procedure, giving speedups while maintaining performance. For the
-simulated results,
-we use $K = 140$ bins, and $(\ell, u) = (0.657, 9.972)$, (these numbers are
-inspired by the discretization scheme for the original DORN network in
-\cite{Fu2018})
- For the indoor caputred results, we use $K = 600$ bins, and $(\ell, u)=(0.4, 9) + \epsilon$ 
-and for the outdoor captured results, we use $K=600$ and $(\ell, u)=(0.4, 11) +
-\epsilon$ where $\epsilon \approx 0.094$ is the $z$ offset between the
-SPAD and the Kinect (see Hardware for details).
+This rebinning procedure allows us to use a reduced number of bins in the histogram
+matching procedure, reducing computation time while maintaining accuracy. For
+the simulated results we follow Fu et al.\ and use $K = 140$ bins with $(\ell, u)
+= (0.657, 9.972)$~\cite{Fu2018}. The output of the rebinning procedure is the
+target histogram $h_\text{target}$ which we use for histogram matching.
 
@@
 % \end{algorithm}
-Histogram matching is a procedure that takes a source image and a target
-histogram and maps the pixel values of the source image so that the image's
-histogram matches the target histogram. Given a single RGB image, we pass it
-through an MDE to produce a depth map. In a parallel processing step,
-we compute an estimate $W$ of the scene albedo using an intrinsic imaging method and
-take the color channel of the resulting albedo image that corresponds to the
-wavelength of the laser illumination.
-We then compute a weighted histogram $h_{source}$ of the depth map $\hat z_0$ where the
-per-pixel weights are given by $W$, and the bin edges are given by the SID
-discretization algorithm in \cite{Fu2018}.
+Histogram matching is a procedure that adjusts pixel values from an input image
+so that the image histogram matches a target histogram. We apply this procedure
+to match the histogram of an input depth map, obtained from an MDE, to the
+post-processed target histogram $h_\text{target}$ from the SPAD.
+
+The MDE cannot be directly histogram-matched to the target histogram
+because the target histogram incorporates the spatially varying reflectance of
+the scene. To account for reflectance in the histogram matching procedure,
+we use the normalized image color channel closest to the laser wavelength as an
+estimate of the reflectance and compute a reflectance-weighted depth histogram
+$h_\text{source}$;
+instead of incrementing a bin in the depth histogram by one for every pixel in the MDE
+at the corresponding depth, we add the estimated reflectance value of the pixel
+to the histogram bin.
 
 We match the histogram $h_{source}$ to $h_{target}$ using the method of
-\cite{Morovic2002}. We compute a pixel movement
-matrix $T$ such that $T[m, n]$ is the amount of mass that must be moved from $h_{source}[m]$
-to $h_{target}[n]$. We do so using the procedure outlined in \ref{alg:ehm}
+Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement
+matrix $T$ such that $T[m, n]$ is the fraction of $h_{source}[m]$ that should be
+moved to $h_{target}[n]$. The details of this procedure are outlined in
+Algorithm~\ref{alg:ehm}. Intuitively, the procedure starts from the first bin of the
+source histogram and distributes its contents to the first bins of the target
+histogram, with successive source histogram bins being shifted to successive
+target bins in sequence.
 
+Finally, we use the movement matrix $T$ to shift the pixels of the MDE depth map
+to match the global depth of the target histogram. For a depth map pixel with
+depth bin $k$, we select the corrected bin by sampling from the distribution $T[k,
+:]/\sum_{n=1}^NT[k,n]$. This sampling procedure handles the
+case where a single input depth bin of the MDE is mapped to
+multiple output bins~\cite{Morovic2002}.
+%
 \begin{algorithm}[H]
@@
 \end{algorithm}
+%
 
-Finally, once we have obtained $T$, for a pixel $z_0[i, j]$ in bin $k$, we sample the new bin from the
-distribution $T[k, :]/\sum_{n=1}^NT[k,n]$ (which is a distribution over target
-depth bins $1,\ldots,N$) to get the bin of $\hat z[i,j]$. We can then apply the
-standard SID decoding procedure to get the depth corresponding to that bin
-\textcolor{red}{Does the above seem reasonable to include? Not sure if the
-  pseudocode is helpful/necessary or not.}
 %\subsection{Implementation Details}

### 2019-10-18 paper/cvpr2020/supplement.tex
pass over paper

@@
 
-\graphicspath{{"G:/Shared drives/Stanford Computational
+\graphicspath{{"figures/"}{"G:/Shared drives/Stanford Computational
     Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational

### 2019-10-18 paper/cvpr2020/supplement.tex
Video folder, ablation study, supplement editing.

--- 2019-10-17 paper/cvpr2020/supplement.tex
@@
 Compare RMSE and runtime.
+Simulated on NYU Depth v2. DenseDepth, SBR of 100. Only histogram matching
+was timed, not the running of the MDE or the denoising pipeline.
+\begin{figure}[H]
+  \centering
+  \begin{tabular}{c|cc}
+    \toprule
+    \# of sid bins & RMSE & Approx. Time/image (sec) \\
+    \midrule
+    70  & $0.351$ & $0.24$ \\
+    140 & $0.346$ & $0.63$ \\
+    210 & $0.345$ & $1.12$ \\
+    280 & $0.345$ & $1.84$ \\
+    \bottomrule
+  \end{tabular}
+\end{figure}
+
 \section{Ablation study on effect of reflectance estimation}
+Simulated on NYU v2. DenseDepth, 140 bins. SPAD simulation uses intensity, SBR
+of 100.
 \begin{itemize}
@@
 Compare RMSE and runtime.
+\begin{figure}[H]
+  \centering
+  \begin{tabular}{c|c|cc}
+    \toprule
+    Intensity-weighted histogram & Intensity-aware pixel movement & Avg. RMSE & Approx. Time/image (sec) \\
+    \midrule
+    \multirow{2}{*}{Yes} & Yes & $0.346$ & $4.6$ \\
+                         & No & $0.346$ & $0.6$ \\
+    \midrule
+    \multirow{2}{*}{No} & Yes & $0.444$ & $4.7$ \\
+                        & No & $0.444$ & $0.6$ \\
+    \bottomrule
+  \end{tabular}
+  \caption{Ablation study on simulated data for NYU Depth v2. When the SPAD
+    is simulated with the reflectance info but no reflectance estimate is used
+    to generate a weighted histogram from the CNN depth map, the results are
+    significantly worse. Furthermore, the pixel movement procedure need not take
+  into account the weights of the pixels being moved, since doing so provides no
+improvement and can take appreciably longer than a vectorized implementation
+that does not take pixel weights into account.}
+\end{figure}
 

### 2019-10-18 paper/cvpr2020/sections/discussion.tex
pass over simulated results section

@@
-short summary
+In summary, we demonstrate a method to greatly improve depth estimates from
+monocular depth estimators by correcting the scale ambiguity errors inherent
+with such techniques.  Our approach produces depth maps with accurate absolute
+depth, and helps the generalization of neural networks for MDE across scene
+types, including on data captured with our hardware prototype.  Moreover, we
+require only minimal additional sensing hardware; we show that a single measurement
+histogram from a diffused SPAD sensor contains enough information about global
+scene geometry to correct errors in monocular depth estimates.
 
@@
 
-\begin{itemize}
-	\item laser power vs range tradeoff; may be limited to short--medium range
-	\item if the monocular depth estimation fails, so will the histogram matching 
-\end{itemize}
+Since our method relies on the monocular depth estimate, the accuracy of the
+output depth map also relies on the performance of the initial depth estimate.
+The demonstrated results show that when the MDE technique produces a depth map
+with good ordinal depth, where the ordering object depth is roughly correct, the
+depth estimate can be corrected to produce accurate absolute depth. However,
+errors in the ordinal depth may not necessarily be corrected in the histogram
+matching procedure and so may propagate to the final output depth map.
+
+Additionally, since our method relies on a diffused pulsed laser, the laser
+power is spread out over the entire scene. So for distant scene points, very
+little light will return to the SPAD, and it may be difficult to accurately
+capture distant scene geometry in the histogram. Thus our method will likely be
+best suited to short to medium-range scenes.
 
@@
 \paragraph{Future Work}
+While our hardware prototype is very large, future work could be done to
+miniaturize this system. Our algorithm or similar sensor fusion algorithms could
+also be integrated into electronics that already contain the required hardware
+components, for example, existing cell phones with single-pixel SPAD
+proximity sensors and RGB cameras.
+
+Other methods for extracting scene information from the SPAD histogram could be
+also employed, including learning-based methods to combine the MDE and
+histogram. One might even consider sensing regimes where the number of
+returning signal photons is very low, such as when the SPAD and camera operate
+at high framerates. While most MDE techniques are tailored to clean RGB images,  
+the SPAD histogram could potentially be used to help MDE
+techniques generalize to noisy scenes under low-light conditions.
 
@@
 \paragraph{Conclusions}
+Neural network-based approaches to monocular depth estimation have yielded
+significant improvements over the past several years for this task. However,
+recently, such improvements have generally relied on new network architectures or
+revised training procedures and have produced only modest improvements. Computational
+photography approaches may provide the measurements needed to achieve much greater
+performance improvements, especially as the sensors in devices we use every day
+become more diverse, complex, and increasingly rely on techniques based on
+sensor fusion and sophisticated computational algorithms.
+
+%\begin{itemize}
+%	\item new depth estimation CNNs achieve marginal gains, let's think about computational photography approaches that augment the measurements to achieve better performance
+%	\item ...
+%\end{itemize}

### 2019-10-18 paper/cvpr2020/sections/introduction.tex

--- 2019-10-03 paper/cvpr2020/sections/introduction.tex
@@
-%Estimating depth from images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
-Dense depth maps are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.
+Estimating dense 3D geometry from 2D images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
+Depth maps are a common representation of scene geometry and are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.
+Additionally, many computer vision tasks rely on depth sensing, including navigation~\cite{geiger2013vision}, semantic segmentation~\cite{gupta2013perceptual,ren2012rgb,silberman2012indoor}, 3D object detection~\cite{gupta2014learning,lin2013holistic,shrivastava2013building,song2014sliding,song2016deep}, and 3D object classification~\cite{maturana2015voxnet,qi2016volumetric,wu20153d}.
 
-Depth sensing is vital for the success of many computer vision tasks, such as navigation~\cite{geiger2013vision}, robotic vision, semantic segmentation~\cite{ren2012rgb,silberman2012indoor,gupta2013perceptual}, 3D object detection~\cite{shrivastava2013building,lin2013holistic,gupta2014learning,song2014sliding,song2016deep}, and 3D object classification~\cite{wu20153d,maturana2015voxnet,qi2016volumetric}.
-However, traditional depth sensing techniques require multiple cameras, active illumination, camera motion, or other aspects that may make their deployment challenging.
+Traditional depth sensing techniques include those based on stereo or multiview, active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
+However, each of these techniques has aspects that may make their deployment challenging.
+For example, stereo or multiview techniques require multiple cameras, active illumination techniques may have limited resolution or require time-consuming scanning procedures, and other techniques require camera motion or multiple exposures at different focus distances.
 
-One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE)~\cite{Saxena2006,Eigen2014,Laina2016,Fu2018,Alhashim2018}.
-Given a single RGB image, a monocular depth estimator uses pictorial cues in the image, such as perspective, occlusion, shading, and relative object size, to predict a dense depth map of the scene.
-While neural networks solving the MDE problem have significantly improved over the last years, this remains an ill-posed inverse problem with inherent scale ambiguity.
-Pictorial cues alone allow for the ordinal depth, that is the relative ordering of objects in a scene, to be robustly estimated~\cite{Eigen2014,Fu2018}.
-However, MDE approaches to date are incapable of reliably estimating absolute distances of a scene.
-Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle access to the ground truth median scene depth, then correcting the output of the estimator to match this median depth produces accurate absolute depth maps.
+One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE), which requires only a single RGB image from a conventional camera to recover a dense depth map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}.
+Recent approaches to MDE employ neural network models that learn to predict depth by exploiting monocular image cues such as perspective, occlusion, shading, and relative object size.
+While such models have significantly improved over recent years, MDE approaches to date are incapable of reliably estimating absolute distances in a scene due to the inherent scale ambiguities of monocular image cues.
+Instead, these models excel in predicting ordinal depth, or the relative ordering of objects in a scene~\cite{Eigen2014,Fu2018}.
+Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth depth of the scene is known, the initial output of a MDE network can be corrected to produce accurate absolute depth.
 
@@
 
-While access to ground truth depth is impossible in a realistic scenario, one of our primary insights is that low-cost sensors capable of capturing aggregated depth information of a scene are readily available and already part of the sensor suite of many cellphones.
-These proximity sensors, for example deployed in Apple's iPhones, contain a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense the distance of one ray direction in front of the camera.
-Coupled with high-power laser sources, SPADs also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}.
-Whereas individual SPADs are easy to fabricate and sufficiently cost effective to be deployed in consumer electronics, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost.
-A single or a few SPADs could certainly be used together with a raster scanning mechanism, which is typical for LiDAR systems, but the mechanical complexity of such a system prevents usage in mobile devices and the inherent tradeoff between scan speed and resolution makes it difficult to capture high-resolution depth maps at high framerates.
+\begin{figure}
+  \includegraphics[width=\linewidth]{teaser.pdf}
+  \caption{Monocular depth estimation predicts a depth map (upper right) from a single RGB image (upper left).
+The ill-posedness of the problem prevents reliable absolute depth estimation, resulting in large errors (inset image).
+The proposed method uses a measurement from a diffused SPAD (lower left), which resembles the shape of a histogram of the ground truth depth map, to correct the output of the depth estimation and optimize the quality of the estimated absolute depth (lower right).}
+  \label{fig:teaser}
+\end{figure}
 
-Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way.
-Rather than optically focusing them to record the distance along one ray, we diffuse the emitted light and the detector over the entire scene.
-This allows us to directly capture the integrated depth of the scene---a depth histogram.
-Technically, a diffused SPAD does not record a true depth histogram but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise.
-However, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram while keeping in mind that they are not exactly the same.
+Although access to the median ground truth depth is impossible in a realistic scenario, low-cost sensors capable of capturing aggregated depth information from a scene are readily available.
+For example, the proximity sensor on recent generation Apple iPhones uses a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense distance to an object directly in front of the phone.
+SPADs have also been used to recover full 3D geometry, forming the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}.
+However, SPADs have not been used for 3D imaging on consumer electronics because the requirement for ultra-fast timing electronics makes it difficult to produce high-resolution arrays at low cost, and because the scanning requirement for single-pixel systems introduces a point of mechanical failure and complicates high-resolution, high-framerate imaging.
+
+%Individual SPADs are easy to fabricate and sufficiently cost-effective to be deployed in consumer electronics.
+When coupled with high-power pulsed lasers, they also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}.
+However, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost.
+Moreover, the scanning requirement for single-pixel systems precludes high-resolution, high-framerate depth mapping and is a barrier to integration in small consumer electronics.
+
+Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene.
+The resulting measurement resembles a histogram of the depth of the scene and can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).
+
+%Technically, a diffused SPAD does not record a true depth histogram, but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise.
+Nevertheless, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram.
 
@@
 
-In this paper, we develop a sensor fusion strategy that processes the ordinal depth computed by some monocular depth estimator to match the output of the diffused SPAD.
-With extensive simulations, we demonstrate that our approach achieves substantial improvements in the quality of the estimated depth maps, comparable to the oracle median depth, disregarding which specific depth estimator is used.
-Moreover, we build an RGB-SPAD camera prototype and again demonstrate that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes than a monocular depth estimator alone.
+To this end, we develop a sensor fusion strategy that processes the ordinal depth computed by a monocular depth estimator to be consistent with the measurements captured by the diffused SPAD.
+We demonstrate in extensive simulations that our approach achieves substantial improvements in the quality of the estimated depth maps, regardless of which specific depth estimator is used.
+Moreover, we build an RGB-SPAD camera prototype and demonstrate in practice that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes compared to MDE alone.
 With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.

### 2019-10-18 paper/cvpr2020/sections/related.tex

@@
 Various experiments using different types of encoder networks (e.g.
-ResNet, DenseNet)~\cite{Laina2016,Alhashim2018} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Xu2018,Hao2018}.
+ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
 Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.
@@
 Despite achieving remarkable success on estimating ordinal depth from a single image, none of these methods are able to resolve inherent scale ambiguity in a principled manner.
-We introduce a new approach that leverages existing monocular depth estimation networks but disambiguates their output with depth histogram-like measurements obtained from a single, diffused SPAD.
-Other approaches to disambiguating monocular depth estimation, for example using optimized freeform lenses~\cite{Wu:2019,Chang:2019:DeepOptics3D} or dual-pixel sensors~\cite{Garg:2019}, these approaches require custom lenses or sensors and specialized image reconstruction methods.
-In contrast, our diffused SPAD can simply be added to an existing camera, as it is on many cellphones already, and it does not require the standard camera ISP to be changed.
+We introduce a new approach that leverages existing monocular depth estimation networks and disambiguates the output using depth histogram-like measurements obtained from a single, diffused SPAD.
+Other approaches to disambiguating monocular depth estimation use optimized freeform lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors and specialized image reconstruction methods.
+In contrast, our approach is potentially compatible with existing camera systems (\eg deployed on current cell phones) and our algorithms could be used in tandem with existing camera ISPs.
 
@@
 %
-Emerging single-photon LiDAR systems use single photon avalanche diodes (SPADs) to record the time of flight of individual photons.
-Whereas SPAD detectors can be fabricated using standard CMOS processes, the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost.
-For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Lamb2010,Kirmani:2014,pawlikowska2017single,Li:2019}.
+Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs) to record the time of flight of individual photons.
+SPAD detectors can be fabricated using standard CMOS processes, but the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost.
+For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single}.
 Unfortunately, this makes it challenging to scan dynamic scenes at high resolution and scanners can also be expensive, difficult to calibrate, and prone to mechanical failure.
-To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2016linospad,burri2017linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}.
-Yet, single-pixel SPADs remain the only viable option for low cost consumer devices today.
+To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}.
+Yet, single-pixel SPADs remain the only viable option for low-cost consumer devices today.
 
-The proposed method uses a single-pixel SPAD, but rather than aiming it at one point in the scene as proximity sensors do, we propose to diffuse it along with the pulsed light source.
-This is a unique configuration that allows us capture a transient that closely resembles the shape of the depth histogram of the scene.
-We develop a sensor fusion algorithm to combine the output of a monocular depth estimator and this depth histogram to achieve more reliable absolute depth estimation.
-While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, in that work an intensity image was primarily used to guide a denoising and upsampling step of recorded 2D SPAD array.
+The proposed method uses a single-pixel SPAD and pulsed light source that are diffused across the entire scene instead of aimed at a single point, as with proximity sensors.
+This unique configuration captures a measurement that closely resembles the depth histogram of the scene.
+Our sensor fusion algorithm achieves reliable absolute depth estimation by combining the SPAD measurement with the output of a monocular depth estimator using a histogram matching technique.
+While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, the RGB image was primarily used to guide the denoising and upsampling of measurements from a SPAD array.
 
@@
 Histogram matching is a well-known image processing technique for adjusting an image so that its histogram matches some pre-specified histogram (often derived from another image)~\cite{gonzales1977gray,Gonzalez2008}.
-Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels that allows an exact histogram match to be obtained.
-Morovic et al.~\cite{Morovic2002} provide a simple and concise method that also achieves an exact histogram match while being very fast.
+Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels, yielding an exact histogram match.
+Morovic et al.~\cite{Morovic2002} provide an efficient and precise method for fast histogram matching which supports weighted pixel values.
 In the image reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram to form an image prior based on the Wasserstein distance for image denoising and inpainting.
 Rother et al.~\cite{Rother2006} use a histogram prior to create an energy function that penalizes foreground segmentations with dissimilar histograms.
-In a slightly different vein, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.
+In a slightly different application area, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.
 
-Because the single SPAD produces a weighted histogram of the depth map, we adapt
-the algorithm in Morovic et al. to accommodate general per-pixel
-weights, which allows us to compensate for different scene reflectances during
-the histogram matching.
+In our procedure, the diffused SPAD measurements capture a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects.
+We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.
+
 % \textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case.

### 2019-10-18 paper/cvpr2020/sections/simulation.tex

--- 2019-10-09 paper/cvpr2020/sections/simulation.tex
@@
-\begin{figure*}[!t]
+\begin{table*}[!t]
 \begin{center}
 \input{sections/figures/sim_table.tex}
-\caption{Quantitative evaluation using NYU Depth v2.
-Bold indicates best performance for that metric, while underline indicates second best.
-The proposed scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or even outperforms the median rescaling scheme and histogram matching with the exact depth map histogram, even though these methods have access to ground truth.
-}
+\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
+performance for that metric, while underline indicates second best. The proposed
+scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
+even outperforms the median rescaling scheme and histogram matching with the
+exact depth map histogram, even though those methods have access to ground truth. }
+\label{tab:comparison}
 \end{center}
-\end{figure*}
+\end{table*}
 
-\begin{figure*}[!t]
-  \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.png}
-  \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.png}
+\begin{figure*}[!h]
+  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
+  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
+  \includegraphics[width=\textwidth]{comparison.pdf}
   %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
-  \caption{Simulated results from NYU v2 computed with the DenseDepth CNN.
-The depth maps estimated by the CNN are reasonable, but contain systematic error.
-Oracle access to the ground truth depth maps, either through the median depth or the depth histogram, can remove this error and correct the depth maps.
-The proposed method uses a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
+  \caption{Simulated results from NYU v2 computed with the DenseDepth
+  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
+  but contain systematic error. Oracle access to the ground truth depth maps,
+  either through the median depth or the depth histogram, can remove this error
+  and correct the depth maps.
+The proposed method uses measurements from a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
 	\label{fig:results_simulated}
@@
 
-We use the NYU Depth v2 dataset to evaluate our method.
-This dataset consists of 249~training and 215~testing scenes of RGB-D data captured using a Microsoft Kinect.
-\textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
+We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
+249~training and 215~testing scenes with RGB-D images captured using a Microsoft
+Kinect.
+
+To simulate a SPAD histogram, we take the provided depth map and 
+calculate a weighted depth histogram by weighting the pixel contributions to
+each depth bin by the luminance of each pixel. To model radiometric falloff, we
+multiply each bin by $1/z^2$, and convolve with a modeled system temporal
+response, which we approximate as a Gaussian with a full-width at half-maximum of 70ps. We scale
+the histogram by the total number of observed signal photon counts (set to 
+$10^6$) and  add a fixed number of background photons $b \in \set{10^5, 2\times
+10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
+count detections, and the different background levels correspond to
+signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
+each bin is Poisson sampled to produce the final simulated SPAD transient.
+
+% \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
 
@@
 
-We show an extensive quantitative evaluation in Table~1.
+We show an extensive quantitative evaluation in Table~\ref{tab:comparison}.
 Here, we evaluate three recent monocular depth estimation techniques: DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and MiDaS~\cite{Lasinger:2019}.
@@
 
-We simulate the measurements of a single diffused SPAD as discussed in Section~\ref{sec:method} and also add Poisson noise and background signal.
-In table~1, results are shown for several different signal-to-background ratios (SBRs).
-We see that the proposed method achieves high-quality results for correcting the raw depth map estimated by the respective CNNs for all cases.
-The quality of the resulting depth maps is almost as good as that achieved with the oracle ground truth histogram, which can be interpreted as an approximate upper bound on the performance, despite a relatively high amount of noise and background signal.
-These results demonstrate that the proposed method is agnostic to the specific depth estimation CNN applied to get the initial depth map and that it generally achieves significant improvements in the estimated depth maps, clearly surpassing the variation of performance between depth estimation CNNs.
+Instead, our method uses the simulated measurements from a single diffused SPAD
+to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
+signal-to-background ratios (SBRs). We see that the proposed method achieves
+high-quality results for correcting the raw depth map estimated by the
+respective CNNs for all cases. The quality of the resulting depth maps is almost
+as good as that achieved with the oracle ground truth histogram, which can be
+interpreted as an approximate upper bound on the performance, despite a
+relatively high amount of noise and background signal. These results demonstrate
+that the proposed method is agnostic to the specific depth estimation CNN
+applied to get the initial depth map and that it generally achieves significant
+improvements in the estimated depth maps, clearly surpassing the variation in
+performance between depth estimation CNNs.
 
-In Figure~\ref{fig:results_simulated}, we also show qualitative results of our simulations.
-For each of these scenes, we show the RGB reference image, the ground truth depth map, the raw output of the DenseDepth CNN, the result of rescaling the CNN output by the median ground truth depth, the result of histogram-matching the CNN output by the ground truth depth map histogram, and the result achieved by the proposed method for an SBR of 100.
-Error maps for all the depth estimation methods are shown.
-As expected, the CNN outputs depth maps that look reasonable but that have an average root mean squared error (RMSE) of about 50--60~cm.
-Re-scaling this depth map by the median ground truth depth value slightly improves the quality and histogram-matching it with the ground truth depth histogram improves the depth map a lot.
-The quality of the proposed method is close to that using the oracle histogram, despite relying on noisy SPAD measurements.
-Additional simulations using DenseDepth and other depth estimation CNNs for a variety of scenes are shown in the supplement.
+In Figure~\ref{fig:results_simulated}, we also show qualitative results of our
+simulations. For each of these scenes, we show the RGB reference image, the
+ground truth depth map, the raw output of the DenseDepth CNN, the result of
+rescaling the CNN output by the median ground truth depth, the result of
+histogram-matching the CNN output by the ground truth depth map histogram, and
+the result achieved by the proposed method for an SBR of 100. Error maps for all
+the depth estimation methods are shown. As expected, the CNN outputs depth maps
+that look reasonable but that have an average root mean squared error (RMSE) of
+about 50--60~cm. Re-scaling this depth map by the median ground truth depth
+value slightly improves the quality and histogram-matching with the ground
+truth depth histogram shows a large amount of improvement. The quality of the
+proposed method is close to using the oracle histogram, despite relying on
+noisy SPAD measurements. Additional simulations using DenseDepth and other depth
+estimation CNNs for a variety of scenes are shown in the supplement.

### 2019-10-19 paper/cvpr2020/sections/method.tex
Mark's edits.

@@
   \includegraphics[width=\columnwidth]{method.pdf}
-  \caption{\textbf{Overview of processing pipeline} The processing pipeline uses
+  \caption{Overview of processing pipeline. The processing pipeline uses
       the input SPAD measurements and an RGB image to produce an accurate depth
@@
         &\hat n_\text{last}=\max\{n : h[n'_\text{last}] > \tau,
-    \cdots, h[n+1] > \tau, h[n] > \tau\}.
+    \cdots, h[n-1] > \tau, h[n] > \tau\}.
     \end{split}
 \end{equation}
-The remaining ambient counts are discarded by settings the recorded counts to
-zero for all bins where $n < n_\text{last}$ and $n > n_\text{last}$.
+The remaining ambient counts are discarded by setting the recorded counts to
+zero for all bins where $n < n_\text{last}$ and $n > n_\text{last}$. We use 
+$\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.
 
@@
 \begin{algorithm}[H]
- \caption{Pixel Movement} 
+ \caption{Find Pixel Movement} 
  \label{alg:ehm}
  \begin{algorithmic}
-  \Procedure{FindMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
+  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
     \State Initialize $T$ as an $M \times N$ array of zeros.

### 2019-10-19 paper/cvpr2020/supplement.tex
Mark's edits.

@@
 \section{Ablation study on number of SID bins}
-\begin{itemize}
-  \item Simulation: 70, 140, 210, 280 bins
-  \item Captured: 70, 140, 210, 280 bins
-\end{itemize}
-Compare RMSE and runtime.
-Simulated on NYU Depth v2. DenseDepth, SBR of 100. Only histogram matching
-was timed, not the running of the MDE or the denoising pipeline.
+% \begin{itemize}
+%   \item Simulation: 70, 140, 210, 280 bins
+%   \item Captured: 70, 140, 210, 280 bins
+% \end{itemize}
+% Compare RMSE and runtime.
+We conducted an ablation study to assess the effect of the number of SID bins
+\cite{Fu2018} on both runtime and RMSE. We performed this analysis using SPAD
+data with a signal-to-background (SBR) of 100, simulated on the test set of NYU Depth v2. Our
+MDE was DenseDepth, and only the actual histogram matching portion 
+was timed, not the running of the MDE nor the denoising pipeline.
 \begin{figure}[H]
@@
   \end{tabular}
+  \caption{Effect of number of SID bins on RMSE and runtime. The marginal
+    improvement in RMSE is offset by the increase in runtime as the number of
+    bins grows.}
+  \label{fig:sid_ablation}
 \end{figure}
@@
 \section{Ablation study on effect of reflectance estimation}
-Simulated on NYU v2. DenseDepth, 140 bins. SPAD simulation uses intensity, SBR
-of 100.
-\begin{itemize}
-  \item Intensity used to initialize histogram, not used to move pixels
-  \item Intensity used to initialize histogram and move pixels
-  \item Intensity not used to initialize histogram, used to move pixels
-  \item Intensity not used to initialize histogram, not used to move pixels
-\end{itemize}
-Compare RMSE and runtime.
+We conducted an ablation study to assess whether the use of a reflectance
+estimate has an impact on the runtime and quality of the solution.
+We performed this analysis using SPAD
+data with a signal-to-background (SBR) of 100, simulated on the test set of NYU Depth v2. Our
+MDE was DenseDepth, and only the actual histogram matching portion 
+was timed, not the running of the MDE nor the denoising pipeline.
+
+% \begin{itemize}
+%   \item Intensity used to initialize histogram, not used to move pixels
+%   \item Intensity used to initialize histogram and move pixels
+%   \item Intensity not used to initialize histogram, used to move pixels
+%   \item Intensity not used to initialize histogram, not used to move pixels
+% \end{itemize}
+% Compare RMSE and runtime.
 \begin{figure}[H]
@@
     to generate a weighted histogram from the CNN depth map, the results are
-    significantly worse. Furthermore, the pixel movement procedure need not take
+    significantly worse. Furthermore, once the pixel movement matrix has been
+    computed, the pixel movement procedure need not take
   into account the weights of the pixels being moved, since doing so provides no

### 2019-10-20 paper/cvpr2020/main.tex
Mark's edits.
Added abstract, changed conclusion, minor edits elsewhere

@@
 \begin{abstract}
-abstract
+Existing monocular depth estimation algorithms do an outstanding job of predicting the relative depth {order} of objects in a scene.
+However, because of the fundamental scale ambiguity associated with monocular images, these algorithms do a poor job at predicting an object's true metric depth. 
+In this work, we demonstrate how depth histograms, which can be readily captured using single photon avalanche diodes (SPADs), can be fused with existing monocular depth estimation algorithms to resolve the depth ambiguity problem.
+We validate this novel sensor fusion technique experimentally and in extensive simulation and show that it dramatically improves the performance of several state-of-the-art monocular depth estimation algorithms.
 \end{abstract}
@@
 {\small
-\bibliographystyle{ieee_fullname}
+\bibliographystyle{ieeetr}
 \bibliography{references}

### 2019-10-20 paper/cvpr2020/sections/discussion.tex
Added abstract, changed conclusion, minor edits elsewhere

@@
 \paragraph{Limitations}
-
-Since our method relies on the monocular depth estimate, the accuracy of the
-output depth map also relies on the performance of the initial depth estimate.
-The demonstrated results show that when the MDE technique produces a depth map
+The performance of our method is highly dependent on the accuracy of the initial depth map output by the monocular depth estimation algorithm.
+%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
+Our results demonstrate that when the MDE technique produces a depth map
 with good ordinal depth, where the ordering object depth is roughly correct, the
-depth estimate can be corrected to produce accurate absolute depth. However,
-errors in the ordinal depth may not necessarily be corrected in the histogram
-matching procedure and so may propagate to the final output depth map.
+depth estimate can be corrected to produce accurate absolute depth.
+However, if the ordinal depth of the initial estimate is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.
 
 Additionally, since our method relies on a diffused pulsed laser, the laser
-power is spread out over the entire scene. So for distant scene points, very
-little light will return to the SPAD, and it may be difficult to accurately
-capture distant scene geometry in the histogram. Thus our method will likely be
-best suited to short to medium-range scenes.
+power is spread out over the entire scene. Accordingly for distant scene points very
+little light will return to the SPAD and it may be difficult to accurately
+capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.
 
@@
 \paragraph{Conclusions}
-Neural network-based approaches to monocular depth estimation have yielded
-significant improvements over the past several years for this task. However,
-recently, such improvements have generally relied on new network architectures or
-revised training procedures and have produced only modest improvements. Computational
-photography approaches may provide the measurements needed to achieve much greater
-performance improvements, especially as the sensors in devices we use every day
-become more diverse, complex, and increasingly rely on techniques based on
-sensor fusion and sophisticated computational algorithms.
+Since their introduction, the performance of monocular depth estimation algorithms has improved tremendously.
+However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements.
+This suggests we are approaching the limits of what can be achieved using a monocular image alone. 
+In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
+Such histograms are cheap to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
+%Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.
+%Computational photography approaches may provide the measurements needed to achieve much greater performance improvements, especially as the sensors in devices we use every day become more diverse, complex, and increasingly rely on techniques based on sensor fusion and sophisticated computational algorithms.
 

### 2019-10-20 paper/cvpr2020/sections/hardware.tex
Added abstract, changed conclusion, minor edits elsewhere

@@
 
-As shown in Figure~\ref{fig:prototype}, our prototype camera comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
+As shown in Figure~\ref{fig:prototype}, our prototype comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
 The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.
@@
 The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
-This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparison with the captured depth.
-Monocular depth estimation is calculated using the RGB image captured by the Kinect v2.
+This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth.
+The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.
 
 We determined camera intrinsics and extrinsics for the Kinect's RGB camera and
-the scanning system using the standard camera calibration toolbox in MATLAB.
-While the SPAD histogram and RGB image are captured from slightly different viewpoints, we approximately calibrate the SPAD histogram for this by shifting the 1D transient by the calibrated $z$ offset from the RGB camera.
+the scanning system using MATLAB's camera calibration toolbox. 
+The SPAD histogram and RGB image were captured from slightly different viewpoints; we account for this in the SPAD histogram by shifting the 1D transient according to the SPAD's offset from the RGB camera.
 %We use the camera extrinsics to Once the SPAD volume has been summed over the spatial dimensions, it is unclear

### 2019-10-20 paper/cvpr2020/sections/introduction.tex
Mark's edits.
Added abstract, changed conclusion, minor edits elsewhere

@@
   \includegraphics[width=\linewidth]{teaser.pdf}
-  \caption{Monocular depth estimation predicts a depth map (upper right) from a single RGB image (upper left).
-The ill-posedness of the problem prevents reliable absolute depth estimation, resulting in large errors (inset image).
-The proposed method uses a measurement from a diffused SPAD (lower left), which resembles the shape of a histogram of the ground truth depth map, to correct the output of the depth estimation and optimize the quality of the estimated absolute depth (lower right).}
+  \caption{Monocular depth estimation predicts a depth map (upper right) from a
+    single RGB image (upper left). The ill-posedness of the problem prevents
+    reliable absolute depth estimation, resulting in large errors (inset image).
+    The proposed method uses a measurement from a diffused SPAD (lower left),
+    which resembles the shape of a histogram of the ground truth depth map, to
+    correct the output of the depth estimation and optimize the quality of the
+    estimated absolute depth (lower right).}
   \label{fig:teaser}
@@
 \begin{itemize}
-	\item We introduce the idea of augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
+	\item We propose augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
   \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.

### 2019-10-20 paper/cvpr2020/sections/method.tex
Added abstract, changed conclusion, minor edits elsewhere

@@
 
+\vspace{0.8em}\noindent{\bf Background Subtraction.}
 In the first step, we remove the background counts from the
@@
 
+\vspace{0.8em}\noindent{\bf Falloff Compensation.}
 In the second step, we compensate for distance falloff effects by multiplying the histogram
@@
 
+\vspace{0.8em}\noindent{\bf Histogram Re-binning.}
 Last, we re-bin the transient so that the bin widths increase for increasingly
@@
 \begin{equation}
-  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad i = 0,\ldots, K.
+  t_i = e^{\log(\ell) + \frac{\log(u/\ell) \cdot i}{K}}  \qquad\text{for}\qquad i = 0,\ldots, K.
   \label{eq:sid_bin_edges}

### 2019-10-20 paper/cvpr2020/main.tex
pass over paper

--- 2019-10-18 paper/cvpr2020/main.tex
@@
 
-\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
+\def\cvprPaperID{2224} % *** Enter the CVPR Paper ID here
 \def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
@@
 \begin{abstract}
-abstract
+Existing monocular depth estimation algorithms successfully predict the relative depth {order} of objects in a scene.
+However, because of the fundamental scale ambiguity associated with monocular images, these algorithms fail at correctly predicting an object's true metric depth. 
+In this work, we demonstrate how a depth histogram of the scene, which can be readily captured using a single-pixel diffused single-photon avalanche diode (SPAD), can be fused with the output of existing monocular depth estimation algorithms to resolve the depth ambiguity problem.
+We validate this novel sensor fusion technique experimentally and in extensive simulation.
+We show that it dramatically improves the performance of several state-of-the-art monocular depth estimation algorithms.
 \end{abstract}

### 2019-10-20 paper/cvpr2020/sections/discussion.tex
pass over paper

@@
 \paragraph{Future Work}
-While our hardware prototype is very large, future work could be done to
-miniaturize this system. Our algorithm or similar sensor fusion algorithms could
+While our hardware prototype is large, future work could miniaturize this system. Our algorithm or similar sensor fusion algorithms could
 also be integrated into electronics that already contain the required hardware
@@
 histogram. One might even consider sensing regimes where the number of
-returning signal photons is very low, such as when the SPAD and camera operate
+returning signal photons is low, such as when the SPAD and camera operate
 at high framerates. While most MDE techniques are tailored to clean RGB images,  
-the SPAD histogram could potentially be used to help MDE
+the SPAD histogram could be used to help MDE
 techniques generalize to noisy scenes under low-light conditions.
@@
 In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
-Such histograms are cheap to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
+Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
 %Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.

### 2019-10-20 paper/cvpr2020/sections/hardware.tex
pass over paper

@@
 The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
-The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth map with an accuracy of about 1~cm.
+The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm.
 A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
@@
 	\caption{Experimental results.
-For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left subimages).
-A monocular depth CNN predicts an initial depth map (top middle subimages), which is corrected with the diffused SPAD histogram using the proposed method (top right subimages).
-As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right subimages).
+For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left).
+A monocular depth CNN predicts an initial depth map (top middle), which is corrected with the diffused SPAD histogram using the proposed method (top right).
+As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right).
 The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print.

### 2019-10-20 paper/cvpr2020/sections/introduction.tex
pass over paper

@@
 Additionally, many computer vision tasks rely on depth sensing, including navigation~\cite{geiger2013vision}, semantic segmentation~\cite{gupta2013perceptual,ren2012rgb,silberman2012indoor}, 3D object detection~\cite{gupta2014learning,lin2013holistic,shrivastava2013building,song2014sliding,song2016deep}, and 3D object classification~\cite{maturana2015voxnet,qi2016volumetric,wu20153d}.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{teaser.pdf}
+  \caption{Monocular depth estimation predicts a depth map (upper right) from a
+    single RGB image (upper left). The ill-posedness of the problem prevents
+    reliable absolute depth estimation, resulting in large errors (inset image).
+    The proposed method uses a measurement from a diffused SPAD (lower left),
+    which resembles the shape of a histogram of the ground truth depth map, to
+    correct the output of the depth estimation and optimize the quality of the
+    estimated absolute depth (lower right).}
+  \label{fig:teaser}
+\end{figure}
 
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{teaser.pdf}
-  \caption{Monocular depth estimation predicts a depth map (upper right) from a
-    single RGB image (upper left). The ill-posedness of the problem prevents
-    reliable absolute depth estimation, resulting in large errors (inset image).
-    The proposed method uses a measurement from a diffused SPAD (lower left),
-    which resembles the shape of a histogram of the ground truth depth map, to
-    correct the output of the depth estimation and optimize the quality of the
-    estimated absolute depth (lower right).}
-  \label{fig:teaser}
-\end{figure}
-
 Although access to the median ground truth depth is impossible in a realistic scenario, low-cost sensors capable of capturing aggregated depth information from a scene are readily available.
@@
 Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene.
-The resulting measurement resembles a histogram of the depth of the scene and can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).
+The resulting measurement resembles a histogram of the depth of the scene and we demonstrate that this can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).
 
@@
 \begin{itemize}
-	\item We propose augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
+	\item We propose augmenting an RGB camera with a global depth histogram captured by a diffused SPAD to address scale ambiguity error in monocular depth estimators.	
   \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.

### 2019-10-20 paper/cvpr2020/sections/method.tex
pass over paper

@@
 In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD).
-We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the diffused SPAD.
+We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the SPAD.
 
@@
 \subsection{Image Formation Model of a Diffused SPAD}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{method.pdf}
+  \caption{Overview of processing pipeline. The processing pipeline uses
+      the input SPAD measurements and an RGB image to produce an accurate depth
+      map. The SPAD measurements are pre-processed to adjust for ambient photon
+      detections, radiometric falloff factors, and to calibrate the bin widths.
+      From the RGB image, an MDE estimates an initial depth map
+      and the scene reflectance is estimated. A reflectance-weighted
+      depth histogram is compared to the processed SPAD measurements to
+      calculate a histogram matching matrix which is used to output the corrected depth.
+  }
+  \label{fig:pipeline}
+\end{figure}
 
@@
 %
-where $(n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
+where $[n\Delta t, (n+1) \Delta t)$ models the $n^\text{th}$ time interval or bin of the
 temporal histogram, $\eta$ is the photon detection probability of the SPAD, $f$
@@
 \textit{transient} for the histogram $h[n]$~\cite{Xin2019}.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{method.pdf}
-  \caption{Overview of processing pipeline. The processing pipeline uses
-      the input SPAD measurements and an RGB image to produce an accurate depth
-      map. The SPAD measurements are pre-processed to adjust for ambient photon
-      detections, radiometric falloff factors, and to calibrate the bin widths.
-      From the RGB image, an MDE estimates an initial depth map
-      and the scene reflectance is estimated. A reflectance-weighted
-      depth histogram is compared to the processed SPAD measurements to
-      calculate a histogram matching matrix which is used to output the corrected depth map.
-  }
-  \label{fig:pipeline}
-\end{figure}
 
@@
 In the first step, we remove the background counts from the
-transient by initally estimating the average amount of background counts
+transient by initially estimating the average amount of background counts
 in each time bin. For nearly all natural scenes, the closest objects to the
@@
 \begin{equation}
-    h'[n] = h[n] \cdot r_n^2.
+    h'[n] = h[n] \cdot z_n^2.
   \label{eq:h_scaled}
 \end{equation}
-Here, $r_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
+Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
 corresponding to bin $n$, and this radiometric falloff model is consistent with
@@
 %
+
+{ \footnotesize
 \begin{algorithm}[H]
@@
  \begin{algorithmic}
+	\footnotesize
   \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
@@
 \end{algorithm}
+}
 %

### 2019-10-20 paper/cvpr2020/sections/related.tex
pass over paper

@@
 predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function.
-Various experiments using different types of encoder networks (e.g.
-ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
+Various experiments using different types of encoder networks (\eg ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
 Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.
@@
 
-In our procedure, the diffused SPAD measurements capture a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects.
+In our procedure, the diffused SPAD measurements closely resemble a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects.
 We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.

### 2019-10-20 paper/cvpr2020/sections/simulation.tex
pass over paper

@@
 multiply each bin by $1/z^2$, and convolve with a modeled system temporal
-response, which we approximate as a Gaussian with a full-width at half-maximum of 70ps. We scale
+response, which we approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
 the histogram by the total number of observed signal photon counts (set to 

### 2019-10-20 paper/cvpr2020/supplement.tex
pass over paper

@@
 %%%%%%%%% TITLE
-\title{Supplementary Information: Improving Monocular Depth Estimation with
-  Global Depth Histogram Matching}
+\title{Supplementary Information: Optimizing Monocular Depth Estimation with Global Depth Histogram
+  Matching using a Single SPAD Transient}
 

### 2019-10-20 paper/cvpr2020/sections/discussion.tex
Updated figures, shortened back to 8 pages.

@@
 \paragraph{Limitations}
-The performance of our method is highly dependent on the accuracy of the initial depth map output by the monocular depth estimation algorithm.
+The performance of our method is highly dependent on the accuracy of the initial
+depth map of the MDE algorithm.
 %Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
 Our results demonstrate that when the MDE technique produces a depth map
-with good ordinal depth, where the ordering object depth is roughly correct, the
-depth estimate can be corrected to produce accurate absolute depth.
-However, if the ordinal depth of the initial estimate is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.
+with good ordinal accuracy, where the ordering of object depths is roughly correct, the
+depth estimate can be corrected to produce accurate absolute depth. However, if
+the ordering of the initial depths is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.
 
 Additionally, since our method relies on a diffused pulsed laser, the laser
-power is spread out over the entire scene. Accordingly for distant scene points very
+power is spread out over the entire scene. Accordingly, for distant scene points very
 little light will return to the SPAD and it may be difficult to accurately
@@
 Other methods for extracting scene information from the SPAD histogram could be
-also employed, including learning-based methods to combine the MDE and
+employed, including learning-based methods to combine the MDE and
 histogram. One might even consider sensing regimes where the number of
@@
 \paragraph{Conclusions}
-Since their introduction, the performance of monocular depth estimation algorithms has improved tremendously.
+Since their introduction, monocular depth estimation algorithms have improved tremendously.
 However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements.
-This suggests we are approaching the limits of what can be achieved using a monocular image alone. 
-In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histograms measurements. 
+In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
 Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.

### 2019-10-20 paper/cvpr2020/sections/hardware.tex
Updated figures, shortened back to 8 pages.

@@
 	\includegraphics[width=\columnwidth]{captured.pdf}
-	\caption{Experimental results.
-For each scene, we record a ground truth depth map that is raster-scanned with the SPAD (upper left subimages), and an RGB image (lower left).
-A monocular depth CNN predicts an initial depth map (top middle), which is corrected with the diffused SPAD histogram using the proposed method (top right).
-As shown by the error maps and root mean squared error (RMSE) for each example (lower center, right).
-The CNN is confused when we show it a photograph of a poster (bottom scene); it incorrectly predicts the depth of the scene depicted on the flat print.
-Our method is able to correct this error.
-}
+	\caption{Experimental results. For each scene, we record a ground truth depth
+    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
+    image (lower left). A monocular depth CNN predicts an initial depth map (top
+    middle), which is corrected with the diffused SPAD histogram using the
+    proposed method (top right), as shown by the error maps and root mean
+    squared error (RMSE) for each example (lower center, right). The CNN is
+    confused when we show it a photograph of a poster (bottom scene); it
+    incorrectly predicts the depth of the scene depicted on the flat print. Our
+    method is able to correct this error.}
 	\label{fig:results_captured}

### 2019-11-04 paper/cvpr2020/sections/simulation.tex
Fixed results table, adjusted spacing to maintain page count.

@@
 even outperforms the median rescaling scheme and histogram matching with the
-exact depth map histogram, even though those methods have access to ground truth. }
+exact depth map histogram, even though those methods have access to ground
+truth.}
+\vspace{-2em}
 \label{tab:comparison}
@@
   either through the median depth or the depth histogram, can remove this error
-  and correct the depth maps.
-The proposed method uses measurements from a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
+  and correct the depth maps. The proposed method uses measurements from a
+  single diffused SPAD and does not rely on ground truth depth, but it achieves
+  a quality that closely matches the best-performing oracle.}
 	\label{fig:results_simulated}
+  \vspace{-1em}
 \end{figure*}
@@
 We show an extensive quantitative evaluation in Table~\ref{tab:comparison}.
-Here, we evaluate three recent monocular depth estimation techniques: DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and MiDaS~\cite{Lasinger:2019}.
-To evaluate the quality of DORN and DenseDepth, we report various standard error metrics.
-Moreover, we show a simple post-processing step that rescales their outputs by the median ground truth depth~\cite{Alhashim2018}.
-We also show the results of histogram matching the output of the CNNs with the ground truth depth map histogram.
-Note that we do not report the quality of the direct output of MiDaS as this algorithm does not output metric depth.
-However, we do show its output histogram matched with the ground truth depth map histogram.
-In all cases, post-processing the estimated depth maps either with the median depth or depth histogram significantly improves the absolute depth estimation, often by a large margin compared to the raw output of the CNNs.
-Unfortunately, ground truth depth is typically not accessible so neither of these two post-processing methods are viable in practical application scenarios.
+Here, we evaluate three recent monocular depth estimation techniques:
+DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and
+MiDaS~\cite{Lasinger:2019}. To evaluate the quality of DORN and DenseDepth, we
+report various standard error metrics. Moreover, we show a simple
+post-processing step that rescales their outputs by the median ground truth
+depth~\cite{Alhashim2018}. We also show the results of histogram matching the
+output of the CNNs with the ground truth depth map histogram. Note that we do
+not report the quality of the direct output of MiDaS as this algorithm does not
+output metric depth. However, we do show its output histogram matched with the
+ground truth depth map histogram. In all cases, post-processing the estimated
+depth maps either with the median depth or depth histogram significantly
+improves the absolute depth estimation, often by a large margin compared to the
+raw output of the CNNs. Unfortunately, ground truth depth is typically not
+accessible so neither of these two post-processing methods are viable in
+practical application scenarios.
 

### 2019-11-09 paper/cvpr2020/sections/discussion.tex
Cleaning up paper (Mark).

@@
 Other methods for extracting scene information from the SPAD histogram could be
-employed, including learning-based methods to combine the MDE and
+employed, including learning-based methods to combine the MDE estimates and
 histogram. One might even consider sensing regimes where the number of

### 2019-11-09 paper/cvpr2020/sections/method.tex
Cleaning up paper (Mark).

@@
       the input SPAD measurements and an RGB image to produce an accurate depth
-      map. The SPAD measurements are pre-processed to adjust for ambient photon
+      map. The SPAD measurements are preprocessed to adjust for ambient photon
       detections, radiometric falloff factors, and to calibrate the bin widths.
@@
 \subsection{Ambient Rejection and Falloff Correction} Before performing
-histogram matching, we apply three pre-processing steps to (1)
+histogram matching, we apply three preprocessing steps to (1)
 remove background counts from the transient, (2) compensate for distance
@@
 estimate after applying histogram matching.  Instead, we estimate the temporal
-support of histogram bins containing signal photons (\ie the range of depths the
+support of histogram bins containing signal photons (\ie the range of depths in the
 scene) and only subtract $\hat{b}$ from these bins. We assume that other
@@
 so that the image histogram matches a target histogram. We apply this procedure
-to match the histogram of an input depth map, obtained from an MDE, to the
+to match the histogram of an input depth map, obtained from a monocular depth estimator, to the
 post-processed target histogram $h_\text{target}$ from the SPAD.
 
-The MDE cannot be directly histogram-matched to the target histogram
+The input depth map cannot be directly histogram-matched to the target histogram
 because the target histogram incorporates the spatially varying reflectance of
@@
 
-We match the histogram $h_{source}$ to $h_{target}$ using the method of
+We match the histogram $h_\text{source}$ to $h_\text{target}$ using the method of
 Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement
-matrix $T$ such that $T[m, n]$ is the fraction of $h_{source}[m]$ that should be
-moved to $h_{target}[n]$. The details of this procedure are outlined in
+matrix $T$ such that $T[m, n]$ is the fraction of $h_\text{source}[m]$ that should be
+moved to $h_\text{target}[n]$. The details of this procedure are outlined in
 Algorithm~\ref{alg:ehm}. Intuitively, the procedure starts from the first bin of the
@@
 
-Finally, we use the movement matrix $T$ to shift the pixels of the MDE depth map
+Finally, we use the movement matrix $T$ to shift the pixels of the input depth map
 to match the global depth of the target histogram. For a depth map pixel with

### 2019-11-09 paper/cvpr2020/sections/related.tex
Cleaning up paper (Mark).

@@
 %
-Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs) to record the time of flight of individual photons.
-SPAD detectors can be fabricated using standard CMOS processes, but the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost.
-For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single}.
-Unfortunately, this makes it challenging to scan dynamic scenes at high resolution and scanners can also be expensive, difficult to calibrate, and prone to mechanical failure.
-To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}.
-Yet, single-pixel SPADs remain the only viable option for low-cost consumer devices today.
+Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs)
+to record the time of flight of individual photons. SPAD detectors can be
+fabricated using standard CMOS processes, but the required picosecond-accurate
+time-stamping electronics are challenging to miniaturize and fabricate at low
+cost. For this reason, many single-photon 3D imaging approaches use a single
+SPAD combined with a raster scanning
+mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
+Unfortunately, this makes it challenging to scan dynamic scenes at high
+resolution and scanners can also be expensive, difficult to calibrate, and prone
+to mechanical failure. To reduce the scanning complexity to one dimension, 1D
+SPAD arrays have been
+developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD
+arrays are also an active area of
+research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
+single-pixel SPADs remain the only viable option for low-cost consumer devices
+today.
 
-The proposed method uses a single-pixel SPAD and pulsed light source that are diffused across the entire scene instead of aimed at a single point, as with proximity sensors.
-This unique configuration captures a measurement that closely resembles the depth histogram of the scene.
-Our sensor fusion algorithm achieves reliable absolute depth estimation by combining the SPAD measurement with the output of a monocular depth estimator using a histogram matching technique.
-While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, the RGB image was primarily used to guide the denoising and upsampling of measurements from a SPAD array.
+The proposed method uses a single-pixel SPAD and pulsed light source that are
+diffused across the entire scene instead of aimed at a single point, as with
+proximity sensors. This unique configuration captures a measurement that closely
+resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
+reliable absolute depth estimation by combining the SPAD measurement with the
+output of a monocular depth estimator using a histogram matching technique.
+While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
+the RGB image was primarily used to guide the denoising and upsampling of
+measurements from a SPAD array.
 
-%Previous work (see \cite{Horaud2016} for a survey) has been able to use single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in tandem with various scanning or DMD devices to capture 3D volumes of photon arrivals that can be used to reconstruct depth.
-Lindell et.
-al.
-\cite{Lindell2018} use a LinoSPAD and epipolar scanline and fuse the SPAD data with an RGB image to produce high-quality depth.
-Our approach uses a single pixel SPAD but does not require any scanning or DMD mechanism.
+%Previous work (see \cite{Horaud2016} for a survey) has been able to use
+%single-pixel SPADs \cite{Lamb2010} and also 1D LinoSPADs in tandem with various
+%scanning or DMD devices to capture 3D volumes of photon arrivals that can be
+%used to reconstruct depth. Lindell et. al. \cite{Lindell2018} use a LinoSPAD
+%and epipolar scanline and fuse the SPAD data with an RGB image to produce
+%high-quality depth.  Our approach uses a single pixel SPAD but does not require
+%any scanning or DMD mechanism.
 
@@
 %
-Histogram matching is a well-known image processing technique for adjusting an image so that its histogram matches some pre-specified histogram (often derived from another image)~\cite{gonzales1977gray,Gonzalez2008}.
-Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels, yielding an exact histogram match.
-Morovic et al.~\cite{Morovic2002} provide an efficient and precise method for fast histogram matching which supports weighted pixel values.
-In the image reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram to form an image prior based on the Wasserstein distance for image denoising and inpainting.
-Rother et al.~\cite{Rother2006} use a histogram prior to create an energy function that penalizes foreground segmentations with dissimilar histograms.
-In a slightly different application area, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.
+Histogram matching is a well-known image processing technique for adjusting an
+image so that its histogram matches some pre-specified histogram (often derived
+from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et
+al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the
+image pixels, yielding an exact histogram match. Morovic et
+al.~\cite{Morovic2002} provide an efficient and precise method for fast
+histogram matching which supports weighted pixel values. In the image
+reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram
+to form an image prior based on the Wasserstein distance for image denoising and
+inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an
+energy function that penalizes foreground segmentations with dissimilar
+histograms. In a slightly different application area, Zhang et
+al.~\cite{Zhang2017} train a neural network to produce realistically colorized
+images given only a black-and-white image and a histogram of global color
+information.
 
-In our procedure, the diffused SPAD measurements closely resemble a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects.
-We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.
+In our procedure, the diffused SPAD measurements closely resemble a histogram of
+the depth map where the histogram values are weighted by spatially varying scene
+reflectances and inverse-square falloff effects. We therefore adapt the
+algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general
+per-pixel weights during histogram matching.
 

### 2019-11-09 paper/cvpr2020/supplement.tex
Cleaning up paper (Mark).

@@
 % Compare RMSE and runtime.
-We conducted an ablation study to assess the effect of the number of SID bins
+We conducted an ablation study on the effect of the number of SID bins
 \cite{Fu2018} on both runtime and RMSE. We performed this analysis using SPAD
-data with a signal-to-background (SBR) of 100, simulated on the test set of NYU Depth v2. Our
-MDE was DenseDepth, and only the actual histogram matching portion 
-was timed, not the running of the MDE nor the denoising pipeline.
+data with a signal-to-background (SBR) of 100, simulated on the test set of NYU
+Depth v2. We used DenseDepth~\cite{Alhashim2018} for our MDE CNN.
+Only the histogram matching portion was timed, not the CNN nor the
+denoising pipeline.
+
 \begin{figure}[H]
@@
 \section{Ablation study on effect of reflectance estimation}
-We conducted an ablation study to assess whether the use of a reflectance
+We conducted an ablation study on whether the use of a reflectance
 estimate has an impact on the runtime and quality of the solution.
 We performed this analysis using SPAD
-data with a signal-to-background (SBR) of 100, simulated on the test set of NYU Depth v2. Our
-MDE was DenseDepth, and only the actual histogram matching portion 
-was timed, not the running of the MDE nor the denoising pipeline.
+data with a signal-to-background (SBR) of 100, simulated on the test set of NYU
+Depth v2 and using DenseDepth~\cite{Alhashim2018} for our MDE CNN.
+Only the histogram matching portion was timed, not the CNN nor the denoising pipeline.
 
@@
   \end{tabular}
-  \caption{Ablation study on simulated data for NYU Depth v2. When the SPAD
+  \caption{Effect of reflectance modeling on RMSE and runtime. When the SPAD
     is simulated with the reflectance info but no reflectance estimate is used
@@
 
+\section{A note on pixel shifting and dither artifacts}
+We give pseudocode for our pixel shifting algorithm here. The pixels of the
+image $I$ take depth bin values in $\set{0,\ldots,K-1}$. 
+{ \footnotesize
+  \begin{algorithm}[H]
+    \caption{Move Pixels}
+    \label{alg:move_pixels}
+    \begin{algorithmic}
+      \footnotesize \Procedure{MovePixels}{input image $I$ size $M \times N$,
+        pixel movement matrix $T$ of size $K \times K$} \For{$k$ in $0,\ldots,
+        K-1$} \State $p[k,:] \gets T[k,:]/\sum_{i=1}^K T[k,i]$ \EndFor \For{$m$
+        in $1,\ldots,M$} \For{$n$ in $1,\ldots,N$} \State Sample $k'$ according
+      to $p[I[m,n],:]$. \State $I[m,n] \gets k'$. \EndFor \EndFor \State
+      \textbf{return} $I$ \EndProcedure
+    \end{algorithmic}
+  \end{algorithm}
+} Because the pixel shifting process in Algorithm \ref{alg:move_pixels} contains
+a sampling step, it is possible for
+\textit{dither artifacts} to appear in the output image $I$, as shown in figure
+\ref{fig:dither}. Specifically, when there are multiple possible output depth
+bins for a given input depth bin, and a large region of equal depth in the input
+image, the randomness in the pixel shifting algorithm will distribute the pixels
+of large, equal-depth region in the input across the multiple possible output
+depth bins in a random fashion.
+
+\begin{figure}[H]
+  \centering \includegraphics[width=0.66\textwidth]{dither.pdf}
+  \caption{Example of dither artifacts. Sometimes, when our histogram matching
+    is applied to images with large regions of similar depths, dither artifacts
+    will occur.}
+  \label{fig:dither}
+\end{figure}
+
 \section{Additional results on NYU Depth v2}
-Figures \ref{fig:densedepth_1}--\ref{fig:dorn_3} show additional results
+Figures \ref{fig:densedepth_1}--\ref{fig:midas_3} show additional results
 for our method on the NYU Depth v2 dataset when the depth estimate is
 initialized with the DenseDepth \cite{Alhashim2018} (Figures
-\ref{fig:densedepth_1}--\ref{fig:densedepth_3}), and DORN \cite{Fu2018} (Figures
-\ref{fig:dorn_1}--\ref{fig:dorn_3}) monocular depth estimators.
-% and MiDaS \cite{MiDaS} (Figures \ref{midas_1} -- \ref{midas_3}).
-% network of \cite{Alhashim2019}.
+\ref{fig:densedepth_1}--\ref{fig:densedepth_3}), DORN \cite{Fu2018} (Figures
+\ref{fig:dorn_1}--\ref{fig:dorn_3}) 
+and MiDaS \cite{Lasinger:2019} (Figures \ref{fig:midas_1} -- \ref{fig:midas_3}) monocular depth estimators.
+
 We compare the output of the network $z_0$, the
@@
 our histogram matching method under a signal-to-background ratio (SBR) of 100.
-We use the Y channel of the YCbCr-transformed RGB image as our reflectance map
+We use the luminance of the RGB image as our reflectance map
 for both SPAD simulation and histogram matching.

### 2019-11-09 paper/cvpr2020/sections/figures/sync_figures.sh

@@ -11,3 +11,4 @@ rsync -R ././captured/**/**/?(gt_z_proj_crop_depth_fig|z_init_depth_fig|z_med_sc
 rsync -R ././captured/**/**/?(diff_colorbar|depth_colorbar).pdf "$gdrive" 
 rsync method.pdf "$gdrive"
 rsync captured.pdf "$gdrive"
+rsync dither.pdf "$gdrive"

### 2020-02-25 paper/cvpr2020/rebuttal/rebuttal.tex
Adding eccv submission

\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Include other packages here, before hyperref.
\usepackage{float}
% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%%%%%%%%% PAPER ID  - PLEASE UPDATE
\def\cvprPaperID{2224} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\raggedbottom
\begin{document}
\title{Optimizing MDE with Global Depth Histogram
  Matching using a Single SPAD Transient}

\maketitle
\thispagestyle{empty}
%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank our reviewers for their constructive feedback and will make every
effort to address their concerns.

We propose a technique for augmenting the capabilities of monocular depth
estimation using transient data from a single-pixel SPAD and diffuse laser
illumination using a straightforward histogram matching algorithm. We agree with
all of our reviewers that the idea of using such a depth transient is novel and
worth investigating.

\vspace{1mm}\noindent\textbf{Equivalence of scanning and diffuse SPAD (R1, R2)}
First, for
both scanned and diffuse modes, pileup can be corrected \cite{heide2018subpico} or avoided by operating in the
low-flux regime. 
Second, we empirically validate that the digitally summed scanned SPAD
measurements and the diffused measurements are almost identical. We will add
discussions of both of these points to the paper.
\vspace{-2mm}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/figure.pdf}
  \caption{Setup and captured transients for scanned and diffuse mode.}
\end{figure}

\vspace{-3mm}\noindent\textbf{Energy of diffuse SPAD (R1, R2, R3)}
Assuming an ambient spectral irradiance of $I_A = 0.1$ $mW/m^2$, we can calculate the
laser power required to achieve a minimum SBR of 5 for a diffuse scene at $r = 2$ m
and a field of view of $\theta = 40^\circ$ as
\begin{equation}
  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}}
\end{equation}
Which gives $P_{\text{min}} = 1.1$ W. laserpointersafety.com gives the Nominal
Ocular Hazard Distance for this laser as 0.34m, i.e. the laser light level is
safe beyond this distance. Given that there are VCELs with well above
this capability, we feel that our method is a very competitive, eye safe, option for short
range indoor scenes.

% McManamon 2012 provide the following equation for any LiDAR setup:
% \begin{equation}
%   P_R = P_T \cdot \frac{\rho_tA_t}{A_{\text{illum}}} \cdot \frac{A_{\text{rec}}}{\pi R^2} \cdot \eta_{\text{atm}}^2 \cdot \eta_{\text{sys}}
% \end{equation}
%   In the diffused setting, With a laser at 450 nm, and under the assumptions of $P_T=0.0003, \rho_t = 0.5,
%   A_t = A_{\text{illum}}, A_{\text{rec}} = 7\times 10^{-8}$ (corresponding to a
%   SPAD with aperture diameter $300$ $\mu$m), $R = 5, \eta_{\text{atm}} = 1$, and
%   $\eta_{\text{sys}} = 0.5$ we
%   accumulate $10^6$ signal photons in 0.04 sec, 0.8 sec in the low-flux regime.
%   At 10MHz, this corresponds to 8 million pulses, or the equivalent of scanning
%   each point in a $512 \times 512$ grid 30 times. (Include ambient flux levels?)

\vspace{1mm}\noindent\textbf{Justification for two-step method (R1)} We believe
our final architecture's strength is the fact that it is agnostic to the
MDE strategy used and will note this in the paper.

\vspace{1mm}\noindent\textbf{Kinect/Dual Pixels (R2)} While each of these methods has its own
benefits and disadvantages, our approach adds minimal additional hardware to a
single RGB camera. We will rephrase our comparisons to these methods accordingly.

\vspace{1mm}\noindent\textbf{Failure/limited improvement cases (R2)} We show at least one example in
the supplement where our method improves in RMSE by only 0.062. In general, our
method struggles with scenes where the inital depth map contains ordinal depth
errors.

\vspace{1mm}\noindent\textbf{Maximum SBR used for simulated results (R2)} The
experimental results are intended to show the performance of the method under
more realistic conditions. For example, the SBR of the outdoor scene was
apprximately 0.15. Detailed statistics for the experimental scenes will be
included to help strengthen our argument for practicality.

\vspace{1mm}\noindent\textbf{Interreflections (R2)} We neglect interreflections
as a second-order effect following existing work on flash LiDAR systems. \cite{iddan20013dstudio}

\vspace{1mm}\noindent\textbf{Uniform background assumption and negative
  histogram values (R2)} When operating in the low-flux condition, we follow the
many papers \cite{lindell2018} which model background photons as a constant term that adds equally to all bins.
Also, our algorithm clips all negative histogram values to zero after the background
subtraction step and we will update the section to reflect this.

\vspace{1mm}\noindent\textbf{Number of acquisition cycles (R1)} In simulation, the histogram
is directly computed via equation (2).
Scan times varied from 5 to 25 mins indoors and 3 mins for the outdoor
scene (the number of $512 \times 512$
frames can be computed from the scan time and the laser pulse rate of 10MHz).
While this seems excessively long, this was a deliberate decision to maximize the fidelity of our
ground truth reconstructions, not to simulate the real capture setting. We
will report the scan times and number of acquisitions in the paper.

\vspace{1mm}\noindent\textbf{Selection of $K$, $\ell$, and $u$ (R1)} For both simulation and
experiment, $K$ is chosen to tradeoff between speed and accuracy. For
$h_{\text{source}}$, $(\ell, u)$ are set to encompass all possible scene depths. For 
    $h_{\text{target}}$, $(\ell, u)$ are chosen based on the depth values for
    the bins $\hat n_{\text{first}}$ and $\hat n_{\text{last}}$, respectively.
    We will update the paper to clarify this point.

\vspace{1mm}\noindent\textbf{Use of overdramatic or imprecise language (R1, R2)} We will make various
wording adjustments, such as using ``moderate'' instead of
``slight'' to describe the improvement from median rescaling, using
``augmenting'' instead of ``optimizing'', and changing improper uses of
``histogram'' to ``transient''.

\vspace{1mm}\noindent\textbf{Teaser colormaps misleadingly scaled (R2)} We will adjust both
    figures to use the same scale.

\vspace{1mm}\noindent\textbf{Approximating Poisson dist. with Gaussian (R3)} We will add a
    footnote explaining our usage of this approximation where it occurs.

\vspace{1mm}\noindent\textbf{Typo in L388 (R3)} We will correct $n < n_{\text{last}}$ to $n <
    n_{\text{first}}$.

{\small
\bibliographystyle{ieeetr}
\bibliography{references}
}

\end{document}

### 2020-02-25 paper/eccv2020/main.tex
Adding eccv submission

--- 2019-10-20 paper/cvpr2020/main.tex
@@
-% TODO:
-%@article{caramazza2018neural,
-%  title={Neural network identification of people hidden from view with a single-pixel, single-photon detector},
-%  author={Caramazza, Piergiorgio and Boccolini, Alessandro and Buschek, Daniel and Hullin, Matthias and Higham, Catherine F and Henderson, Robert and Murray-Smith, Roderick and Faccio, Daniele},
-%  journal={Scientific reports},
-%  volume={8},
-%  number={1},
-%  pages={11945},
-%  year={2018},
-%  publisher={Nature Publishing Group}
-%}
-%
+% updated April 2002 by Antje Endemann
+% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016; AAS, 2020
 
-\documentclass[10pt,twocolumn,letterpaper]{article}
+\documentclass[runningheads]{llncs}
+\usepackage{graphicx}
+\usepackage{comment}
+\usepackage{amsmath,amssymb} % define this before the line numbering.
+\usepackage{color}
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+% INITIAL SUBMISSION - The following two lines are NOT commented
+% CAMERA READY - Comment OUT the following two lines
+% \usepackage{ruler}
+% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 
-% Include other packages here, before hyperref.
 \usepackage{booktabs}
 \usepackage{caption}
-\usepackage{subcaption}
 \usepackage{array}
@@
 \input{mark_defs.tex}
+% \DeclareRobustCommand\onedot{\futurelet\@let@token\@onedot}
+% \def\@onedot{\ifx\@let@token.\else.\null\fi\xspace}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-
-% \cvprfinalcopy % *** Uncomment this line for the final submission
-
-\def\cvprPaperID{2224} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
-
+\def\eg{\emph{e.g.}} \def\Eg{\emph{E.g.}}
+\def\ie{\emph{i.e.}} \def\Ie{\emph{I.e.}}
+\def\cf{\emph{c.f.}} \def\Cf{\emph{C.f.}}
+\def\etc{\emph{etc}} \def\vs{\emph{vs.}}
+\def\wrt{w.r.t.} \def\dof{d.o.f.}
+\def\etal{\emph{et al.}}
 \graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
@@
 % Pages are numbered in submission mode, and unnumbered in camera-ready
-\ifcvprfinal\pagestyle{empty}\fi
+
 \begin{document}
+% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
+% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
+% \linenumbers
+\pagestyle{headings}
+\mainmatter
+\def\ECCVSubNumber{3668}  % Insert your submission number here
 
-%%%%%%%%% TITLE
-\title{Optimizing Monocular Depth Estimation with Global Depth Histogram
-  Matching using a Single SPAD Transient}
+\title{Improving Monocular Depth Estimation with Global Depth Histogram
+  Matching using a Single SPAD Transient} % Replace with your title
 
-\author{First Author\\
-Institution1\\
-Institution1 address\\
-{\tt\small firstauthor@i1.org}
-% For a paper whose authors are all at the same institution,
-% omit the following lines up until the closing ``}''.
-% Additional authors and addresses can be added with ``\and'',
-% just like the second author.
-% To save space, use either the email address or home page, not both
-\and
-Second Author\\
-Institution2\\
-First line of institution2 address\\
-{\tt\small secondauthor@i2.org}
-}
+% INITIAL SUBMISSION 
+%\begin{comment}
+\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
+\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
+\author{Anonymous ECCV submission}
+\institute{Paper ID \ECCVSubNumber}
+%\end{comment}
+%******************
 
+% CAMERA READY SUBMISSION
+\begin{comment}
+\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Princeton University, Princeton NJ 08544, USA \and
+Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\email{lncs@springer.com}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+\email{\{abc,lncs\}@uni-heidelberg.de}}
+\end{comment}
+%******************
 \maketitle
-%\thispagestyle{empty}
 
-%%%%%%%%% ABSTRACT
 \begin{abstract}
-Existing monocular depth estimation algorithms successfully predict the relative depth {order} of objects in a scene.
-However, because of the fundamental scale ambiguity associated with monocular images, these algorithms fail at correctly predicting an object's true metric depth. 
-In this work, we demonstrate how a depth histogram of the scene, which can be readily captured using a single-pixel diffused single-photon avalanche diode (SPAD), can be fused with the output of existing monocular depth estimation algorithms to resolve the depth ambiguity problem.
-We validate this novel sensor fusion technique experimentally and in extensive simulation.
-We show that it dramatically improves the performance of several state-of-the-art monocular depth estimation algorithms.
+  Existing monocular depth estimation algorithms successfully predict the
+  relative depth {order} of objects in a scene.
+  However, because of the fundamental scale ambiguity associated with monocular
+  images, these algorithms fail at correctly predicting an object's true metric
+  depth.
+  In this work, we demonstrate how a depth histogram of the scene, which can be
+  readily captured using a single-pixel diffused single-photon avalanche diode
+  (SPAD), can be fused with the output of existing monocular depth estimation
+  algorithms to resolve the depth ambiguity problem.
+  We validate this novel sensor fusion technique experimentally and in extensive
+  simulation. We show that it dramatically improves the performance of several
+  state-of-the-art monocular depth estimation algorithms.
+  \dots
+  \keywords{monocular depth estimation, single-photon avalanche diode, histogram
+  matching, LiDAR}
 \end{abstract}
-
-%%%%%%%%% BODY TEXT
 
@@
 
-{\small
-\bibliographystyle{ieeetr}
+\clearpage
+% ---- Bibliography ----
+%
+% BibTeX users should specify bibliography style 'splncs04'.
+% References will then be sorted and formatted in the correct style.
+%
+\bibliographystyle{splncs04}
 \bibliography{references}
-}
-
 \end{document}

### 2020-02-25 paper/eccv2020/sections/simulation.tex
Adding eccv submission

--- 2019-11-04 paper/cvpr2020/sections/simulation.tex
@@
 the histogram by the total number of observed signal photon counts (set to 
-$10^6$) and  add a fixed number of background photons $b \in \set{10^5, 2\times
+$10^6$) and  add a fixed number of background photons $b \in \set{2\times 10^5, 10^5, 2\times
 10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
 count detections, and the different background levels correspond to
-signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
+signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively. Finally,
 each bin is Poisson sampled to produce the final simulated SPAD transient.
-
-% \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}
 
@@
 We show an extensive quantitative evaluation in Table~\ref{tab:comparison}.
-Here, we evaluate three recent monocular depth estimation techniques:
+Here, we evaluate three recent monocular depth estimation CNNs:
 DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and
 MiDaS~\cite{Lasinger:2019}. To evaluate the quality of DORN and DenseDepth, we
-report various standard error metrics. Moreover, we show a simple
-post-processing step that rescales their outputs by the median ground truth
+report various standard error metrics~\cite{Eigen2014}. Moreover, we show a simple
+post-processing step that rescales their outputs to match the median ground truth
 depth~\cite{Alhashim2018}. We also show the results of histogram matching the
@@
 ground truth depth map, the raw output of the DenseDepth CNN, the result of
-rescaling the CNN output by the median ground truth depth, the result of
+rescaling the CNN output with the median ground truth depth, the result of
 histogram-matching the CNN output by the ground truth depth map histogram, and
@@
 that look reasonable but that have an average root mean squared error (RMSE) of
-about 50--60~cm. Re-scaling this depth map by the median ground truth depth
+about 50--60~cm. Rescaling this depth map to match the median ground truth depth
 value slightly improves the quality and histogram-matching with the ground

### 2020-02-25 nyuv2/captured/analyze_all_scenes.py

@@ -38,22 +38,22 @@ def cfg():
     # bin_width_ps is the bin width in picoseconds of the SPAD for that particular scene
     # min_r and max_r are set to reject direct reflections off the beam splitter.
     scenes = {
-        "8_29_kitchen_scene": {"offset": (-10, -8), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_29_conference_room_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_30_conference_room2_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        # "8_29_kitchen_scene": {"offset": (-10, -8), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        # "8_29_conference_room_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        # "8_30_conference_room2_scene": {"offset": (-16, -12), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        # "8_30_Hallway": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
         "8_30_poster_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
-        "8_31_outdoor3": {"offset": (0, 0), "bin_width_ps": 32, "min_r": 0.4, "max_r": 11.},
+        # "8_30_small_lab_scene": {"offset": (0, 0), "bin_width_ps": 16, "min_r": 0.4, "max_r": 9.},
+        # "8_31_outdoor3": {"offset": (0, 0), "bin_width_ps": 32, "min_r": 0.4, "max_r": 11.},
     }
     # rgb in [0, 255]
     models = {
         "midas": {"load": lambda model_path, device: get_midas("MiDaS/model.pt", device),
                   "run": lambda model, rgb, depth_range, device: midas_predict(model, rgb/255., depth_range, device)},
-        "dorn": {"load": lambda model_path, device: DORN(),
[…]

### 2020-02-25 nyuv2/captured/capture_utils.py

@@ -136,9 +136,7 @@ def depth_imwrite(img, filepath):
     :param filepath:
     :return:
     """
-    # print("depth_imwrite to {}".format(filepath))
-    # print(np.max(img))
-    # print(np.min(img))
+    print("depth_imwrite to {}".format(filepath))
     img_scaled = ((img - np.min(img)) * 65535./(np.max(img) - np.min(img))).astype(np.uint16)
     cv2.imwrite(filepath + ".png", img_scaled)
 

### 2020-02-25 paper/cvpr2020/rebuttal/figures/remove_dc_from_spad.py

@@ -1,0 +1,24 @@
+import numpy as np
+
+def remove_dc_from_spad_edge(spad, ambient, grad_th=1e3, n_std=1.):
+    """
+    Create a "bounding box" that is bounded on the left and the right
+    by using the gradients and below by using the ambient estimate.
+    """
+    # Detect edges:
+    assert len(spad.shape) == 1
+    edges = np.abs(np.diff(spad)) > grad_th
+    print(np.abs(np.diff(spad)))
+    first = np.nonzero(edges)[0][1] + 1  # Want the right side of the first edge
+    last = np.nonzero(edges)[0][-1]      # Want the left side of the second edge
+    below = ambient + n_std*np.sqrt(ambient)
+    # Walk first and last backward and forward until we encounter a value below the threshold
+    while first >= 0 and spad[first] > below:
+        first -= 1
+    while last < len(spad) and spad[last] > below:
+        last += 1
+    spad[:first] = 0.
+    spad[last+1:] = 0.
+    print(first)
+    print(last)
+    return np.clip(spad - ambient, a_min=0., a_max=None)

### 2020-02-25 paper/eccv2020/sections/figures/refresh_tables.sh

@@ -1,0 +1,1 @@
+rsync -r markn1@ares:~/spad_single/nyuv2/weighted_histogram_matching/figures/sim_table.tex ~/Documents/Stanford/ares/spad_single/paper/cvpr2020/sections/figures/sim_table.tex

### 2020-02-25 paper/eccv2020/sections/figures/sync_figures.sh

@@ -1,0 +1,14 @@
+#!/usr/bin/env bash
+# Sync figures with Google Drive or other folders so everyone can see them
+gdrive="/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/";
+rsync captured/midas/8_30_small_lab_scene/teaser.pdf "$gdrive"
+rsync full_pipeline/full_pipeline.jpeg "$gdrive"
+shopt -s extglob  #Allows for | in bash pattern matching below
+rsync -r comparison/*.pdf "$gdrive/comparison"
+rsync comparison.pdf "$gdrive"
+rsync prototype_single_col.pdf "$gdrive"
+rsync -R ././captured/**/**/?(gt_z_proj_crop_depth_fig|z_init_depth_fig|z_med_scaled_depth_fig|z_pred_depth_fig|rgb_cropped_fig|z_init_diff_fig|z_med_scaled_diff_fig|z_pred_diff_fig).png "$gdrive"
+rsync -R ././captured/**/**/?(diff_colorbar|depth_colorbar).pdf "$gdrive" 
+rsync method.pdf "$gdrive"
+rsync captured.pdf "$gdrive"
+rsync dither.pdf "$gdrive"

### 2020-02-26 paper/eccv2020/sections/discussion.tex
Updated with eccv format, initial revisions.

--- 2019-11-09 paper/cvpr2020/sections/discussion.tex
@@
 depth estimate can be corrected to produce accurate absolute depth. However, if
-the ordering of the initial depths is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.
+the ordering of the initial depths is not correct, these errors will not be
+corrected by our histogram matching procedure and may propagate to the final
+output depth map.
 
@@
 little light will return to the SPAD and it may be difficult to accurately
-capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.
+capture distant scene geometry in the histogram. Thus our method is best suited
+to short to medium-range scenes. For example, assume an indoor scene with
+fluorescent bulbs and an ambient spectral irradiance of $I_A =
+2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
+to the laser). The laser power required to achieve a minimum SBR of 5 for a
+diffuse scene at $r = 2$ m
+and a field of view of $\theta = 40^\circ$ can be calculated as
+\begin{equation}
+  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
+\end{equation} 
+giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect.
 
@@
 \paragraph{Future Work}
-While our hardware prototype is large, future work could miniaturize this system. Our algorithm or similar sensor fusion algorithms could
+While our hardware prototype is large, future work could miniaturize this
+system. Our algorithm or similar sensor fusion algorithms could
 also be integrated into electronics that already contain the required hardware

### 2020-02-26 paper/eccv2020/sections/hardware.tex
Adding eccv submission
Updated with eccv format, initial revisions.

--- 2019-10-20 paper/cvpr2020/sections/hardware.tex
@@
-\begin{figure}[t!]
-	\centering
-  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
-  \caption{Prototype scanning setup. The pulsed light from the laser travels
-    through a beam splitter before being guided by the galvo to the scene.
-    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
-    camera is used to capture the image used to generate the monocular depth estimate
-    (the depth camera is not used).}
-  \label{fig:prototype}
-\end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-As shown in Figure~\ref{fig:prototype}, our prototype comprises a color camera (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis galvanometer mirror system (Thorlabs GVS012).
-The laser operates at 670~nm with a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power of 0.5~mW.
+As shown in Figure~\ref{fig:prototype}, our prototype comprises a color camera
+(Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM
+series, free-running), a laser (ALPHALAS PICOPOWER-LD-450-50), and a two-axis
+galvanometer mirror system (Thorlabs GVS012). The laser operates at 670~nm with
+a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power
+of 0.5~mW.
 
-The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps.
-The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
-The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm.
-A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
-The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
-This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth.
-The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.
+The monocular depth estimate is calculated
+using the RGB image captured by the Kinect v2.
+The SPAD records temporal histograms with 4096 bins, each corresponding to a
+time window of 16~ps. The SPAD and laser are co-axially aligned using a beam
+splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the
+combined laser pulse width and SPAD jitter is about 70~ps, allowing the system
+to record depth maps with an accuracy of about 1~cm. A National Instruments data
+acquisition device (NI-DAQ USB-6343) provides synchronization signals for the
+galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a
+resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD
+measurement is generated by summing all of these measurements for a specific
+scene. This allows us to validate the accuracy of the proposed histogram
+matching algorithm, which only uses the integrated single histogram, by
+comparing it with the captured depth. To empirically assess the equivalence of
+diffused SPAD measurements and summed scanned measurements, we captured the
+following scene under both raster-scanned and diffuse mode conditions:
+
+\begin{figure}[t]
+	\centering
+  \includegraphics[width=0.8\columnwidth]{scanned_diffuse.pdf}
+  \caption{Scene and measurements for diffused and summed scanned mode. The observed
+    counts in the diffuse mode match closely with the sum of the raster-scanned
+    measurements.}
+  \label{fig:scanned_diffuse}
+  % \vspace{-0.5em}
+\end{figure}
 
@@
 the scanning system using MATLAB's camera calibration toolbox. 
-The SPAD histogram and RGB image were captured from slightly different viewpoints; we account for this in the SPAD histogram by shifting the 1D transient according to the SPAD's offset from the RGB camera.
+The SPAD histogram and RGB image were captured from slightly different
+viewpoints; we account for this in the SPAD histogram by shifting the 1D
+transient according to the SPAD's offset from the RGB camera. We re-bin the
+captured 1D transient for the indoor captured results
+using Equation~\ref{eq:sid_bin_edges} with $K = 600$ bins, and $(\ell, u)=(0.4, 9.)$.
+For the outdoor captured result, we use $K=600$ and $(\ell, u)=(0.4, 11)$.
 %We use the camera extrinsics to Once the SPAD volume has been summed over the spatial dimensions, it is unclear
@@
 
-We re-bin the captured 1D transient for the indoor captured results 
-using Equation~\ref{eq:sid_bin_edges} with $K = 600$ bins, and $(\ell, u)=(0.4, 9.)$.
-For the outdoor captured result, we use $K=600$ and $(\ell, u)=(0.4, 11)$. 
 %% \textcolor{red}{Mark, please write a short paragraph on calibration details, including any warping of the SPAD histograms you did to compensate for the offset in camera and SPAD position.}
@@
 downsample the image to a resolution of $353 \times 257$. We then feed this RGB
-image into the monocular depth estimation algorithm.
-In Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among the depth estimators we tested.
-Additional scenes, also processed with other MDE approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are included in the supplement.
-The ground truth depth is captured with the scanned SPAD, as described above, and regions with low signal-to-noise ratio are masked out (shown in black).
+image into the monocular depth estimation algorithm. In
+Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and
+processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among
+the depth estimators we tested. Additional scenes, also processed with other MDE
+approaches, including DenseDepth~\cite{Alhashim2018} and DORN~\cite{Fu2018}, are
+included in the supplement. The ground truth depth is captured with the scanned
+SPAD, as described above, and regions with low signal-to-noise ratio are masked
+out (shown in black).
 
-In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we see that the monocular depth CNN estimates the ordinal depth of the scene reasonably well.
-However, the root mean squared error (RMSE) for these two scenes is relatively high ranging from 2.6--3.2~m (see red/white error maps in Fig.~\ref{fig:results_captured}).
-The proposed method using a single diffused SPAD measurement corrects this systematic depth estimation error and brings the RMSE down to 0.6--0.9~m.
-The ``Poster'' scene is meant to confuse the CNN---it shows a flat poster with a printed scene.
-As expected, the CNN predicts that the statue is closer than the arches in the background, which is incorrect in this case.
-The proposed method uses the SPAD histogram to correctly flatten the estimated depth map.
+In the first two examples, the ``Hallway'' and ``Conference Room'' scenes, we
+see that the monocular depth CNN estimates the ordinal depth of the scene
+reasonably well. However, the root mean squared error (RMSE) for these two
+scenes is relatively high ranging from 2.6--3.2~m (see red/white error maps in
+Fig.~\ref{fig:results_captured}). The proposed method using a single diffused
+SPAD measurement corrects this systematic depth estimation error and brings the
+RMSE down to 0.6--0.9~m. The ``Poster'' scene is meant to confuse the CNN---it
+shows a flat poster with a printed scene. As expected, the CNN predicts that the
+statue is closer than the arches in the background, which is incorrect in this
+case. The proposed method uses the SPAD histogram to correctly flatten the
+estimated depth map.
 
+\begin{figure}[t]
+	\centering
+  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
+  \caption{Prototype scanning setup. The pulsed light from the laser travels
+    through a beam splitter before being guided by the galvo to the scene.
+    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
+    camera is used to capture the image used to generate the monocular depth estimate
+    (the depth camera is not used).}
+  \label{fig:prototype}
+  % \vspace{-0.5em}
+\end{figure}
 \begin{figure}[t]

### 2020-02-26 paper/eccv2020/sections/method.tex
Updated with eccv format, initial revisions.

--- 2019-11-09 paper/cvpr2020/sections/method.tex
@@
 times per second with the specific number of emitted pulses being controlled by
-the repetition rate of the laser.  Each detected photon arrival event is
+the repetition rate of the laser. As derived in previous work, the resulting measurement
+can be modeled as an inhomogeneous Poisson process
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}. Each detected photon arrival event is
 discretized into a histogram $h$ of the form
@@
 represents background detections from ambient light and false positive detections known as \textit{dark
-count}. As derived in previous work, the combination of signal and background
-can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015}. Finally, we adopt the term
+count}. Like previous work, we neglect scene interreflections
+and confine ourselves to the low-flux condition (where the number of photon
+detections is controlled to be much smaller than the number of emitted pulses)
+to avoid pileup~\cite{Shin2016}. Finally, we adopt the term
 \textit{transient} for the histogram $h[n]$~\cite{Xin2019}.
@@
 remove background counts from the transient, (2) compensate for distance
-falloff effects, and (3) re-bin the histogram to improve relative accuracy
+falloff effects, and (3) re-bin the transient to improve relative accuracy
 with increasing distance. An overview of the processing pipeline, including
@@
 estimate after applying histogram matching.  Instead, we estimate the temporal
-support of histogram bins containing signal photons (\ie the range of depths in the
-scene) and only subtract $\hat{b}$ from these bins. We assume that other
-histogram bins contain only background counts that can be discarded.
+support of transient bins containing signal photons (\ie the range of depths in the
+scene) and only subtract $\hat{b}$ from these bins (clipping negative bin values
+to 0). We assume that other
+transient bins contain only background counts that can be discarded.
 
@@
 We estimate $n_\text{first}$ and $n_\text{last}$ by calculating  
-first order differences of the histogram $d[n] = \abs{h[n] - h[n+1]}$. 
-For a moderate number of background counts, the variance of $h[n] - h[n+1]$ can be approximated  
-as a Gaussian with mean $0$ and variance $2b$, and we identify candidate discontinuities
+first order differences of the transient $d[n] = \abs{h[n] - h[n+1]}$. 
+For a moderate number of background counts, each background bin $h[n]$ can be
+approximated as a Gaussian with mean and variance $b$, and thus $h[n] - h[n+1]$ can be approximated  
+as a Gaussian with mean $0$ and variance $2b$. We identify candidate discontinuities
 $\mathcal{E}$ with a threshold on the measured differences:
@@
 The remaining ambient counts are discarded by setting the recorded counts to
-zero for all bins where $n < n_\text{last}$ and $n > n_\text{last}$. We use 
+zero for all bins where $n < n_\text{first}$ and $n > n_\text{last}$. We use 
 $\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.
@@
 \vspace{0.8em}\noindent{\bf Falloff Compensation.}
-In the second step, we compensate for distance falloff effects by multiplying the histogram
-by distance-dependent scaling factor,
+In the second step, we compensate for distance falloff effects by multiplying
+the transient
+by the distance-dependent scaling factor,
 \begin{equation}
@@
 
-\vspace{0.8em}\noindent{\bf Histogram Re-binning.}
+\vspace{0.8em}\noindent{\bf Transient Re-binning.}
 Last, we re-bin the transient so that the bin widths increase for increasingly
@@
 This rebinning procedure allows us to use a reduced number of bins in the histogram
-matching procedure, reducing computation time while maintaining accuracy. For
-the simulated results we follow Fu et al.\ and use $K = 140$ bins with $(\ell, u)
-= (0.657, 9.972)$~\cite{Fu2018}. The output of the rebinning procedure is the
+matching procedure, reducing computation time while maintaining accuracy. The
+value of $K$ is selected to trade off between speed and accuracy. For
+the simulated results we use $K = 140$ bins with $(\ell,
+u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
+n_{\text{last}}$ respectively.
+ The output of the rebinning procedure is the
 target histogram $h_\text{target}$ which we use for histogram matching.
@@
 to match the histogram of an input depth map, obtained from a monocular depth estimator, to the
-post-processed target histogram $h_\text{target}$ from the SPAD.
+post-processed target histogram $h_\text{target}$ from the SPAD. This
+initialize-then-refine approach allows us to swap out the monocular depth
+estimator to deal with different scene types without requiring end-to-end retraining.
 
@@
 at the corresponding depth, we add the estimated reflectance value of the pixel
-to the histogram bin.
+to the histogram bin. We also re-bin this histogram, again following Fu et al.\
+and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.
 
-We match the histogram $h_\text{source}$ to $h_\text{target}$ using the method of
+We match the re-binned histogram $h_\text{source}$ to $h_\text{target}$ using the method of
 Morovic et al.~\cite{Morovic2002}. The method involves computing a pixel movement

### 2020-02-26 paper/eccv2020/sections/related.tex
Updated with eccv format, initial revisions.

--- 2019-11-09 paper/cvpr2020/sections/related.tex
@@
 %
-Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}.
-More recently, deep neural networks have been applied to this problem.
-For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
-predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function.
-Various experiments using different types of encoder networks (\eg ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
-Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.
+Estimating a depth map from a single RGB image has been approached using Markov
+Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and
+non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
+networks have been applied to this problem. For example, Eigen et
+al.~\cite{Eigen2014} use a multi-scale neural network to predict depth maps,
+Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a
+network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic
+depth discretization scheme with an ordinal regression loss function. Various
+experiments using different types of encoder networks (\eg ResNet,
+DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
+success, as have approaches mixing deep learning with conditional random
+fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}.
+Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of
+monocular depth estimation using cross-dataset transfer.
 
-Despite achieving remarkable success on estimating ordinal depth from a single image, none of these methods are able to resolve inherent scale ambiguity in a principled manner.
-We introduce a new approach that leverages existing monocular depth estimation networks and disambiguates the output using depth histogram-like measurements obtained from a single, diffused SPAD.
-Other approaches to disambiguating monocular depth estimation use optimized freeform lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors and specialized image reconstruction methods.
-In contrast, our approach is potentially compatible with existing camera systems (\eg deployed on current cell phones) and our algorithms could be used in tandem with existing camera ISPs.
+Despite achieving remarkable success on estimating ordinal depth from a single
+image, none of these methods are able to resolve inherent scale ambiguity in a
+principled manner. We introduce a new approach that leverages existing monocular
+depth estimation networks and disambiguates the output using depth
+histogram-like measurements obtained from a single, diffused SPAD. Other
+approaches to disambiguating monocular depth estimation use optimized freeform
+lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel
+sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
+and specialized image reconstruction methods. In contrast, our approach adds
+minimal additional hardware to a single RGB camera, and leverages sensors currently
+deployed in consumer electronics.
 

### 2020-02-27 paper/eccv2020/sections/discussion.tex
Moving figures around, adding edit red text.

--- 2019-11-09 paper/cvpr2020/sections/discussion.tex
@@
 little light will return to the SPAD and it may be difficult to accurately
-capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.
+capture distant scene geometry in the histogram. Thus our method is best suited
+to short to medium-range scenes. \edit{For example, assume an indoor scene with
+fluorescent bulbs and an ambient spectral irradiance of $I_A =
+2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
+to the laser). The laser power required to achieve a minimum SBR of 5 for a
+diffuse scene at $r = 2$ m
+and a field of view of $\theta = 40^\circ$ can be calculated as}
+\begin{equation}
+  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
+\end{equation} 
+\edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect.}
 

### 2020-02-27 paper/eccv2020/sections/introduction.tex
Moving figures around, adding edit red text.

--- 2019-10-20 paper/cvpr2020/sections/introduction.tex
@@
-Estimating dense 3D geometry from 2D images is an important open problem with applications to robotics, autonomous driving, and medical imaging.
-Depth maps are a common representation of scene geometry and are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.
-Additionally, many computer vision tasks rely on depth sensing, including navigation~\cite{geiger2013vision}, semantic segmentation~\cite{gupta2013perceptual,ren2012rgb,silberman2012indoor}, 3D object detection~\cite{gupta2014learning,lin2013holistic,shrivastava2013building,song2014sliding,song2016deep}, and 3D object classification~\cite{maturana2015voxnet,qi2016volumetric,wu20153d}.
+Estimating dense 3D geometry from 2D images is an important open problem with
+applications to robotics, autonomous driving, and medical imaging. Depth maps
+are a common representation of scene geometry and are useful precursors to
+higher-level scene understanding tasks such as pose estimation and object
+detection. Additionally, many computer vision tasks rely on depth sensing,
+including navigation~\cite{geiger2013vision}, semantic
+segmentation~\cite{gupta2013perceptual,ren2012rgb,silberman2012indoor}, 3D
+object
+detection~\cite{gupta2014learning,lin2013holistic,shrivastava2013building,song2014sliding,song2016deep},
+and 3D object
+classification~\cite{maturana2015voxnet,qi2016volumetric,wu20153d}.
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{teaser.pdf}
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=0.6\columnwidth]{teaser.pdf}
   \caption{Monocular depth estimation predicts a depth map (upper right) from a
@@
 
-Traditional depth sensing techniques include those based on stereo or multiview, active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
-However, each of these techniques has aspects that may make their deployment challenging.
-For example, stereo or multiview techniques require multiple cameras, active illumination techniques may have limited resolution or require time-consuming scanning procedures, and other techniques require camera motion or multiple exposures at different focus distances.
+Traditional depth sensing techniques include those based on stereo or multiview,
+active illumination, camera motion, or focus cues~\cite{szeliski2010computer}.
+However, each of these techniques has aspects that may make their deployment
+challenging. For example, stereo or multiview techniques require multiple
+cameras, active illumination techniques may have limited resolution or require
+time-consuming scanning procedures, and other techniques require camera motion
+or multiple exposures at different focus distances.
 
-One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE), which requires only a single RGB image from a conventional camera to recover a dense depth map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}.
-Recent approaches to MDE employ neural network models that learn to predict depth by exploiting monocular image cues such as perspective, occlusion, shading, and relative object size.
-While such models have significantly improved over recent years, MDE approaches to date are incapable of reliably estimating absolute distances in a scene due to the inherent scale ambiguities of monocular image cues.
-Instead, these models excel in predicting ordinal depth, or the relative ordering of objects in a scene~\cite{Eigen2014,Fu2018}.
-Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth depth of the scene is known, the initial output of a MDE network can be corrected to produce accurate absolute depth.
+One of the most promising approaches to overcoming these challenges is monocular
+depth estimation (MDE), which requires only a single RGB image from a
+conventional camera to recover a dense depth
+map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
+to MDE employ neural network models that learn to predict depth by exploiting
+monocular image cues such as perspective, occlusion, shading, and relative
+object size. While such models have significantly improved over recent years,
+MDE approaches to date are incapable of reliably estimating absolute distances
+in a scene due to the inherent scale ambiguities of monocular image cues.
+Instead, these models excel in predicting ordinal depth, or the relative
+ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim
+and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth
+depth of the scene is known, the initial output of a MDE network can be
+corrected to produce accurate absolute depth.
 
-%For example, a larger object at a far distance to the camera results in the same 2D camera image as a smaller object of the same type that is closer to the camera.
-Therefore, MDE approaches to date are incapable of reliably estimating absolute distances of a scene.
-Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle access to the ground truth median depth, then correcting the output of the CNN to match this median depth produces accurate absolute depth maps both qualitatively and quantitatively.
+%For example, a larger object at a far distance to the camera results in the
+%same 2D camera image as a smaller object of the same type that is closer to the
+%camera. Therefore, MDE approaches to date are incapable of reliably estimating
+%absolute distances of a scene. Interestingly, Alhashim and
+%Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle
+%access to the ground truth median depth, then correcting the output of the CNN
+%to match this median depth produces accurate absolute depth maps both
+%qualitatively and quantitatively.
 
 % move to discussion
-%However, traditional approaches to depth estimation, such as stereo, suffer from lower performance when confronted with small angles or faraway objects.
-More exotic approaches use FMCW or time-of-flight LiDAR technologies, but these approaches are currently expensive and bulky.
+%However, traditional approaches to depth estimation, such as stereo, suffer
+%from lower performance when confronted with small angles or faraway objects.
+%More exotic approaches use FMCW or time-of-flight LiDAR technologies, but these
+%approaches are currently expensive and bulky.
 
-%The most promising solution to these issues uses deep learning and convolutional neural networks to perform \textit{monocular depth estimation}, estimating dense depth maps from single RGB images.
-However, this problem is underconstrained due to \textit{inherent scale ambiguity}, the unresolvable tradeoff between size and distance in single images.
-In practice, this issue commonly manifests itself in many monocular depth networks, and indeed, Wonka et.
-al.
-(cite) showed that if the method has oracle access to the ground truth median depth, then correcting the output of the CNN to match this median depth produces better depth maps both qualitatively and quantitatively.
+%The most promising solution to these issues uses deep learning and
+%convolutional neural networks to perform \textit{monocular depth estimation},
+%estimating dense depth maps from single RGB images.  However, this problem is
+%underconstrained due to \textit{inherent scale ambiguity}, the unresolvable
+%tradeoff between size and distance in single images. In practice, this issue
+%commonly manifests itself in many monocular depth networks, and indeed, Wonka
+%et. al. (cite) showed that if the method has oracle access to the ground truth
+%median depth, then correcting the output of the CNN to match this median depth
+%produces better depth maps both qualitatively and quantitatively.
 
-Although access to the median ground truth depth is impossible in a realistic scenario, low-cost sensors capable of capturing aggregated depth information from a scene are readily available.
-For example, the proximity sensor on recent generation Apple iPhones uses a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense distance to an object directly in front of the phone.
-SPADs have also been used to recover full 3D geometry, forming the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}.
-However, SPADs have not been used for 3D imaging on consumer electronics because the requirement for ultra-fast timing electronics makes it difficult to produce high-resolution arrays at low cost, and because the scanning requirement for single-pixel systems introduces a point of mechanical failure and complicates high-resolution, high-framerate imaging.
+Although access to the median ground truth depth is impossible in a realistic
+scenario, low-cost sensors capable of capturing aggregated depth information
+from a scene are readily available. For example, the proximity sensor on recent
+generation Apple iPhones uses a low-power pulsed light source and a
+single-pixel, single-photon avalanche diode (SPAD) to sense distance to an
+object directly in front of the phone. SPADs have also been used to recover full
+3D geometry, forming the backbone of emerging single-photon LiDAR
+systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, SPADs have
+not been used for 3D imaging on consumer electronics because the requirement for
+ultra-fast timing electronics makes it difficult to produce high-resolution
+arrays at low cost, and because the scanning requirement for single-pixel
+systems introduces a point of mechanical failure and complicates
+high-resolution, high-framerate imaging.
 
-%Individual SPADs are easy to fabricate and sufficiently cost-effective to be deployed in consumer electronics.
-When coupled with high-power pulsed lasers, they also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}.
-However, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost.
-Moreover, the scanning requirement for single-pixel systems precludes high-resolution, high-framerate depth mapping and is a barrier to integration in small consumer electronics.
+%Individual SPADs are easy to fabricate and sufficiently cost-effective to be
+%deployed in consumer electronics. When coupled with high-power pulsed lasers,
+%they also form the backbone of emerging single-photon LiDAR
+%systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}. However, the
+%required ultra-fast time-stamping electronics make it difficult to fabricate
+%high-resolution SPAD arrays at low cost. Moreover, the scanning requirement for
+%single-pixel systems precludes high-resolution, high-framerate depth mapping
+%and is a barrier to integration in small consumer electronics.
 
-Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene.
-The resulting measurement resembles a histogram of the depth of the scene and we demonstrate that this can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).
+Here, we propose to use a single-pixel SPAD and pulsed light source in an
+unconventional way: rather than optically focusing them to record the distance
+to a single scene point, we diffuse the emitted light and the detector over the
+entire scene. The resulting measurement resembles a histogram of the depth of
+the scene and we demonstrate that this can be used to achieve accurate absolute
+depth when combined with a monocular depth estimate
+(\cf~Figure~\ref{fig:teaser}).
 
-%Technically, a diffused SPAD does not record a true depth histogram, but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise.
-Nevertheless, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram.
+%Technically, a diffused SPAD does not record a true depth histogram, but a
+%transient that is affected by square-distance falloff of the backscattered
+%light, spatially varying reflectance of the scene, ambient photons, and
+%detector noise. Nevertheless, we can interpret the measurements of a
+%single-pixel SPAD as something similar to a depth histogram.
 
-%In this paper, we go further and show that by augmenting the RGB image with a histogram of global image depths, we can achieve substantially improved performance (and generalizability) over state-of-the-art monocular depth estimators.
-By performing an exact, weighted histogram matching on the output depth map of the depth estimator, we can match the depth histogram of the scene to the depth histogram of our estimate.
-This histogram matching is described in (cite) and is flexible enough to accommodate different pixel reflectances in the RGB image.
-Finally, this histogram can be captured relatively inexpensively using only a single pixel single-photon avalanche diode (SPAD) and pulsed laser illumination diffused over the field of view, representing a significant improvement in cost and simplicity over multi-pixel LiDAR arrays with expensive scanning mechanisms.
-It is worth noting that SPADs of this type have already made their way into existing smartphones, such as the iPhone X, and will likely play a role in future mobile sensing platforms as well.
+%In this paper, we go further and show that by augmenting the RGB image with a
+%histogram of global image depths, we can achieve substantially improved
+%performance (and generalizability) over state-of-the-art monocular depth
+%estimators. By performing an exact, weighted histogram matching on the output
+%depth map of the depth estimator, we can match the depth histogram of the scene
+%to the depth histogram of our estimate. This histogram matching is described in
+%(cite) and is flexible enough to accommodate different pixel reflectances in
+%the RGB image. Finally, this histogram can be captured relatively inexpensively
+%using only a single pixel single-photon avalanche diode (SPAD) and pulsed laser
+%illumination diffused over the field of view, representing a significant
+%improvement in cost and simplicity over multi-pixel LiDAR arrays with expensive
+%scanning mechanisms. It is worth noting that SPADs of this type have already
+%made their way into existing smartphones, such as the iPhone X, and will likely
+%play a role in future mobile sensing platforms as well.
 
 % move to discussion
-%Our method is not without limitations.
-It still requires a laser and single-pixel LiDAR detector, and as such, is sensitive to ambient photons.
-Being  a variant of histogram matching, our method is unable to transpose the values of pixels (i.e.
-if pixel $a$ is farther than pixel $b$ in the input, it will be farther than pixel $b$ in the output).
-In other words, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object).
-Finally, our method is non-differentiable, and is therefore unsuitable for end-to-end optimization of multi-part networks.
 
-To this end, we develop a sensor fusion strategy that processes the ordinal depth computed by a monocular depth estimator to be consistent with the measurements captured by the diffused SPAD.
-We demonstrate in extensive simulations that our approach achieves substantial improvements in the quality of the estimated depth maps, regardless of which specific depth estimator is used.
-Moreover, we build an RGB-SPAD camera prototype and demonstrate in practice that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes compared to MDE alone.
-With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.
-Specifically, we make the following contributions:
+To this end, we develop a sensor fusion strategy that processes the ordinal
+depth computed by a monocular depth estimator to be consistent with the
+measurements captured by the diffused SPAD. We demonstrate in extensive
+simulations that our approach achieves substantial improvements in the quality
+of the estimated depth maps, regardless of which specific depth estimator is
+used. \edit{Moreover, we build an RGB-SPAD camera prototype that takes scanned
+measurements of a scene and digitally sums them to approximate the effect of a
+diffused laser and SPAD. While this approximation is not perfect, it is
+sufficient to demonstrate that our sensor
+fusion strategy can produce higher-quality
+depth maps for a variety of captured scenes compared to MDE alone.}  With this
+work, we present a practical way to disambiguate depth estimation with RGB
+images using minimal additional sensing hardware. Specifically, we make the
+following contributions:
+
 %
@@
 \end{itemize}
+
+\edit{Our method is not without limitations. It still requires a laser and
+single-pixel LiDAR detector and is sensitive to ambient photons, which limit the
+maximum range.
+Being a variant of histogram matching, our method is
+not able to resolve ordinal depth errors (errors where an object is wrongly
+placed closer or farther relative to another object). In spite of these
+limitations, we find that our method performs remarkably well in practice.}

### 2020-02-27 paper/eccv2020/sections/method.tex
Moving figures around, adding edit red text.

@@
 
-\begin{figure}
+\begin{figure}[t!]
   \centering
-  \includegraphics[width=\columnwidth]{method.pdf}
+  \includegraphics[width=0.6\columnwidth]{method.pdf}
   \caption{Overview of processing pipeline. The processing pipeline uses
@@
 times per second with the specific number of emitted pulses being controlled by
-the repetition rate of the laser. As derived in previous work, the resulting measurement
+the repetition rate of the laser. \edit{As derived in previous work, the resulting measurement
 can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}. Each detected photon arrival event is
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}.} Each detected photon arrival event is
 discretized into a histogram $h$ of the form
@@
 represents background detections from ambient light and false positive detections known as \textit{dark
-count}. Like previous work, we neglect scene interreflections
+count}. \edit{Like previous work, we neglect scene interreflections
 and confine ourselves to the low-flux condition (where the number of photon
 detections is controlled to be much smaller than the number of emitted pulses)
-to avoid pileup~\cite{Shin2016}. Finally, we adopt the term
+to avoid pileup~\cite{Shin2016}.} Finally, we adopt the term
 \textit{transient} for the histogram $h[n]$~\cite{Xin2019}.
@@
 photons by locating discontinuities in the recorded counts~\cite{Xin2019}. An initial spike in
-the measurements at bin $n_\text{first}$ results from the onset of backscattered signal from the closest
-object, and a steep dropoff occurs after bin $n_\text{last}$ after backscattered photons from the
+the measurements at bin $n_\text{first}$ results from the onset of backscattered
+signal from the closest object, and a steep dropoff occurs after bin
+$n_\text{last}$ after backscattered photons from the
 furthest object are recorded. 
@@
 first order differences of the transient $d[n] = \abs{h[n] - h[n+1]}$. 
-For a moderate number of background counts, each background bin $h[n]$ can be
+\edit{For a moderate number of background counts, each background bin $h[n]$ can be
 approximated as a Gaussian with mean and variance $b$, and thus $h[n] - h[n+1]$ can be approximated  
-as a Gaussian with mean $0$ and variance $2b$. We identify candidate discontinuities
+as a Gaussian with mean $0$ and variance $2b$.} We identify candidate discontinuities
 $\mathcal{E}$ with a threshold on the measured differences:
@@
 The remaining ambient counts are discarded by setting the recorded counts to
-zero for all bins where $n < n_\text{first}$ and $n > n_\text{last}$. We use 
+zero for all bins where \edit{$n < n_\text{first}$} and $n > n_\text{last}$. We use 
 $\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.
@@
 This rebinning procedure allows us to use a reduced number of bins in the histogram
-matching procedure, reducing computation time while maintaining accuracy. The
-value of $K$ is selected to trade off between speed and accuracy. For
-the simulated results we use $K = 140$ bins with $(\ell,
+matching procedure, reducing computation time while maintaining accuracy.
+\edit{For the simulated results we use $K = 140$ bins with $(\ell,
 u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
-n_{\text{last}}$ respectively.
+n_{\text{last}}$ respectively.}
  The output of the rebinning procedure is the
@@
 % \end{algorithm}
+{ \footnotesize
+\begin{algorithm}
+ \caption{Find Pixel Movement} 
+ \label{alg:ehm}
+ \begin{algorithmic}
+	\footnotesize
+  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
+    \State Initialize $T$ as an $M \times N$ array of zeros.
+    \For{$m$ in $1,\ldots,M$}
+      \For{$n$ in $1,\ldots,N$}
+        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
+        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
+        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
+      \EndFor
+    \EndFor
+    \State \textbf{return} $T$
+  \EndProcedure
+ \end{algorithmic}
+\end{algorithm}
+}
+
 Histogram matching is a procedure that adjusts pixel values from an input image
@@
 at the corresponding depth, we add the estimated reflectance value of the pixel
-to the histogram bin. We also re-bin this histogram, again following Fu et al.\
-and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.
+to the histogram bin. \edit{We also re-bin this histogram, again following Fu et al.\
+and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}
 
@@
 
-{ \footnotesize
-\begin{algorithm}[H]
- \caption{Find Pixel Movement} 
- \label{alg:ehm}
- \begin{algorithmic}
-	\footnotesize
-  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
-    \State Initialize $T$ as an $M \times N$ array of zeros.
-    \For{$m$ in $1,\ldots,M$}
-      \For{$n$ in $1,\ldots,N$}
-        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
-        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
-        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
-      \EndFor
-    \EndFor
-    \State \textbf{return} $T$
-  \EndProcedure
- \end{algorithmic}
-\end{algorithm}
-}
 %

### 2020-02-27 paper/eccv2020/sections/related.tex
Moving figures around, adding edit red text.

@@
 sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
-and specialized image reconstruction methods. In contrast, our approach adds
+and specialized image reconstruction methods. \edit{In contrast, our approach adds
 minimal additional hardware to a single RGB camera, and leverages sensors currently
-deployed in consumer electronics.
+deployed in consumer electronics.}
 
@@
 energy function that penalizes foreground segmentations with dissimilar
-histograms. In a slightly different application area, Zhang et
+histograms. \edit{Caramazza et al.~\cite{caramazza2018neural} use a single
+non-line-of-sight transient to recover the identity of a person hidden from
+view.} In a slightly different application area, Zhang et
 al.~\cite{Zhang2017} train a neural network to produce realistically colorized

### 2020-02-28 paper/eccv2020/main.tex
Updated with eccv format, initial revisions.
Moving figures around, adding edit red text.
pass over intro

@@
 % CAMERA READY - Comment OUT the following two lines
-% \usepackage{ruler}
-% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+\usepackage{ruler}
+\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 
@@
 \def\etal{\emph{et al.}}
+
+\newcommand{\edit}[1]{\textcolor{red}{#1}}
+
 \graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
@@
 
-\title{Improving Monocular Depth Estimation with Global Depth Histogram
-  Matching using a Single SPAD Transient} % Replace with your title
+%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
+\title{\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient}} % Replace with your title
 
@@
 \begin{abstract}
-  Existing monocular depth estimation algorithms successfully predict the
+  Monocular depth estimation algorithms successfully predict the
   relative depth {order} of objects in a scene.
   However, because of the fundamental scale ambiguity associated with monocular
-  images, these algorithms fail at correctly predicting an object's true metric
+  images, these algorithms fail at correctly predicting true metric
   depth.
-  In this work, we demonstrate how a depth histogram of the scene, which can be
-  readily captured using a single-pixel diffused single-photon avalanche diode
-  (SPAD), can be fused with the output of existing monocular depth estimation
-  algorithms to resolve the depth ambiguity problem.
+In this work, we demonstrate how a depth histogram of the scene, which can be readily captured using a \textcolor{red}{single-pixel time-resolved detector}, can be fused with the output of existing monocular depth estimation algorithms to resolve the depth ambiguity problem.
   We validate this novel sensor fusion technique experimentally and in extensive
-  simulation. We show that it dramatically improves the performance of several
+  simulation. We show that it significantly improves the performance of several
   state-of-the-art monocular depth estimation algorithms.  
-  \dots
-  \keywords{monocular depth estimation, single-photon avalanche diode, histogram
-  matching, LiDAR}
+  \keywords{depth estimation, time-of-flight imaging}
 \end{abstract}
@@
 \bibliography{references}
+
 \end{document}

### 2020-02-28 paper/eccv2020/sections/introduction.tex
pass over intro

@@
-Estimating dense 3D geometry from 2D images is an important open problem with
+Estimating dense 3D geometry from 2D images is an important problem with
 applications to robotics, autonomous driving, and medical imaging. Depth maps
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{teaser.pdf}
+  \includegraphics[width=0.3\columnwidth]{teaser.pdf}
   \caption{Monocular depth estimation predicts a depth map (upper right) from a
@@
     reliable absolute depth estimation, resulting in large errors (inset image).
-    The proposed method uses a measurement from a diffused SPAD (lower left),
-    which resembles the shape of a histogram of the ground truth depth map, to
-    correct the output of the depth estimation and optimize the quality of the
+    The proposed method uses a \edit{single transient measurement aggregating the time-of-flight information of the entire scene (lower left)} to correct the output of the depth estimation and optimize the quality of the
     estimated absolute depth (lower right).}
@@
 generation Apple iPhones uses a low-power pulsed light source and a
-single-pixel, single-photon avalanche diode (SPAD) to sense distance to an
-object directly in front of the phone. SPADs have also been used to recover full
-3D geometry, forming the backbone of emerging single-photon LiDAR
-systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, SPADs have
+single-pixel \edit{time-resolved detector} %, single-photon avalanche diode (SPAD) 
+to sense distance to an
+object directly in front of the phone. %SPADs 
+\edit{
+Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel.
+These detectors form the backbone of modern LiDAR
+systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, single-photon sensor arrays} have
 not been used for 3D imaging on consumer electronics because the requirement for
@@
 
-Here, we propose to use a single-pixel SPAD and pulsed light source in an
+Here, we propose to use a single-pixel \edit{time-resolved detector} and pulsed light source in an
 unconventional way: rather than optically focusing them to record the distance
-to a single scene point, we diffuse the emitted light and the detector over the
-entire scene. The resulting measurement resembles a histogram of the depth of
+to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
+entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the depth of
 the scene and we demonstrate that this can be used to achieve accurate absolute
-depth when combined with a monocular depth estimate
-(\cf~Figure~\ref{fig:teaser}).
+depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (\cf~Figure~\ref{fig:teaser}).
 
@@
 depth computed by a monocular depth estimator to be consistent with the
-measurements captured by the diffused SPAD. We demonstrate in extensive
+measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
 simulations that our approach achieves substantial improvements in the quality
 of the estimated depth maps, regardless of which specific depth estimator is
-used. \edit{Moreover, we build an RGB-SPAD camera prototype that takes scanned
-measurements of a scene and digitally sums them to approximate the effect of a
-diffused laser and SPAD. While this approximation is not perfect, it is
-sufficient to demonstrate that our sensor
-fusion strategy can produce higher-quality
-depth maps for a variety of captured scenes compared to MDE alone.}  With this
+used. \edit{Moreover, we build an camera prototype that combines an RGB camera and a single-pixel time-resolved detector.}  With this
 work, we present a practical way to disambiguate depth estimation with RGB
@@
 following contributions:
-
 %
 \begin{itemize}
-	\item We propose augmenting an RGB camera with a global depth histogram captured by a diffused SPAD to address scale ambiguity error in monocular depth estimators.	
+	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a diffused time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
   \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
-	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types.
+	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types.
 \end{itemize}
 
-\edit{Our method is not without limitations. It still requires a laser and
-single-pixel LiDAR detector and is sensitive to ambient photons, which limit the
-maximum range.
-Being a variant of histogram matching, our method is
-not able to resolve ordinal depth errors (errors where an object is wrongly
-placed closer or farther relative to another object). In spite of these
-limitations, we find that our method performs remarkably well in practice.}
+\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single diffused measurement.
+The benefit of this approach is that we have access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data.
+However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup.
+In these conditions, the emulated measurements may differ from a single optically diffused measurement.
+Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt to do this.}
+
+%\edit{Our method is not without limitations.
+It still requires a laser and single-pixel LiDAR detector and is sensitive to ambient photons, which limit the maximum range.
+Being a variant of histogram matching, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object).
+In spite of these limitations, we find that our method performs remarkably well in practice.}

### 2020-02-28 paper/eccv2020/sections/hardware.tex
Moving figures around, adding edit red text.
pass over paper

@@
 % The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
+\begin{figure}[t]
+	\centering
+  \includegraphics[width=0.4\columnwidth]{prototype_single_col.pdf}
+  \caption{Prototype scanning setup. The pulsed light from the laser travels
+    through a beam splitter before being guided by the galvo to the scene.
+    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
+    camera is used to capture the image used to generate the monocular depth estimate
+    (the depth camera is not used).}
+  \label{fig:prototype}
+  % \vspace{-0.5em}
+\end{figure}
 
@@
     counts in the diffuse mode match closely with the sum of the raster-scanned
-    measurements.}
+    measurements. \edit{PLEASE EDIT THIS FIGURE TO MAKE BOTH PANELS THE SAME HEIGHT. MAYBE JUST COMBINE IT WITH THE PROTOTYPE INTO A SINGLE 2-PANEL FIGURE.}}
   \label{fig:scanned_diffuse}
@@
 \subsection{Experimental Results}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\columnwidth]{captured.pdf}
+	\caption{Experimental results. For each scene, we record a ground truth depth
+    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
+    image (lower left). A monocular depth CNN predicts an initial depth map (top
+    middle), which is corrected with the diffused SPAD histogram using the
+    proposed method (top right), as shown by the error maps and root mean
+    squared error (RMSE) for each example (lower center, right). The CNN is
+    confused when we show it a photograph of a poster (bottom scene); it
+    incorrectly predicts the depth of the scene depicted on the flat print. Our
+    method is able to correct this error.}
+	\label{fig:results_captured}
+\end{figure}
 
@@
 estimated depth map.
-
-\begin{figure}[t]
-	\centering
-  \includegraphics[width=0.8\columnwidth]{prototype_single_col.pdf}
-  \caption{Prototype scanning setup. The pulsed light from the laser travels
-    through a beam splitter before being guided by the galvo to the scene.
-    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
-    camera is used to capture the image used to generate the monocular depth estimate
-    (the depth camera is not used).}
-  \label{fig:prototype}
-  % \vspace{-0.5em}
-\end{figure}
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\columnwidth]{captured.pdf}
-	\caption{Experimental results. For each scene, we record a ground truth depth
-    map that is raster-scanned with the SPAD (upper left subimages), and an RGB
-    image (lower left). A monocular depth CNN predicts an initial depth map (top
-    middle), which is corrected with the diffused SPAD histogram using the
-    proposed method (top right), as shown by the error maps and root mean
-    squared error (RMSE) for each example (lower center, right). The CNN is
-    confused when we show it a photograph of a poster (bottom scene); it
-    incorrectly predicts the depth of the scene depicted on the flat print. Our
-    method is able to correct this error.}
-	\label{fig:results_captured}
-\end{figure}

### 2020-02-28 paper/eccv2020/sections/introduction.tex
pass over paper

@@
     The proposed method uses a \edit{single transient measurement aggregating the time-of-flight information of the entire scene (lower left)} to correct the output of the depth estimation and optimize the quality of the
-    estimated absolute depth (lower right).}
+    estimated absolute depth (lower right). \edit{PLEASE CHANGE FIGURE LAYOUT!}}
   \label{fig:teaser}
@@
 However, each of these techniques has aspects that may make their deployment
-challenging. For example, stereo or multiview techniques require multiple
+challenging \edit{in certain scenarios}. For example, stereo or multiview techniques require multiple
 cameras, active illumination techniques may have limited resolution or require
@@
 map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches
-to MDE employ neural network models that learn to predict depth by exploiting
-monocular image cues such as perspective, occlusion, shading, and relative
+to MDE employ neural networks that learn to predict depth by exploiting
+\edit{pictorial depth} cues such as perspective, occlusion, shading, and relative
 object size. While such models have significantly improved over recent years,
@@
 \edit{
-Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel.
+Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel (Fig.~\ref{fig:teaser}).
 These detectors form the backbone of modern LiDAR
 systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, single-photon sensor arrays} have
-not been used for 3D imaging on consumer electronics because the requirement for
+not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
 ultra-fast timing electronics makes it difficult to produce high-resolution
-arrays at low cost, and because the scanning requirement for single-pixel
+arrays at low cost and because the scanning requirement for single-pixel
 systems introduces a point of mechanical failure and complicates
@@
 to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
-entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the depth of
-the scene and we demonstrate that this can be used to achieve accurate absolute
-depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (\cf~Figure~\ref{fig:teaser}).
+entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the scene depth and we demonstrate that this can be used to achieve accurate absolute
+depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (Fig.~\ref{fig:teaser}).
 
@@
 \begin{itemize}
-	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a diffused time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
+	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
   \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
@@
 
-\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single diffused measurement.
-The benefit of this approach is that we have access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data.
+\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement.
+The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data.
 However, when operating SPADs in certain conditions, they may observe a nonlinear aggregation effect known as pileup.
-In these conditions, the emulated measurements may differ from a single optically diffused measurement.
-Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt to do this.}
+In these conditions, the aggregated measurements may differ from a single optically diffused measurement.
+Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.}
 

### 2020-02-28 paper/eccv2020/sections/method.tex
pass over paper

@@
-In this section, we describe the image formation of a diffused pulsed laser and single-photon avalanche diode (SPAD).
-We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the SPAD.
+In this section, we describe the image formation of a diffused pulsed laser and time-resolved detector.
+\edit{Although our model is derived for the specific case of imaging with a single-photon avalanche diode (SPAD), the resulting image formation model equally applies to other time-resolved detectors}.
+We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the \edit{transient}.
 
@@
   \caption{Overview of processing pipeline. The processing pipeline uses
-      the input SPAD measurements and an RGB image to produce an accurate depth
-      map. The SPAD measurements are preprocessed to adjust for ambient photon
+      the input \edit{transient measurement} and an RGB image to produce an accurate depth
+      map. The \edit{transient is} preprocessed to adjust for ambient photon
       detections, radiometric falloff factors, and to calibrate the bin widths.
@@
       and the scene reflectance is estimated. A reflectance-weighted
-      depth histogram is compared to the processed SPAD measurements to
-      calculate a histogram matching matrix which is used to output the corrected depth.
+      depth histogram is compared to the processed \edit{transient} to
+      calculate a histogram matching matrix which is used to output the corrected depth. \edit{PLEASE CHANGE FIGURE LAYOUT!}
   }
@@
 estimate after applying histogram matching.  Instead, we estimate the temporal
-support of transient bins containing signal photons (\ie the range of depths in the
+support of transient bins containing signal photons (\ie, the range of depths in the
 scene) and only subtract $\hat{b}$ from these bins (clipping negative bin values
@@
 by the distance-dependent scaling factor,
+%
 \begin{equation}
@@
 \end{equation}
+%
 Here, $z_n= \paren*{n + \frac12}\paren*{\frac{c\Delta t}{2}}$ is the distance
 corresponding to bin $n$, and this radiometric falloff model is consistent with
-measurements captured with our hardware prototype.
+measurements captured with our prototype.
 
@@
 parameterized by the number of bins $K$ and the range of distances $[\ell, u]$: 
+%
 \begin{equation}
@@
 \end{equation}
+%
 This rebinning procedure allows us to use a reduced number of bins in the histogram
@@
 \begin{algorithm}
- \caption{Find Pixel Movement} 
+ \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
  \label{alg:ehm}
@@
 at the corresponding depth, we add the estimated reflectance value of the pixel
-to the histogram bin. \edit{We also re-bin this histogram, again following Fu et al.\
-and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}
+to the histogram bin. \edit{We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}
 
@@
 multiple output bins~\cite{Morovic2002}.
-%
+
+\edit{Pseudo-code for this procedure is included in the supplement; we will make source code and data available.}
 

### 2020-02-28 paper/eccv2020/sections/related.tex
pass over paper

@@
 non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
-networks have been applied to this problem. For example, Eigen et
-al.~\cite{Eigen2014} use a multi-scale neural network to predict depth maps,
-Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a
-network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic
-depth discretization scheme with an ordinal regression loss function. Various
-experiments using different types of encoder networks (\eg ResNet,
+networks have been applied to this problem, \edit{for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
+using an unsupervised approach that trains a network using stereo pairs~\cite{Godard2017}, and using a logarithmic
+depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}}. Various
+experiments using different types of encoder networks (\eg, ResNet,
 DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some
@@
 Despite achieving remarkable success on estimating ordinal depth from a single
-image, none of these methods are able to resolve inherent scale ambiguity in a
+image, none of these methods is able to resolve inherent scale ambiguity in a
 principled manner. We introduce a new approach that leverages existing monocular
 depth estimation networks and disambiguates the output using depth
-histogram-like measurements obtained from a single, diffused SPAD. Other
+histogram--like measurements obtained from a single \edit{time-resolved detector}. Other
 approaches to disambiguating monocular depth estimation use optimized freeform
@@
 and specialized image reconstruction methods. \edit{In contrast, our approach adds
-minimal additional hardware to a single RGB camera, and leverages sensors currently
+minimal additional hardware to a single RGB camera, and may leverage sensors currently
 deployed in consumer electronics.}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Depth Imaging and Sensor Fusion with SPADs}
+\paragraph{Depth Imaging and Sensor Fusion with Time-resolved Detectors}
 %
-Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs)
-to record the time of flight of individual photons. SPAD detectors can be
-fabricated using standard CMOS processes, but the required picosecond-accurate
-time-stamping electronics are challenging to miniaturize and fabricate at low
-cost. For this reason, many single-photon 3D imaging approaches use a single
-SPAD combined with a raster scanning
+\edit{Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
+to record the time of flight of individual photons. These time-resolved detectors} can be
+fabricated using standard CMOS processes, but the required time-stamping electronics are challenging to miniaturize and fabricate at low
+cost. For this reason, many \edit{LiDAR systems}, especially those using SPADs, use a single \edit{or a few detectors}
+combined with a  scanning
 mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single,gupta2019photonflooded}.
@@
 resolution and scanners can also be expensive, difficult to calibrate, and prone
-to mechanical failure. To reduce the scanning complexity to one dimension, 1D
-SPAD arrays have been
-developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD
-arrays are also an active area of
+to mechanical failure. To reduce the scanning complexity to one dimension, \edit{1D
+detector arrays} have been
+developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of
 research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
-single-pixel SPADs remain the only viable option for low-cost consumer devices
+single-pixel \edit{time-resolved detectors} remain the only viable option for low-cost consumer devices
 today.
 
-The proposed method uses a single-pixel SPAD and pulsed light source that are
+The proposed method uses a single-pixel \edit{APD or SPAD} and pulsed light source that are
 diffused across the entire scene instead of aimed at a single point, as with
@@
 resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
-reliable absolute depth estimation by combining the SPAD measurement with the
+reliable absolute depth estimation by combining the \edit{transient} measurement with the
 output of a monocular depth estimator using a histogram matching technique.
@@
 
-In our procedure, the diffused SPAD measurements closely resemble a histogram of
+In our procedure, the \edit{transient measurements} closely resemble a histogram of
 the depth map where the histogram values are weighted by spatially varying scene

### 2020-02-28 paper/eccv2020/sections/simulation.tex
Moving figures around, adding edit red text.

@@
-\begin{table*}[!t]
-\begin{center}
-\input{sections/figures/sim_table.tex}
-\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
-performance for that metric, while underline indicates second best. The proposed
-scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
-even outperforms the median rescaling scheme and histogram matching with the
-exact depth map histogram, even though those methods have access to ground
-truth.}
-\vspace{-2em}
-\label{tab:comparison}
-\end{center}
-\end{table*}
-
-\begin{figure*}[!h]
-  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
-  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
-  \includegraphics[width=\textwidth]{comparison.pdf}
-  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
-  \caption{Simulated results from NYU v2 computed with the DenseDepth
-  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
-  but contain systematic error. Oracle access to the ground truth depth maps,
-  either through the median depth or the depth histogram, can remove this error
-  and correct the depth maps. The proposed method uses measurements from a
-  single diffused SPAD and does not rely on ground truth depth, but it achieves
-  a quality that closely matches the best-performing oracle.}
-	\label{fig:results_simulated}
-  \vspace{-1em}
-\end{figure*}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-To simulate a SPAD histogram, we take the provided depth map and 
+To simulate a \edit{transient}, we take the provided depth map and 
 calculate a weighted depth histogram by weighting the pixel contributions to
@@
 signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively. Finally,
-each bin is Poisson sampled to produce the final simulated SPAD transient.
+each bin is Poisson sampled to produce the final simulated transient.
 
@@
 \subsection{Simulated Results}
+\begin{table*}[!t]
+\begin{center}
+\input{sections/figures/sim_table.tex}
+\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
+performance for that metric, while underline indicates second best. The proposed
+scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
+even outperforms the median rescaling scheme and histogram matching with the
+exact depth map histogram, even though those methods have access to ground
+truth. \edit{DECREASE FONT SIZE!}}
+\vspace{-2em}
+\label{tab:comparison}
+\end{center}
+\end{table*}
 
@@
 
-Instead, our method uses the simulated measurements from a single diffused SPAD
-to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
+Instead, our method uses the simulated measurements from a single \edit{aggregated transient} to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
 signal-to-background ratios (SBRs). We see that the proposed method achieves
@@
 performance between depth estimation CNNs.
+
+\begin{figure*}[!h]
+  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
+  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
+  \includegraphics[width=\textwidth]{comparison.pdf}
+  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
+  \caption{Simulated results from NYU v2 computed with the DenseDepth
+  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
+  but contain systematic error. Oracle access to the ground truth depth maps,
+  either through the median depth or the depth histogram, can remove this error
+  and correct the depth maps. \edit{The proposed method uses a single transient measurement} and does not rely on ground truth depth, but it achieves
+  a quality that closely matches the best-performing oracle.}
+	\label{fig:results_simulated}
+  \vspace{-1em}
+\end{figure*}
 
@@
 proposed method is close to using the oracle histogram, despite relying on
-noisy SPAD measurements. Additional simulations using DenseDepth and other depth
+noisy \edit{transient} measurements. Additional simulations using DenseDepth and other depth
 estimation CNNs for a variety of scenes are shown in the supplement.

### 2020-02-29 paper/eccv2020/sections/hardware.tex
Updated teaser for eccv
First pass over figures, added supplement.

--- 2020-02-26 paper/eccv2020/sections/hardware.tex
@@
 % The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
+% \begin{figure}[t]
+% 	\centering
+%   \includegraphics[width=0.5\columnwidth]{prototype_single_col.pdf}
+%   \caption{Prototype scanning setup. The pulsed light from the laser travels
+%     through a beam splitter before being guided by the galvo to the scene.
+%     Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
+%     camera is used to capture the image used to generate the monocular depth estimate
+%     (the depth camera is not used).}
+%   \label{fig:prototype}
+%   % \vspace{-0.5em}
+% \end{figure}
 
-As shown in Figure~\ref{fig:prototype}, our prototype comprises a color camera
+As shown in Figure~\ref{fig:hardware}, our prototype comprises a color camera
 (Microsoft Kinect v2), a single-pixel SPAD (Micro Photon Devices 100~$\mu m$ PDM
@@
 	\centering
-  \includegraphics[width=0.8\columnwidth]{scanned_diffuse.pdf}
-  \caption{Scene and measurements for diffused and summed scanned mode. The observed
+  \includegraphics[width=\columnwidth]{hardware.pdf}
+  \caption{(a) Prototype scanning setup. The pulsed light from the laser travels
+    through a beam splitter before being guided by the galvo to the scene.
+    Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
+    camera is used to capture the image used to generate the monocular depth estimate
+    (the depth bccamera is not used). (b) Scene and (c) measurements for diffused and summed scanned mode. The observed
     counts in the diffuse mode match closely with the sum of the raster-scanned
     measurements.}
-  \label{fig:scanned_diffuse}
+  \label{fig:hardware}
   % \vspace{-0.5em}

### 2020-02-29 paper/eccv2020/sections/introduction.tex
Updated teaser for eccv
First pass over figures, added supplement.

@@
   \centering
-  \includegraphics[width=0.3\columnwidth]{teaser.pdf}
-  \caption{Monocular depth estimation predicts a depth map (upper right) from a
-    single RGB image (upper left). The ill-posedness of the problem prevents
-    reliable absolute depth estimation, resulting in large errors (inset image).
-    The proposed method uses a \edit{single transient measurement aggregating the time-of-flight information of the entire scene (lower left)} to correct the output of the depth estimation and optimize the quality of the
-    estimated absolute depth (lower right). \edit{PLEASE CHANGE FIGURE LAYOUT!}}
+  \includegraphics[width=\columnwidth]{teaser_eccv.pdf}
+  \caption{Monocular depth estimation predicts a depth map (second from right) from a
+    single RGB image (second from left). The ill-posedness of the problem prevents
+    reliable absolute depth estimation, resulting in large errors (inset images).
+    The proposed method uses a \edit{single transient measurement aggregating
+      the time-of-flight information of the entire scene (leftmost)} to correct
+    the output of the depth estimation and optimize the quality of the
+    estimated absolute depth (rightmost).}
   \label{fig:teaser}
@@
 \edit{
-Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs), measure the full waveform of time-resolved incident radiance at each pixel (Fig.~\ref{fig:teaser}).
-These detectors form the backbone of modern LiDAR
-systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, single-photon sensor arrays} have
+Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon
+avalanche diodes (SPADs), measure the full waveform of time-resolved incident
+radiance at each pixel (Fig.~\ref{fig:teaser}). These detectors form the
+backbone of modern LiDAR
+systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However,
+single-photon sensor arrays} have
 not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
@@
 to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
-entire scene with the detector}. The resulting \edit{transient} measurement resembles a histogram of the scene depth and we demonstrate that this can be used to achieve accurate absolute
-depth when combined with the estimate of \edit{any monocular depth estimator in a post-processing step} (Fig.~\ref{fig:teaser}).
+entire scene with the detector}. The resulting \edit{transient} measurement
+resembles a histogram of the scene depth and we demonstrate that this can be
+used to achieve accurate absolute depth when combined with the estimate of
+\edit{any monocular depth estimator in a post-processing step}
+(Fig.~\ref{fig:teaser}).
 

### 2020-02-29 paper/eccv2020/sections/method.tex
Updated teaser for eccv
First pass over figures, added supplement.

@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{method.pdf}
+  \includegraphics[width=\columnwidth]{method_eccv.pdf}
   \caption{Overview of processing pipeline. The processing pipeline uses
@@
       depth histogram is compared to the processed \edit{transient} to
-      calculate a histogram matching matrix which is used to output the corrected depth. \edit{PLEASE CHANGE FIGURE LAYOUT!}
+      calculate a histogram matching matrix which is used to output the corrected depth.
   }
@@
 % \end{algorithm}
-{ \footnotesize
-\begin{algorithm}
- \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
- \label{alg:ehm}
- \begin{algorithmic}
-	\footnotesize
-  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
-    \State Initialize $T$ as an $M \times N$ array of zeros.
-    \For{$m$ in $1,\ldots,M$}
-      \For{$n$ in $1,\ldots,N$}
-        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
-        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
-        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
-      \EndFor
-    \EndFor
-    \State \textbf{return} $T$
-  \EndProcedure
- \end{algorithmic}
-\end{algorithm}
-}
 
@@
 matrix $T$ such that $T[m, n]$ is the fraction of $h_\text{source}[m]$ that should be
-moved to $h_\text{target}[n]$. The details of this procedure are outlined in
-Algorithm~\ref{alg:ehm}. Intuitively, the procedure starts from the first bin of the
+moved to $h_\text{target}[n]$. \edit{We refer the reader to the supplement for
+  pseudocode.} Intuitively, the procedure starts from the first bin of the
 source histogram and distributes its contents to the first bins of the target

### 2020-02-29 paper/eccv2020/sections/simulation.tex
First pass over figures, added supplement.

@@
   \begin{center}
+   {\fontsize{7pt}{8pt}\selectfont 
       \input{sections/figures/sim_table.tex}
-\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
+   } 
+\caption{
+  Quantitative evaluation using NYU Depth v2. Bold indicates best
 performance for that metric, while underline indicates second best. The proposed
@@
 exact depth map histogram, even though those methods have access to ground
-truth. \edit{DECREASE FONT SIZE!}}
-\vspace{-2em}
+truth.}
 \label{tab:comparison}
@@
 
-\begin{figure*}[!h]
+\begin{figure*}[t]
   % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}

### 2020-02-29 paper/eccv2020/supplement.tex
First pass over figures, added supplement.

--- 2019-11-09 paper/cvpr2020/supplement.tex
@@
-\documentclass[10pt,letterpaper]{article}
+% updated April 2002 by Antje Endemann
+% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016; AAS, 2020
 
-\usepackage{cvpr}
-\usepackage{times}
-\usepackage{epsfig}
+\documentclass[runningheads]{llncs}
 \usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{amssymb}
+\usepackage{comment}
+\usepackage{amsmath,amssymb} % define this before the line numbering.
+\usepackage{color}
 
-% Include other packages here, before hyperref.
+% INITIAL SUBMISSION - The following two lines are NOT commented
+% CAMERA READY - Comment OUT the following two lines
+\usepackage{ruler}
+\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+
 \usepackage{booktabs}
 \usepackage{caption}
-\usepackage{subcaption}
 \usepackage{array}
@@
 \input{mark_defs.tex}
+% \DeclareRobustCommand\onedot{\futurelet\@let@token\@onedot}
+% \def\@onedot{\ifx\@let@token.\else.\null\fi\xspace}
 
-% If you comment hyperref and then uncomment it, you should delete
-% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
-% run, let it finish, and you should be clear).
-\usepackage[breaklinks=true,bookmarks=false]{hyperref}
+\def\eg{\emph{e.g.}} \def\Eg{\emph{E.g.}}
+\def\ie{\emph{i.e.}} \def\Ie{\emph{I.e.}}
+\def\cf{\emph{c.f.}} \def\Cf{\emph{C.f.}}
+\def\etc{\emph{etc}} \def\vs{\emph{vs.}}
+\def\wrt{w.r.t.} \def\dof{d.o.f.}
+\def\etal{\emph{et al.}}
 
-%\cvprfinalcopy % *** Uncomment this line for the final submission
+\newcommand{\edit}[1]{\textcolor{red}{#1}}
 
-\graphicspath{{"figures/"}{"G:/Shared drives/Stanford Computational
+\graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
     Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
@@
   {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
+% Pages are numbered in submission mode, and unnumbered in camera-ready
 
-\def\cvprPaperID{2224} % *** Enter the CVPR Paper ID here
-\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
+\begin{document}
+% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
+% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
+% \linenumbers
+\pagestyle{headings}
+\mainmatter
+\def\ECCVSubNumber{3668}  % Insert your submission number here
 
-% Pages are numbered in submission mode, and unnumbered in camera-ready
-%\ifcvprfinal\pagestyle{empty}\fi
-\setcounter{page}{4321}
-\begin{document}
+%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
+\title{\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single
+    Transient: Supplemental Information}} % Replace with your title
 
-%%%%%%%%% TITLE
-\title{Supplementary Information: Optimizing Monocular Depth Estimation with Global Depth Histogram
-  Matching using a Single SPAD Transient}
+% INITIAL SUBMISSION 
+%\begin{comment}
+\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
+\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
+\author{Anonymous ECCV submission}
+\institute{Paper ID \ECCVSubNumber}
+%\end{comment}
+%******************
 
+% CAMERA READY SUBMISSION
+\begin{comment}
+\titlerunning{Abbreviated paper title}
+% If the paper title is too long for the running head, you can set
+% an abbreviated paper title here
+%
+\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
+Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
+Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+%
+\authorrunning{F. Author et al.}
+% First names are abbreviated in the running head.
+% If there are more than two authors, 'et al.' is used.
+%
+\institute{Princeton University, Princeton NJ 08544, USA \and
+Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
+\email{lncs@springer.com}\\
+\url{http://www.springer.com/gp/computer-science/lncs} \and
+ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
+\email{\{abc,lncs\}@uni-heidelberg.de}}
+\end{comment}
+%******************
 \maketitle
+
 \section{Ablation study on number of SID bins}
@@
   \centering
-  \begin{tabular}{c|c|cc}
+  \begin{tabular}{c|c|c|c}
     \toprule
-    Intensity-weighted histogram & Intensity-aware pixel movement & Avg. RMSE & Approx. Time/image (sec) \\
+    Intensity-weighted & Intensity-aware & Avg. & Time \\ histogram & pixel movement & RMSE & per image (sec) \\
     \midrule
@@
 
-\section{A note on pixel shifting and dither artifacts}
-We give pseudocode for our pixel shifting algorithm here. The pixels of the
-image $I$ take depth bin values in $\set{0,\ldots,K-1}$. 
+\section{Pseudocode, pixel shifting, and dither artifacts}
+We give pseudocode for our algorithm here. In the first part of our algorithm we
+compute the pixel shifting matrix mapping the histogram $h_s$ (computed from the
+initial depth map and reflectance estimate)to $h_t$ (computed from the captured
+transient).
+{ \footnotesize
+\begin{algorithm}
+ \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
+ \label{alg:ehm}
+ \begin{algorithmic}
+	\footnotesize
+  \Procedure{FindPixelMovement}{$h_s$ of length $M$, $h_t$ of length $N$} 
+    \State Initialize $T$ as an $M \times N$ array of zeros.
+    \For{$m$ in $1,\ldots,M$}
+      \For{$n$ in $1,\ldots,N$}
+        \State $p_s \gets \sum_{i=1}^{n-1} T[m, i]$
+        \State $p_t \gets \sum_{i=1}^{m-1} T[i, n]$
+        \State $T[m, n] \gets \min(h_s[m] - p_s, h_t[n] - p_t)$
+      \EndFor
+    \EndFor
+    \State \textbf{return} $T$
+  \EndProcedure
+ \end{algorithmic}
+\end{algorithm}
+}
+
+Given this pixel movement matrix $T$, we apply the appropriate movements to the
+initial depth map $I$. The pixels of the image $I$ take depth bin values in $\set{0,\ldots,K-1}$. 
 { \footnotesize
@@
     \begin{algorithmic}
-      \footnotesize \Procedure{MovePixels}{input image $I$ size $M \times N$,
-        pixel movement matrix $T$ of size $K \times K$} \For{$k$ in $0,\ldots,
-        K-1$} \State $p[k,:] \gets T[k,:]/\sum_{i=1}^K T[k,i]$ \EndFor \For{$m$
-        in $1,\ldots,M$} \For{$n$ in $1,\ldots,N$} \State Sample $k'$ according
-      to $p[I[m,n],:]$. \State $I[m,n] \gets k'$. \EndFor \EndFor \State
-      \textbf{return} $I$ \EndProcedure
+      \footnotesize
+      \Procedure{MovePixels}{input image $I$ size $M \times N$,
+        pixel movement matrix $T$ of size $K \times K$}
+      \For{$k$ in $0,\ldots, K-1$}
+        \State $p[k,:] \gets T[k,:]/\sum_{i=1}^K T[k,i]$
+      \EndFor
+      \For{$m$ in $1,\ldots,M$}
+        \For{$n$ in $1,\ldots,N$}
+          \State Sample $k'$ according to $p[I[m,n],:]$.
+          \State $I[m,n] \gets k'$.
+        \EndFor
+      \EndFor
+      \State \textbf{return} $I$
+      \EndProcedure
     \end{algorithmic}
@@
 the root-mean-square error (RMSE) for each example.
-\input{sections/supplement/simulation_comparison.tex}
+% \input{sections/supplement/simulation_comparison.tex}
 
@@
 calculation, and appear as an absolute difference of 0 in the difference maps.
-\input{sections/supplement/hardware_comparison.tex}
+% \input{sections/supplement/hardware_comparison.tex}
+
+\clearpage
 
 {\small
-\bibliographystyle{ieeetr}
+\bibliographystyle{splncs04}
 \bibliography{references}
 }
-
 \end{document}

### 2020-03-02 paper/eccv2020/sections/discussion.tex
pass over intro
Figure edits, first pass over discussion.

--- 2019-11-09 paper/cvpr2020/sections/discussion.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\paragraph{Limitations}
+%\paragraph{Limitations}
+
 The performance of our method is highly dependent on the accuracy of the initial
@@
 depth estimate can be corrected to produce accurate absolute depth. However, if
-the ordering of the initial depths is not correct, these errors will not be corrected by our histogram matching procedure and may propagate to the final output depth map.
+the ordering of the initial depths is not correct, these errors will not be
+corrected by our histogram matching procedure and may propagate to the final
+output depth map.
 
-Additionally, since our method relies on a diffused pulsed laser, the laser
+\edit{Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
+Because the SPAD must be quenched before it can
+detect another photon, earlier photons
+from closer objects may systematically prevent detection of photons from further
+objects, causing strong distortion of the transient. Fortunately, at the expense of
+longer acquisition times, pileup can be mitigated
+to a large extent by operating in the low-flux regime
+where the number of photon events per second is controlled to be at most 5\% the
+number of laser pulses per second~\cite{Single photon paper}. Finally, even in
+the high-flux regime, it is sometimes possible to
+correct pileup computationally~\cite{felix pileup correction}.}
+
+\edit{While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
+avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
+this low-flux regime, which would yield identical measurement models and identical
+results. Figure~\ref{fig:hardware}(b)-(c) empirically shows that collecting and summing scanned
+measurements is nearly identical to capturing diffused measurements. ?!We show
+empirical comparisons between the two modes on a more complex scene in the supplement?!}
+
+\edit{Even if diffused and scanned/summed measurements are equivalent
+  computationally, they are not equivalent energetically. In the diffuse
+  setting, }the laser
 power is spread out over the entire scene. Accordingly, for distant scene points very
 little light will return to the SPAD and it may be difficult to accurately
-capture distant scene geometry in the histogram. Thus our method is best suited to short to medium-range scenes.
+capture distant scene geometry in the histogram. Thus our method is best suited
+to short to medium-range scenes. \edit{Nevertheless, assuming an indoor scene with
+fluorescent bulbs and an ambient spectral irradiance of $I_A =
+2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
+to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
+diffuse scene at $r = 2$ m
+and a field of view of $\theta = 40^\circ$ can be calculated as}
+%
+\begin{equation}
+  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
+\end{equation} 
+\edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect. Note
+  that this calculation involves only on the signal-to-background photon ratio,
+  which is independent of the actual number of counts recorded per exposure. In
+  other words, pileup and laser energy concerns may 
+  be addressed entirely independently. As for acquisition time, at a 10 MHz
+  pulse rate with
+  a 5\% photon detection rate, it takes just two seconds to acquire a million
+  photon events. This number is dependent on scene albedo, but all time-of-flight imaging
+systems share this dependency.}
 

### 2020-03-03 paper/eccv2020/sections/discussion.tex
Restructured discussion

--- 2020-02-27 paper/eccv2020/sections/discussion.tex
@@
 
-Additionally, since our method relies on a diffused pulsed laser, the laser
+\edit{In the diffuse setting, the laser
 power is spread out over the entire scene. Accordingly, for distant scene points very
@@
 capture distant scene geometry in the histogram. Thus our method is best suited
-to short to medium-range scenes. \edit{For example, assume an indoor scene with
+to short to medium-range scenes.} \edit{Nevertheless, assuming an indoor scene with
 fluorescent bulbs and an ambient spectral irradiance of $I_A =
 2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
-to the laser). The laser power required to achieve a minimum SBR of 5 for a
+to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
 diffuse scene at $r = 2$ m
 and a field of view of $\theta = 40^\circ$ can be calculated as}
+%
 \begin{equation}
@@
 \edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect.}
+
+\edit{Under these scene parameters, we can compute the total incident 
+  flux on the SPAD per second (derived in~\cite{mcmanamon2012ladar}) as}
+  \begin{equation}
+    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
+  \end{equation}
+  \edit{where $P_T$ is the illumination power in the visible region, $\rho$ is its
+  albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
+  the object, and $\eta$ is the quantum efficiency of the detector. For nominal
+  values of these quantities, and a laser pulse repitition rate of 10 MHz, we find that the number of photon detections is well
+  above the threshold required to assume the low-flux condition (roughly 1-5\%
+  of the number of illuminations per second~\cite{oconnortcspc}).
+  } \edit{Given this high incident photon count, we would envision using an optical
+    element such as an aperture or neutral density filter to return to the
+    low-flux regime, or use a pile-up correction technique~\cite{Heide:2018}.}
+
+  \edit{Lastly, Figure~\ref{fig:hardware}(b)-(c) empirically shows that in the
+  low-flux regime, collecting and summing scanned
+measurements is nearly identical to capturing diffused measurements. ?!We show
+empirical comparisons between the two modes on a more complex scene in the supplement?!}
+
+  %\edit{Note
+  % that this calculation involves only on the signal-to-background photon ratio,
+  % which is independent of the actual number of counts recorded per exposure. In
+  % other words, pileup and laser energy concerns may 
+  % be addressed entirely independently. As for acquisition time, at a 10 MHz
+  % pulse rate with
+  % a 5\% photon detection rate, it takes just two seconds to acquire a million
+  % photon events.}
+
+% \edit{Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
+% Because the SPAD must be quenched before it can
+% detect another photon, earlier photons
+% from closer objects may systematically prevent detection of photons from further
+% objects, causing strong distortion of the transient. Fortunately, at the expense of
+% longer acquisition times, pileup can be mitigated
+% to a large extent by operating in the low-flux regime
+% where the number of photon events per second is controlled to be at most 5\% the
+% number of laser pulses per second~\cite{oconnortcspc}. Finally, even in
+% the high-flux regime, it is sometimes possible to correct pileup computationally~\cite{Heide:2018}.}
+
+% \edit{While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
+% avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
+% this low-flux regime, which would yield identical measurement models and identical
+% results. Figure~\ref{fig:hardware}(b)-(c) empirically shows that collecting and summing scanned
+% measurements is nearly identical to capturing diffused measurements. ?!We show
+% empirical comparisons between the two modes on a more complex scene in the supplement?!}
+
+% \edit{Even if diffused and scanned/summed measurements are equivalent
+%   computationally, they are not equivalent energetically.  This number is dependent on scene albedo, but all time-of-flight imaging
+% systems share this dependency.}
 

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Added discussion about the the two spad histograms

@@
 matching algorithm, which only uses the integrated single histogram, by
-comparing it with the captured depth. To empirically assess the equivalence of
-diffused SPAD measurements and summed scanned measurements, we captured the
-following scene under both raster-scanned and diffuse mode conditions:
+comparing it with the captured depth --- \edit{such validation would not be possible if we were to capture measurements with an actual diffused SPAD.}
+
+\edit{To verify that our simulated diffused SPAD measurements are equivalent to measurements produced by an actual diffused SPAD, we setup a system consisting of a diffused and scanned SPAD side-by-side.
+Details about this system can be found in the supplement.
+We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs.
+The aggregated measurements from the scanned SPAD are shown alongside the diffuse SPAD's measurements in Figure ~\ref{fig:hardware}(c).
+These results demonstrate the two systems produce near equivalent measurements; the slight differences in their two histograms can be attributed to a baseline difference of about 10cm.
+That is, they see the scene from slightly different perspectives.
+}
 

### 2020-03-05 paper/eccv2020/main.tex
Restructured discussion

@@
 %\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
-\title{\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient}} % Replace with your title
+\title{Disambiguating Monocular Depth Estimation with a Single Transient} % Replace with your title
 
@@
   images, these algorithms fail at correctly predicting true metric
-  depth.
-In this work, we demonstrate how a depth histogram of the scene, which can be readily captured using a \textcolor{red}{single-pixel time-resolved detector}, can be fused with the output of existing monocular depth estimation algorithms to resolve the depth ambiguity problem.
+  depth. In this work, we demonstrate how a depth histogram of the scene, which
+  can be readily captured using a single-pixel time-resolved
+    detector, can be fused with the output of existing monocular depth
+  estimation algorithms to resolve the depth ambiguity problem.
   We validate this novel sensor fusion technique experimentally and in extensive

### 2020-03-05 paper/eccv2020/sections/discussion.tex
pass over discussion

@@
 capture distant scene geometry in the histogram. Thus our method is best suited
-to short to medium-range scenes.} \edit{Nevertheless, assuming an indoor scene with
+to short to medium-range scenes with a reasonable power budget for the diffused
+illumination.} \edit{For example, assuming an indoor scene with
 fluorescent bulbs and an ambient spectral irradiance of $I_A =
@@
 \end{equation} 
-\edit{giving $P_{\text{min}}=21$ mW, less than the 60 mW of the Kinect.}
+\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
+less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}
 
@@
   albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
-  the object, and $\eta$ is the quantum efficiency of the detector. For nominal
-  values of these quantities, and a laser pulse repitition rate of 10 MHz, we find that the number of photon detections is well
-  above the threshold required to assume the low-flux condition (roughly 1-5\%
-  of the number of illuminations per second~\cite{oconnortcspc}).
-  } \edit{Given this high incident photon count, we would envision using an optical
-    element such as an aperture or neutral density filter to return to the
-    low-flux regime, or use a pile-up correction technique~\cite{Heide:2018}.}
-
-  \edit{Lastly, Figure~\ref{fig:hardware}(b)-(c) empirically shows that in the
-  low-flux regime, collecting and summing scanned
-measurements is nearly identical to capturing diffused measurements. ?!We show
-empirical comparisons between the two modes on a more complex scene in the supplement?!}
+  the object, and $\eta$ is the quantum efficiency of the detector. For a range of 
+  values similar to those of our experiments (detailed in the supplement), we find that
+  the ratio of photon detections to illumination pulses is roughly 4\%, or well within 
+  low-flux regime where pileup is negligible~\cite{oconnortcspc}.
+  We also empirically validate that our method works with a diffused setup and an output power of 
+  approximately 25 mW without significant pileup effects as detailed in the supplement.
+  } \edit{However, even for operation in the high-flux regime, pileup can be mitigated  
+    by reducing the amount of incident light, for example by reducing the aperture size or 
+    using neutral density filters, or by using a pile-up correction technique~\cite{Heide:2018}.}
 

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Added discussion about the the two spad histograms
pass over discussion

@@
 
-\edit{To verify that our simulated diffused SPAD measurements are equivalent to measurements produced by an actual diffused SPAD, we setup a system consisting of a diffused and scanned SPAD side-by-side.
+\edit{To verify that our simulated diffused SPAD measurements match measurements produced by an actual diffused SPAD, we set up a system consisting of a diffused and scanned SPAD side-by-side.
 Details about this system can be found in the supplement.
 We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs.
-The aggregated measurements from the scanned SPAD are shown alongside the diffuse SPAD's measurements in Figure ~\ref{fig:hardware}(c).
-These results demonstrate the two systems produce near equivalent measurements; the slight differences in their two histograms can be attributed to a baseline difference of about 10cm.
-That is, they see the scene from slightly different perspectives.
+The aggregated measurements from the scanned SPAD are shown alongside the diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c).
+These results demonstrate that the two systems produce near equivalent measurements.
+Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions.
+That is, they observe scene from slightly different perspectives.
 }

### 2020-03-05 paper/eccv2020/sections/discussion.tex
merging.

--- 2020-03-03 paper/eccv2020/sections/discussion.tex
@@
 However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements.
-In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
+In this work we dramatically improve the performance of several monocular depth
+estimation algorithms by fusing their estimates with transient measurements. 
 Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.

### 2020-03-05 pileup.jl

@@ -1,0 +1,7 @@
+R = 2   # m
+θ = 40  # degrees
+
+I_amb = 2e-3    # mW/m^2
+P_L =
+
+P_B = I_amb*(2*R*tand(θ/2))^2

### 2020-03-05 paper/eccv2020/supplement.tex

@@
 
+\section{Comparison of diffused vs. scanned imaging}
+In our experiments, we capture measurements by scanning the scene with a
+single-pixel SPAD detector whose optical path is aligned with a laser. This
+arrangement allows us to capture a reference ``ground truth'' depth map for
+quantitative validation of our method. To emulate measurements captured using a
+system where the laser and detector are diffused over the scene, we digitally
+sum the measurements to obtain a single transient.
+
+In order to verify that digital summation of scanned measurements yields results
+that are similar to those captured by a diffused laser and detector, we capture
+an example scene using a modified hardware prototype in both scanned and
+diffused modes. The hardware prototype (shown in Fig.~\ref{fig:hardware})
+consists of a more powerful laser (Katana 05HP, 532 nm) which we operate at
+approximately 25 mW output power with two single-pixel SPAD detectors. One SPAD
+is aligned with the optical path of the laser, and the other SPAD is operated
+without a lens to integrate light from the entire scene. Both SPADs are fitted
+with a 10 nm bandpass filter centered at 532 nm, which reduces the amount of
+integrated ambient light. We attach a holographic diffuser (Thorlabs ED1-S50) to
+the laser output in order to diffuse light onto the scene or alternatively
+remove the diffuser and use a pair of scanning mirrors to scan the scene.
+
+The modified hardware setup is used to capture an example scene in both scanned and
+diffused modes, and the resulting transients are used to refine an initial depth
+estimate from the Kinect RGB image. We illustrate the results of this procedure
+in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
+measurements are similar in reconstruction quality and also show similar
+quantitative improvement in terms or error over the initial depth estimate. The
+normalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
+note that the counts show similar trends. The number of recorded photons in
+these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
+rate of detected photons is far less ($<$5\%) than the number of emitted laser
+pulses, and so we conclude that the measurements are captured in the low-flux
+regime where pileup effects are negligible. We attribute most of the differences
+between the scanned and diffused transients to the baseline between the
+positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).
+
+\begin{figure}[H]
+  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
+  \caption{Modified hardware setup. The setup is used to compare scanned and
+  diffused measurements and employs two SPAD detectors and two laser
+  configurations. In the first configuration, the scene is illuminated by
+  sending the laser light through a holographic diffuser and a lensless SPAD 
+  integrates light from the entire scene. In the second, the SPAD is aligned
+  with the optical path of the laser and the scene is scanned using a pair of
+  scanning mirrors. The baseline between the two SPADs (right) results in some
+  observed differences in the recorded transients.}
+  \label{fig:dither}
+\end{figure}
+
+\begin{table}[ht!]
+    \renewcommand{\arraystretch}{1.3}
+    \setlength{\tabcolsep}{10pt}
+     \centering
+     \begin{tabular}{lccc} \toprule
+         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
+         \textbf{Scanned} & XXX & $6\times10^7$ & XXX \\
+         \textbf{Diffused} & XXX & $6\times10^7$ & XXX \\
+        \bottomrule
+    \end{tabular}
+    \vspace{0.4em}
+    \caption{\textbf{Recorded photons for diffused vs.
+scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
+    \label{tab:photon_counts}
+\end{table}
+
 \section{Additional results on NYU Depth v2}
@@
 the root-mean-square error (RMSE) for each example.
-% \input{sections/supplement/simulation_comparison.tex}
+\input{sections/supplement/simulation_comparison.tex}
 
@@
 calculation, and appear as an absolute difference of 0 in the difference maps.
-% \input{sections/supplement/hardware_comparison.tex}
+ \input{sections/supplement/hardware_comparison.tex}
 

### 2020-03-05 paper/eccv2020/sections/hardware.tex
merging
Updated figures and discussion.

@@
 % \end{figure}
+
+\begin{figure}[t]
+	\centering
+  \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
+  \caption{Diffused SPAD results captured at $\sim$25mW laser power indoors.
+    The resulting corrected depth maps from both scanning and summing transient measurements and diffusing
+    the laser illumination are very similar qualitatively and quantitatively.}
+  \label{fig:captured_diffuse_small}
+  % \vspace{-0.5em}
+\end{figure}
 
@@
 
-\edit{To verify that our simulated diffused SPAD measurements match measurements produced by an actual diffused SPAD, we set up a system consisting of a diffused and scanned SPAD side-by-side.
-Details about this system can be found in the supplement.
-We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs.
-The aggregated measurements from the scanned SPAD are shown alongside the diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c).
-These results demonstrate that the two systems produce near equivalent measurements.
-Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions.
-That is, they observe scene from slightly different perspectives.
-}
+\edit{To verify that our simulated diffused SPAD measurements match measurements
+  produced by an actual diffused SPAD, we set up a system consisting of a
+  diffused and scanned SPAD side-by-side. Details about this system can be found
+  in the supplement. We then captured measurements of the simple scene shown in
+  Figure~\ref{fig:hardware}(b) with both SPADs. The aggregated measurements from
+  the scanned SPAD are shown alongside the diffused SPAD's measurements in
+  Figure ~\ref{fig:hardware}(c). These results demonstrate that the two systems
+  produce near equivalent measurements. Slight differences in their two
+  histograms can be attributed to a baseline difference of about 10cm between
+  the SPAD positions. That is, they observe scene from slightly different
+  perspectives.NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?}
+\edit{We show proof-of-concept results captured by this system in
+  Figure~\ref{fig:captured_diffuse_small}. For}
 

### 2020-03-05 paper/eccv2020/supplement.tex
Updated figures and discussion.

@@
 \begin{algorithm}
- \caption{Find Pixel Movement \edit{MOVE TO SUPPLEMENT!}} 
+ \caption{Find Pixel Movement} 
  \label{alg:ehm}
@@
 
+\section{Nominal values for SBR calculation}
+Here we give the values used in the equation for received power, repeated here
+for convenience:
+  \begin{equation}
+    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
+  \end{equation}
+The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
+\begin{figure}[H]
+  \centering
+  \begin{tabular}{c|c|c}
+    \toprule
+    Symbol & Description & Nominal Value \\
+    \midrule
+    $\rho$  & Albedo of lambertian surface & $0.3$ \\
+    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
+    $R$ & Distance to surface (m) & $3$ \\
+    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
+    $\eta$ & Quantum efficiency of detector & $0.3$ \\
+    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
+    \bottomrule
+  \end{tabular}
+  \caption{}
+  \label{fig:sbr_calculation}
+\end{figure}
+Once $P_R$ is determined, we compute the number of photons using the laser
+wavelength $\lambda = 532$ nm as
+\begin{equation}
+  N = \frac{P_R\lambda}{hc}
+\end{equation}
+where $h \approx 6.626 \tiems 10^{-34}$ is Planck's constant and $c \approx 3
+\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
+MHz, we get the number of photons per pulse as $0.043$, which puts us in the
+low-flux regime.
+
 \section{Comparison of diffused vs. scanned imaging}
@@
 quantitative improvement in terms or error over the initial depth estimate. The
-normalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
+unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
 note that the counts show similar trends. The number of recorded photons in
@@
 positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).
+\begin{figure}[H]
+  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
+  \caption{Comparing Scan + Sum and Diffused SPAD. The transients shown are
+    equal-time (and thus equal energy), and display qualitative similarity in
+    the absence of pileup.}
+  \label{fig:comparison}
+\end{figure}
 
@@
          \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
-         \textbf{Scanned} & XXX & $6\times10^7$ & XXX \\
-         \textbf{Diffused} & XXX & $6\times10^7$ & XXX \\
+         \textbf{Scanned} & $1.4\times10^7$ & $6\times10^8$ & $2.3\%$ \\
+         \textbf{Diffused} & $2.4\times10^7$ & $6\times10^8$ & $4.0\%$ \\
         \bottomrule

### 2020-03-05 paper/eccv2020/sections/figures/sync_figures.sh

@@ -15,3 +15,5 @@ rsync captured.pdf "$gdrive"
 rsync dither.pdf "$gdrive"
 rsync hardware.pdf "$gdrive"
 rsync scanned_diffuse.pdf "$gdrive"
+rsync captured_diffuse.pdf "$gdrive"
+rsync capture_diffuse_small.pdf "$gdrive"

### 2020-03-05 paper/eccv2020/sections/discussion.tex
merging
final pass (hopefully)

--- 2020-03-05 paper/eccv2020/sections/discussion.tex
@@
 
-\edit{In the diffuse setting, the laser
+\edit{In the optically diffused configuration, the laser
 power is spread out over the entire scene. Accordingly, for distant scene points very
-little light will return to the SPAD and it may be difficult to accurately
+little light may return to the SPAD and it may be difficult to accurately
 capture distant scene geometry in the histogram. Thus our method is best suited
@@
 \edit{Under these scene parameters, we can compute the total incident 
-  flux on the SPAD per second (derived in~\cite{mcmanamon2012ladar}) as}
+  flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as}
   \begin{equation}
@@
   the ratio of photon detections to illumination pulses is roughly 4\%, or well within 
-  low-flux regime where pileup is negligible~\cite{oconnortcspc}.
+  low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
   We also empirically validate that our method works with a diffused setup and an output power of 
-  approximately 25 mW without significant pileup effects as detailed in the supplement.
+  approximately 25 mW without significant pileup effects as shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.
   } \edit{However, even for operation in the high-flux regime, pileup can be mitigated  
     by reducing the amount of incident light, for example by reducing the aperture size or 
-    using neutral density filters, or by using a pile-up correction technique~\cite{Heide:2018}.}
+    using neutral density filters, or by using a pileup correction~\cite{Heide:2018,Rapp:2019}.}
 
@@
 
-Other methods for extracting scene information from the SPAD histogram could be
+Other methods for extracting scene information from a depth histogram could be
 employed, including learning-based methods to combine the MDE estimates and
 histogram. One might even consider sensing regimes where the number of
-returning signal photons is low, such as when the SPAD and camera operate
+returning signal photons is low, such as when the time-resolved detector and camera operate
 at high framerates. While most MDE techniques are tailored to clean RGB images,  
-the SPAD histogram could be used to help MDE
+the depth histogram could be used to help MDE
 techniques generalize to noisy scenes under low-light conditions.
@@
 In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
-Such histograms are easy to capture using SPADs and are poised to become an important component of future low-cost imaging systems.
+Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.
 %Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.

### 2020-03-05 paper/eccv2020/sections/hardware.tex
final pass (hopefully)

--- 2020-03-05 paper/eccv2020/sections/hardware.tex
@@
 a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power
-of 0.5~mW.
+of 0.5~mW. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single transient is generated by summing all of these measurements for a specific
+scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by
+comparing it with the captured depth.
+To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD (see Figure~\ref{fig:hardware}(b,c)), we set up a slightly modified version of our prototype consisting of both scanned and optically diffused SPADs side-by-side.
+Additional details about the hardware prototype can be found in the supplement.
 
-The monocular depth estimate is calculated
-using the RGB image captured by the Kinect v2.
-The SPAD records temporal histograms with 4096 bins, each corresponding to a
-time window of 16~ps. The SPAD and laser are co-axially aligned using a beam
-splitter (Thorlabs PBS251). The full width at half maximum (FWHM) of the
-combined laser pulse width and SPAD jitter is about 70~ps, allowing the system
-to record depth maps with an accuracy of about 1~cm. A National Instruments data
-acquisition device (NI-DAQ USB-6343) provides synchronization signals for the
-galvos, SPAD, and laser. The ground truth depth map is raster-scanned at a
-resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD
-measurement is generated by summing all of these measurements for a specific
-scene. This allows us to validate the accuracy of the proposed histogram
-matching algorithm, which only uses the integrated single histogram, by
-comparing it with the captured depth --- \edit{such validation would not be possible if we were to capture measurements with an actual diffused SPAD.}
+% show this in supplement
+%The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.
+The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps.
+The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
+The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm.
+A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
+The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
+This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---\edit{such validation would not be possible if we were to capture measurements with an optically diffused SPAD.}
 
-\edit{To verify that our simulated diffused SPAD measurements are equivalent to measurements produced by an actual diffused SPAD, we setup a system consisting of a diffused and scanned SPAD side-by-side.
+% show this in supplement
+%\edit{To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side.
 Details about this system can be found in the supplement.
 We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs.
-The aggregated measurements from the scanned SPAD are shown alongside the diffuse SPAD's measurements in Figure ~\ref{fig:hardware}(c).
-These results demonstrate the two systems produce near equivalent measurements; the slight differences in their two histograms can be attributed to a baseline difference of about 10cm.
-That is, they see the scene from slightly different perspectives.
-}
+The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c).
+These results demonstrate that the two systems produce near equivalent measurements.
+Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions.
+That is, they observe scene from slightly different perspectives.}
+	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}
 
@@
 	\centering
-  \includegraphics[width=\columnwidth]{hardware.pdf}
+  \includegraphics[width=0.8\columnwidth]{hardware.pdf}
   \caption{(a) Prototype scanning setup. The pulsed light from the laser travels
@@
     image (lower left). A monocular depth CNN predicts an initial depth map (top
-    middle), which is corrected with the diffused SPAD histogram using the
+    middle), which is corrected with the digitally aggregated SPAD histogram using the
     proposed method (top right), as shown by the error maps and root mean
@@
 
+\begin{figure}[t]
+	\centering
+  \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
+  \caption{Captured result comparing the direct output of the MiDaS MDE and depth maps corrected by our method using the digitally aggregated transient of the scanned SPAD (center right) and a single transient captured by an optically diffused SPAD (right).
+Both of these approaches result in very similar results and both are significantly better than the output of the MDE, as shown by the error maps in the insets.
+The diffused SPAD results are captured at $\sim$25mW laser power indoors.
+			%The resulting corrected depth maps from both scanning and summing transient measurements and diffusing the laser illumination are very similar qualitatively and quantitatively.
+		}
+  \label{fig:captured_diffuse_small}
+  % \vspace{-0.5em}
+\end{figure}
+
 Using the hardware prototype, we captured a number of scenes as shown in
-Figure~\ref{fig:results_captured} and in the supplement. We crop the RGB image
+Figures~\ref{fig:results_captured},~\ref{fig:captured_diffuse_small}, and in the supplement. We crop the RGB image
 to have dimensions that are multiples of 32. For DORN only, we further
@@
 estimated depth map.
+
+Figure~\ref{fig:captured_diffuse_small} shows the RGB image of a scene along with the monocular depth estimate computed by MiDaS and depth maps corrected by our method using both the digitally aggregated transients from the scanned SPAD and the single optically diffused measurement, which are very similar.
+%Both scanned \& summed and diffused transients result in very similar depth maps and both are significantly better than the raw output of the MDE.
+The transient measurements for this scene are shown in the supplement.

### 2020-03-05 paper/eccv2020/sections/introduction.tex
final pass (hopefully)

@@
 Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon
-avalanche diodes (SPADs), measure the full waveform of time-resolved incident
+avalanche diodes (SPADs), can measure the full waveform of time-resolved incident
 radiance at each pixel (Fig.~\ref{fig:teaser}). These detectors form the
@@
 \begin{itemize}
-	\item We propose augmenting an RGB camera with a global depth histogram \edit{aggregated by a time-resolved detector} to address scale ambiguity error in monocular depth estimators.	
+	\item We propose augmenting an RGB camera with a global depth histogram aggregated by a time-resolved detector to address scale ambiguity in MDE.	
   \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
@@
 
-\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement.
+%\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement.
 The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data.

### 2020-03-05 paper/eccv2020/sections/method.tex
final pass (hopefully)

@@
 %
-This rebinning procedure allows us to use a reduced number of bins in the histogram
-matching procedure, reducing computation time while maintaining accuracy.
+This rebinning procedure allows us to use a reduced number of bins by the histogram
+matching, reducing computation time while maintaining accuracy.
 \edit{For the simulated results we use $K = 140$ bins with $(\ell,

### 2020-03-05 paper/eccv2020/sections/discussion.tex
reformat supplement, move hardware details to supplement, pass through main paper

@@
 fluorescent bulbs and an ambient spectral irradiance of $I_A =
-2~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
+1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
 to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
-diffuse scene at $r = 2$ m
+diffuse scene at $R = 3$ m
 and a field of view of $\theta = 40^\circ$ can be calculated as}
@@
 \begin{equation}
-  P_{\text{min}} = I_A \cdot 4 r^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
+  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
 \end{equation} 
@@
 
-Other methods for extracting scene information from a depth histogram could be
+Other methods for extracting scene information from a transient could be
 employed, including learning-based methods to combine the MDE estimates and
@@
 at high framerates. While most MDE techniques are tailored to clean RGB images,  
-the depth histogram could be used to help MDE
+the transient could be used to help MDE
 techniques generalize to noisy scenes under low-light conditions.
@@
 However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements.
-In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with depth histogram measurements. 
+In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with transient measurements. 
 Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.

### 2020-03-05 paper/eccv2020/sections/hardware.tex
reformat supplement, move hardware details to supplement, pass through main paper

@@
   \includegraphics[width=\columnwidth]{captured_diffuse_small.pdf}
-  \caption{Captured result comparing the direct output of the MiDaS MDE and depth maps corrected by our method using the digitally aggregated transient of the scanned SPAD (center right) and a single transient captured by an optically diffused SPAD (right).
+  \caption{Captured result comparing the direct output of the MiDaS MDE and depth maps corrected by our method using the digitally aggregated transient of the scanned SPAD (center right) and a single transient captured by an optically diffused SPAD and laser (right).
 Both of these approaches result in very similar results and both are significantly better than the output of the MDE, as shown by the error maps in the insets.

### 2020-03-05 paper/eccv2020/supplement.tex
final pass (hopefully)
reformat supplement, move hardware details to supplement, pass through main paper

@@
 
-\newcommand{\edit}[1]{\textcolor{red}{#1}}
+\newcommand{\edit}[1]{\textcolor{black}{#1}}
 
@@
 %\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
-\title{\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single
+\title{\textcolor{black}{Disambiguating Monocular Depth Estimation with a Single
     Transient: Supplemental Information}} % Replace with your title
@@
 \maketitle
+
+\section{Hardware prototype details}
+% show this in supplement
+The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.
+The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps.
+The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
+The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm.
+A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
+The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
+This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---such validation would not be possible if we were to capture measurements with an optically diffused SPAD.
+
+\section{Comparison of diffused vs. scanned imaging}
+In our experiments, we capture measurements by scanning the scene with a
+single-pixel SPAD detector whose optical path is aligned with a laser. This
+arrangement allows us to capture a reference ``ground truth'' depth map for
+quantitative validation of our method. To emulate measurements captured using a
+system where the laser and detector are diffused over the scene, we digitally
+sum the measurements to obtain a single transient.
+
+% show this in supplement
+%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side.
+Details about this system can be found in the supplement.
+We then captured measurements of the simple scene shown in Figure~\ref{fig:hardware}(b) with both SPADs.
+The aggregated measurements from the scanned SPAD are shown alongside the optically diffused SPAD's measurements in Figure ~\ref{fig:hardware}(c).
+These results demonstrate that the two systems produce near equivalent measurements.
+Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions.
+That is, they observe scene from slightly different perspectives.
+	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}
+
+In order to verify that digital summation of scanned measurements yields results
+that are similar to those captured by a diffused laser and detector, we capture
+an example scene using a modified hardware prototype in both scanned and
+diffused modes. This hardware prototype (shown in Fig.~\ref{fig:hardware}) is less mobile than 
+our unmodified prototype, but allows us to use a more powerful laser (Katana
+05HP, 532 nm) operated at approximately 25 mW average power. We also use two
+single-pixel SPAD detectors, where one SPAD is aligned with the optical path of
+the laser, and the other SPAD is operated without a lens to integrate light
+from the entire scene. Both SPADs are fitted with a 10 nm bandpass filter
+centered at 532 nm, which reduces the amount of integrated ambient light. We
+attach a holographic diffuser (Thorlabs ED1-S50) to the laser output in order
+to diffuse light onto the scene. Alternatively, we remove the diffuser and use a
+pair of scanning mirrors to scan the scene.
+
+The modified hardware setup is used to capture an example scene in both scanned and
+diffused modes, and the resulting transients are used to refine an initial depth
+estimate from the Kinect RGB image. We illustrate the results of this procedure
+in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
+measurements are similar in reconstruction quality and also show similar
+quantitative improvement in terms of error over the initial depth estimate. The
+unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
+note that the counts show similar trends. The number of recorded photons in
+these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
+rate of detected photons is far less ($<$5\%) than the number of emitted laser
+pulses, and so we conclude that the measurements are captured in the low-flux
+regime where pileup effects are negligible. We attribute most of the differences
+between the scanned and diffused transients to the approximately 16 cm vertical
+baseline between the positions of the diffused and scanned SPADs (see
+Fig.~\ref{fig:hardware}).
+\begin{figure}[H]
+  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
+  \caption{Modified hardware setup. The setup is used to compare scanned and
+  diffused measurements and employs two SPAD detectors and two laser
+  configurations. In the first configuration, the scene is illuminated by
+  sending the laser light through a holographic diffuser and a lensless SPAD 
+  integrates light from the entire scene. In the second, the SPAD is aligned
+  with the optical path of the laser and the scene is scanned using a pair of
+  scanning mirrors. The baseline between the two SPADs (right) results in some
+  observed differences in the recorded transients.}
+  \label{fig:hardware}
+\end{figure}
+
+\begin{figure}[H]
+  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
+  \caption{Comparison of scan + sum and diffused SPAD. The transients are captured
+      with the same total exposure time and are qualitatively similar without 
+      noticeable pileup effects.}
+  \label{fig:comparison}
+\end{figure}
+
+\begin{table}[ht!]
+    \renewcommand{\arraystretch}{1.3}
+    \setlength{\tabcolsep}{10pt}
+     \centering
+     \begin{tabular}{lccc} \toprule
+         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
+         \textbf{Scanned} & $1.4\times10^7$ & $6\times10^8$ & $2.3\%$ \\
+         \textbf{Diffused} & $2.4\times10^7$ & $6\times10^8$ & $4.0\%$ \\
+        \bottomrule
+    \end{tabular}
+    \vspace{0.4em}
+    \caption{\textbf{Recorded photons for diffused vs.
+scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
+    \label{tab:photon_counts}
+\end{table}
+
+\section{Nominal values for SBR calculation}
+Here we give the values used in the equation for received power, repeated here
+for convenience:
+  \begin{equation}
+    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
+  \end{equation}
+The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
+\begin{figure}[H]
+  \centering
+  \begin{tabular}{c|c|c}
+    \toprule
+    Symbol & Description & Nominal Value \\
+    \midrule
+    $\rho$  & Albedo of lambertian surface & $0.3$ \\
+    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
+    $R$ & Distance to surface (m) & $3$ \\
+    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
+    $\eta$ & Quantum efficiency of detector & $0.3$ \\
+    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
+    \bottomrule
+  \end{tabular}
+  \caption{}
+  \label{fig:sbr_calculation}
+\end{figure}
+Once $P_R$ is determined, we compute the number of photons using the laser
+wavelength $\lambda = 532$ nm as
+\begin{equation}
+  N = \frac{P_R\lambda}{hc}
+\end{equation}
+where $h \approx 6.626 \times 10^{-34}$ is Planck's constant and $c \approx 3
+\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
+MHz, we get the number of photons per pulse as $0.043$, which puts us in the
+low-flux regime.
 
@@
 
-\section{Nominal values for SBR calculation}
-Here we give the values used in the equation for received power, repeated here
-for convenience:
-  \begin{equation}
-    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
-  \end{equation}
-The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
-\begin{figure}[H]
-  \centering
-  \begin{tabular}{c|c|c}
-    \toprule
-    Symbol & Description & Nominal Value \\
-    \midrule
-    $\rho$  & Albedo of lambertian surface & $0.3$ \\
-    $P_T$ & Total irradiance at wavelength (W/$\text{m}^2$) & $0.026$ \\
-    $R$ & Distance to surface (m) & $3$ \\
-    $A_{rec}$ & Area of detector ($\text{m}^2$) & $1.96 \times 10^{-9}$ \\
-    $\eta$ & Quantum efficiency of detector & $0.3$ \\
-    $P_R$ & Received power at detector (W) & $1.62 \times 10^{-13}$ \\
-    \bottomrule
-  \end{tabular}
-  \caption{}
-  \label{fig:sbr_calculation}
-\end{figure}
-Once $P_R$ is determined, we compute the number of photons using the laser
-wavelength $\lambda = 532$ nm as
-\begin{equation}
-  N = \frac{P_R\lambda}{hc}
-\end{equation}
-where $h \approx 6.626 \tiems 10^{-34}$ is Planck's constant and $c \approx 3
-\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
-MHz, we get the number of photons per pulse as $0.043$, which puts us in the
-low-flux regime.
-
-\section{Comparison of diffused vs. scanned imaging}
-In our experiments, we capture measurements by scanning the scene with a
-single-pixel SPAD detector whose optical path is aligned with a laser. This
-arrangement allows us to capture a reference ``ground truth'' depth map for
-quantitative validation of our method. To emulate measurements captured using a
-system where the laser and detector are diffused over the scene, we digitally
-sum the measurements to obtain a single transient.
-
-In order to verify that digital summation of scanned measurements yields results
-that are similar to those captured by a diffused laser and detector, we capture
-an example scene using a modified hardware prototype in both scanned and
-diffused modes. The hardware prototype (shown in Fig.~\ref{fig:hardware})
-consists of a more powerful laser (Katana 05HP, 532 nm) which we operate at
-approximately 25 mW output power with two single-pixel SPAD detectors. One SPAD
-is aligned with the optical path of the laser, and the other SPAD is operated
-without a lens to integrate light from the entire scene. Both SPADs are fitted
-with a 10 nm bandpass filter centered at 532 nm, which reduces the amount of
-integrated ambient light. We attach a holographic diffuser (Thorlabs ED1-S50) to
-the laser output in order to diffuse light onto the scene or alternatively
-remove the diffuser and use a pair of scanning mirrors to scan the scene.
-
-The modified hardware setup is used to capture an example scene in both scanned and
-diffused modes, and the resulting transients are used to refine an initial depth
-estimate from the Kinect RGB image. We illustrate the results of this procedure
-in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
-measurements are similar in reconstruction quality and also show similar
-quantitative improvement in terms or error over the initial depth estimate. The
-unnormalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
-note that the counts show similar trends. The number of recorded photons in
-these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
-rate of detected photons is far less ($<$5\%) than the number of emitted laser
-pulses, and so we conclude that the measurements are captured in the low-flux
-regime where pileup effects are negligible. We attribute most of the differences
-between the scanned and diffused transients to the baseline between the
-positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).
-\begin{figure}[H]
-  \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
-  \caption{Comparing Scan + Sum and Diffused SPAD. The transients shown are
-    equal-time (and thus equal energy), and display qualitative similarity in
-    the absence of pileup.}
-  \label{fig:comparison}
-\end{figure}
-
-\begin{figure}[H]
-  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
-  \caption{Modified hardware setup. The setup is used to compare scanned and
-  diffused measurements and employs two SPAD detectors and two laser
-  configurations. In the first configuration, the scene is illuminated by
-  sending the laser light through a holographic diffuser and a lensless SPAD 
-  integrates light from the entire scene. In the second, the SPAD is aligned
-  with the optical path of the laser and the scene is scanned using a pair of
-  scanning mirrors. The baseline between the two SPADs (right) results in some
-  observed differences in the recorded transients.}
-  \label{fig:dither}
-\end{figure}
-
-\begin{table}[ht!]
-    \renewcommand{\arraystretch}{1.3}
-    \setlength{\tabcolsep}{10pt}
-     \centering
-     \begin{tabular}{lccc} \toprule
-         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
-         \textbf{Scanned} & $1.4\times10^7$ & $6\times10^8$ & $2.3\%$ \\
-         \textbf{Diffused} & $2.4\times10^7$ & $6\times10^8$ & $4.0\%$ \\
-        \bottomrule
-    \end{tabular}
-    \vspace{0.4em}
-    \caption{\textbf{Recorded photons for diffused vs.
-scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
-    \label{tab:photon_counts}
-\end{table}
-
+\clearpage
 \section{Additional results on NYU Depth v2}
@@
 the root-mean-square error (RMSE) for each example.
+
+\newpage
 \input{sections/supplement/simulation_comparison.tex}
 
+\clearpage
 \section{Additional results for hardware prototype}
@@
 calculation, and appear as an absolute difference of 0 in the difference maps.
+
+\newpage
+
 \input{sections/supplement/hardware_comparison.tex}

### 2020-03-05 paper/eccv2020/sections/discussion.tex
Fixed typos and changed one sentence in the introduction

@@
 with such techniques.  Our approach produces depth maps with accurate absolute
-depth, and helps the generalization of neural networks for MDE across scene
+depth, and helps MDE neural networks generalize across scene
 types, including on data captured with our hardware prototype.  Moreover, we

### 2020-03-05 paper/eccv2020/sections/hardware.tex
Fixed typos and changed one sentence in the introduction

@@
 Figure~\ref{fig:results_captured} we show a subset of the scenes we captured and
-processed with MiDAS~\cite{Lasinger:2019}, which achieved the best results among
+processed with MiDaS~\cite{Lasinger:2019}, which achieved the best results among
 the depth estimators we tested. Additional scenes, also processed with other MDE

### 2020-03-05 paper/eccv2020/sections/introduction.tex
Fixed typos and changed one sentence in the introduction

@@
 of the estimated depth maps, regardless of which specific depth estimator is
-used. \edit{Moreover, we build an camera prototype that combines an RGB camera and a single-pixel time-resolved detector.}  With this
-work, we present a practical way to disambiguate depth estimation with RGB
-images using minimal additional sensing hardware. Specifically, we make the
+used.
+\edit{Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique.} % With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.
+
+In summary, we make the
 following contributions:

### 2020-03-05 paper/eccv2020/sections/simulation.tex
final pass (hopefully)
Fixed typos and changed one sentence in the introduction

@@
 We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
-249~training and 215~testing scenes with RGB-D images captured using a Microsoft
-Kinect.
+249~training and 215~testing RGB-D images captured with a Kinect.
 
@@
   %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
-  \caption{Simulated results from NYU v2 computed with the DenseDepth
+  \caption{Simulated results from NYU Depth v2 computed with the DenseDepth
   CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,

### 2020-03-06 paper/eccv2020/sections/method.tex
Changed captured_diffuse figure titles.

@@
 The remaining ambient counts are discarded by setting the recorded counts to
-zero for all bins where \edit{$n < n_\text{first}$} and $n > n_\text{last}$. We use 
+zero for all bins where \edit{$n < \hat n_\text{first}$} and $n > \hat n_\text{last}$. We use 
 $\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.

### 2020-07-09 paper/eccv2020CR/main.tex
Added eccv2020 camera-ready draft.

--- 2020-03-05 paper/eccv2020/main.tex
@@
 % CAMERA READY - Comment OUT the following two lines
-\usepackage{ruler}
-\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
+% \usepackage{ruler}
+% \usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}
 
@@
 \newcommand{\edit}[1]{\textcolor{red}{#1}}
+% \newcommand{\edit}[1]{#1}
 
@@
 
-%\title{Improving Monocular Depth Estimation with Global Depth Histogram Matching using a Single SPAD Transient} % Replace with your title
 \title{Disambiguating Monocular Depth Estimation with a Single Transient} % Replace with your title
 
-% INITIAL SUBMISSION 
-%\begin{comment}
-\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
-\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCVSubNumber}
-%\end{comment}
-%******************
-
 % CAMERA READY SUBMISSION
-\begin{comment}
-\titlerunning{Abbreviated paper title}
+% \begin{comment}
+\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
 % If the paper title is too long for the running head, you can set
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Mark Nishimura  \and
+David B. Lindell \and
+Chris Metzler \and
+Gordon Wetzstein}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{M. Nishimura et al.}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
-\end{comment}
+\institute{Stanford University, Stanford, CA \\
+\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
 %******************

### 2020-07-09 paper/eccv2020CR/sections/discussion.tex
Added eccv2020 camera-ready draft.

--- 2020-03-05 paper/eccv2020/sections/discussion.tex
@@
 types, including on data captured with our hardware prototype.  Moreover, we
-require only minimal additional sensing hardware; we show that a single measurement
-histogram from a diffused SPAD sensor contains enough information about global
-scene geometry to correct errors in monocular depth estimates.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\paragraph{Limitations}
+require only minimal additional sensing hardware; we show that a single
+measurement histogram from a diffused SPAD sensor contains enough information
+about global scene geometry to correct errors in monocular depth estimates.
 
 The performance of our method is highly dependent on the accuracy of the initial
-depth map of the MDE algorithm.
-%Since our method relies on the monocular depth estimate, the accuracy of the output depth map also relies on the performance of the initial depth estimate.
-Our results demonstrate that when the MDE technique produces a depth map
-with good ordinal accuracy, where the ordering of object depths is roughly correct, the
-depth estimate can be corrected to produce accurate absolute depth. However, if
-the ordering of the initial depths is not correct, these errors will not be
-corrected by our histogram matching procedure and may propagate to the final
-output depth map.
+depth map of the MDE algorithm. Our results demonstrate that when the MDE
+technique produces a depth map with good ordinal accuracy, where the ordering of
+object depths is roughly correct, the depth estimate can be corrected to produce
+accurate absolute depth. However, if the ordering of the initial depths is not
+correct, these errors will not be corrected by our histogram matching procedure
+and may propagate to the final output depth map.
 
-\edit{In the optically diffused configuration, the laser
-power is spread out over the entire scene. Accordingly, for distant scene points very
-little light may return to the SPAD and it may be difficult to accurately
-capture distant scene geometry in the histogram. Thus our method is best suited
-to short to medium-range scenes with a reasonable power budget for the diffused
-illumination.} \edit{For example, assuming an indoor scene with
+In the optically diffused configuration, the laser
+power is spread out over the entire scene. Accordingly, for distant scene points
+very little light may return to the SPAD, \edit{ making reconstruction difficult (an analogous
+  problem occurs with dark objects).} \edit{Thus, our method is best suited
+  to short to medium-range scenes.}
+\edit{CONSIDER MOVE THIS ENTIRE CALCULATION TO
+SUPPLEMENT} For example, assuming an indoor scene with
 fluorescent bulbs and an ambient spectral irradiance of $I_A =
 1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
-to the laser), we find that the laser power required to achieve a minimum SBR of 5 for a
-diffuse scene at $R = 3$ m
-and a field of view of $\theta = 40^\circ$ can be calculated as}
+to the laser), we find that the laser power required to achieve a minimum SBR of
+5 for a diffuse scene at $R = 3$ m and a field of view of
+$\theta = 40^\circ$\textdegree can be calculated as
 %
@@
 \end{equation}
-\edit{giving $P_{\text{min}}=21$ mW. We note that this is significantly 
-less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.}
+giving $P_{\text{min}}=21$ mW. We note that this is significantly
+less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.
 
-\edit{Under these scene parameters, we can compute the total incident 
-  flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as}
+Under these scene parameters, we can compute the total incident
+flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
 \begin{equation}
@@
 \end{equation}
-  \edit{where $P_T$ is the illumination power in the visible region, $\rho$ is its
-  albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to
-  the object, and $\eta$ is the quantum efficiency of the detector. For a range of 
-  values similar to those of our experiments (detailed in the supplement), we find that
-  the ratio of photon detections to illumination pulses is roughly 4\%, or well within 
-  low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
-  We also empirically validate that our method works with a diffused setup and an output power of 
-  approximately 25 mW without significant pileup effects as shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.
-  } \edit{However, even for operation in the high-flux regime, pileup can be mitigated  
-    by reducing the amount of incident light, for example by reducing the aperture size or 
-    using neutral density filters, or by using a pileup correction~\cite{Heide:2018,Rapp:2019}.}
+where $P_T$ is the illumination power in the visible region, $\rho$ is its
+albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
+object, and $\eta$ is the quantum efficiency of the detector. For a range of
+values similar to those of our experiments (detailed in the supplement), we find
+that the ratio of photon detections to illumination pulses is roughly 4\%, or
+well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
+We also empirically validate that our method works with a diffused setup and
+an output power of approximately 25 mW without significant pileup effects as
+shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.
 
-  %\edit{Note
+\edit{We acknowledge that pileup in bright environments will ultimately limit
+  the maximum range of our method. However, even when operating in the high-flux
+  regime, pileup can be mitigated by reducing the amount of incident light, for
+  example by reducing the aperture size or using neutral density filters, or by
+  using pileup correction~\cite{Heide:2018,Rapp:2019}. Another approach to
+  mitigate pileup involves taking two transient measurements, one with and one
+  without laser illumination, and using their difference to approximate the
+  backgrond-free transient.}
+
+  %Note
   % that this calculation involves only on the signal-to-background photon ratio,
@@
 
-% \edit{Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
+% Furthermore, our system uses a SPAD and is therefore susceptible to pileup.
 % Because the SPAD must be quenched before it can
@@
 
-% \edit{While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
+% While our prototype shows results for scanned/summed measurements, our scanning prototype operates in the low-flux regime,
 % avoiding pileup. A hypothetical diffused SPAD prototype could also operate in
@@
 
-% \edit{Even if diffused and scanned/summed measurements are equivalent
+% Even if diffused and scanned/summed measurements are equivalent
 %   computationally, they are not equivalent energetically.  This number is dependent on scene albedo, but all time-of-flight imaging
@@
 \paragraph{Future Work}
-While our hardware prototype is large, future work could miniaturize this
-system. Our algorithm or similar sensor fusion algorithms could
-also be integrated into electronics that already contain the required hardware
+\edit{DELETE While our hardware prototype is large, future work could miniaturize this
+system.} Our algorithm or similar sensor fusion algorithms could
+\edit{DELETE also} be integrated into electronics that already contain the required hardware
 components, for example, existing cell phones with single-pixel SPAD
-proximity sensors and RGB cameras.
+proximity sensors and RGB cameras \edit{The small baseline of such sensors
+  would also mitigate the effects of shading and complex BRDFs. Necessary
+  adjustments, such as pairing near-infrared (NIR) SPADs with NIR sensors,
+  could be made. More sophisticated intrinsic imaging techniques could also be
+  employed, replacing the primitive RGB channel method described here.}
 
@@
 histogram. One might even consider sensing regimes where the number of
-returning signal photons is low, such as when the time-resolved detector and camera operate
-at high framerates. While most MDE techniques are tailored to clean RGB images,  
-the transient could be used to help MDE
-techniques generalize to noisy scenes under low-light conditions.
+returning signal photons is low, such as when the time-resolved detector and
+camera operate at high framerates. While most MDE techniques are tailored to
+clean RGB images, the transient could be used to help MDE techniques generalize
+to noisy scenes under low-light conditions.
 

### 2020-07-09 paper/eccv2020CR/sections/hardware.tex
Added eccv2020 camera-ready draft.

--- 2020-03-05 paper/eccv2020/sections/hardware.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Prototype RGB-SPAD Camera Hardware}
-
-% The laser operates at 450~nm with a pulse repetition rate of 25~MHz with a peak power of 450~mW and average power of 0.5~mW.
-% \begin{figure}[t]
-% 	\centering
-%   \includegraphics[width=0.5\columnwidth]{prototype_single_col.pdf}
-%   \caption{Prototype scanning setup. The pulsed light from the laser travels
-%     through a beam splitter before being guided by the galvo to the scene.
-%     Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB 
-%     camera is used to capture the image used to generate the monocular depth estimate
-%     (the depth camera is not used).}
-%   \label{fig:prototype}
-%   % \vspace{-0.5em}
-% \end{figure}
-
 As shown in Figure~\ref{fig:hardware}, our prototype comprises a color camera
@@
 a pulse repetition rate of 10~MHz with a peak power of 450~mW and average power
-of 0.5~mW. The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single transient is generated by summing all of these measurements for a specific
-scene. This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by
-comparing it with the captured depth.
-To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD (see Figure~\ref{fig:hardware}(b,c)), we set up a slightly modified version of our prototype consisting of both scanned and optically diffused SPADs side-by-side.
-Additional details about the hardware prototype can be found in the supplement.
+of 0.5~mW. The ground truth depth map is raster-scanned at a resolution of
+$512 \times 512$ pixels, and the single transient is generated by summing all of
+these measurements for a specific scene. This allows us to validate the accuracy
+of the proposed histogram matching algorithm, which only uses the integrated
+single histogram, by comparing it with the captured depth. To verify that our
+digitally aggregated scanned SPAD measurements match measurements produced by an
+optically diffused SPAD (see Figure~\ref{fig:hardware}(b,c)), we set up a
+slightly modified version of our prototype consisting of both scanned and
+optically diffused SPADs side-by-side. Additional details about the hardware
+prototype can be found in the supplement.
 
@@
 The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
-This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---\edit{such validation would not be possible if we were to capture measurements with an optically diffused SPAD.}
+This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---such validation would not be possible if we were to capture measurements with an optically diffused SPAD.
 
 % show this in supplement
-%\edit{To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side.
+%To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side.
 Details about this system can be found in the supplement.
@@
 Slight differences in their two histograms can be attributed to a baseline difference of about 10cm between the SPAD positions.
-That is, they observe scene from slightly different perspectives.}
-	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} \edit{We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For}
+That is, they observe scene from slightly different perspectives.
+	%NOTE:JUSTIFY USE OF DIFFERENT PROTOTYPE FOR RESULTS IN THE WILD WITH EYE SAFETY?} We show proof-of-concept results captured by this system in   Figure~\ref{fig:captured_diffuse_small}. For
 
@@
 	\includegraphics[width=\columnwidth]{captured.pdf}
-	\caption{Experimental results. For each scene, we record a ground truth depth
+	\caption{\edit{Experimental results. For each scene, we record a ground truth depth
     map that is raster-scanned with the SPAD (upper left subimages), and an RGB
-    image (lower left). A monocular depth CNN predicts an initial depth map (top
-    middle), which is corrected with the digitally aggregated SPAD histogram using the
-    proposed method (top right), as shown by the error maps and root mean
-    squared error (RMSE) for each example (lower center, right). The CNN is
-    confused when we show it a photograph of a poster (bottom scene); it
+    image (upper right subimages). A monocular depth CNN predicts an initial depth map (top
+    middle left subimages), which is corrected with the digitally aggregated SPAD histogram using the
+    proposed method (bottom left subimages), as shown by the error maps and root mean
+    squared error (RMSE) for each example (middle left, bottom subimages). The CNN is
+    confused when we show it a photograph of a poster (rightmost scene); it
     incorrectly predicts the depth of the scene depicted on the flat print. Our
-    method is able to correct this error.}
+    method is able to correct this error.}}
 	\label{fig:results_captured}

### 2020-07-09 paper/eccv2020CR/sections/introduction.tex
Added eccv2020 camera-ready draft.

--- 2020-03-05 paper/eccv2020/sections/introduction.tex
@@
     reliable absolute depth estimation, resulting in large errors (inset images).
-    The proposed method uses a \edit{single transient measurement aggregating
-      the time-of-flight information of the entire scene (leftmost)} to correct
+    The proposed method uses a single transient measurement aggregating
+      the time-of-flight information of the entire scene (leftmost) to correct
     the output of the depth estimation and optimize the quality of the
@@
 However, each of these techniques has aspects that may make their deployment
-challenging \edit{in certain scenarios}. For example, stereo or multiview techniques require multiple
+challenging in certain scenarios. For example, stereo or multiview techniques require multiple
 cameras, active illumination techniques may have limited resolution or require
@@
 to MDE employ neural networks that learn to predict depth by exploiting
-\edit{pictorial depth} cues such as perspective, occlusion, shading, and relative
+pictorial depth cues such as perspective, occlusion, shading, and relative
 object size. While such models have significantly improved over recent years,
@@
 generation Apple iPhones uses a low-power pulsed light source and a
-single-pixel \edit{time-resolved detector} %, single-photon avalanche diode (SPAD) 
+single-pixel time-resolved detector %, single-photon avalanche diode (
 to sense distance to an
 object directly in front of the phone. %SPADs 
-\edit{
 Time-resolved detectors, such as avalanche photon diodes (APDs) or single-photon
@@
 systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However,
-single-photon sensor arrays} have
+single-photon sensor arrays have
 not yet been used for 3D imaging on consumer electronics, primarily because the requirement for
@@
 
-Here, we propose to use a single-pixel \edit{time-resolved detector} and pulsed light source in an
-unconventional way: rather than optically focusing them to record the distance
-to a single scene point, we diffuse the emitted light and \edit{aggregate the reflected light over the
-entire scene with the detector}. The resulting \edit{transient} measurement
-resembles a histogram of the scene depth and we demonstrate that this can be
-used to achieve accurate absolute depth when combined with the estimate of
-\edit{any monocular depth estimator in a post-processing step}
+Here, we propose to use a single-pixel time-resolved detector and pulsed light
+source in an unconventional way: rather than optically focusing them to record
+the distance to a single scene point, we diffuse the emitted light and aggregate
+the reflected light over the entire scene with the detector. \edit{The resulting
+transient measurement resembles a histogram of the scene and can be used to
+achieve accurate absolute depth in conjunction with a monocular depth estimate}
 (Fig.~\ref{fig:teaser}).
@@
 depth computed by a monocular depth estimator to be consistent with the
-measurements captured by the \edit{aggregated time-resolved} detector. We demonstrate in extensive
+measurements captured by the aggregated time-resolved detector. We demonstrate in extensive
 simulations that our approach achieves substantial improvements in the quality
@@
 used.
-\edit{Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique.} % With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.
+Moreover, we build a camera prototype that combines an RGB camera and a single-pixel time-resolved detector and use it to validate the proposed depth estimation technique.
+% With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware.
 
-In summary, we make the
-following contributions:
+In summary, we make the following contributions:
 %
 \begin{itemize}
-	\item We propose augmenting an RGB camera with a global depth histogram aggregated by a time-resolved detector to address scale ambiguity in MDE.	
-  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
-	\item We build a prototype camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types.
+	\item We propose augmenting an RGB camera with a global depth transient
+    aggregated by a time-resolved detector to address scale ambiguity in MDE.
+  \item \edit{We introduce a depth reconstruction algorithm that uses the
+    detector's image formation model in conjunction with a modified version of
+    histogram matching, to produce a depth map from a single RGB image and
+    transient. The algorithm can be applied instantly to any existing and
+    future MDE algorithms.}
+  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset
+    and demonstrate that our approach is able to resolve scale ambiguity while
+    being fast and easy to implement.
+	\item We build a prototype camera and evaluate its efficacy on captured data,
+    assessing both the quality and the ability of our method to help
+    generalization of monocular depth estimators across scene types.
 \end{itemize}
 
-%\edit{\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement.
+%\emph{Overview of Limitations:} our prototype camera uses a scanned SPAD and digitally aggregates the captured transients to emulate a single optically diffused measurement.
 The benefit of this approach is access to ground truth depth, allowing us to evaluate the efficacy of our method with measured data.
@@
 In these conditions, the aggregated measurements may differ from a single optically diffused measurement.
-Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.}
+Yet, we experimentally verify that digitally and optically aggregated measurements captured with our system are very similar and pileup could also be computationally corrected~\cite{Heide:2018,Rapp:2019}, although we did not attempt this.
 
-%\edit{Our method is not without limitations.
+%Our method is not without limitations.
 It still requires a laser and single-pixel LiDAR detector and is sensitive to ambient photons, which limit the maximum range.
 Being a variant of histogram matching, our method is not able to resolve ordinal depth errors (errors where an object is wrongly placed closer or farther relative to another object).
-In spite of these limitations, we find that our method performs remarkably well in practice.}
+In spite of these limitations, we find that our method performs remarkably well in practice.

### 2020-07-09 paper/eccv2020CR/sections/related.tex
Added eccv2020 camera-ready draft.

--- 2020-02-28 paper/eccv2020/sections/related.tex
@@
 non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural
-networks have been applied to this problem, \edit{for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
+networks have been applied to this problem, for example using a multi-scale neural network to predict depth maps~\cite{Eigen2014},
 using an unsupervised approach that trains a network using stereo pairs~\cite{Godard2017}, and using a logarithmic
-depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}}. Various
+depth discretization scheme combined with an ordinal regression loss function~\cite{Fu2018}. Various
 experiments using different types of encoder networks (\eg, ResNet,
@@
 depth estimation networks and disambiguates the output using depth
-histogram--like measurements obtained from a single \edit{time-resolved detector}. Other
+histogram--like measurements obtained from a single time-resolved detector. Other
 approaches to disambiguating monocular depth estimation use optimized freeform
@@
 sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors
-and specialized image reconstruction methods. \edit{In contrast, our approach adds
+and specialized image reconstruction methods. In contrast, our approach adds
 minimal additional hardware to a single RGB camera, and may leverage sensors currently
-deployed in consumer electronics.}
+deployed in consumer electronics.
 
@@
 %
-\edit{Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
-to record the time of flight of individual photons. These time-resolved detectors} can be
+Emerging LiDAR systems use avalanche photon diodes (APDs) or single-photon avalanche diodes (SPADs)
+to record the time of flight of individual photons. These time-resolved detectors can be
 fabricated using standard CMOS processes, but the required time-stamping electronics are challenging to miniaturize and fabricate at low
-cost. For this reason, many \edit{LiDAR systems}, especially those using SPADs, use a single \edit{or a few detectors}
+cost. For this reason, many LiDAR systems, especially those using SPADs, use a single or a few detectors
 combined with a  scanning
@@
 resolution and scanners can also be expensive, difficult to calibrate, and prone
-to mechanical failure. To reduce the scanning complexity to one dimension, \edit{1D
-detector arrays} have been
+to mechanical failure. To reduce the scanning complexity to one dimension, 1D
+detector arrays have been
 developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of
 research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet,
-single-pixel \edit{time-resolved detectors} remain the only viable option for low-cost consumer devices
+single-pixel time-resolved detectors remain the only viable option for low-cost consumer devices
 today.
 
-The proposed method uses a single-pixel \edit{APD or SPAD} and pulsed light source that are
+The proposed method uses a single-pixel APD or SPAD and pulsed light source that are
 diffused across the entire scene instead of aimed at a single point, as with
@@
 resembles the depth histogram of the scene. Our sensor fusion algorithm achieves
-reliable absolute depth estimation by combining the \edit{transient} measurement with the
+reliable absolute depth estimation by combining the transient measurement with the
 output of a monocular depth estimator using a histogram matching technique.
@@
 energy function that penalizes foreground segmentations with dissimilar
-histograms. \edit{Caramazza et al.~\cite{caramazza2018neural} use a single
+histograms. Caramazza et al.~\cite{caramazza2018neural} use a single
 non-line-of-sight transient to recover the identity of a person hidden from
-view.} In a slightly different application area, Zhang et
+view. In a slightly different application area, Zhang et
 al.~\cite{Zhang2017} train a neural network to produce realistically colorized
@@
 
-In our procedure, the \edit{transient measurements} closely resemble a histogram of
+In our procedure, the transient measurements closely resemble a histogram of
 the depth map where the histogram values are weighted by spatially varying scene

### 2020-07-09 paper/eccv2020CR/sections/simulation.tex
Added eccv2020 camera-ready draft.

--- 2020-02-28 paper/eccv2020/sections/simulation.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Implementation Details}
@@
 We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
-249~training and 215~testing scenes with RGB-D images captured using a Microsoft
-Kinect.
+249~training and 215~testing RGB-D images captured with a Kinect.
 
-To simulate a \edit{transient}, we take the provided depth map and 
-calculate a weighted depth histogram by weighting the pixel contributions to
-each depth bin by the luminance of each pixel. To model radiometric falloff, we
-multiply each bin by $1/z^2$, and convolve with a modeled system temporal
-response, which we approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
+To simulate a transient, we take the provided depth map and calculate a weighted
+depth histogram by weighting the pixel contributions to each depth bin by the
+luminance of each pixel. To model radiometric falloff, we multiply each bin by
+$1/z^2$, and convolve with a modeled system temporal response, which we
+approximate as a Gaussian with a full-width at half-maximum of 70~ps. We scale
 the histogram by the total number of observed signal photon counts (set to
-$10^6$) and  add a fixed number of background photons $b \in \set{2\times 10^5, 10^5, 2\times
-10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
-count detections, and the different background levels correspond to
-signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively. Finally,
-each bin is Poisson sampled to produce the final simulated transient.
+$10^6$) and  add a fixed number of background photons
+$b \in \set{2\times 10^5, 10^5, 2\times 10^4, 10^4}$. The background counts are
+evenly distributed across all bins to simulate the ambient and dark count
+detections, and the different background levels correspond to
+signal-to-background ratios (SBR) of $5, 10, 50$ and $100$ respectively.
+Finally, each bin is Poisson sampled to produce the final simulated transient.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Simulated Results}
@@
       \input{sections/figures/sim_table.tex}
-\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
+\caption{
+  Quantitative evaluation using NYU Depth v2. Bold indicates best
 performance for that metric, while underline indicates second best. The proposed
@@
 exact depth map histogram, even though those methods have access to ground
-truth. \edit{DECREASE FONT SIZE!}}
-\vspace{-2em}
+truth. \edit{Metric definitions can be found in~\cite{Eigen2014}.}}
 \label{tab:comparison}
@@
 MiDaS~\cite{Lasinger:2019}. To evaluate the quality of DORN and DenseDepth, we
-report various standard error metrics~\cite{Eigen2014}. Moreover, we show a simple
-post-processing step that rescales their outputs to match the median ground truth
-depth~\cite{Alhashim2018}. We also show the results of histogram matching the
-output of the CNNs with the ground truth depth map histogram. Note that we do
-not report the quality of the direct output of MiDaS as this algorithm does not
-output metric depth. However, we do show its output histogram matched with the
-ground truth depth map histogram. In all cases, post-processing the estimated
-depth maps either with the median depth or depth histogram significantly
-improves the absolute depth estimation, often by a large margin compared to the
-raw output of the CNNs. Unfortunately, ground truth depth is typically not
-accessible so neither of these two post-processing methods are viable in
-practical application scenarios.
+report various standard error metrics~\cite{Eigen2014}. Moreover, we show a
+simple post-processing step that rescales their outputs to match the median
+ground truth depth~\cite{Alhashim2018}. We also show the results of histogram
+matching the output of the CNNs with the ground truth depth map histogram. Note
+that we do not report the quality of the direct output of MiDaS as this
+algorithm does not output metric depth. However, we do show its output histogram
+matched with the ground truth depth map histogram. In all cases, post-processing
+the estimated depth maps either with the median depth or depth histogram
+significantly improves the absolute depth estimation, often by a large margin
+compared to the raw output of the CNNs. Unfortunately, ground truth depth is
+typically not accessible so neither of these two post-processing methods are
+viable in practical application scenarios.
 
-Instead, our method uses the simulated measurements from a single \edit{aggregated transient} to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
-signal-to-background ratios (SBRs). We see that the proposed method achieves
-high-quality results for correcting the raw depth map estimated by the
-respective CNNs for all cases. The quality of the resulting depth maps is almost
-as good as that achieved with the oracle ground truth histogram, which can be
-interpreted as an approximate upper bound on the performance, despite a
-relatively high amount of noise and background signal. These results demonstrate
-that the proposed method is agnostic to the specific depth estimation CNN
-applied to get the initial depth map and that it generally achieves significant
-improvements in the estimated depth maps, clearly surpassing the variation in
-performance between depth estimation CNNs.
+Instead, our method uses the simulated measurements from a single aggregated
+transient to correct the depth map. In Table~\ref{tab:comparison}, results are
+shown for several different signal-to-background ratios (SBRs). We see that the
+proposed method achieves high-quality results for correcting the raw depth map
+estimated by the respective CNNs for all cases. The quality of the resulting
+depth maps is almost as good as that achieved with the oracle ground truth
+histogram, which can be interpreted as an approximate upper bound on the
+performance, despite a relatively high amount of noise and background signal.
+These results demonstrate that the proposed method is agnostic to the specific
+depth estimation CNN applied to get the initial depth map and that it generally
+achieves significant improvements in the estimated depth maps, clearly
+surpassing the variation in performance between depth estimation CNNs.
 
-\begin{figure*}[!h]
-  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
-  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
+\begin{figure*}[t]
   \includegraphics[width=\textwidth]{comparison.pdf}
-  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
-  \caption{Simulated results from NYU v2 computed with the DenseDepth
+  \caption{Simulated results from NYU Depth v2 computed with the DenseDepth
     CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
     but contain systematic error. Oracle access to the ground truth depth maps,
-  either through the median depth or the depth histogram, can remove this error
-  and correct the depth maps. \edit{The proposed method uses a single transient measurement} and does not rely on ground truth depth, but it achieves
-  a quality that closely matches the best-performing oracle.}
+    either through the median depth or the depth histogram, can remove this
+    error and correct the depth maps. The proposed method uses a single
+    transient measurement and does not rely on ground truth depth, but it
+    achieves a quality that closely matches the best-performing oracle.}
 	\label{fig:results_simulated}
-  \vspace{-1em}
 \end{figure*}
@@
 proposed method is close to using the oracle histogram, despite relying on
-noisy \edit{transient} measurements. Additional simulations using DenseDepth and other depth
-estimation CNNs for a variety of scenes are shown in the supplement.
+noisy transient measurements. Additional simulations using DenseDepth and other
+depth estimation CNNs for a variety of scenes are shown in the supplement.

### 2020-07-09 paper/eccv2020CR/sections/supplement/hardware_comparison.tex
Added eccv2020 camera-ready draft.

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground
      truth. MiDaS does not output metric depth, so the CNN depth maps are
      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.}
    \label{fig:midas_captured_1}
%    \vspace{-1.5em}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \vspace{-1em}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground
      truth.MiDaS does not output metric depth, so the CNN depth maps are
      scaled to be in the range $(0.494, 9.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.}
    \label{fig:midas_captured_2}
%    \vspace{-1.5em}
\end{figure}

% %% MiDaS outdoor scene
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/midas/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/midas/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/midas/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground
      truth. MiDaS does not output metric depth, so the CNN depth map is
      scaled to be in the range $(0.494, 11.094)$ by default. However, MiDaS does produce
      accurate ordinal depth, leading to stronger performance of our histogram
      matching compared to other methods.
}
    \label{fig:midas_captured_3}
%    \vspace{-1.5em}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_1}
%    \vspace{-1.5em}
\end{figure}
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/densedepth/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/densedepth/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_2}
%    \vspace{-1.5em}
\end{figure}
%% DenseDepth outdoor scene
\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/densedepth/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/densedepth/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/densedepth/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DenseDepth CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:densedepth_captured_3}
%    \vspace{-1.5em}
\end{figure}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_29_kitchen_scene/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_29_kitchen_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}& 
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_29_conference_room_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured_1}
%    \vspace{-1.5em}
\end{figure}

\begin{figure}[H]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Hallway}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_Hallway/depth_colorbar.pdf}\\
      & & & & & \\

      & 
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_Hallway/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_30_Hallway/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Poster}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_poster_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_poster_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_poster_scene/rmses.tex}& \\

      \rule{0pt}{3ex}  & & & & & \\
      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Bookshelf}}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_small_lab_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/rgb_cropped_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=0.93in, height=0.93in]{captured/dorn/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/dorn/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured_2}
%    \vspace{-1.5em}
\end{figure}
% %% DORN outdoor scene
% \begin{figure}
%     \centering
%     \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
%       \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
%       &
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_init_depth_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_med_scaled_depth_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_pred_depth_fig.png}&
%       \includegraphics[height=0.93in]{captured/dorn/8_31_outdoor3/depth_colorbar.pdf}\\
% %      & RGB &  &  &  & \\
%       &
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/rgb_cropped_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_init_diff_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_med_scaled_diff_fig.png}&
%       \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_pred_diff_fig.png}&
%       \includegraphics[height=0.93in]{captured/dorn/8_31_outdoor3/diff_colorbar.pdf}\\
%       & RGB & \input{sections/figures/captured/dorn/8_31_outdoor3/rmses.tex}& \\ 
%     \end{tabular}
%     \caption{Captured results initialized using the DORN CNN on an outdoor scene.
%       Second row shows absolute difference between above estimates and ground truth.}
%     \label{fig:dorn_outdoor_captured}
% %    \vspace{-1.5em}
% \end{figure}

\begin{figure}[t]
    \centering
    \begin{tabular}{p{5mm}*{4}{>{\centering\arraybackslash}p{0.93in}}c}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Outdoor Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_init_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_med_scaled_depth_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_pred_depth_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_31_outdoor3/depth_colorbar.pdf}\\
%      & RGB &  &  &  & \\
      &
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/rgb_cropped_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_init_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_med_scaled_diff_fig.png}&
      \includegraphics[height=0.93in, width=0.93in]{captured/dorn/8_31_outdoor3/z_pred_diff_fig.png}&
      \includegraphics[height=0.93in]{captured/dorn/8_31_outdoor3/diff_colorbar.pdf}\\
      & RGB & \input{sections/figures/captured/dorn/8_31_outdoor3/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the DORN CNN on an outdoor scene.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:dorn_captured_3}
%    \vspace{-1.5em}
\end{figure}

### 2020-07-09 paper/eccv2020CR/supplement.tex
Added eccv2020 camera-ready draft.

--- 2020-03-05 paper/eccv2020/supplement.tex
@@
 \maketitle
+\begin{abstract}
+  TODO: Abstract
+\end{abstract}
 
@@
       with the same total exposure time and are qualitatively similar without 
-      noticeable pileup effects.}
+      noticeable pileup effects. We Use $K = 300$ bins for the reconstruction
+      and a depth range of $[0.8, 6]$ meters. MiDaS \cite{Lasinger:2019} does
+      not produce globally-scaled depth, so we scale it to fit this depth range.
+      We inpaint the depth map from the Kinect's depth camera to acquire ground
+      truth depth.}
   \label{fig:comparison}
@@
 
-\section{Nominal values for SBR calculation}
+\section{Nominal values for radiometric calculation}
 Here we give the values used in the equation for received power, repeated here
@@
   \end{equation}
-The object in question is a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
+  For our scene, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
 \begin{figure}[H]
@@
   \end{tabular}
-  \caption{}
+  \caption{Table of nominal values for radiometric calculation.}
   \label{fig:sbr_calculation}
@@
 \end{equation}
-where $h \approx 6.626 \times 10^{-34}$ is Planck's constant and $c \approx 3
-\times 10^8$ is the speed of light. Now using the fact that our laser runs at 10
-MHz, we get the number of photons per pulse as $0.043$, which puts us in the
-low-flux regime.
+where $h \approx 6.626 \times 10^{-34}$ $\text{J} \cdot \text{s}$ is Planck's constant and $c \approx 3
+\times 10^8$ $\text{m}/\text{s}$ is the speed of light. Using the fact that our laser runs at 10
+MHz, we get the number of photons per pulse as $0.043$ or $4.3\%$, which puts us in the
+low-flux regime (where photons per pulse is $< 5\%$).
 
@@
 Depth v2 and using DenseDepth~\cite{Alhashim2018} for our MDE CNN.
-Only the histogram matching portion was timed, not the CNN nor the denoising pipeline.
+Only the histogram matching portion was timed, not the CNN nor the denoising
+pipeline. Using the intensity to produce the initial weighted histogram
+$h_{\text{source}} $ provides noticable improvements
+in RMSE, but intensity may safely be ignored during the pixel movement step,
+resulting in noticeable speed improvements.
 

### 2020-07-09 paper/eccv2020CR/sections/figures/refresh_images.sh

@@ -1,0 +1,7 @@
+#!/usr/bin/env bash
+# rsync -r markn1@ares:~/spad_single/paper/spad_single/sections/figures/comparison_table ~/Documents/Stanford/ares/spad_single/paper/spad_single/sections/figures
+# rsync -r markn1@ares:~/spad_single/paper/spad_single/sections/figures/spad_example ~/Documents/Stanford/ares/spad_single/paper/spad_single/sections/figures
+rsync -r markn1@ares:~/spad_single/nyuv2/weighted_histogram_matching/figures/comparison ~/Documents/Stanford/ares/spad_single/paper/eccv2020/sections/figures
+rsync -r markn1@ares:~/spad_single/nyuv2/weighted_histogram_matching/figures/video ~/Documents/Stanford/ares/spad_single/paper/eccv2020/sections/figures
+rsync -r markn1@ares:~/spad_single/nyuv2/captured/figures/* ~/Documents/Stanford/ares/spad_single/paper/eccv2020/sections/figures/captured --exclude='*.npy'
+

### 2020-07-09 paper/eccv2020CR/sections/figures/sync_figures.sh

@@ -1,0 +1,19 @@
+#!/usr/bin/env bash
+# Sync figures with Google Drive or other folders so everyone can see them
+gdrive="/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/";
+rsync -r . "$gdrive/raw"
+rsync captured/midas/8_30_small_lab_scene/teaser_eccv.pdf "$gdrive"
+rsync full_pipeline/full_pipeline.jpeg "$gdrive"
+shopt -s extglob  #Allows for | in bash pattern matching below
+rsync -r comparison/*.pdf "$gdrive/comparison"
+rsync comparison.pdf "$gdrive"
+rsync prototype_single_col.pdf "$gdrive"
+rsync -R ././captured/**/**/?(gt_z_proj_crop_depth_fig|z_init_depth_fig|z_med_scaled_depth_fig|z_pred_depth_fig|rgb_cropped_fig|z_init_diff_fig|z_med_scaled_diff_fig|z_pred_diff_fig).png "$gdrive"
+rsync -R ././captured/**/**/?(diff_colorbar|depth_colorbar).pdf "$gdrive" 
+rsync method.pdf "$gdrive"
+rsync captured.pdf "$gdrive"
+rsync dither.pdf "$gdrive"
+rsync hardware.pdf "$gdrive"
+rsync scanned_diffuse.pdf "$gdrive"
+rsync captured_diffuse.pdf "$gdrive"
+rsync capture_diffuse_small.pdf "$gdrive"

### 2020-07-09 paper/eccv2020CR/sections/related.tex
compress figures, add related work, adjust author spelling

@@
 output of a monocular depth estimator using a histogram matching technique.
-While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018},
+\edit{While other recent work also explored RGB-SPAD sensor
+fusion~\cite{Lindell2018,sun2020spadnet},
 the RGB image was primarily used to guide the denoising and upsampling of
-measurements from a SPAD array.
+measurements from a SPAD array.}
 
@@
 energy function that penalizes foreground segmentations with dissimilar
-histograms. Caramazza et al.~\cite{caramazza2018neural} use a single
+histograms. \edit{In the area of non-line-of-sight
+imaging~\cite{faccio2020non,lindell2019wave,liu2020phasor,liu2019non,o2018confocal},
+Caramazza et al.~\cite{caramazza2018neural} use a single
 non-line-of-sight transient to recover the identity of a person hidden from
-view. In a slightly different application area, Zhang et
+view.} In a slightly different application area, Zhang et
 al.~\cite{Zhang2017} train a neural network to produce realistically colorized

### 2020-07-09 paper/eccv2020CR/sections/introduction.tex
Minor changes and added citation

@@
 the reflected light over the entire scene with the detector. \edit{The resulting
-transient measurement resembles a histogram of the scene and can be used to
+transient measurement resembles a histogram of the scene's depth and can be used to
 achieve accurate absolute depth in conjunction with a monocular depth estimate}
@@
 	\item We build a prototype camera and evaluate its efficacy on captured data,
-    assessing both the quality and the ability of our method to help
-    generalization of monocular depth estimators across scene types.
+    assessing both the quality and the ability of our method to improve generalization of monocular depth estimators across scene types.
 \end{itemize}

### 2020-07-09 paper/cvpr2020/rebuttal/figures/remove_dc_from_spad.py

@@ -1,24 +1,0 @@
-import numpy as np
-
-def remove_dc_from_spad_edge(spad, ambient, grad_th=1e3, n_std=1.):
-    """
-    Create a "bounding box" that is bounded on the left and the right
-    by using the gradients and below by using the ambient estimate.
-    """
-    # Detect edges:
-    assert len(spad.shape) == 1
-    edges = np.abs(np.diff(spad)) > grad_th
-    print(np.abs(np.diff(spad)))
-    first = np.nonzero(edges)[0][1] + 1  # Want the right side of the first edge
-    last = np.nonzero(edges)[0][-1]      # Want the left side of the second edge
-    below = ambient + n_std*np.sqrt(ambient)
-    # Walk first and last backward and forward until we encounter a value below the threshold
-    while first >= 0 and spad[first] > below:
-        first -= 1
-    while last < len(spad) and spad[last] > below:
-        last += 1
-    spad[:first] = 0.
-    spad[last+1:] = 0.
-    print(first)
-    print(last)
-    return np.clip(spad - ambient, a_min=0., a_max=None)

### 2020-07-09 paper/cvpr2020/sections/figures/refresh_tables.sh

@@ -1,1 +1,0 @@
-rsync -r markn1@ares:~/spad_single/nyuv2/weighted_histogram_matching/figures/sim_table.tex ~/Documents/Stanford/ares/spad_single/paper/cvpr2020/sections/figures/sim_table.tex

### 2020-07-11 paper/eccv2020CR/sections/discussion.tex
Updated While we acknowledge sentence
Paper down to 14 pages, ignore random log files.

@@
 accurate absolute depth. However, if the ordering of the initial depths is not
-correct, these errors will not be corrected by our histogram matching procedure
-and may propagate to the final output depth map.
+correct, these errors may propagate to the final output depth map.
 
@@
 power is spread out over the entire scene. Accordingly, for distant scene points
-very little light may return to the SPAD, \edit{ making reconstruction difficult (an analogous
-  problem occurs with dark objects).} \edit{Thus, our method is best suited
-  to short to medium-range scenes.}
-\edit{CONSIDER MOVE THIS ENTIRE CALCULATION TO
-SUPPLEMENT} For example, assuming an indoor scene with
-fluorescent bulbs and an ambient spectral irradiance of $I_A =
-1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
-to the laser), we find that the laser power required to achieve a minimum SBR of
-5 for a diffuse scene at $R = 3$ m and a field of view of
-$\theta = 40^\circ$\textdegree can be calculated as
-%
-\begin{equation}
-  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
-\end{equation}
-giving $P_{\text{min}}=21$ mW. We note that this is significantly
-less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.
-
-Under these scene parameters, we can compute the total incident
-flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
-\begin{equation}
-  P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
-\end{equation}
-where $P_T$ is the illumination power in the visible region, $\rho$ is its
-albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
-object, and $\eta$ is the quantum efficiency of the detector. For a range of
-values similar to those of our experiments (detailed in the supplement), we find
-that the ratio of photon detections to illumination pulses is roughly 4\%, or
-well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
-We also empirically validate that our method works with a diffused setup and
-an output power of approximately 25 mW without significant pileup effects as
-shown in Figure~\ref{fig:captured_diffuse_small} and detailed in the supplement.
-
-\edit{We acknowledge that pileup in bright environments will ultimately limit
-  the maximum range of our method. However, even when operating in the high-flux
-  regime, pileup can be mitigated by reducing the amount of incident light, for
-  example by reducing the aperture size or using neutral density filters, or by
-  using pileup correction~\cite{Heide:2018,Rapp:2019}. Another approach to
-  mitigate pileup involves taking two transient measurements, one with and one
-  without laser illumination, and using their difference to approximate the
-  backgrond-free transient.}
+very little light may return to the SPAD, \edit{ making reconstruction difficult
+(an analogous problem occurs with dark objects).} \edit{Thus, our method is
+best suited to short- to medium-range scenes.}
+\edit{On the other hand, in bright environments, pileup will ultimately limit the range of our
+  method. However, this can be mitigated with optical elements to reduce the amount
+  of incident light, with pileup correction~\cite{Heide:2018,Rapp:2019}, or
+  even by taking two transient measurements, one with and one without laser
+  illumination, and using their difference to approximate the background-free
+  transient.}
+\edit{Finally, under normal indoor conditions, it is theoretically possible to
+  achieve an SBR of 5 at a range of 3 meters with a laser of only 21 mW while
+  remaining in the low-flux regime. We confirm this empirically with our
+  diffused setup, which operates without significant pileup effects while using
+  approximately 25 mW of laser power (see
+  Figure~\ref{fig:captured_diffuse_small} and the supplement for details).}
 
@@
 \paragraph{Future Work}
-\edit{DELETE While our hardware prototype is large, future work could miniaturize this
-system.} Our algorithm or similar sensor fusion algorithms could
-\edit{DELETE also} be integrated into electronics that already contain the required hardware
-components, for example, existing cell phones with single-pixel SPAD
-proximity sensors and RGB cameras \edit{The small baseline of such sensors
-  would also mitigate the effects of shading and complex BRDFs. Necessary
+\edit{Future work could implement our algorithm or similar sensor fusion
+  algorithms on smaller platforms such as existing cell phones with single-pixel SPAD
+proximity sensors and RGB cameras. Necessary
   adjustments, such as pairing near-infrared (NIR) SPADs with NIR sensors,
-  could be made. More sophisticated intrinsic imaging techniques could also be
-  employed, replacing the primitive RGB channel method described here.}
+  could be made. The small baseline of such sensors
+  would also mitigate the effects of shading and complex BRDFs on the
+  reflectance
+  estimation step. More sophisticated intrinsic imaging techniques could also be
+  employed.}
 
-Other methods for extracting scene information from a transient could be
-employed, including learning-based methods to combine the MDE estimates and
-histogram. One might even consider sensing regimes where the number of
-returning signal photons is low, such as when the time-resolved detector and
-camera operate at high framerates. While most MDE techniques are tailored to
-clean RGB images, the transient could be used to help MDE techniques generalize
-to noisy scenes under low-light conditions.
+% \edit{DELETE Learning-based methods to combine the MDE estimates and
+% histogram. One might even consider sensing regimes where the number of
+% returning signal photons is low, such as when the time-resolved detector and
+% camera operate at high framerates. While most MDE techniques are tailored to
+% clean RGB images, the transient could be used to help MDE techniques generalize
+% to noisy scenes under low-light conditions.}
 
@@
 \paragraph{Conclusions}
-Since their introduction, monocular depth estimation algorithms have improved tremendously.
-However, recent advances, which have generally relied on new network architectures or revised training procedures, have produced only modest performance improvements.
-In this work we dramatically improve the performance of several monocular depth estimation algorithms by fusing their estimates with transient measurements. 
-Such histograms are easy to capture using time-resolved single-photon detectors and are poised to become an important component of future low-cost imaging systems.
+Since their introduction, monocular depth estimation algorithms have improved
+tremendously.  However, recent advances, which have generally relied on new
+network architectures or revised training procedures, have produced only modest
+performance improvements. In this work we dramatically improve the performance
+of several monocular depth estimation algorithms by fusing their estimates with
+transient measurements. Such histograms are easy to capture using time-resolved
+single-photon detectors and are poised to become an important component of
+future low-cost imaging systems.
+
 %Moving forward, sensor fusion is poised to become an even more important component of a variety of vision systems.

### 2020-07-11 paper/eccv2020CR/supplement.tex
Paper down to 14 pages, ignore random log files.

@@
 
-\section{Nominal values for radiometric calculation}
-Here we give the values used in the equation for received power, repeated here
-for convenience:
+\section{Radiometric calculation}
+Assuming an indoor scene with fluorescent bulbs and an ambient spectral irradiance of $I_A =
+1~\text{mW}/\text{m}^2$ (across the 1 nm pass band of a spectral filter matched
+to the laser), we find that the laser power required to achieve a minimum SBR of
+5 for a diffuse scene at $R = 3$ m and a field of view of
+$\theta = 40^\circ$\textdegree can be calculated as
+%
 \begin{equation}
-    P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta.
+  P_{\text{min}} = I_A \cdot 4 R^2 \tan^2(\theta/2) \cdot SBR_{\text{min}},
 \end{equation}
-  For our scene, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
+giving $P_{\text{min}}=21$ mW. We note that this is significantly
+less than the 60 mW used by the Kinect sensor to diffusely illuminate a scene.
+
+Under these scene parameters, we can compute the total incident
+flux on the detector per second (derived in~\cite{mcmanamon2012ladar}) as
+\begin{equation}
+  P_R = P_T \cdot \rho \cdot \frac{A_{rec}}{\pi R^2} \cdot \eta
+\end{equation}
+where $P_T$ is the illumination power in the visible region, $\rho$ is its
+albedo, $A_{rec}$ is the area of the detector region, $R$ is the distance to the
+object, and $\eta$ is the quantum efficiency of the detector.
+% For a range of
+% values similar to those of our experiments, we find
+% that the ratio of photon detections to illumination pulses is roughly 4\%, or
+% well within low-flux regime where SPAD pileup is negligible~\cite{oconnortcspc}.
+
+For scene itself, we assume a vertical, planar, perfectly Lambertian surface. The following table gives the values used for this calculation.
 \begin{figure}[H]
@@
 MHz, we get the number of photons per pulse as $0.043$ or $4.3\%$, which puts us in the
-low-flux regime (where photons per pulse is $< 5\%$).
+low-flux regime (where photons per pulse is $< 5\%$)~\cite{oconnortcspc}.
 

### 2020-07-15 paper/eccv2020CR/sections/hardware.tex
Fixed Gordon's name, misc supp. changes.

@@
     Returning light is measured by the single-pixel SPAD. The Kinect v2 RGB
-    camera is used to capture the image used to generate the monocular depth estimate
-    (the depth bccamera is not used). (b) Scene and (c) measurements for diffused and summed scanned mode. The observed
+    camera is used to capture the image used to generate the monocular depth
+    estimate (the depth camera is not used). (b) Scene and (c) measurements for
+    diffused and summed scanned mode (10s capture, aligned peaks). The observed
     counts in the diffuse mode match closely with the sum of the raster-scanned
@@
   \label{fig:hardware}
-  % \vspace{-0.5em}
 \end{figure}

### 2020-07-15 paper/eccv2020CR/supplement.tex
Fixed Gordon's name, misc supp. changes.

@@
 %\begin{comment}
-\titlerunning{ECCV-20 submission ID \ECCVSubNumber} 
-\authorrunning{ECCV-20 submission ID \ECCVSubNumber} 
-\author{Anonymous ECCV submission}
-\institute{Paper ID \ECCVSubNumber}
+% \titlerunning{ECCV-20 submission ID \ECCVSubNumber}
+% \authorrunning{ECCV-20 submission ID \ECCVSubNumber}
+% \author{Anonymous ECCV submission}
+% \institute{Paper ID \ECCVSubNumber}
 %\end{comment}
@@
 % CAMERA READY SUBMISSION
-\begin{comment}
-\titlerunning{Abbreviated paper title}
+% \begin{comment}
+\titlerunning{Disambiguating Monocular Depth Estimation with a Single Transient}
 % If the paper title is too long for the running head, you can set
@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333} \and
-Second Author\inst{2,3}\orcidID{1111-2222-3333-4444} \and
-Third Author\inst{3}\orcidID{2222--3333-4444-5555}}
+\author{Mark Nishimura  \and
+David B. Lindell \and
+Christopher A. Metzler \and \\
+Gordon Wetzstein}
+
 %
-\authorrunning{F. Author et al.}
+\authorrunning{M. Nishimura et al.}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA \and
-Springer Heidelberg, Tiergartenstr. 17, 69121 Heidelberg, Germany
-\email{lncs@springer.com}\\
-\url{http://www.springer.com/gp/computer-science/lncs} \and
-ABC Institute, Rupert-Karls-University Heidelberg, Heidelberg, Germany\\
-\email{\{abc,lncs\}@uni-heidelberg.de}}
-\end{comment}
+\institute{Stanford University, Stanford, CA \\
+\email{\{markn1, lindell, cmetzler, gordon.wetzstein\}@stanford.edu}}
+% \end{comment}
 %******************
 \maketitle
-\begin{abstract}
-  TODO: Abstract
-\end{abstract}
+% \begin{abstract}
+%   TODO: Abstract
+% \end{abstract}
 
@@
 % show this in supplement
-The monocular depth estimate is calculated using the RGB image captured by the Kinect v2.
-The SPAD records temporal histograms with 4096 bins, each corresponding to a time window of 16~ps.
-The SPAD and laser are co-axially aligned using a beam splitter (Thorlabs PBS251).
-The full width at half maximum (FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps, allowing the system to record depth maps with an accuracy of about 1~cm.
-A National Instruments data acquisition device (NI-DAQ USB-6343) provides synchronization signals for the galvos, SPAD, and laser.
-The ground truth depth map is raster-scanned at a resolution of $512 \times 512$ pixels, and the single-pixel, diffused SPAD measurement is generated by summing all of these measurements for a specific scene.
-This allows us to validate the accuracy of the proposed histogram matching algorithm, which only uses the integrated single histogram, by comparing it with the captured depth---such validation would not be possible if we were to capture measurements with an optically diffused SPAD.
+The monocular depth estimate is calculated using the RGB image captured by the
+Kinect v2. The SPAD records temporal histograms with 4096 bins, each
+corresponding to a time window of 16~ps. The SPAD and laser are co-axially
+aligned using a beam splitter (Thorlabs PBS251). The full width at half maximum
+(FWHM) of the combined laser pulse width and SPAD jitter is about 70~ps,
+allowing the system to record depth maps with an accuracy of about 1~cm. A
+National Instruments data acquisition device (NI-DAQ USB-6343) provides
+synchronization signals for the galvos, SPAD, and laser. The ground truth depth
+map is raster-scanned at a resolution of $512 \times 512$ pixels, and the
+single-pixel, diffused SPAD measurement is generated by summing all of these
+measurements for a specific scene. This allows us to validate the accuracy of
+the proposed histogram matching algorithm, which only uses the integrated single
+histogram, by comparing it with the captured depth---such validation would not
+be possible if we were to capture measurements with an optically diffused SPAD.
 
@@
 
-% show this in supplement
 %To verify that our digitally aggregated scanned SPAD measurements match measurements produced by an optically diffused SPAD, we set up a slightly modified version of our prototype consisting of both scanned and diffused SPADs side-by-side.
@@
 diffused modes. This hardware prototype (shown in Fig.~\ref{fig:hardware}) is less mobile than 
-our unmodified prototype, but allows us to use a more powerful laser (Katana
-05HP, 532 nm) operated at approximately 25 mW average power. We also use two
-single-pixel SPAD detectors, where one SPAD is aligned with the optical path of
-the laser, and the other SPAD is operated without a lens to integrate light
-from the entire scene. Both SPADs are fitted with a 10 nm bandpass filter
-centered at 532 nm, which reduces the amount of integrated ambient light. We
-attach a holographic diffuser (Thorlabs ED1-S50) to the laser output in order
-to diffuse light onto the scene. Alternatively, we remove the diffuser and use a
-pair of scanning mirrors to scan the scene.
+our unmodified prototype (which was able capture a wider variety of scenes,
+including outdoors, along with their ground truth
+depths), but allows us to use a more powerful laser (Katana 05HP, 532 nm)
+operated at approximately 25 mW average power. We also use two single-pixel SPAD
+detectors, where one SPAD is aligned with the optical path of the laser, and the
+other SPAD is operated without a lens to integrate light from the entire scene.
+Both SPADs are fitted with a 10 nm bandpass filter centered at 532 nm, which
+reduces the amount of integrated ambient light. We attach a holographic diffuser
+(Thorlabs ED1-S50) to the laser output in order to diffuse light onto the scene.
+Alternatively, we remove the diffuser and use a pair of scanning mirrors to scan
+the scene.
 
@@
 Fig.~\ref{fig:hardware}).
-\begin{figure}[H]
-  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
+\begin{figure}[ht!]
+  \centering \includegraphics[width=0.8\textwidth]{diffused_hardware/setup.pdf}
   \caption{Modified hardware setup. The setup is used to compare scanned and
@@
 
-\begin{figure}[H]
+\begin{figure}[ht!]
   \centering \includegraphics[width=\textwidth]{captured_diffuse.pdf}
@@
       with the same total exposure time and are qualitatively similar without 
-      noticeable pileup effects. We Use $K = 300$ bins for the reconstruction
+      noticeable pileup effects. We use $K = 300$ bins for the reconstruction
       and a depth range of $[0.8, 6]$ meters. MiDaS \cite{Lasinger:2019} does

### 2020-07-19 paper/eccv2020CR/final/3668/3668.tex
Final camera-ready submission.

--- 2020-07-09 paper/eccv2020CR/main.tex
@@
 
-\newcommand{\edit}[1]{\textcolor{red}{#1}}
+\newcommand{\edit}[1]{\textcolor{black}{#1}}
 % \newcommand{\edit}[1]{#1}
 
-\graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
-    Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
-    Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
-    drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
-  {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
+% \graphicspath{{figures/}{"G:/Shared drives/Stanford Computational
+%     Imaging/Projects/single_spad_depth/figures/"}{"H:/Shared drives/Stanford Computational
+%     Imaging/Projects/single_spad_depth/figures/"}{"/Users/gordon/mount/teamdrive/Shared
+%     drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}
+%   {"/Volumes/GoogleDrive/Shared drives/Stanford Computational Imaging/Projects/single_spad_depth/figures/"}}
+\graphicspath{{figures/}}
 % Pages are numbered in submission mode, and unnumbered in camera-ready
@@
 %
-\author{Mark Nishimura  \and
-David B. Lindell \and
-Chris Metzler \and
-Gordon Wetzstein}
+\author{Mark Nishimura\orcidID{0000-0003-3976-254X}  \and
+David B. Lindell\orcidID{0000-0002-6999-3958} \and
+Christopher Metzler\orcidID{0000-0001-6827-7207} \and \\
+Gordon Wetzstein\orcidID{0000-0002-9243-6885}}
 %
@@
   Monocular depth estimation algorithms successfully predict the
-  relative depth {order} of objects in a scene.
+  relative depth order of objects in a scene.
   However, because of the fundamental scale ambiguity associated with monocular
@@
 
+\vspace{-5pt}
 \section{Introduction}
+\vspace{-5pt}
 \label{sec:intro}
@@
 
+\vspace{-5pt}
 \section{Related Work}
+\vspace{-5pt}
 \label{sec:related}
@@
 
+\vspace{-5pt}
 \section{Method}
+\vspace{-5pt}
 \label{sec:method}
@@
 
+\vspace{-5pt}
 \section{Evaluation and Assessment}
+\vspace{-5pt}
 \label{sec:evaluation}
@@
 
+\vspace{-5pt}
 \section{Experimental Demonstration}
+\vspace{-5pt}
 \label{sec:prototype}
@@
 
+\vspace{-5pt}
 \section{Discussion}
+\vspace{-5pt}
 \label{sec:discussion}
 \input{sections/discussion}
+
+\vspace{-4 pt}
+\subsection*{Acknowledgments}
+D.L.~was supported by a Stanford Graduate Fellowship. 
+C.M.~was supported by an ORISE Intelligence Community Postdoctoral Fellowship.
+G.W.~was supported by an NSF CAREER Award (IIS 1553333), a Sloan Fellowship, by the KAUST Office of Sponsored Research through the Visual Computing Center CCF grant, and a PECASE by the ARL.
 
@@
 \bibliographystyle{splncs04}
-\bibliography{references}
+% \bibliography{references}
+\input{3668.bbl}
 

### 2020-07-19 paper/eccv2020CR/final/3668/sections/method.tex
Final camera-ready submission.

--- 2020-03-05 paper/eccv2020/sections/method.tex
@@
-In this section, we describe the image formation of a diffused pulsed laser and time-resolved detector.
-\edit{Although our model is derived for the specific case of imaging with a single-photon avalanche diode (SPAD), the resulting image formation model equally applies to other time-resolved detectors}.
-We also describe an approach for correcting a depth map generated with a monocular depth estimator to match the global scene information captured by the \edit{transient}.
+In this section, we describe the image formation of a diffused pulsed laser and
+time-resolved detector. Although our model is derived for the specific case of
+imaging with a single-photon avalanche diode (SPAD), the resulting image
+formation model equally applies to other time-resolved detectors. We also
+describe an approach for correcting a depth map generated with a monocular depth
+estimator to match the global scene information captured by the transient.
 
-%In this section, we describe the measurement model for a single-pixel time-of-flight lidar sensor under diffuse, pulsed laser illumination.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Image Formation Model of a Diffused SPAD}
@@
   \includegraphics[width=\columnwidth]{method_eccv.pdf}
-  \caption{Overview of processing pipeline. The processing pipeline uses
-      the input \edit{transient measurement} and an RGB image to produce an accurate depth
-      map. The \edit{transient is} preprocessed to adjust for ambient photon
-      detections, radiometric falloff factors, and to calibrate the bin widths.
-      From the RGB image, an MDE estimates an initial depth map
-      and the scene reflectance is estimated. A reflectance-weighted
-      depth histogram is compared to the processed \edit{transient} to
-      calculate a histogram matching matrix which is used to output the corrected depth.
+  \caption{Overview of processing pipeline. The processing pipeline uses the
+    input transient measurement and an RGB image to produce an accurate depth
+    map. The transient is preprocessed to adjust for ambient photon detections,
+    radiometric falloff factors, and to calibrate the bin widths. From the RGB
+    image, an MDE estimates an initial depth map and the scene reflectance is
+    estimated. A reflectance-weighted depth histogram is compared to the
+    processed transient to calculate a histogram matching matrix which is used
+    to output the corrected depth.
   }
@@
 times per second with the specific number of emitted pulses being controlled by
-the repetition rate of the laser. \edit{As derived in previous work, the resulting measurement
+the repetition rate of the laser. As derived in previous work, the resulting measurement
 can be modeled as an inhomogeneous Poisson process
-$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}.} Each detected photon arrival event is
+$\mathcal{P}$~\cite{Kirmani:2014,Shin2015,Shin2016}. Each detected photon arrival event is
 discretized into a histogram $h$ of the form
@@
 represents background detections from ambient light and false positive detections known as \textit{dark
-count}. \edit{Like previous work, we neglect scene interreflections
+count}. Like previous work, we neglect scene interreflections
 and confine ourselves to the low-flux condition (where the number of photon
 detections is controlled to be much smaller than the number of emitted pulses)
-to avoid pileup~\cite{Shin2016}.} Finally, we adopt the term
+to avoid pileup~\cite{Shin2016}. Finally, we adopt the term
 \textit{transient} for the histogram $h[n]$~\cite{Xin2019}.
@@
 
-\vspace{0.8em}\noindent{\bf Background Subtraction.}
+\noindent{\bf Background Subtraction.}
 In the first step, we remove the background counts from the
@@
 first order differences of the transient $d[n] = \abs{h[n] - h[n+1]}$. 
-\edit{For a moderate number of background counts, each background bin $h[n]$ can be
+For a moderate number of background counts, each background bin $h[n]$ can be
 approximated as a Gaussian with mean and variance $b$, and thus $h[n] - h[n+1]$ can be approximated  
-as a Gaussian with mean $0$ and variance $2b$.} We identify candidate discontinuities
+as a Gaussian with mean $0$ and variance $2b$. We identify candidate discontinuities
 $\mathcal{E}$ with a threshold on the measured differences:
@@
 The remaining ambient counts are discarded by setting the recorded counts to
-zero for all bins where \edit{$n < n_\text{first}$} and $n > n_\text{last}$. We use 
+zero for all bins where $n < \hat n_\text{first}$ and $n > \hat n_\text{last}$. We use
 $\tau = \hat b + \sqrt{\hat b}$ in all of our experiments.
 
-%Finally, we reject all photons outside of the valid range by
-%clamping those bins to 0, and we subtract our ambient estimate from the photons
-%within the valid range:
-%\begin{equation}
-%  h'_{clean}[n] = \begin{cases}
-%    0 & n < \hat n_{first} \\
-%    \max(h[n] - \hat b, 0) & \hat n_{first} \leq  n \leq \hat n_{last} \\
-%    0 & n > \hat n_{last} \\
-%  \end{cases}.
-%  \label{eq:h_clean}
-%\end{equation}
-
-\vspace{0.8em}\noindent{\bf Falloff Compensation.}
+\noindent{\bf Falloff Compensation.}
 In the second step, we compensate for distance falloff effects by multiplying
@@
 
-\vspace{0.8em}\noindent{\bf Transient Re-binning.}
+\noindent{\bf Transient Re-binning.}
 Last, we re-bin the transient so that the bin widths increase for increasingly
@@
 %
-This rebinning procedure allows us to use a reduced number of bins by the histogram
-matching, reducing computation time while maintaining accuracy.
-\edit{For the simulated results we use $K = 140$ bins with $(\ell,
+This rebinning procedure allows us to use a reduced number of bins \edit{in} the
+histogram matching, reducing computation time while maintaining accuracy.
+For the simulated results we use $K = 140$ bins with $(\ell,
 u)$ corresponding to the depth values of bins $\hat n_{\text{first}}$ and $\hat
-n_{\text{last}}$ respectively.}
+n_{\text{last}}$ respectively.
  The output of the rebinning procedure is the
@@
 at the corresponding depth, we add the estimated reflectance value of the pixel
-to the histogram bin. \edit{We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.}
+to the histogram bin. We also re-bin this histogram, following Fu et al. and using $K = 140$ with $(\ell, u) = (0.657, 9.972)$~\cite{Fu2018}.
 
@@
 matrix $T$ such that $T[m, n]$ is the fraction of $h_\text{source}[m]$ that should be
-moved to $h_\text{target}[n]$. \edit{We refer the reader to the supplement for
-  pseudocode.} Intuitively, the procedure starts from the first bin of the
+moved to $h_\text{target}[n]$. We refer the reader to the supplement for
+  pseudocode. Intuitively, the procedure starts from the first bin of the
 source histogram and distributes its contents to the first bins of the target
@@
 
-\edit{Pseudo-code for this procedure is included in the supplement; we will make source code and data available.}
+Pseudo-code for this procedure is included in the supplement; we will make source code and data available.
 

### 2020-07-19 paper/eccv2020CR/final/3668/sections/related.tex
Final camera-ready submission.

--- 2020-07-09 paper/eccv2020CR/sections/related.tex
@@
 \edit{While other recent work also explored RGB-SPAD sensor
-fusion~\cite{Lindell2018,sun2020spadnet},
+fusion~\cite{Lindell2018,sun2020spadnet,ahmad2020extensible},
 the RGB image was primarily used to guide the denoising and upsampling of

### 2020-07-19 paper/eccv2020CR/supplement.tex
Final camera-ready submission.

@@
 5 for a diffuse scene at $R = 3$ m and a field of view of
-$\theta = 40^\circ$\textdegree can be calculated as
+$\theta = 40^\circ$ can be calculated as
 %
